### 2022-01-07 BuildOM/BuildOMVPA2OM.Rmd
lots of changes
I ran some new MSEs an restructure the folders so that now there are several subfolders in RunMSE

---
title: "Build Operating Models for SA Species"
author: "Nikolai"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
urlcolor: blue
---

```{r setup, include=FALSE, echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(comment=NA,echo=FALSE,message=FALSE,warning=FALSE,fig.height=8,fig.width=6)

library(car)
library(faux) # Simulation for Factorial Designs
# devtools::install_github("james-thorson/FishLife")
library(FishLife)
library(Hmisc)
library(MultiRNG) # Multivariate Pseudo-Random Number Generation
library(measurements) # Unit conversion functions like conv_unit()
library(openMSE)
library(rfishbase)
library(stringr)

library(bamExtras) # Nikolai's package

```

```{r user}
length_sc <- 0.1 # Scalar (multiplier) to convert length units. MSEtool examples seem to use cm whereas BAM uses mm.
plot_OM <- TRUE # Switch for plotting OM. It takes a while to plot them all

# OM
nsim <- 250 # The number of simulations (48 is the minimum number you can run in parallel)
proyears <- 50 # The number of projected years
interval <- 1  # The assessment interval - how often would you like to update the management system? (should be set to 1 when using the make_interim_MP function using)
set_Fage0_to_zero <- TRUE # Should we assume F-at-age zero is zero for stocks where age zero was not modeled?

# Set recruitment process error (cpars$Perr_y)
Perr_y_user <- NA # Set to 1 to remove process error (set to NA in order to leave it as it is)
```

```{r user bam species}
bam_common_name_sub <- c(
  "BlackSeaBass",
  #"BluelineTilefish",
  #"Cobia",
  #"GagGrouper",
  #"GrayTriggerfish",
  #"GreaterAmberjack",
  #"MenhadenAtl",
  #"RedGrouper",
  "RedPorgy",
  #"RedSnapper",
  #"SnowyGrouper",
  #"SpanishMackerel",
  #"Tilefish",
  "VermilionSnapper"
  )

bam_rdat_sub <- paste("rdat",bam_common_name_sub,sep="_")

```

```{r build OM VPA2OM, eval=TRUE}
list_Nage_F0_pr_sc <- list() # List for storing values of Nage_F0_pr_sc
vec_to_mat <- function(vec){
  matrix(vec,nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                    dimnames=dimnames(naa)[2:3])
}

mat_to_array <- function(mat,nsim){
  mat_data <- rep(as.numeric(mat),each=nsim)
  array(mat_data, dim=c(nsim,nrow(mat),ncol(mat)),
               dimnames=list("sim"=1:nsim, "ages"=rownames(mat), "year"=colnames(mat)))
}

for(rdat_name_i in bam_rdat_sub){
  rdat_i <- standardize_rdat(get(rdat_name_i))
  Name_i <- gsub("rdat_","",rdat_name_i)
  herm_i <- bamStockMisc[Name_i, "herm"]
  OM_name_i <- gsub("rdat","OM",rdat_name_i)
  a.series_i <- rdat_i$a.series
  t.series_i <- rdat_i$t.series

  ageinit_i <- a.series_i$age
  ageinitmin_i <- min(ageinit_i)
  parms_i <- rdat_i$parms
  parm.cons_i <- rdat_i$parm.cons

  years_i <- paste(parms_i$styr:parms_i$endyr)

  Linf_i <- parm.cons_i$Linf[8]*length_sc
  K_i <- parm.cons_i$K[8]
  t0_i <- parm.cons_i$t0[8]
  steep_i <- parm.cons_i$steep[8]
  R0_i <- exp(parm.cons_i$log_R0[8])

  # Compute the number of years at the end of the assessment where rec devs weren't estimated
  nyrNoRecDevEnd <- if (any(t.series_i$logR.dev!=0)) {
    length(t.series_i$logR.dev)-max(which(t.series_i$logR.dev!=0))}else{
      1
    }

if(min(ageinit_i)>0){
  warning(paste(Name_i,": Minimum age > 0. Age-based data extrapolated to age-0"))
  a.series_i <- data_polate(a.series_i,xout=0:max(a.series_i$age))
  a.series_i <- data_lim(a.series_i,xlim=c(0,Inf))
  a.series_i <- data_lim(a.series_i,xname=c("prop.female","prop.male","mat.female","mat.male"),xlim=c(0,1))
  a.series_i <- as.data.frame(a.series_i)
  rownames(a.series_i) <- a.series_i$age
}

  age_i <- a.series_i$age

  # NOTE: this will have no effect in ageinitmin_i=0 
  Nage_F0_pr <- expDecay(age=age_i,Z=a.series_i$M,N0=1)                  # Unfished N-at-age per recruit
  Nage_F0_pr_sc <- (Nage_F0_pr/Nage_F0_pr[[paste(ageinitmin_i)]])[["0"]] # Scaling factor for computing unfished numbers at age-0
  R0_i <- R0_i*Nage_F0_pr_sc                                             # Scaled value of R0

  naa_mat <- cbind("age"=ageinit_i,t(rdat_i$N.age[years_i,]))
  naa_mat2 <- data_polate(naa_mat,xout = age_i)
  rownames(naa_mat2) <- age_i
  naa_mat2["0",-1] <- naa_mat2[paste(ageinitmin_i),-1]*Nage_F0_pr_sc # Compute numbers at age-0
  naa_mat2[naa_mat2<0] <- 1 # Don't let value be less than 1
  naa <- mat_to_array(naa_mat2[,-1],nsim=nsim)

  faa_mat <- cbind("age"=ageinit_i,t(rdat_i$F.age[years_i,]))
  faa_mat2 <- data_polate(faa_mat,xout = age_i)
  rownames(faa_mat2) <- age_i
  faa_mat2[faa_mat2<0] <- 0 # Don't let F be negative
  if(set_Fage0_to_zero){
    faa_mat2["0",-1] <- 0 # Set F at age-0 to zero
  }

  faa <- mat_to_array(faa_mat2[,-1],nsim=nsim)

  mat_waa_klb <- matrix(a.series_i$wgt.klb,
                        nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                        dimnames=dimnames(naa)[2:3])
  waa <- mat_to_array(mat_waa_klb,nsim=nsim)

  mat_pmat <- matrix(pmatage(a.series_i,herm=herm_i)$pmat,
                        nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                        dimnames=dimnames(naa)[2:3])
  Mataa <- mat_to_array(mat_pmat,nsim=nsim)

  mat_M <- matrix(a.series_i$M,
                        nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                        dimnames=dimnames(naa)[2:3])
  Maa <- mat_to_array(mat_M,nsim=nsim)

  mat_laa <- matrix(a.series_i$length*length_sc,
                        nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                        dimnames=dimnames(naa)[2:3])
  laa <- mat_to_array(mat_laa,nsim=nsim)

  CurrentYr_i = parms_i$endyr

 OM_i <- VPA2OM(Name=Name_i,
                proyears = proyears,
                interval = interval,
                CurrentYr = CurrentYr_i,
                h=steep_i, R0=R0_i,
                Obs = MSEtool::Perfect_Info,
                Imp = MSEtool::Perfect_Imp,
                naa=naa, faa=faa, waa=waa, Mataa=Mataa, Maa=Maa, laa=laa,
                nyr_par_mu = 3,
                LowerTri = nyrNoRecDevEnd,
                recind = 0,
                plusgroup = TRUE,
                altinit = 0,
                fixq1 = TRUE,)

 OM_i@cpars$K <- rep(K_i,nsim)
 OM_i@cpars$Linf <- rep(Linf_i,nsim)
 OM_i@cpars$t0 <- rep(t0_i,nsim)

 if(!is.na(Perr_y_user)){
 OM_i@cpars$Perr_y[] <- Perr_y_user
 }

 list_Nage_F0_pr_sc[[Name_i]] <- Nage_F0_pr_sc

 # Save rdat modifications
 rdatmods_name_i <- gsub("rdat","rdatmods",rdat_name_i)
 assign(rdatmods_name_i,
        list(
          "Name"=Name_i,
          "CurrentYr" = CurrentYr_i,
          "steep"=steep_i,
          "R0"=R0_i,
          "a.series"=a.series_i,
          "Nage_F0_pr_sc" = Nage_F0_pr_sc,
          "N.age" = t(naa_mat2[,-1]),
          "F.age" = t(faa_mat2[,-1]),
          "B.age" = t(naa_mat2[,-1])*t(mat_waa_klb)

          )
        )

 assign(OM_name_i,OM_i)
}  
```

```{r generate Hist and save OM}
OM_name_bam <- gsub("rdat","OM",bam_rdat_sub) # OM names from bam models

if(plot_OM){

for(OM_name_i in OM_name_bam){
  OM_i <- get(OM_name_i)

  cat(paste0("\n\nWorking on ",OM_name_i,"\n"))
  Hist_i <- MSEtool::Simulate(OM_i) # Generate historical data

  if(OM_name_i%in%OM_name_bam){
  Hist_name_i <- gsub("OM","Hist",OM_name_i)
  assign(Hist_name_i,Hist_i)
  saveRDS(Hist_i, file = file.path("Hist","SEFSC",paste0(Hist_name_i,".rds")))
  saveRDS(OM_i,file=file.path("OM","SEFSC",paste0(OM_name_i,".rds")),compress=FALSE)
  }

}
}
```

```{r plot Hist with bam  results, eval=TRUE}
pdf("HistBam.pdf")
CIpct = 95

for(i in bam_common_name_sub){
rdat_name_i <- paste0("rdat_",i)
rdatmods_name_i <- gsub("rdat","rdatmods",rdat_name_i)

OM_i <- get(paste0("OM_",i))
# Data_i <- get(paste0("Data_",i))
Hist_i <- get(paste0("Hist_",i))
rdat_i <- get(rdat_name_i)
rdatmods_i <- get(rdatmods_name_i)

parms_i <- rdat_i$parms
years_i <- paste(parms_i$styr:parms_i$endyr)
t.series_i <- rdat_i$t.series[years_i,]

Nage_F0_pr_sc_i <- list_Nage_F0_pr_sc[[i]]

par(mfrow=c(3,2),mgp=c(0.9,0.1,0),tck=-0.01,mar=c(2,2.5,1,1),oma=c(0,0,1.5,1))

# Landings
Lmatrix <- Hist_i@TSdata$Landings[,,1]+Hist_i@TSdata$Landings[,,2]
Lbam <- t.series_i$total.L.klb
Dbam <- t.series_i$total.D.klb
if(!is.null(Dbam)){
  Lbam <- Lbam+Dbam
}
Lylim <- range(c(0,as.numeric(Lmatrix),Lbam))
plot_boot_vec(Lmatrix,CIpct=CIpct,xlab="year",ylab="Landings + Discards (1000 lb)",ylim=Lylim)
points(Lbam,type="o",#axes=FALSE,xlab="",ylab="",
     col="blue")

# Indices
plot_boot_vec(Hist_i@Data@Ind,CIpct=CIpct,xlab="year",ylab="Ind")

# Recruitment
Rmatrix <- Hist_i@AtAge$Number[,1,,1]+Hist_i@AtAge$Number[,1,,2]
plot_boot_vec(Rmatrix,CIpct=CIpct,xlab="year",ylab="recruits")
points(t.series_i$recruits*Nage_F0_pr_sc_i,type="o", col="blue")

# N
Nmatrix <- Hist_i@TSdata$Number[,,1]+Hist_i@TSdata$Number[,,2]
bam.N <- rowSums(rdatmods_i$N.age)
plot_boot_vec(Nmatrix,CIpct=CIpct,xlab="year",ylab="N")
points(bam.N,type="o",col="blue")

# F
Fmatrix <- Hist_i@TSdata$Find
plot_boot_vec(Fmatrix,CIpct=CIpct,xlab="year",ylab="F")
# par(new=TRUE)
 points(t.series_i$year,t.series_i$F.full,type="o",
     col="blue")

# B
Bmatrix <- Hist_i@TSdata$Biomass[,,1]+Hist_i@TSdata$Biomass[,,2]
bam.Bklb <- rowSums(rdatmods_i$B.age)
plot_boot_vec(Bmatrix,CIpct=CIpct,xlab="year",ylab="Biomass (1000 lb)")
par(new=TRUE)
points(bam.Bklb,type="o", #axes=FALSE,xlab="",ylab="",
     col="blue")

mtext(i,side=3,line=0,outer=TRUE)

}
dev.off()
```

### 2022-01-07 RunMSE/HCR_MSY/MSEPlots.Rmd
lots of changes
I ran some new MSEs an restructure the folders so that now there are several subfolders in RunMSE

---
title: "Application of Huynh 2020 Interim Analysis methods to other stocks: investigating if stocks tend toward MSY with HCR_MSY harvest control rule."
author: "Nikolai Klibansky"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    fig_caption: yes
    extra_dependencies:
      longtable: null
      xcolor: null
urlcolor: blue
---

```{r setup, include=FALSE, echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(comment=NA,echo=FALSE,message=FALSE,warning=FALSE,fig.height=7,fig.width=6)

library(Hmisc)
library(knitr)
#library(latex2exp) # lets you use TeX() function to convert latex equations to R expressions for plotting
library(SAMtool)
library(stringr)
library(bamExtras)

source('fn/iMP_NK.R')
# Compute U (harvest rate) from F
F2U <- function(F){1 - exp(-F)}

# Median without NA
median_noNA <- function(x){median(x,na.rm=TRUE)}
```

```{r user}

OMNames_user <- c("MSE_BlackSeaBass","MSE_VermilionSnapper","MSE_RedPorgy")#,
#                    #"OM_Tilefish","OM_Cobia","OM_SnowyGrouper",
#                    #"OM_capelin", "OM_POP", "OM_vs",
#   "OM_Albacore","OM_AlmacoJack", "OM_BandedMorwong"
#                    )
# OMNames_user <- local({
#   a <- gsub(".rds","",list.files("MSE_obj"))
#   b <- gsub("MSE","OM",a)
#   b
# })

OMNames_user <- gsub("MSE","OM",OMNames_user)
scenNames_user <-  c("base","nr"#,#"hs","hd",
                     #"dep","lf",
                     #"epiM"
                     )
OMscenNames_user <- sort(apply(expand.grid(OMNames_user,scenNames_user),1,function(x){paste(x,collapse="_")}))
scenNames_key <- c("base"="Base","nr"="no rec error","hs"="Hyper-stable","hd"="Hyper-deplete",
                   "dep"="Depleted","lf"="Lightly fished","epiM"="Episodic M")
MPNamesSub_user <- c("SCA_1","SCA_10","iMP_avg_10","MP_PerfectMSY")#,"iMP_avg_10","iMP_buffer_10")
MPNamesSub_user_legtext <- c("Annual assessment","Fixed TAC (10)","Averaged Index (10)","Perfect MSY")#,"Buffered Index (10)")
```

```{r plot_LH function, eval=TRUE}
plot_LH <- function(OM,...){
maxage <- OM@maxage
agebins <- 0:maxage
lenbins <- vb_len(Linf=OM@Linf[1],K=OM@K[1],t0=OM@t0[1],a=agebins)
Plenbins <- lenbins/max(lenbins)
Mat_age <- OM@cpars$Mat_age[1,,1] # Maturity at age
V <- OM@cpars$V[1,,1] # Vulnerability (selectivity) at age

plot(agebins,Plenbins,ylim=c(0,1),type="l",lwd=3,...)
points(agebins,Mat_age,type="l",lwd=3,lty=2)
points(agebins,V,type="l",lwd=3,lty=3)
}
```

```{r plot_MSE_ts_Huynh function}

plot_MSE_ts_Huynh <- function(
myvarName,
myvarDenomExpr = NULL,
ylabel = myvarName,
FUN = mean_noNA,
scenNames,
OMNames,
MPNamesSub = c("SCA_10","SCA_1","iMP_avg_10","iMP_buffer_10"),
MPNamesSub_legtext=MPNamesSub,
legtext_o = c(1,2,3,4), # order for plotting legend text
MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
                     "_",
                     rep(scenNames,length(OMNames))
                     ),
colLabs = NULL,
rowLabs = scenNames,

mar=c(1,1,1,1),
cols = setNames(c("black","red","deepskyblue2","green3"),MPNamesSub),
ltys = setNames(c(1,2,1,2),MPNamesSub),
lwds = setNames(c(3,3,3,3),MPNamesSub),
types = setNames(c("l","l","l","l"),MPNamesSub),
xlabel = "Management year",
xlim = NULL,
ylim = NULL,
assessmentYears = seq(10,40,by=10),
x.at = NULL,
y.at = NULL,
# leg.x=NULL,
# leg.y =NULL,
legend_panel=NULL,
legend_cex= 1,
legend_x="bottomleft",
legend_inset=c(0,-0.3),
label_axes="all", # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
hline=1 # values to pass into abline(h=hline)
){
if(is.null(colLabs)){
  colLabs <- local({
  a <- gsub("OM_","",OMNames) # Replace OM_
  b <- str_replace_all(a,"_[A-Za-z]*$","") # Replace underscore and letters following
  c <- str_replace_all(b,"(?<=[a-z])(?=[A-Z])"," ")
  unique(c)
  })
}

xlim_user <- xlim
ylim_user <- ylim
x.at_user <- x.at
y.at_user <- y.at

colLabsAll = as.character(matrix(c(colLabs,rep("",length(MSEoutNames)-length(colLabs))),ncol=length(colLabs),byrow=TRUE))
rowLabsAll = as.character(matrix(c(rep("",length(MSEoutNames)-length(rowLabs)),rowLabs),nrow=length(rowLabs),byrow=FALSE))

nrow <- length(rowLabs)
ncol <- length(colLabs)
npanel <- nrow*ncol

par(mfcol=c(nrow,ncol),mgp=c(1,0.2,0),mar=mar,oma=c(6,4,3,3),tck=-0.01,xpd=FALSE,xaxs="i",yaxs="i")

for(outName_i in MSEoutNames){
topPanels <- (length(scenNames)*(seq_along(OMNames)-1)+1)
bottomPanels <- length(scenNames)*seq_along(OMNames)
leftPanels <- seq_along(scenNames)
rightPanels <- tail(seq_along(MSEoutNames),length(scenNames))

i <- which(MSEoutNames==outName_i)
out_i <- get(outName_i)
MPNames <- out_i@MPs
if(!is.expression(myvarName)){
myvar <- slot(out_i,myvarName)  
}else{
myvar <- eval(myvarName) 
}

if(is.null(legend_panel)){
legend_panel <- bottomPanels[1]
}

if(!is.null(myvarDenomExpr)){
myvarDenom <- eval(myvarDenomExpr)
myvar <- myvar/myvarDenom # Scale myvar
}

if(!is.null(dim(myvar))){
myvarsub <- myvar[,match(MPNamesSub,MPNames),,drop=FALSE]
myvarsubStat <- apply(myvarsub,2,function(x){apply(x,2,FUN)})
}else{
myvarsubStat <- matrix(rep(myvar,length(MPNamesSub)),ncol=length(MPNamesSub))  
}
dimnames(myvarsubStat) <- list(1:nrow(myvarsubStat),MPNamesSub)

xaxt_i <- ifelse(i%in%bottomPanels,"n","n")
yaxt_i <- ifelse(i%in%leftPanels,"n","n")

if(is.null(ylim_user)){
  ylim <- range(myvarsubStat,na.rm=TRUE)
}
if(is.null(xlim_user)){
  xlim <- range(as.numeric(rownames(myvarsubStat)),na.rm=TRUE)
}

matplot(as.numeric(rownames(myvarsubStat)),myvarsubStat,
        col=cols,lty=ltys,lwd=lwds,type=types,
        xaxt=xaxt_i,yaxt=yaxt_i,
        xlim=xlim,ylim=ylim,xlab="",ylab="")
#title(main=colLabsAll[i],line=1)

grid(nx=NA,ny=NULL)
abline(v=assessmentYears,lty="1111",lwd=2)
if(!is.null(hline)){
abline(h=hline)
}

if(is.null(x.at_user)){
  x.at <- pretty(par("usr")[1:2])
}
if(is.null(y.at_user)){
  y.at <- pretty(par("usr")[3:4])
}

if(i%in%topPanels){
col.ct <- which(topPanels==i)
mtext(colLabsAll[i],side=3,line=1,outer=FALSE,font=2)
}

if(i%in%rightPanels){
row.ct <- which(rightPanels==i)
rowcenter <-par("usr")[3]+diff(par("usr")[3:4])/2

text(x=par("usr")[2]*1.05,y=rowcenter,rowLabsAll[i],
     srt=-90,xpd=NA,font=2)
}

if(label_axes=="all"){
  x.at.i <- x.at
  axis(side=1,at=x.at.i)
  y.at.i <- y.at
  axis(side=2,at=y.at.i)
}
if(label_axes=="leftbottom"){
  if(i%in%bottomPanels){
    x.at.i <- x.at
    if(i>bottomPanels[1]){x.at.i <- x.at[-1]}
    axis(side=1,at=x.at.i)
  }
  if(i%in%leftPanels){
    y.at.i <- y.at
    if(i>leftPanels[1]){y.at.i <- y.at[1:(length(y.at)-1)]}
    axis(side=2,at=y.at.i)
  }
}

if(i==legend_panel){
   legend(legend_x,
          inset=legend_inset,
       horiz=TRUE,bty="n",
       legend=MPNamesSub_legtext[legtext_o],
       col=cols[legtext_o],lty=ltys[legtext_o],lwd=lwds[legtext_o],
       cex=legend_cex,
       xpd=NA
       )

}
}

mtext(ylabel,side=2,line=1.5,outer=TRUE)
mtext(xlabel,side=1,line= par("mgp")[1],outer=TRUE)

}
```

```{r plot_results function}
plot_results <- function(OMNames,plots=c("SSB/SSBmsy","F/Fmsy","Catch/MSY","TAC/MSY")){
  speciesNames <- gsub("OM_","",OMNames)

  # SSB/SSBmsy
  if("SSB/SSBmsy"%in%plots){    
    plot_MSE_ts_Huynh(
      OMNames= OMNames, scenNames=scenNames_user,
      myvarName = "SB_SBMSY",
      ylabel = expression(mean~~SSB/SSBmsy),
      FUN = mean,
      ylim=c(0,2),
      MPNamesSub = MPNamesSub_user,
      MPNamesSub_legtext=MPNamesSub_user_legtext,
      rowLabs=scenNames_key[scenNames_user]
    )
  }

  # F/Fmsy      
  if("F/Fmsy"%in%plots){
    plot_MSE_ts_Huynh(
      OMNames= OMNames, scenNames=scenNames_user,
      myvarName = "F_FMSY",
      ylabel = expression(mean~~F/Fmsy),
      FUN = mean,
      ylim=c(0,4),
      MPNamesSub = MPNamesSub_user,
      MPNamesSub_legtext=MPNamesSub_user_legtext,
      rowLabs=scenNames_key[scenNames_user]
    )
  }

  # Catch/MSY
  if("Catch/MSY"%in%plots){    
    plot_MSE_ts_Huynh(
      OMNames= OMNames, scenNames=scenNames_user,
      myvarName = "Catch",
      myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears),drop=FALSE]),
      ylabel = expression(mean~~Catch/MSY),
      FUN = mean,
      ylim=c(0,2),
      MPNamesSub = MPNamesSub_user,
      MPNamesSub_legtext=MPNamesSub_user_legtext,
      rowLabs=scenNames_key[scenNames_user]
    )
  }

  # TAC/MSY
  if("TAC/MSY"%in%plots){ 
    plot_MSE_ts_Huynh(
      OMNames= OMNames, scenNames=scenNames_user,
      myvarName = "TAC",
      myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears),drop=FALSE]),
      ylabel = "TAC/MSY",
      FUN = mean,
      ylim=c(0,4),
      MPNamesSub = MPNamesSub_user,
      MPNamesSub_legtext=MPNamesSub_user_legtext,
      rowLabs=scenNames_key[scenNames_user]
    )
  }

  # Catch/TAC
  if("Catch/TAC"%in%plots){ 
    plot_MSE_ts_Huynh(
      OMNames= OMNames, scenNames=scenNames_user,
      myvarName = "Catch",
      myvarDenomExpr = expression(slot(out_i,"TAC")),
      ylabel = expression(mean~~Catch/TAC),
      FUN = mean,
      ylim=c(0,1.1),
      MPNamesSub = MPNamesSub_user,
      MPNamesSub_legtext=MPNamesSub_user_legtext,
      rowLabs=scenNames_key[scenNames_user]
    )
  }

  # SSB
  if("SSB"%in%plots){ 
    plot_MSE_ts_Huynh(
      OMNames= OMNames, scenNames=scenNames_user,
      myvarName = "SSB",
      ylabel = expression(mean~~SSB),
      FUN = mean,
      MPNamesSub = MPNamesSub_user,
      MPNamesSub_legtext=MPNamesSub_user_legtext,
      rowLabs=scenNames_key[scenNames_user]
    )
  }

  # VB
  if("VB"%in%plots){     
    plot_MSE_ts_Huynh(
      OMNames= OMNames, scenNames=scenNames_user,
      myvarName = "VB",
      ylabel = expression(mean~~VB),
      FUN = mean,
      MPNamesSub = MPNamesSub_user,
      MPNamesSub_legtext=MPNamesSub_user_legtext,
      rowLabs=scenNames_key[scenNames_user]
    )
  }

  # F
  if("F"%in%plots){     
    plot_MSE_ts_Huynh(
      OMNames= OMNames, scenNames=scenNames_user,
      myvarName = "FM",
      ylabel = expression(mean~~F),
      FUN = mean,
      MPNamesSub = MPNamesSub_user,
      MPNamesSub_legtext=MPNamesSub_user_legtext,
      rowLabs=scenNames_key[scenNames_user]
    )
  }

  # Catch
  if("Catch"%in%plots){ 
    plot_MSE_ts_Huynh(
      OMNames= OMNames, scenNames=scenNames_user, 
      myvarName = "Catch",
      ylabel = expression(mean~~Catch),
      FUN = mean,
      MPNamesSub = MPNamesSub_user,
      MPNamesSub_legtext=MPNamesSub_user_legtext,
      rowLabs=scenNames_key[scenNames_user]
    )
  }

  # TAC
  if("TAC"%in%plots){     
    plot_MSE_ts_Huynh(
      OMNames= OMNames, scenNames=scenNames_user,
      myvarName = "TAC",
      FUN = mean,
      MPNamesSub = MPNamesSub_user,
      MPNamesSub_legtext=MPNamesSub_user_legtext,
      rowLabs=scenNames_key[scenNames_user] 
    )
  }

  # MSY
  if("MSY"%in%plots){     
    plot_MSE_ts_Huynh(
      OMNames= OMNames, scenNames=scenNames_user,
      myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears),drop=FALSE]),
      FUN = mean,
      ylabel="MSY",
      MPNamesSub = MPNamesSub_user,
      MPNamesSub_legtext=MPNamesSub_user_legtext,
      rowLabs=scenNames_key[scenNames_user]
    )
  }

  # SSBMSY
  if("SSBMSY"%in%plots){ 
    plot_MSE_ts_Huynh(
      OMNames= OMNames, scenNames=scenNames_user,
      myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears),drop=FALSE]),
      FUN = mean,
      ylabel="SSBMSY",
      MPNamesSub = MPNamesSub_user,
      MPNamesSub_legtext=MPNamesSub_user_legtext,
      rowLabs=scenNames_key[scenNames_user]
    )
  }

  # FMSY
  if("FMSY"%in%plots){     
    plot_MSE_ts_Huynh(
      OMNames= OMNames, scenNames=scenNames_user,
      myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears),drop=FALSE]),
      FUN = mean,
      ylabel="FMSY",
      MPNamesSub = MPNamesSub_user,
      MPNamesSub_legtext=MPNamesSub_user_legtext,
      rowLabs=scenNames_key[scenNames_user]
    )
  }

  # UMSY
  if("UMSY"%in%plots){     
    plot_MSE_ts_Huynh(
      OMNames= OMNames, scenNames=scenNames_user,
      myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears),drop=FALSE])),
      FUN = mean,
      ylabel="UMSY",
      MPNamesSub = MPNamesSub_user,
      MPNamesSub_legtext=MPNamesSub_user_legtext,
      rowLabs=scenNames_key[scenNames_user]
    )
  }  
}
```

```{r data, results='hide'}
# Read in data for original operating models
for(file.i in list.files("OM")){
  assign(gsub(".rds","",file.i),readRDS(file.path("OM",file.i)))
}

# Read in data for modified operating models
for(file.i in list.files("OM_modified")){
  assign(gsub(".rds","",file.i),readRDS(file.path("OM_modified",file.i)))
}

if(is.null(OMNames_user)){
OMNames <- gsub(".rds","",list.files("OM"))
}else{
OMNames <- OMNames_user
}

OM_nsim <- c()
for(OM_Name_i in OMNames){
  i <- which(OMNames==OM_Name_i)
  OM_i <- get(OM_Name_i)
  nsim_i <- OM_i@nsim
  OM_nsim <- c(OM_nsim,nsim_i)
}

nsim_text <- combine_words(unique(OM_nsim),and=" or ")

# Read in MSE results
MSE_res_names <- gsub(".rds","",list.files("MSE_obj"))
#MSE_res_names <- gsub(".rds","",list.files("MSE_obj")[grepl("OM_",list.files("MSE_obj"))])
for(file.i in list.files("MSE_obj")){
  obj_name <- gsub(".rds","",file.i)
  print(obj_name)
  assign(obj_name,readRDS(file.path("MSE_obj",file.i)))
}

```

```{r plot data1, fig.cap=paste0("\\label{fig:lifeHist} Life history (growth and maturity) and vulnerability schedules at age used in the operating models for ",combine_words(speciesNames),". Growth is expressed as mean length-at-age relative to that at the maximum age. Compare with Huynh et al (2020) Figure 1."),eval=FALSE}
# Figure 1 from Huynh et al (2020)

# NOTE: These won't always work if the life history values aren't in the right slots.

par(mfrow=c(length(OMNames),1),mgp=c(1,0.2,0),mar=c(1.5,2,1.5,1),oma=c(1,2,1,1),tck=-0.01)
for(OM_Name_i in OMNames){
i <- which(OMNames==OM_Name_i)  
OM_i <- get(OM_Name_i)
speciesName_i <- gsub("OM_","",OM_Name_i)
plot_LH(OM_i,xlab="",ylab="",main=speciesName_i)
if(i==1){
  legend("bottomright",legend=c("Rel. length","Maturity","Vulnerability"),lwd=c(3,3,3),lty=c(1,2,3),bty="n")
}
if(i==length(OMNames)){
  mtext("Value",2,0,outer = TRUE)
}
}
```

```{r plot results,eval=TRUE}
# ct <- 1
# while(ct<=length(OMscenNames_user)){
#   OMscenNames_i <- as.character(na.omit(OMscenNames_user[ct+0:2]))
#   plot_results(OMNames=OMscenNames_i)
#   ct <- ct+3
# }

  plot_results(OMNames=OMNames_user)

```

### 2022-01-07 RunMSE/SEFSC/MSEPlots.Rmd
lots of changes
I ran some new MSEs an restructure the folders so that now there are several subfolders in RunMSE

---
title: "Application of Huynh 2020 Interim Analysis methods to assessed stocks from the US South Atlantic"
author: "Nikolai Klibansky"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    fig_caption: yes
    extra_dependencies:
      longtable: null
      xcolor: null
urlcolor: blue
---

```{r setup, include=FALSE, echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(comment=NA,echo=FALSE,message=FALSE,warning=FALSE,fig.height=7,fig.width=6)

library(Hmisc)
library(knitr)
library(latex2exp) # lets you use TeX() function to convert latex equations to R expressions for plotting
library(SAMtool)
library(stringr)
library(bamExtras)

source('fn/iMP_NK.R')
# Compute U (harvest rate) from F
F2U <- function(F){1 - exp(-F)}

# Median without NA
median_noNA <- function(x){median(x,na.rm=TRUE)}
```

```{r user}
OMNames_user <- c("OM_BlackSeaBass","OM_VermilionSnapper","OM_RedPorgy")#,
                   #"OM_Tilefish","OM_Cobia","OM_SnowyGrouper",
                   #"OM_capelin", "OM_POP", "OM_vs"
                   #)
scenNames_user <-  c("base",#"hs","hd",
                     "dep","lf",
                     "epiM"
                     )
scenNames_key <- c("base"="Base","hs"="Hyper-stable","hd"="Hyper-deplete",
                   "dep"="Depleted","lf"="Lightly fished","epiM"="Episodic M")
MPNamesSub_user <- c("SCA_10","SCA_1","iMP_avg_10","iMP_buffer_10")
MPNamesSub_user_legtext <- c("Fixed TAC (10)","Annual assessment","Averaged Index (10)","Buffered Index (10)")

# OMNames_user <- c("OM_BlackSeaBass","OM_SnowyGrouper","OM_VermilionSnapper")
# OMNames_user <- c("OM_RedPorgy","OM_Tilefish","OM_Cobia")
```

```{r plot_LH function}
plot_LH <- function(OM,...){
maxage <- OM@maxage
agebins <- 0:maxage
lenbins <- vb_len(Linf=OM@Linf[1],K=OM@K[1],t0=OM@t0[1],a=agebins)
Plenbins <- lenbins/max(lenbins)
Mat_age <- OM@cpars$Mat_age[1,,1] # Maturity at age
V <- OM@cpars$V[1,,1] # Vulnerability (selectivity) at age

plot(agebins,Plenbins,ylim=c(0,1),type="l",lwd=3,...)
points(agebins,Mat_age,type="l",lwd=3,lty=2)
points(agebins,V,type="l",lwd=3,lty=3)
}
```

```{r plot_MSE_ts_Huynh function}

plot_MSE_ts_Huynh <- function(
myvarName,
myvarDenomExpr = NULL,
ylabel = myvarName,
FUN = mean_noNA,
scenNames,
OMNames,
MPNamesSub = c("SCA_10","SCA_1","iMP_avg_10","iMP_buffer_10"),
MPNamesSub_legtext=MPNamesSub,
legtext_o = c(2,3,4,1), # order for plotting legend text
MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
                     "_",
                     rep(scenNames,length(OMNames))
                     ),
colLabs = str_replace_all(gsub("OM_","",OMNames),"(?<=[a-z])(?=[A-Z])"," "),
rowLabs = scenNames,

mar=c(1,1,1,1),
cols = setNames(c("red","black","deepskyblue2","deepskyblue2"),MPNamesSub),
ltys = setNames(c(1,1,1,2),MPNamesSub),
lwds = setNames(c(3,3,3,3),MPNamesSub),
types = setNames(c("l","l","l","l"),MPNamesSub),
xlabel = "Management year",
xlim = NULL,
ylim = NULL,
assessmentYears = seq(10,40,by=10),
x.at = NULL,
y.at = NULL,
# leg.x=NULL,
# leg.y =NULL,
legend_panel=NULL,
legend_cex= 1,
legend_x="bottomleft",
legend_inset=c(0,-0.6),
label_axes="all", # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
hline=1 # values to pass into abline(h=hline)
){
xlim_user <- xlim
ylim_user <- ylim
x.at_user <- x.at
y.at_user <- y.at

colLabsAll = as.character(matrix(c(colLabs,rep("",length(MSEoutNames)-length(colLabs))),ncol=length(colLabs),byrow=TRUE))
rowLabsAll = as.character(matrix(c(rep("",length(MSEoutNames)-length(rowLabs)),rowLabs),nrow=length(rowLabs),byrow=FALSE))

nrow <- length(rowLabs)
ncol <- length(colLabs)
npanel <- nrow*ncol

par(mfcol=c(nrow,ncol),mgp=c(1,0.2,0),mar=mar,oma=c(6,4,3,3),tck=-0.01,xpd=FALSE,xaxs="i",yaxs="i")

for(outName_i in MSEoutNames){
topPanels <- (length(scenNames)*(seq_along(OMNames)-1)+1)
bottomPanels <- length(scenNames)*seq_along(OMNames)
leftPanels <- seq_along(scenNames)
rightPanels <- tail(seq_along(MSEoutNames),length(scenNames))

i <- which(MSEoutNames==outName_i)
out_i <- get(outName_i)
MPNames <- out_i@MPs
if(!is.expression(myvarName)){
myvar <- slot(out_i,myvarName)  
}else{
myvar <- eval(myvarName) 
}

legend_panel <- bottomPanels[1]

if(!is.null(myvarDenomExpr)){
myvarDenom <- eval(myvarDenomExpr)
myvar <- myvar/myvarDenom # Scale myvar
}

if(!is.null(dim(myvar))){
myvarsub <- myvar[,match(MPNamesSub,MPNames),]
myvarsubStat <- apply(myvarsub,2,function(x){apply(x,2,FUN)})
}else{
myvarsubStat <- matrix(rep(myvar,length(MPNamesSub)),ncol=length(MPNamesSub))  
}
dimnames(myvarsubStat) <- list(1:nrow(myvarsubStat),MPNamesSub)

xaxt_i <- ifelse(i%in%bottomPanels,"n","n")
yaxt_i <- ifelse(i%in%leftPanels,"n","n")

if(is.null(ylim_user)){
  ylim <- range(myvarsubStat,na.rm=TRUE)
}
if(is.null(xlim_user)){
  xlim <- range(as.numeric(rownames(myvarsubStat)),na.rm=TRUE)
}

matplot(as.numeric(rownames(myvarsubStat)),myvarsubStat,
        col=cols,lty=ltys,lwd=lwds,type=types,
        xaxt=xaxt_i,yaxt=yaxt_i,
        xlim=xlim,ylim=ylim,xlab="",ylab="")
#title(main=colLabsAll[i],line=1)

grid(nx=NA,ny=NULL)
abline(v=assessmentYears,lty="1111",lwd=2)
if(!is.null(hline)){
abline(h=hline)
}

if(is.null(x.at_user)){
  x.at <- pretty(par("usr")[1:2])
}
if(is.null(y.at_user)){
  y.at <- pretty(par("usr")[3:4])
}

if(i%in%topPanels){
col.ct <- which(topPanels==i)
mtext(colLabsAll[i],side=3,line=1,outer=FALSE,font=2)
}

if(i%in%rightPanels){
row.ct <- which(rightPanels==i)
rowcenter <-par("usr")[3]+diff(par("usr")[3:4])/2

text(x=par("usr")[2]*1.05,y=rowcenter,rowLabsAll[i],
     srt=-90,xpd=NA,font=2)
}

if(label_axes=="all"){
  x.at.i <- x.at
  axis(side=1,at=x.at.i)
  y.at.i <- y.at
  axis(side=2,at=y.at.i)
}
if(label_axes=="leftbottom"){
  if(i%in%bottomPanels){
    x.at.i <- x.at
    if(i>bottomPanels[1]){x.at.i <- x.at[-1]}
    axis(side=1,at=x.at.i)
  }
  if(i%in%leftPanels){
    y.at.i <- y.at
    if(i>leftPanels[1]){y.at.i <- y.at[1:(length(y.at)-1)]}
    axis(side=2,at=y.at.i)
  }
}

if(i==legend_panel){
   legend(legend_x,
          inset=legend_inset,
       horiz=TRUE,bty="n",
       legend=MPNamesSub_legtext[legtext_o],
       col=cols[legtext_o],lty=ltys[legtext_o],lwd=lwds[legtext_o],
       cex=legend_cex,
       xpd=NA
       )

}
}

mtext(ylabel,side=2,line=1.5,outer=TRUE)
mtext(xlabel,side=1,line= par("mgp")[1],outer=TRUE)

}
```

```{r data}
# Read in data for original operating models
for(file.i in list.files("OM")){
  assign(gsub(".rds","",file.i),readRDS(file.path("OM",file.i)))
}

# Read in data for modified operating models
for(file.i in list.files("OM_modified")){
  assign(gsub(".rds","",file.i),readRDS(file.path("OM_modified",file.i)))
}

if(is.null(OMNames_user)){
OMNames <- gsub(".rds","",list.files("OM"))
}else{
OMNames <- OMNames_user
}

OM_nsim <- c()
for(OM_Name_i in OMNames){
  i <- which(OMNames==OM_Name_i)
  OM_i <- get(OM_Name_i)
  nsim_i <- OM_i@nsim
  OM_nsim <- c(OM_nsim,nsim_i)
}

nsim_text <- combine_words(unique(OM_nsim),and=" or ")

# Read in MSE results
MSE_res_names <- gsub(".rds","",list.files("MSE_obj"))
#MSE_res_names <- gsub(".rds","",list.files("MSE_obj")[grepl("OM_",list.files("MSE_obj"))])
for(file.i in list.files("MSE_obj")){
  assign(gsub(".rds","",file.i),readRDS(file.path("MSE_obj",file.i)))
}

# # Merge sets of MSE results
# for(i in  OMNames_user){
#   for(j in scenNames_user){
#     OMscenName <- paste0(i,"_",j)
#     MSEName <- gsub("OM","MSE",OMscenName)
#     a <- mget(MSE_res_names[grepl(OMscenName,MSE_res_names)])
#     b <- do.call(merge_MSE, args=a)
#     assign(MSEName,b)
#   }
# }
# 
# rm(list=MSE_res_names)
# MSE_res_names <- gsub("OM","MSE",apply(expand.grid(OMNames_user,scenNames_user),1,function(x){paste(x,collapse ="_")}))

```

```{r,eval=TRUE}
OMNames <- c("OM_BlackSeaBass","OM_VermilionSnapper","OM_RedPorgy")
speciesNames <- gsub("OM_","",OMNames)
```

```{r plot data1, fig.cap=paste0("\\label{fig:lifeHist} Life history (growth and maturity) and vulnerability schedules at age used in the operating models for ",combine_words(speciesNames),". Growth is expressed as mean length-at-age relative to that at the maximum age. Compare with Huynh et al (2020) Figure 1."),eval=TRUE}
# Figure 1 from Huynh et al (2020)

par(mfrow=c(length(OMNames),1),mgp=c(1,0.2,0),mar=c(1.5,2,1.5,1),oma=c(1,2,1,1),tck=-0.01)
for(OM_Name_i in OMNames){
i <- which(OMNames==OM_Name_i)  
OM_i <- get(OM_Name_i)
speciesName_i <- gsub("OM_","",OM_Name_i)
plot_LH(OM_i,xlab="",ylab="",main=speciesName_i)
if(i==1){
  legend("bottomright",legend=c("Rel. length","Maturity","Vulnerability"),lwd=c(3,3,3),lty=c(1,2,3),bty="n")
}
if(i==length(OMNames)){
  mtext("Value",2,0,outer = TRUE)
}
}
```

```{r plot results1,eval=TRUE}

# SSB/SSBmsy
plot_MSE_ts_Huynh(
  OMNames= OMNames, scenNames=scenNames_user,
  myvarName = "SB_SBMSY",
  ylabel = expression(mean~~SSB/SSBmsy),
  FUN = mean,
  ylim=c(0,2),
  MPNamesSub = MPNamesSub_user,
  MPNamesSub_legtext=MPNamesSub_user_legtext,
  rowLabs=scenNames_key[scenNames_user]
)

# F/Fmsy
plot_MSE_ts_Huynh(
  OMNames= OMNames, scenNames=scenNames_user,
  myvarName = "F_FMSY",
  ylabel = expression(mean~~F/Fmsy),
  FUN = mean,
  ylim=c(0,2),
  MPNamesSub = MPNamesSub_user,
  rowLabs=scenNames_key[scenNames_user]
)

# C/MSY
plot_MSE_ts_Huynh(
  OMNames= OMNames, scenNames=scenNames_user,
  myvarName = "Catch",
  myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
  ylabel = expression(mean~~Catch/MSY),
  FUN = mean,
  ylim=c(0,2),
  MPNamesSub = MPNamesSub_user,
  MPNamesSub_legtext=MPNamesSub_user_legtext,
  rowLabs=scenNames_key[scenNames_user]
)

# TAC/MSY
plot_MSE_ts_Huynh(
  OMNames= OMNames, scenNames=scenNames_user,
  myvarName = "TAC",
  myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
  ylabel = "TAC/MSY",
  FUN = mean,
  ylim=c(0,4),
  MPNamesSub = MPNamesSub_user,
  MPNamesSub_legtext=MPNamesSub_user_legtext,
  rowLabs=scenNames_key[scenNames_user]
)

# C/TAC
plot_MSE_ts_Huynh(
  OMNames= OMNames, scenNames=scenNames_user,  
  myvarName = "Catch",
  myvarDenomExpr = expression(slot(out_i,"TAC")),
  ylabel = expression(mean~~C/TAC),
  FUN = mean,
  ylim=c(0,1.1),
  MPNamesSub = MPNamesSub_user,
  MPNamesSub_legtext=MPNamesSub_user_legtext,
  rowLabs=scenNames_key[scenNames_user]
)

# SSB
plot_MSE_ts_Huynh(
  OMNames= OMNames, scenNames=scenNames_user,
  myvarName = "SSB",
  ylabel = expression(mean~~SSB),
  FUN = mean,
  MPNamesSub = MPNamesSub_user,
  MPNamesSub_legtext=MPNamesSub_user_legtext,
  rowLabs=scenNames_key[scenNames_user]
)

# VB
plot_MSE_ts_Huynh(
OMNames= OMNames, scenNames=scenNames_user,
myvarName = "VB",
ylabel = expression(mean~~VB),
FUN = mean,
MPNamesSub = MPNamesSub_user,
MPNamesSub_legtext=MPNamesSub_user_legtext,
rowLabs=scenNames_key[scenNames_user]
)

# F
plot_MSE_ts_Huynh(
OMNames= OMNames, scenNames=scenNames_user,  
myvarName = "FM",
ylabel = expression(mean~~F),
FUN = mean,
MPNamesSub = MPNamesSub_user,
MPNamesSub_legtext=MPNamesSub_user_legtext,
rowLabs=scenNames_key[scenNames_user]
)

# Catch
plot_MSE_ts_Huynh(
OMNames= OMNames, scenNames=scenNames_user,  
myvarName = "Catch",
ylabel = expression(mean~~Catch),
FUN = mean,
MPNamesSub = MPNamesSub_user,
MPNamesSub_legtext=MPNamesSub_user_legtext,
rowLabs=scenNames_key[scenNames_user]
)

# TAC
plot_MSE_ts_Huynh(
OMNames= OMNames, scenNames=scenNames_user,  
myvarName = "TAC",
FUN = mean,
MPNamesSub = MPNamesSub_user,
MPNamesSub_legtext=MPNamesSub_user_legtext,
rowLabs=scenNames_key[scenNames_user] 
)

# MSY
plot_MSE_ts_Huynh(
OMNames= OMNames, scenNames=scenNames_user,
myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
FUN = mean,
ylabel="MSY",
MPNamesSub = MPNamesSub_user,
MPNamesSub_legtext=MPNamesSub_user_legtext,
rowLabs=scenNames_key[scenNames_user]
)

# SSBMSY
plot_MSE_ts_Huynh(
OMNames= OMNames, scenNames=scenNames_user,
myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears)]),
FUN = mean,
ylabel="SSBMSY",
MPNamesSub = MPNamesSub_user,
MPNamesSub_legtext=MPNamesSub_user_legtext,
rowLabs=scenNames_key[scenNames_user]
)

# FMSY
plot_MSE_ts_Huynh(
OMNames= OMNames, scenNames=scenNames_user,
myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)]),
FUN = mean,
ylabel="FMSY",
MPNamesSub = MPNamesSub_user,
MPNamesSub_legtext=MPNamesSub_user_legtext,
rowLabs=scenNames_key[scenNames_user]
)

# UMSY
plot_MSE_ts_Huynh(
OMNames= OMNames, scenNames=scenNames_user,
myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)])),
FUN = mean,
ylabel="UMSY",
MPNamesSub = MPNamesSub_user,
MPNamesSub_legtext=MPNamesSub_user_legtext,
rowLabs=scenNames_key[scenNames_user]
)

```

### 2022-01-07 RunMSE/HCR_MSY/fn/iMP_NK.R

@@ -1,0 +1,237 @@
+# "perfect" MP suggested by Quang Huynh to investigate deviation of HCR_MSY from MSY reference points
+MP_PerfectMSY <- make_MP(Perfect, HCR_MSY)
+
+# Averaged Index and Buffered Index MPs with (numbers indicate assessment interval)
+iMP_avg_5 <- make_interim_MP(.Assess = "SCA_Pope", .HCR = "HCR_MSY", MSY_frac = 1,
+                             assessment_interval = 5,
+                             type = "mean", type_par = 3)
+iMP_avg_10 <- make_interim_MP(SCA_Pope, .HCR = "HCR_MSY", MSY_frac = 1,
+                              assessment_interval = 10,
+                              type = "mean", type_par = 3)
+
+iMP_buffer_5 <- make_interim_MP(.Assess = "SCA_Pope", .HCR = "HCR_MSY", MSY_frac = 1,
+                                assessment_interval = 5,
+                                type = "buffer", type_par = 1)
+iMP_buffer_10 <- make_interim_MP(.Assess = "SCA_Pope", .HCR = "HCR_MSY", MSY_frac = 1,
+                                 assessment_interval = 10,
+                                 type = "buffer", type_par = 1)
+
+# Fixed TAC MPs (numbers indicate assessment interval) and annual assessment MPs
+SCA_5 <- SCA_10 <- SCA_1 <- make_MP(.Assess = "SCA_Pope", .HCR = "HCR_MSY", MSY_frac = 1,
+                                    diagnostic = "min")
+
+# # Merge batches of MSE output (modified for newer version of SAMtool by Nikolai)
+merge_MSE <- function(...) {
+  dots <- list(...)
+
+  slots_identical <- function(slotname, x = dots, is_logical = FALSE) {
+    res <- lapply(x, getElement, slotname)
+    is_identical <- all(vapply(res[-1], identical, logical(1), res[[1]]))
+    if(is_logical) {
+      return(is_identical)
+    } else return(unique(do.call(c, res)))
+  }
+
+  slots_identical("Name")
+  nyears <- slots_identical("nyears")
+  proyears <- slots_identical("proyears")
+  nsim <- slots_identical("nsim")
[…]

### 2022-01-07 RunMSE/HCR_MSY/run_script_NK_HCR_MSY.R

@@ -1,0 +1,135 @@
+library(openMSE)
+library(TMB)
+
+rm(list=ls())
+t_list <- Sys.time()
+set.seed(1358)
+
+nsim <- 48
+runScenarios <- TRUE # Run scenarios to do MSE or just generate historical data?
+runParallel <- TRUE
+ObsUser <- "Perfect_Info" # Set to NULL to avoid replacing Obs
+ImpUser <- "Perfect_Imp"  # Set to NULL to avoid replacing Imp
+
+OM_name_scen_complete <- local({
+  a <- gsub(".rds","",list.files("MSE_obj"))
+  b <- gsub("MSE","OM",a)
+  b
+})
+
+OM_name_all <- gsub(".rds","",list.files("OM"))
+OM_name <- OM_name_all#[!OM_name_all%in%OM_name_complete]
+OM_name <- c("OM_BlackSeaBass","OM_RedPorgy","OM_VermilionSnapper"
+              #,"OM_RedGrouper", "OM_GagGrouper", "OM_GrayTriggerfish"
+             )
+
+# Setup loops
+scenario <- c("base", "nr" #"hs", "hd",
+              #"lf","dep",
+              # "epiM"
+)
+
+seeds <- setNames(sample(1:10000,length(OM_name),replace = FALSE),OM_name)
+
+MSEtool::setup(12) # Run in parallel over 12 cores
+
+for(OM_name_k in OM_name) { ######### Loop over operating model
+  source('fn/iMP_NK.R')
+
+  MSE_name_k <- gsub("OM","MSE",OM_name_k)
+
+  myOM_init <- readRDS(paste0("OM/", OM_name_k, ".rds"))
+
+  if(runScenarios){
+    for(scenario_i in scenario) { ######### Loop over scenario
+      # All scenarios
+      OM_name_scen <- paste0(OM_name_k, "_", scenario_i)
+      if(!OM_name_scen%in%OM_name_scen_complete){
+      myOM <- myOM_init
+      myOM <- SubCpars(myOM, sims = 1:nsim) # Limit number of simulations
+      if(!is.null(ObsUser)) myOM <- Replace(myOM, get(ObsUser))
+      if(!is.null(ImpUser)) myOM <- Replace(myOM, get(ImpUser))
+
+      # No recruitment process error scenario
+      if(scenario_i == "nr") {
+        myOM@cpars$Perr_y[] <- 1
+      }
+
+      # Hyperstable scenario
[…]

### 2022-01-07 RunMSE/RunMSE_SCAconvIssue/Huynh_plots_args_temp.R

@@ -1,0 +1,32 @@
+myvarName = "Catch"
+myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears),drop=FALSE])
+ylabel = expression(mean~~Catch/MSY)
+FUN = mean_noNA
+scenNames=scenNames_user
+OMNames= OMNames
+MPNamesSub = MPNamesSub_user
+MPNamesSub_legtext=MPNamesSub_user_legtext
+legtext_o = 1 # order for plotting legend text
+MSEoutNames = gsub("OM","MSE",OMNames)
+colLabs = str_replace_all(gsub("OM_","",OMNames),"(?<=[a-z])(?=[A-Z])"," ")
+rowLabs=scenNames_key[scenNames_user]
+
+mar=c(1,1,1,1)
+cols = setNames(c("red","black","deepskyblue2","deepskyblue2"),MPNamesSub)
+ltys = setNames(c(1,1,1,2),MPNamesSub)
+lwds = setNames(c(3,3,3,3),MPNamesSub)
+types = setNames(c("l","l","l","l"),MPNamesSub)
+xlabel = "Management year"
+xlim = NULL
+ylim=c(0,2)
+assessmentYears = seq(10,40,by=10)
+x.at = NULL
+y.at = NULL
+# leg.x=NULL
+# leg.y =NULL
+legend_panel=NULL
+legend_cex= 1
+legend_x="bottomleft"
+legend_inset=c(0,-0.6)
+label_axes="all" # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
+hline=1 # values to pass into abline(h=hline)

### 2022-01-07 RunMSE/RunMSE_SCAconvIssue/Project_NK.R

@@ -1,0 +1,553 @@
+Project_NK <- function (Hist = NULL, MPs = NA, parallel = FALSE, silent = FALSE, 
+                        extended = FALSE, checkMPs = TRUE) 
+{
+  popdynOneTScpp <- MSEtool:::popdynOneTScpp
+  calcRecruitment <- MSEtool:::calcRecruitment
+  tiny <- MSEtool:::tiny
+  CalcMPDynamics <- MSEtool:::CalcMPDynamics
+  updateData <- MSEtool:::updateData
+  CheckMPs <- MSEtool:::CheckMPs
+  # readline("press any key to continue")
+  if (class(Hist) != "Hist") 
+    stop("Must provide an object of class `Hist`")
+  OM <- Hist@OM
+  set.seed(OM@seed)
+  nsim <- OM@nsim
+  nyears <- OM@nyears
+  proyears <- OM@proyears
+  interval <- OM@interval
+  maxF <- OM@maxF
+  pstar <- OM@pstar
+  reps <- OM@reps
+  control <- OM@cpars$control
+  OM@cpars$control <- NULL
+  if (checkMPs) 
+    MPs <- CheckMPs(MPs = MPs, silent = silent)
+  nMP <- length(MPs)
+  if (nMP < 1) 
+    stop("No valid MPs found", call. = FALSE)
+  isrunning <- snowfall::sfIsRunning()
+  if (!parallel & isrunning) 
+    snowfall::sfStop()
+  if (parallel) {
+    if (!isrunning) 
+      setup()
+    Export_customMPs(MPs)
+  }
+  if (length(interval) != nMP) 
+    interval <- rep(interval, nMP)[1:nMP]
+  if (!all(interval == interval[1])) {
+    if (!silent) 
+      message("Variable management intervals:")
+    df <- data.frame(MP = MPs, interval = interval)
+    for (i in 1:nrow(df)) {
+      message(df$MP[i], "has management interval:", df$interval[i])
+    }
+  }
+  MSY_y <- Hist@Ref$ByYear$MSY
+  FMSY_y <- Hist@Ref$ByYear$FMSY
+  SSBMSY_y <- Hist@Ref$ByYear$SSBMSY
+  BMSY_y <- Hist@Ref$ByYear$BMSY
+  VBMSY_y <- Hist@Ref$ByYear$VBMSY
+  F01_YPR_y <- Hist@Ref$ByYear$F01_YPR
[…]

### 2022-01-07 RunMSE/RunMSE_SCAconvIssue/SCA_NK.R

@@ -1,0 +1,584 @@
+SCA_NK <- function (x = 1, Data, AddInd = "B", SR = c("BH", "Ricker", 
+                                            "none"), vulnerability = c("logistic", "dome"), catch_eq = c("Baranov", 
+                                                                                                         "Pope"), comp = c("age", "length"), comp_dist = c("multinomial", 
+                                                                                                                                                           "lognormal"), comp_multiplier = c(50, 50), rescale = "mean1", 
+          max_age = Data@MaxAge, start = NULL, prior = list(), fix_h = TRUE, 
+          fix_F_equilibrium = TRUE, fix_omega = TRUE, fix_tau = TRUE, 
+          tv_M = c("none", "walk", "DD"), M_bounds = NULL, refyear = 1, 
+          LWT = list(), early_dev = c("comp_onegen", "comp", "all"), 
+          late_dev = "comp50", integrate = FALSE, silent = TRUE, opt_hess = FALSE, 
+          n_restart = ifelse(opt_hess, 0, 1), control = list(iter.max = 2e+05, 
+                                                             eval.max = 4e+05), inner.control = list(), ...) 
+{
+  print("running SCA_NK")
+  Assess_I_hist <- SAMtool:::Assess_I_hist
+  make_prior <- SAMtool:::make_prior
+  tiny_comp <- SAMtool:::tiny_comp
+  logit <- SAMtool:::logit
+  optimize_TMB_model <- SAMtool:::optimize_TMB_model
+  SCA_dynamic_SSB0 <- SAMtool:::SCA_dynamic_SSB0
+  ref_pt_SCA <- SAMtool:::ref_pt_SCA
+
+  dependencies <- "Data@Cat, Data@Ind, Data@Mort, Data@L50, Data@L95, Data@CAA, Data@vbK, Data@vbLinf, Data@vbt0, Data@wla, Data@wlb, Data@MaxAge"
+  dots <- list(...)
+  start <- lapply(start, eval, envir = environment())
+  max_age <- as.integer(min(max_age, Data@MaxAge))
+  n_age <- max_age + 1
+  vulnerability <- match.arg(vulnerability)
+  catch_eq <- match.arg(catch_eq)
+  comp <- match.arg(comp, several.ok = TRUE)
[…]

### 2022-01-07 RunMSE/RunMSE_SCAconvIssue/SCA_Pope_NK.R

@@ -1,0 +1,22 @@
+SCA_Pope_NK <- function (x = 1, Data, AddInd = "B", SR = c("BH", "Ricker", 
+                                            "none"), vulnerability = c("logistic", "dome"), CAA_dist = c("multinomial", 
+                                                                                                         "lognormal"), CAA_multiplier = 50, rescale = "mean1", max_age = Data@MaxAge, 
+          start = NULL, prior = list(), fix_h = TRUE, fix_U_equilibrium = TRUE, 
+          fix_tau = TRUE, LWT = list(), early_dev = c("comp_onegen", 
+                                                      "comp", "all"), late_dev = "comp50", integrate = FALSE, 
+          silent = TRUE, opt_hess = FALSE, n_restart = ifelse(opt_hess, 
+                                                              0, 1), control = list(iter.max = 2e+05, eval.max = 4e+05), 
+          inner.control = list(), ...) 
+{
+  print("running SCA_Pope_NK")
+  out <- SCA_NK(x = x, Data = Data, AddInd = AddInd, SR = SR, 
+              vulnerability = vulnerability, catch_eq = "Pope", comp = "age", 
+              comp_dist = CAA_dist, comp_multiplier = CAA_multiplier, 
+              rescale = rescale, max_age = max_age, start = start, 
+              prior = prior, fix_h = fix_h, fix_F_equilibrium = fix_U_equilibrium, 
+              fix_omega = TRUE, fix_tau, LWT = LWT, early_dev = early_dev, 
+              late_dev = late_dev, integrate = integrate, silent = silent, 
+              opt_hess = opt_hess, n_restart = n_restart, control = control, 
+              inner.control = inner.control, ...)
+  return(out)
+}

### 2022-01-07 RunMSE/RunMSE_SCAconvIssue/applyMP_NK.R

@@ -1,0 +1,95 @@
+applyMP_NK <- function (Data, MPs = NA, reps = 100, nsims = NA, silent = FALSE) 
+{
+  print("applyMP_NK: running applyMP_NK")
+  if (class(Data) != "Data") 
+    stop("First argument must be object of class 'Data'", 
+         call. = FALSE)
+  Dataout <- Data
+  if (is.na(nsims)) 
+    nsims <- nrow(Data@Cat)
+  nMPs <- length(MPs)
+  if (.hasSlot(Data, "nareas")) {
+    nareas <- Data@nareas
+  }
+  else {
+    nareas <- 2
+  }
+  returnList <- list()
+  recList <- list()
+  TACout <- array(NA, dim = c(nMPs, reps, nsims))
+  refMPs <- c("FMSYref", "FMSYref50", "FMSYref75", "NFref")
+  runParallel <- snowfall::sfIsRunning()
+  if (!silent) 
+    message("Attempting to run ", length(MPs), " MPs:")
+  for (mp in 1:nMPs) {
+    if (!silent) 
+      message(MPs[mp])
+    mp_ns <- find(MPs[mp])
+    dlmmp <- grepl("DLMtool", mp_ns)
+    if (length(dlmmp) < 1) 
+      dlmmp <- FALSE
+    msemmp <- grepl("MSEtool", mp_ns)
+    if (length(msemmp) < 1) 
+      msemmp <- FALSE
+    if (MPs[mp] %in% c("LBSPR", "LBSPR_MLL")) 
+      dlmmp <- FALSE
+    if (dlmmp | msemmp) 
+      runParallel <- FALSE
+    print("applyMP_NK: Made it here")
+    if (runParallel) {
+      temp <- try(snowfall::sfLapply(1:nsims, MPs[mp], 
+                                     Data = Data, reps = reps), silent = TRUE)
+    }
+    else {
+      temp <- try(lapply(1:nsims, MPs[mp], Data = Data, 
+                         reps = reps), silent = TRUE)
+    }
+    mytemp <<-temp
+    myrecList <<- recList
+    mynsims <<- nsims
+    myDataout <<- Dataout
+    mynareas <<- nareas
+    myTACout<<-TACout
+    if (class(temp) == "try-error") {
+      warning("Method ", MPs[mp], " failed with error: ", 
+              temp)
+    }
+    else {
+      slots <- slotNames(temp[[1]])
+      for (X in slots) {
[…]

### 2022-01-07 RunMSE/RunMSE_SCAconvIssue/iMP_avg_10_NK.R

@@ -1,0 +1,98 @@
+iMP_avg_10_NK <- function (x = 1, Data, reps = 1, assessment_interval = 10, AddInd = "VB", 
+          type = "mean", type_par = 3, diagnostic = "min") 
+{
+  dependencies <- "Data@Cat, Data@Ind, Data@Mort, Data@L50, Data@L95, Data@CAA, Data@vbK, Data@vbLinf, Data@vbt0, Data@wla, Data@wlb, Data@MaxAge, Data@steep, Data@CV_Ind, Data@sigmaR, Data@CV_Cat, Data@Mort, Data@CV_Mort, Data@steep, Data@CV_steep, Data@vbLinf, Data@vbK, Data@vbt0, Data@wla, Data@wlb, Data@MaxAge, Data@L50, Data@L95"
+  interim_get_index <- SAMtool:::interim_get_index
+  Assess_diagnostic <- SAMtool:::Assess_diagnostic
+  
+  
+  ny <- length(Data@Year)
+  Current_Yr <- Data@Year[ny]
+  first_assess_yr <- Current_Yr == Data@LHYear
+  run_assessment <- first_assess_yr || Current_Yr == Data@Misc[[x]]$interim$next_assess_yr
+  run_interim <- !run_assessment
+  print(paste("iMP_avg_10_NK: Current_Yr=",Current_Yr))
+  print(paste("iMP_avg_10_NK: run_assessment=",run_assessment))
+  if (run_assessment) {
+    do_Assessment <- SCA_Pope_NK(x = x, Data = Data, AddInd = "VB")
+    if (diagnostic != "none") {
+      Assess_diag_output <- Assess_diagnostic(x, Data, 
+                                              do_Assessment, include_assessment = FALSE)
+    }
+    if (do_Assessment@conv) {
+      Rec <- HCR_MSY(Assessment = do_Assessment, reps = reps, 
+                     MSY_frac = 1)
+      if (diagnostic != "none") 
+        Rec@Misc$diagnostic <- Assess_diag_output$diagnostic
+      if (!is.null(do_Assessment@info$Misc)) 
+        Rec@Misc <- c(Rec@Misc, do_Assessment@info$Misc)
+      Rec@Misc$interim <- list(Cref = Rec@TAC, Iref = do_Assessment@Index[ny, 
+                                                                          1], next_assess_yr = Current_Yr + assessment_interval)
+      if (type == "buffer") {
+        Rec@Misc$interim$s <- log(do_Assessment@Obs_Index[, 
[…]

### 2022-01-07 RunMSE/RunMSE_SCAconvIssue/runMSE_NK.R

@@ -1,0 +1,42 @@
+runMSE_NK <- function (OM = MSEtool::testOM, MPs = NA, Hist = FALSE, silent = FALSE,
+                       parallel = FALSE, extended = FALSE, checkMPs = TRUE)
+{
+  CheckMPs <- MSEtool:::CheckMPs
+  if (class(OM) == "OM") {
+    if (OM@nsim <= 1)
+      stop("OM@nsim must be > 1", call. = FALSE)
+  }
+  else if (class(OM) == "Hist") {
+    if (!silent)
+      message("Using `Hist` object to reproduce historical dynamics")
+  }
+  else {
+    stop("You must specify an operating model")
+  }
+  if (checkMPs & !Hist)
+    MPs <- CheckMPs(MPs = MPs, silent = silent)
+  if (class(OM) == "OM") {
+    HistSims <- Simulate(OM, parallel, silent)
+  }
+  else {
+    HistSims <- OM
+  }
+  if (Hist) {
+    if (!silent)
+      message("Returning historical simulations")
+    return(HistSims)
+  }
+  myHistSims <<- HistSims
+  if (!silent)
+    message("Running forward projections")
+  MSEout <- try(Project_NK(Hist = HistSims, MPs, parallel, silent,
+                        extended = extended, checkMPs = FALSE), silent = TRUE)
+  if (class(MSEout) == "try-error") {
+    message("The following error occured when running the forward projections: ",
+            crayon::red(attributes(MSEout)$condition))
+    message("Returning the historical simulations (class `Hist`). To avoid re-running spool up, ",
+            "the forward projections can be run with ", "`runMSE(Hist, MPs, ...)`")
+    return(HistSims)
+  }
+  MSEout
+}

### 2022-01-07 RunMSE/RunMSE_SCAconvIssue/run_script_MSEfails.R

@@ -1,0 +1,61 @@
+library(openMSE)
+library(TMB)
+
+rm(list=ls())
+t_list <- Sys.time()
+set.seed(1358)
+
+nsim <- 48
+runParallel <- TRUE
+ObsUser <- "Perfect_Info" # Set to NULL to avoid replacing Obs
+ImpUser <- "Perfect_Imp"  # Set to NULL to avoid replacing Imp
+
+OM_name <- "OM_RedGrouper"
+
+# Setup loops
+scenario <- "base"
+
+seeds <- setNames(sample(1:10000,length(OM_name),replace = FALSE),OM_name)
+
+MSEtool::setup(12) # Run in parallel over 12 cores
+
+iMP_avg_10 <- make_interim_MP(SCA_Pope, .HCR = "HCR_MSY", MSY_frac = 1,
+                              assessment_interval = 10,
+                              type = "mean", type_par = 3)
+
+for(OM_name_k in OM_name) { ######### Loop over operating model
+  MSE_name_k <- gsub("OM","MSE",OM_name_k)
+
+  myOM_init <- readRDS(paste0(OM_name_k, ".rds"))
+
+
+    for(scenario_i in scenario) { ######### Loop over scenario
+      # All scenarios
+      OM_name_scen <- paste0(OM_name_k, "_", scenario_i)
+      myOM <- myOM_init
+      myOM <- SubCpars(myOM, sims = 1:nsim) # Limit number of simulations
+      if(!is.null(ObsUser)) myOM <- Replace(myOM, get(ObsUser))
+      if(!is.null(ImpUser)) myOM <- Replace(myOM, get(ImpUser))
+
+      # # Save OM to object
+      OM_name_ki <- paste0(OM_name_k, "_", scenario_i)
+
+      ######## Fixed TAC MPs and Averaged Index MPs
+      myOM@interval <- 1
+
+      message(paste("Fixed TAC and Averaged MPs for:", OM_name_ki))
+      t_list <- c(t_list,Sys.time())
+      message(paste0("at: ",tail(t_list,1),".(",round(diff(tail(t_list,2)),2)," since start)"))
+
+      MSE_batch_1 <- runMSE(myOM, MPs = "iMP_avg_10", parallel = TRUE)
+      message(paste0("batch 1 finished at ",tail(t_list,1),".(",round(diff(tail(t_list,2)),2)," duration"))
+
+      ######## Merge MSE and save output
[…]

### 2022-01-07 RunMSE/RunMSE_SCAconvIssue/tmpCrap.R

@@ -1,0 +1,45 @@
+myvarName = "SB_SBMSY"
+myvarDenomExpr = NULL
+ylabel = myvarName
+FUN = mean_noNA
+OMNames=OMNames_user
+scenNames=scenNames_user
+# MSEoutNames = gsub("OM","MSE",OMNames)
+MPNamesSub = c("SCA_10","SCA_1","iMP_avg_10","iMP_buffer_10")
+MPNamesSub_legtext=MPNamesSub
+legtext_o = c(2,3,4,1) # order for plotting legend text
+MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
+                     "_",
+                     rep(scenNames,length(OMNames))
+)
+colLabs = NULL
+rowLabs = scenNames
+
+mar=c(1,1,1,1)
+cols = setNames(c("red","black","deepskyblue2","deepskyblue2"),MPNamesSub)
+ltys = setNames(c(1,1,1,2),MPNamesSub)
+lwds = setNames(c(3,3,3,3),MPNamesSub)
+types = setNames(c("l","l","l","l"),MPNamesSub)
+xlabel = "Management year"
+xlim = NULL
+ylim = NULL
+assessmentYears = seq(10,40,by=10)
+x.at = NULL
+y.at = NULL
+# leg.x=NULL
+# leg.y =NULL
+legend_panel=NULL
+legend_cex= 1
+legend_x="bottomleft"
+legend_inset=c(0,-0.2)
+label_axes="all" # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
+hline=1 # values to pass into abline(h=hline)
+
+
+
+ylabel = expression(mean~~SSB/SSBmsy)
+FUN = mean
+ylim=c(0,2)
+MPNamesSub = MPNamesSub_user
+MPNamesSub_legtext=MPNamesSub_user_legtext
+rowLabs=scenNames_key[scenNames_user]

### 2022-01-07 RunMSE/SEFSC/run_script_NK.R

@@ -1,0 +1,115 @@
+library(openMSE)
+
+rm(list=ls())
+t1 <- Sys.time()
+set.seed(1358)
+
+runScenarios <- TRUE # Run scenarios to do MSE or just generate historical data?
+
+# assessment_type <-  "SCA_Pope"
+# HCR_type <-  "HCR_MSY"
+# MSY_frac <- 0.75 # Passed to HCR_MSY and multiplied by Fmsy
+
+# Setup loops
+scenario <- c("base"#, #"hs", "hd",
+              #"lf","dep",
+              # "epiM"
+               )
+ OM_name <- c(
+   "OM_RedPorgy"#,
+   #"OM_BlackSeaBass",
+   #"OM_VermilionSnapper"#,
+   #"OM_RedGrouper",
+   # "OM_RedSnapper",
+   # "OM_SnowyGrouper"
+             )
+seeds <- setNames(sample(1:10000,length(OM_name),replace = FALSE),OM_name)
+
+MSEtool::setup(12) # Run in parallel over 12 cores
+
+for(OM_name_k in OM_name) { ######### Loop over operating model
+  source('fn/iMP_NK.R')
+  #source('fn/iMP.R')
+
+  MSE_name_k <- gsub("OM","MSE",OM_name_k)
+
+  myOM_init <- readRDS(paste0("OM/", OM_name_k, ".rds"))
+
+
+  if(runScenarios){
+    for(scenario_i in scenario) { ######### Loop over scenario
+      myOM <- myOM_init
+
+      if(scenario_i == "hs") myOM@beta <- c(1/3, 2/3) # beta values below 1 lead to hyperstability
+      if(scenario_i == "hd") myOM@beta <- c(1.5, 3)
+      if(scenario_i == "dep") {
+        myOM@cpars$D <- 0.5 * myOM@cpars$D
+        # Remove qs so that runMSE will Optimize for user-specified depletion in last historical year
+        myOM@cpars <- myOM@cpars[names(myOM@cpars)[names(myOM@cpars)!="qs"]]
+        }
+      if(scenario_i == "lf")  {
+        myOM@cpars$D <- 1.5 * myOM@cpars$D
+        # Remove qs so that runMSE will Optimize for user-specified depletion in last historical year
+        myOM@cpars <- myOM@cpars[names(myOM@cpars)[names(myOM@cpars)!="qs"]]
+      }
+
+      # NK modified this section to apply to M-at-age
[…]

### 2022-01-07 RunMSE/run_script_NK.R

@@ -1,118 +1,0 @@
-library(openMSE)
-
-rm(list=ls())
-t1 <- Sys.time()
-set.seed(1358)
-
-runScenarios <- TRUE # Run scenarios to do MSE or just generate historical data?
-
-# assessment_type <-  "SCA_Pope"
-# HCR_type <-  "HCR_MSY"
-# MSY_frac <- 0.75 # Passed to HCR_MSY and multiplied by Fmsy
-
-# Setup loops
-scenario <- c("base", #"hs", "hd",
-              "lf","dep",
-               "epiM"
-               )
- OM_name <- c(
-   "OM_RedPorgy",
-   "OM_BlackSeaBass",
-   "OM_VermilionSnapper"#,
-   #"OM_RedGrouper",
-   # "OM_RedSnapper",
-   # "OM_SnowyGrouper"
-             )
-seeds <- setNames(sample(1:10000,length(OM_name),replace = FALSE),OM_name)
-
-MSEtool::setup(12) # Run in parallel over 12 cores
-
-for(OM_name_k in OM_name) { ######### Loop over operating model
-  source('fn/iMP_NK.R')
-  #source('fn/iMP.R')
-
-  MSE_name_k <- gsub("OM","MSE",OM_name_k)
-
-
-  myOM_init <- readRDS(paste0("OM/", OM_name_k, ".rds"))
-  # Generate historic data
-  # MSE_Hist <- runMSE(myOM_init, Hist=TRUE, ntrials = ntrials)
-  # saveRDS(MSE_Hist, file = paste0("MSE_obj/", OM_name_k, "_", "Hist", ".rds"))
-
-  if(runScenarios){
-    for(scenario_i in scenario) { ######### Loop over scenario
-      myOM <- myOM_init
-
-      if(scenario_i == "hs") myOM@beta <- c(1/3, 2/3) # beta values below 1 lead to hyperstability
-      if(scenario_i == "hd") myOM@beta <- c(1.5, 3)
-      if(scenario_i == "dep") {
-        myOM@cpars$D <- 0.5 * myOM@cpars$D
-        # Remove qs so that runMSE will Optimize for user-specified depletion in last historical year
-        myOM@cpars <- myOM@cpars[names(myOM@cpars)[names(myOM@cpars)!="qs"]]
-        }
-      if(scenario_i == "lf")  {
-        myOM@cpars$D <- 1.5 * myOM@cpars$D
[…]

### 2022-03-07 BuildOM/2022-02-14/BuildOMVPA2OM.Rmd
recent runs and new fn

--- 2022-01-07 BuildOM/BuildOMVPA2OM.Rmd
@@
 Perr_y_user <- NA # Set to 1 to remove process error (set to NA in order to leave it as it is)
+
+# Specify observation model (Huynh et al. used the "Precise_Unbiased" Obs model)
+ObsUser <- Perfect_Info
+
+run_rdat_to_Obs <- TRUE   # If TRUE, OM will start with ObsUser but then run rdat_to_Obs on the appropriate
+                          # rdat to modify the Obs object to reflect sampling observed in data used in BAM
+                          # assessments
+
+# Specify implementation model (Huynh et al. used the "Perfect_Imp" Imp model)
+ImpUser <- Perfect_Imp
+
+# Add suffix to OM names
+OM_name_suffix <- ""
+
+# Set vulnerability-at-age (V) to a constant vector in OM@cpars@V
+Vconstant <- FALSE
+
+# Limit maximum value of proportion mature of first age class (usually age-1)
+# Some models fail when maturity of first age class is too high (e.g. >0.5)
+Mat_age1_max <- 0.49
+
+# # par_cv: When generating parameters for Stock objects, mean values are observed from rdat.
+# #         Coefficient of variation (CV) values are set to compute the standard deviation of
+# #         a normal distribution from which to sample parameter values
+# par_cv <- c("TLinfinity"=0.1,"K"=0.1,"M"=0.1)
+# 
+# # OM
+# Agency <- "NMFS SEFSC"
+# Region <- "Southeast US Atlantic"
+# Sponsor <- "none"
+# Latitude <-  mean(c(25.0,35.6))
+# Longitude <- mean(c(-81.5,-74.0))
+# nsim <- 250 # The number of simulations (48 is the minimum number you can run in parallel)
+# proyears <- 50 # The number of projected years
+# interval <- 1  # The assessment interval - how often would you like to update the management system? (should be set to 1 when using the make_interim_MP function using)
+# pstar <- 0.5 # The percentile of the sample of the management recommendation for each method
+# maxF <- 3.0 # Maximum instantaneous fishing mortality rate that may be simulated for any given age class
+# reps <- 1 # Number of samples of the management recommendation for each method. Note that when this is set to 1, the mean value of the data inputs is used
+
 ```
@@
   "BlackSeaBass",
-  #"BluelineTilefish",
-  #"Cobia",
-  #"GagGrouper",
-  #"GrayTriggerfish",
-  #"GreaterAmberjack",
+  "BluelineTilefish",
+  "Cobia",
+  "GagGrouper",
+  "GrayTriggerfish",
+  "GreaterAmberjack",
   #"MenhadenAtl",
-  #"RedGrouper",
+  "RedGrouper",
   "RedPorgy",
-  #"RedSnapper",
-  #"SnowyGrouper",
+  "RedSnapper",
+  "SnowyGrouper",
   #"SpanishMackerel",
-  #"Tilefish",
+  "Tilefish",
   "VermilionSnapper"
@@
 
+OMNames <- gsub("rdat_","OM_",bam_rdat_sub)
+```
+
+```{r build Data, eval=TRUE}
+for(rdat_name_i in bam_rdat_sub){
+  rdat_i <- get(rdat_name_i)
+
+  Data_name_i <- gsub("rdat","Data",rdat_name_i)
+  Data_i <- rdat_to_Data(rdat_i, Mat_age1_max=Mat_age1_max, length_sc = length_sc)
+  # This is to try to solve a problem that occurs later when running Simulate on OM_GreaterAmberjack that has something to do with CAL
+  # I think it might be occurring because there are length comps in a year with no age comps. Maybe. It doesn't occur with Cobia which also
+  # has CAL with values for only a single year.
+  if(Data_name_i=="Data_GreaterAmberjack"){
+    Data_i@CAL <- array(NA,c(1,1,1))
+    Data_i@CAL_bins <- as.numeric(NA)
+    Data_i@CAL_mids <- as.numeric(NA)
+  }
+  #Data_i@wla <- Data_i@wla*0.00220462 # Convert kg to klb
+
+  assign(Data_name_i,Data_i)
+}  
 ```
@@
 
+          if(!is.null(ObsUser)) {
+          if(run_rdat_to_Obs){
+            my_rdat <- get(gsub("OM","rdat",OM_name_i))
+            ObsUser <- rdat_to_Obs(
+                            rdat=my_rdat,
+                            Obs=ObsUser,
+                            Ind_abb=c("CVID","CVT","Mcvt","sCT","sM","VID"),
+                            CAA_abb=c("CVID","CVT","Mcvt","sCT","sM","VID"),
+                            CAL_abb=c("CVID","CVT","Mcvt","sCT","sM","VID")
+                            )
+          }
+        }
+
  OM_i <- VPA2OM(Name=Name_i,
@@
                 h=steep_i, R0=R0_i,
-                Obs = MSEtool::Perfect_Info,
-                Imp = MSEtool::Perfect_Imp,
+                Obs = ObsUser,
+                Imp = ImpUser,
                 naa=naa, faa=faa, waa=waa, Mataa=Mataa, Maa=Maa, laa=laa,
@@
  OM_i@cpars$Perr_y[] <- Perr_y_user
+ }
+
+ if(Vconstant){
+   OM_i@cpars$V <- local({
+     V <- OM_i@cpars$V
+     V2 <- aperm(V, perm = c(2, 1, 3))
+     Vc <- V[1,,OM_i@nyears+1]
+     V3 <- array(Vc,dim=dim(V2))
+     aperm(V3, perm = c(2, 1, 3))
+   })
  }
@@
 
+```{r}
+par(mfrow=c(4,1),mgp=c(1,0.2,0),mar=c(3,2,1.5,1),oma=c(1,2,1,1),tck=-0.01)
+for(OMName_i in OMNames){
+OM_i <- get(OMName_i)
+V_i <- OM_i@cpars$V
+nyears_i <- OM_i@nyears
+proyears_i <- OM_i@proyears
+cols_i <- rainbow(nyears_i)
+matplot(V_i[1,,1:nyears_i],type="l",lty=1,col=cols_i,main=OMName_i,xlab="age",ylab="V")
+matpoints(V_i[1,,nyears_i+(1:proyears_i)],type="l",lty=1,col="black",lwd=2)
+}
+```
+
 ```{r generate Hist and save OM}
@@
   saveRDS(Hist_i, file = file.path("Hist","SEFSC",paste0(Hist_name_i,".rds")))
-  saveRDS(OM_i,file=file.path("OM","SEFSC",paste0(OM_name_i,".rds")),compress=FALSE)
+  saveRDS(OM_i,file=file.path("OM","SEFSC",paste0(OM_name_i,OM_name_suffix,".rds")),compress=FALSE)
   }
@@
 
+legend("bottomleft",
+       legend=c("sim","BAM"),
+       lty=c(2,1),
+       pch=c(NA,1),
+       col=c("black","blue"),
+       bg=rgb(1,1,1,0.5),
+       inset=0.05
+       )
+
 # Indices

### 2022-03-07 BuildOM/BuildOMVPA2OM.Rmd
recent runs and new fn

@@
 length_sc <- 0.1 # Scalar (multiplier) to convert length units. MSEtool examples seem to use cm whereas BAM uses mm.
-plot_OM <- TRUE # Switch for plotting OM. It takes a while to plot them all
+generate_Hist <- TRUE # Switch for running Simulate on all of the OM to generate Hist objects. (takes a while)
+plot_Hist <- TRUE # Plot hist objects
 
@@
 
+OMNames <- gsub("rdat_","OM_",bam_rdat_sub)
+```
+
+```{r build Data, eval=TRUE}
+for(rdat_name_i in bam_rdat_sub){
+  rdat_i <- get(rdat_name_i)
+
+  Data_name_i <- gsub("rdat","Data",rdat_name_i)
+  Data_i <- rdat_to_Data(rdat_i, Mat_age1_max=Mat_age1_max, length_sc = length_sc,nsim=nsim)
+  # This is to try to solve a problem that occurs later when running Simulate on OM_GreaterAmberjack that has something to do with CAL
+  # I think it might be occurring because there are length comps in a year with no age comps. Maybe. It doesn't occur with Cobia which also
+  # has CAL with values for only a single year.
+  # if(Data_name_i=="Data_GreaterAmberjack"){
+  #   Data_i@CAL <- array(NA,c(1,1,1))
+  #   Data_i@CAL_bins <- as.numeric(NA)
+  #   Data_i@CAL_mids <- as.numeric(NA)
+  # }
+  #Data_i@wla <- Data_i@wla*0.00220462 # Convert kg to klb
+
+  assign(Data_name_i,Data_i)
+  saveRDS(Data_i,file=file.path("Data","SEFSC",paste0(Data_name_i,".rds")),compress=FALSE)
+}  
 ```
@@
   steep_i <- parm.cons_i$steep[8]
-  R0_i <- exp(parm.cons_i$log_R0[8])
+  R0_i <- exp(parm.cons_i$log.R0[8])
 
@@
 
+          if(!is.null(ObsUser)) {
+          if(run_rdat_to_Obs){
+            my_rdat <- get(gsub("OM","rdat",OM_name_i))
+            ObsUser <- rdat_to_Obs(
+                            rdat=my_rdat,
+                            Obs=ObsUser,
+                            Ind_abb=c("sCT","sTV","sVD"),
+                            CAA_abb=c("sCT","sTV","sVD"),
+                            CAL_abb=c("sCT","sTV","sVD")
+                            )
+          }
+        }
+
  OM_i <- VPA2OM(Name=Name_i,
@@
 
-```{r generate Hist and save OM}
+```{r plot selectivity}
+par(mfrow=c(4,1),mgp=c(1,0.2,0),mar=c(3,2,1.5,1),oma=c(1,2,1,1),tck=-0.01)
+for(OMName_i in OMNames){
+OM_i <- get(OMName_i)
+V_i <- OM_i@cpars$V
+nyears_i <- OM_i@nyears
+proyears_i <- OM_i@proyears
+cols_i <- rainbow(nyears_i)
+matplot(V_i[1,,1:nyears_i],type="l",lty=1,col=cols_i,main=OMName_i,xlab="age",ylab="V")
+matpoints(V_i[1,,nyears_i+(1:proyears_i)],type="l",lty=1,col="black",lwd=2)
+}
+```
+
+```{r save OM}
 OM_name_bam <- gsub("rdat","OM",bam_rdat_sub) # OM names from bam models
 
-if(plot_OM){
+for(OM_name_i in OM_name_bam){
+  OM_i <- get(OM_name_i)
+
+  if(OM_name_i%in%OM_name_bam){  saveRDS(OM_i,file=file.path("OM","SEFSC",paste0(OM_name_i,OM_name_suffix,".rds")),compress=FALSE)
+  }
+
+}
+```
+
+```{r generate Hist}
+if(generate_Hist){
 
@@
   saveRDS(Hist_i, file = file.path("Hist","SEFSC",paste0(Hist_name_i,".rds")))
-  saveRDS(OM_i,file=file.path("OM","SEFSC",paste0(OM_name_i,".rds")),compress=FALSE)
   }
@@
 ```{r plot Hist with bam  results, eval=TRUE}
+if(plot_Hist){
 pdf("HistBam.pdf")
@@
      col="blue")
+
+legend("bottomleft",
+       legend=c("sim","BAM"),
+       lty=c(2,1),
+       pch=c(NA,1),
+       col=c("black","blue"),
+       bg=rgb(1,1,1,0.5),
+       inset=0.05
+       )
 
@@
 dev.off()
+}
 ```

### 2022-03-07 RunMSE/SEFSC/MSEPlots.Rmd
recent runs and new fn

@@
       xcolor: null
+      pdflscape: null
 urlcolor: blue
@@
 rm(list=ls())
-knitr::opts_chunk$set(comment=NA,echo=FALSE,message=FALSE,warning=FALSE,fig.height=7,fig.width=6)
+knitr::opts_chunk$set(comment=NA,echo=FALSE,message=FALSE,warning=FALSE,fig.height=10,fig.width=8)
 
@@
 
-source('fn/iMP_NK.R')
+#source('fn/iMP.R')
 # Compute U (harvest rate) from F
@@
 ```{r user}
-OMNames_user <- c("OM_BlackSeaBass","OM_VermilionSnapper","OM_RedPorgy")#,
-                   #"OM_Tilefish","OM_Cobia","OM_SnowyGrouper",
+OMNames_user <- c("OM_BlackSeaBass","OM_VermilionSnapper",
+                  "OM_RedPorgy",
+                   #"OM_Tilefish","OM_Cobia",
+                  "OM_SnowyGrouper"#,
+                  #"OM_GagGrouper")#,
                    #"OM_capelin", "OM_POP", "OM_vs"
-                   #)
-scenNames_user <-  c("base",#"hs","hd",
+                   )
+OMNames_huynh <- c("OM_CapelinHuynh", "OM_PacificOceanPerchHuynh", "OM_VermilionSnapperHuynh")
+
+scenNames_user <-  c("base",
+                     #"hs","hd",
+                     "nolag",
                      "dep","lf",
-                     "epiM"
+                     #"epiM",
+                     "rc","ubias","ucvhi","ucvlo"
                      )
-scenNames_key <- c("base"="Base","hs"="Hyper-stable","hd"="Hyper-deplete",
-                   "dep"="Depleted","lf"="Lightly fished","epiM"="Episodic M")
-MPNamesSub_user <- c("SCA_10","SCA_1","iMP_avg_10","iMP_buffer_10")
-MPNamesSub_user_legtext <- c("Fixed TAC (10)","Annual assessment","Averaged Index (10)","Buffered Index (10)")
+scenNames_key <- c("base"="Base",
+                   "nolag"="No data lag",
+                   "hs"="Hyper-stable","hd"="Hyper-deplete",
+                   "dep"="Depleted","lf"="Lightly fished","epiM"="Episodic M",
+                   "rc"="Regime\nchange", "ubias"="Index\nbiased","ucvhi"="Index\nHigh CV","ucvlo"="Index\nLow CV")
+
+MPNamesAll <-         c("AvC","DCAC","DBSRA","SPMSY",
+                        "SCA_1","SCA_5","SCA_10",
+                        "iMP_avg_5","iMP_avg_10","iMP_buffer_5","iMP_buffer_10"
+                        )
+
+MPNamesAll_key <- c("AvC"="average catch",
+                    "DCAC"= "depletion corrected average catch",
+                    "DBSRA" = "depletion based stock reduction analysis",
+                    "SPMSY" = "surplus production model",
+                    "SCA_1" = "SCA 1 yr",
+                    "SCA_5" = "SCA 5 yr",
+                    "SCA_10"= "SCA 10 yr",
+                    "iMP_avg_5" = "avg. index (5 yr)",
+                    "iMP_avg_10" = "avg. index (10 yr)",
+                    "iMP_buffer_5" = "buffer index (5 yr)",
+                    "iMP_buffer_10" = "buffer index (10 yr)"
+                        )
+MPNamesAll_legtext <- MPNamesAll
+
+MPNamesSub_user <- c("SCA_10","SCA_5","SCA_1","iMP_avg_10"#,"iMP_buffer_10"
+                     )
+MPNamesSub_user_legtext <- c("Fixed TAC (10)","Fixed TAC (5)","Annual assessment","Averaged Index (10)"#,"Buffered Index (10)"
+                             )
 
@@
 # OMNames_user <- c("OM_RedPorgy","OM_Tilefish","OM_Cobia")
+```
+
+## Built in performance metrics (PMs)
+
+* `P10`	  Probability B > 0.1 BMSY
+* `P50`	  Probability B > 0.5 BMSY
+* `P100`  Probability B > BMSY
+* `PNOF`  Probability F < FMSY
+* `LTY`	  Probability Long-Term Yield > 0.5 Relative Yield
+* `STY`	  Probability Short-Term Yield > 0.5 Relative Yield
+* `AAVY`	Probability AAVY < 0.2 (Average Annual Variability in Yield)
+* `AAVE`	Probability AAVE < 0.2 (Average Annual Variability in Effort)
+* `Yield`	Average Yield (relative to Reference Yield)
+
+- can easily vary reference values and years
+- PMs compute probabilities across years for each simulation and return mean values across simulations (but we could recompute them however we want from the raw MSE objects)
+
+```{r functions}
+# color function like rainbow() but without yellow (or indigo)
+ROGBP <- colorRampPalette(c("red","orange","green","blue","purple"))
+# Makes an ROGBP function with an alpha channel
+ROGBP_alpha <- function(alpha){
+  x <- colorRampPalette(c(
+    rgb(1,0,0,alpha), # red
+    rgb(1,0.5,0.25,alpha), # orange
+    rgb(0,1,0,alpha), # green 
+    rgb(0,0,1,alpha), # blue
+    rgb(0.5,0,0.5,alpha)), # purple
+    alpha=TRUE)
+  return(x)
+}
+
+P75 <- function(...,Ref=0.75){P50(...,Ref=Ref)}
+
+AAVY10 <- function(MSEobj = NULL, Ref = 0.1, Yrs = NULL){AAVY(MSEobj = MSEobj, Ref = Ref, Yrs = Yrs)}
+
 ```
@@
 Plenbins <- lenbins/max(lenbins)
-Mat_age <- OM@cpars$Mat_age[1,,1] # Maturity at age
-V <- OM@cpars$V[1,,1] # Vulnerability (selectivity) at age
+styr_proj <- OM@nyears+1
+Mat_age <- apply(OM@cpars$Mat_age[,,styr_proj],2,mean) # Maturity at age
+V <- apply(OM@cpars$V[,,styr_proj],2,mean) # Vulnerability (selectivity) at age
 
@@
 
-```{r plot_MSE_ts_Huynh function}
+```{r plot_MSE_ts function}
+# Time series plots
 
-plot_MSE_ts_Huynh <- function(
-myvarName,
+plot_MSE_ts <- function(
+myvarName="SSB",
 myvarDenomExpr = NULL,
 ylabel = myvarName,
-FUN = mean_noNA,
+FUN = mean,
 scenNames,
 OMNames,
-MPNamesSub = c("SCA_10","SCA_1","iMP_avg_10","iMP_buffer_10"),
+MPNamesSub = NULL,
 MPNamesSub_legtext=MPNamesSub,
-legtext_o = c(2,3,4,1), # order for plotting legend text
+MPNamesRef = NULL, # Name of reference MP
+FUNRef = function(myvarsubStat,MPNamesRef){ # Function for comparing MPs with reference MP
+  (myvarsubStat-myvarsubStat[,MPNamesRef])/myvarsubStat[,MPNamesRef]},
+legtext_o = NULL, # order for plotting legend text
 MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
@@
 rowLabs = scenNames,
-
+plot_type="huynh", # "huynh" plots time series by MP like in the Huynh et al paper
+                   # "boot" plots times series of bootstrapped data  with bamExtras::plot_boot_vec
+                   # "phase" plots phase plots of F/Fmsy versus SSB/SSBmsy
+                   # "tradeoff" plots tradeoff plots by MP
+                   # "addind" plot additional indices from AddInd
+proyear_phase=NULL,
+PMx = Yield, # Performance metric function x (x-axis) for tradeoff plots)
+PMy = P75, # Performance metric function y (y-axis) for tradeoff plots)
 mar=c(1,1,1,1),
-cols = setNames(c("red","black","deepskyblue2","deepskyblue2"),MPNamesSub),
-ltys = setNames(c(1,1,1,2),MPNamesSub),
-lwds = setNames(c(3,3,3,3),MPNamesSub),
-types = setNames(c("l","l","l","l"),MPNamesSub),
+oma=c(6,4,3,3),
+mgp=c(1.5,0.2,0),
+cols = setNames(ROGBP(length(MPNamesSub)),MPNamesSub),
+ltys = setNames(rep(1,length(MPNamesSub)),MPNamesSub),
+pchs = setNames(rep(16,length(MPNamesSub)),MPNamesSub),
+lwds = setNames(rep(3,length(MPNamesSub)),MPNamesSub),
+types = setNames(rep("l",length(MPNamesSub)),MPNamesSub),
 xlabel = "Management year",
@@
 ){
+if(is.null(legtext_o)){
+  legtext_o <- seq_along(MPNamesSub)
+}
+
 xlim_user <- xlim
@@
 ncol <- length(colLabs)
-npanel <- nrow*ncol
 
-par(mfcol=c(nrow,ncol),mgp=c(1,0.2,0),mar=mar,oma=c(6,4,3,3),tck=-0.01,xpd=FALSE,xaxs="i",yaxs="i")
+par(mfcol=c(nrow,ncol),mgp=mgp,mar=mar,oma=oma,tck=-0.01,xpd=FALSE,xaxs="i",yaxs="i")
+
+### LOOP THROUGH MSE OBJECTS
+for(outName_i in MSEoutNames){
+topPanels <- (length(scenNames)*(seq_along(OMNames)-1)+1)
+bottomPanels <- length(scenNames)*seq_along(OMNames)
+leftPanels <- seq_along(scenNames)
+rightPanels <- tail(seq_along(MSEoutNames),length(scenNames))
+
+i <- which(MSEoutNames==outName_i)
+out_i <- get(outName_i)
+MPNames <- out_i@MPs
+if(!is.expression(myvarName)){
+myvar <- slot(out_i,myvarName)  
+}else{
+myvar <- eval(myvarName) 
+}
+
+legend_panel <- bottomPanels[1]
+
+if(!is.null(myvarDenomExpr)){
+myvarDenom <- eval(myvarDenomExpr)
+myvar <- myvar/myvarDenom # Scale myvar
+}
+
+xaxt_i <- ifelse(i%in%bottomPanels,"n","n")
+yaxt_i <- ifelse(i%in%leftPanels,"n","n")
+
+MPNamesSubix <- match(MPNamesSub,MPNames)
+
+if(plot_type=="huynh"){
+if(!is.null(dim(myvar))){
+myvarsub <- myvar[,match(MPNamesSub,MPNames),]
+myvarsubStat <- apply(myvarsub,2,function(x){apply(x,2,FUN)})
+}else{
+myvarsubStat <- matrix(rep(myvar,length(MPNamesSub)),ncol=length(MPNamesSub))  
+}
+dimnames(myvarsubStat) <- list(1:nrow(myvarsubStat),MPNamesSub)
+
+if(!is.null(MPNamesRef)){
+myvarsubStat <- FUNRef(myvarsubStat,MPNamesRef)
+}
+
+if(is.null(ylim_user)){
+  ylim <- range(myvarsubStat,na.rm=TRUE)
+}
+if(is.null(xlim_user)){
+  xlim <- range(as.numeric(rownames(myvarsubStat)),na.rm=TRUE)
+}
+
+matplot(as.numeric(rownames(myvarsubStat)),myvarsubStat,
+        col=cols,lty=ltys,lwd=lwds,type=types,
+        xaxt=xaxt_i,yaxt=yaxt_i,
+        xlim=xlim,ylim=ylim,xlab="",ylab="")
+#title(main=colLabsAll[i],line=1)
+
+grid(nx=NA,ny=NULL)
+abline(v=assessmentYears,lty="1111",lwd=2)
+}
+
+if(plot_type=="addind"){
+if(!is.null(dim(myvar))){
+myvarsub <- myvar
+myvarsubStat <- apply(myvarsub,2,function(x){apply(x,2,FUN)})
+}else{
+# myvarsubStat <- matrix(rep(myvar,length(MPNamesSub)),ncol=length(MPNamesSub))  
+}
+# dimnames(myvarsubStat) <- list(1:nrow(myvarsubStat),MPNamesSub)
+
+# if(!is.null(MPNamesRef)){
+# myvarsubStat <- FUNRef(myvarsubStat,MPNamesRef)
+# }
+
+if(is.null(ylim_user)){
+  ylim <- range(myvarsubStat,na.rm=TRUE)
+}
+if(is.null(xlim_user)){
+  xlim <- c(1,nrow(myvarsubStat))
+}
+
+matplot(myvarsubStat,
+        col=cols,lty=ltys,lwd=lwds,type=types,
+        xaxt=xaxt_i,yaxt=yaxt_i,
+        xlim=xlim,ylim=ylim,xlab="",ylab="")
+#title(main=colLabsAll[i],line=1)
+
+grid(nx=NA,ny=NULL)
+abline(v=assessmentYears,lty="1111",lwd=2)
+}
+
+if(plot_type=="boot"){
+  if(is.null(ylim_user)){
+  ylim <- range(myvar,na.rm=TRUE)
+}
+  bamExtras::plot_boot_vec(myvar,ylim=ylim)
+  abline(v=out_i@nyears,lwd=2,lty=2) # Plot vertical line at end of historical period
+}
+
+if(plot_type=="phase"){
+ltys <-  setNames(rep(0,length(MPNamesSub)),MPNamesSub)
+# pchs <-  setNames(rep(1,length(MPNamesSub)),MPNamesSub)
+lwds <-  setNames(rep(0,length(MPNamesSub)),MPNamesSub)
+types <- setNames(rep("p",length(MPNamesSub)),MPNamesSub)  
+xlabel <- "F/Fmsy"  
+ylabel <- "SSB/SSBmsy"
+
+if(is.null(proyear_phase)){
+  proyear_phase <- out_i@proyears
+}
+Bstatus <- out_i@SB_SBMSY[,MPNamesSubix,proyear_phase]
+Fstatus <- out_i@F_FMSY[,MPNamesSubix,proyear_phase]
+
+matplot(Fstatus,Bstatus,
+        col=cols,lty=ltys,lwd=lwds,pch=pchs,type=types,
+        xaxt=xaxt_i,yaxt=yaxt_i,
+        xlab="",ylab="",xlim=xlim,ylim=ylim
+        )
+points(apply(Fstatus,2,median),
+       apply(Bstatus,2,median),pch=21,cex=3,lwd=2,col="black",bg=cols)
+
+  abline(v=1,lty=3)
+  abline(h=1,lty=3)
+
+}
+
+if(plot_type=="tradeoff"){
+  out_i <- get(outName_i)
+
+PMx_out <- PMx(out_i)
+PMy_out <- PMy(out_i)
+
+plot(PMx_out@Mean[MPNamesSubix],PMy_out@Mean[MPNamesSubix],pch=16,col=cols,
+     xaxt=xaxt_i,yaxt=yaxt_i,
+     xlab="",ylab="",
+     xlim=xlim,ylim=ylim
+     )
+
+# legend("top",legend=MPs,col=MPcols,pch=16,bty="n")
+
+ltys <-  setNames(rep(0,length(MPNamesSub)),MPNamesSub)
+lwds <-  setNames(rep(0,length(MPNamesSub)),MPNamesSub)
+types <- setNames(rep("p",length(MPNamesSub)),MPNamesSub)  
+xlabel <- PMx_out@Caption 
+ylabel <- PMy_out@Caption
+
+}
+
+if(!is.null(hline)){
+abline(h=hline)
+}
+
+if(is.null(x.at_user)){
+  x.at <- pretty(par("usr")[1:2])
+}
+if(is.null(y.at_user)){
+  y.at <- pretty(par("usr")[3:4])
+}
+
+if(i%in%topPanels){
+col.ct <- which(topPanels==i)
+mtext(colLabsAll[i],side=3,line=1,outer=FALSE,font=2)
+}
+
+if(i%in%rightPanels){
+row.ct <- which(rightPanels==i)
+rowcenter <-par("usr")[3]+diff(par("usr")[3:4])/2
+
+text(x=par("usr")[2]*1.05,y=rowcenter,rowLabsAll[i],
+     srt=-90,xpd=NA,font=2)
+}
+
+if(label_axes=="all"){
+  x.at.i <- x.at
+  axis(side=1,at=x.at.i)
+  y.at.i <- y.at
+  axis(side=2,at=y.at.i)
+}
+if(label_axes=="leftbottom"){
+  if(i%in%bottomPanels){
+    x.at.i <- x.at
+    if(i>bottomPanels[1]){x.at.i <- x.at[-1]}
+    axis(side=1,at=x.at.i,outer=TRUE)
+  }
+  if(i%in%leftPanels){
+    y.at.i <- y.at
+    if(i>leftPanels[1]){y.at.i <- y.at[1:(length(y.at)-1)]}
+    axis(side=2,at=y.at.i,outer=TRUE)
+  }
+}
+
+if(i==legend_panel&plot_type%in%c("huynh","phase","tradeoff")){
+   legend(legend_x,
+          inset=legend_inset,
+       horiz=TRUE,bty="n",
+       legend=MPNamesSub_legtext[legtext_o],
+       col=cols[legtext_o],lty=ltys[legtext_o],lwd=lwds[legtext_o],pch=pchs[legtext_o],
+       cex=legend_cex,
+       xpd=NA,
+       x.intersp=0.5
+       )
+
+}
+}
+
+mtext(ylabel,side=2,line=par("mgp")[1],outer=TRUE)
+mtext(xlabel,side=1,line= par("mgp")[1],outer=TRUE)
+
+}
+```
+
+```{r plot_MSE_dw function}
+# Dot and whisker plots
+
+plot_MSE_dw <- function(
+myvarName,
+myvarDenomExpr = NULL,
+ylabel = myvarName,
+FUN = cv,  # MSEtool::cv
+scenNames,
+OMNames,
+MPNamesSub = c("SCA_10","SCA_1","iMP_avg_10","iMP_buffer_10"),
+MPNamesSub_legtext=MPNamesSub,
+legtext_o = c(3,2,1,4), # order for plotting legend text
+MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
+                     "_",
+                     rep(scenNames,length(OMNames))
+                     ),
+colLabs = str_replace_all(gsub("OM_","",OMNames),"(?<=[a-z])(?=[A-Z])"," "),
+rowLabs = scenNames,
+
+mar=c(0,0,0,0),
+oma=c(10,4,3,3),
+mgp=c(1,0.3,0),
+cols = setNames(ROGBP(length(MPNamesSub)),MPNamesSub),
+ltys = setNames(rep(1,length(MPNamesSub)),MPNamesSub),
+lwds = setNames(rep(1,length(MPNamesSub)),MPNamesSub),
+pchs = setNames(rep(16,length(MPNamesSub)),MPNamesSub),
+types = setNames(rep("l",length(MPNamesSub)),MPNamesSub),
+textlabpos = rep("lo",length(MSEoutNames)),#c(rep("lo",6),rep("up",7),"lo",rep("up",4)),
+xlabel = "Management procedure",
+xlabel_line=9,
+xlim = NULL,
+ylim = c(0,0.6),
+x.at = NULL,
+y.at = NULL,
+# leg.x=NULL,
+# leg.y =NULL,
+# legend_panel=NULL,
+# legend_cex= 1,
+# legend_x="bottomleft",
+# legend_inset=c(0,-0.6),
+label_axes="leftbottom", # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
+hline=1 # values to pass into abline(h=hline)
+){
+
+xlim_user <- xlim
+ylim_user <- ylim
+x.at_user <- x.at
+y.at_user <- y.at
+
+colLabsAll = as.character(matrix(c(colLabs,rep("",length(MSEoutNames)-length(colLabs))),ncol=length(colLabs),byrow=TRUE))
+rowLabsAll = as.character(matrix(c(rep("",length(MSEoutNames)-length(rowLabs)),rowLabs),nrow=length(rowLabs),byrow=FALSE))
+
+nrow <- length(rowLabs)
+ncol <- length(colLabs)
+
+par(mfcol=c(nrow,ncol),mgp=mgp,mar=mar,oma=oma,tck=-0.01,xpd=FALSE,xaxs="i",
+    yaxs="r",lend="butt")
 
@@
 
-if(is.null(ylim_user)){
-  ylim <- range(myvarsubStat,na.rm=TRUE)
-}
 if(is.null(xlim_user)){
-  xlim <- range(as.numeric(rownames(myvarsubStat)),na.rm=TRUE)
+  xlim <- c(0,length(MPNamesSub)+1)
 }
 
-matplot(as.numeric(rownames(myvarsubStat)),myvarsubStat,
-        col=cols,lty=ltys,lwd=lwds,type=types,
+################################
+
+Statmed <- apply(myvarsubStat,2,median)
+Statmedtext <- round(Statmed,2)
+StatQ1 <- apply(myvarsubStat,2,quantile,probs=0.25,na.rm=TRUE)
+StatQ3 <- apply(myvarsubStat,2,quantile,probs=0.75,na.rm=TRUE)
+
+xaxt_i <- ifelse(i%in%bottomPanels,"n","n")
+yaxt_i <- ifelse(i%in%leftPanels,"n","n")
+x <- seq_along(MPNamesSub)
+plot(x,Statmed,
+        col=cols,pch=pchs,type="n",bg="white",
         xaxt=xaxt_i,yaxt=yaxt_i,
         xlim=xlim,ylim=ylim,xlab="",ylab="")
-#title(main=colLabsAll[i],line=1)
+arrows(x0=x,y0=StatQ1,y1=StatQ3,
+       col=cols,lty=ltys,lwd=lwds,length=0
+       )
+points(x,Statmed,
+        col=cols,pch=pchs,type="p",bg="white",cex=1.2,
+        xaxt=xaxt_i,yaxt=yaxt_i,
+        xlim=xlim,ylim=ylim,xlab="",ylab="")
 
-grid(nx=NA,ny=NULL)
-abline(v=assessmentYears,lty="1111",lwd=2)
-if(!is.null(hline)){
-abline(h=hline)
-}
+if(textlabpos[i]=="lo"){text(x=x,y=rep(par("usr")[3]),labels=Statmedtext,srt=90,adj=c(-0.1,0.5),font=2)}
+if(textlabpos[i]=="up"){text(x=x,y=rep(par("usr")[4]),labels=Statmedtext,srt=90,adj=c(1.2,0.5),font=2)}
 
-if(is.null(x.at_user)){
-  x.at <- pretty(par("usr")[1:2])
-}
-if(is.null(y.at_user)){
-  y.at <- pretty(par("usr")[3:4])
-}
+################################
 
@@
     if(i>bottomPanels[1]){x.at.i <- x.at[-1]}
-    axis(side=1,at=x.at.i)
+    # axis(side=1,at=x.at.i)
+    axis(side=1,at=x,labels=MPNamesSub_legtext,las=2)
   }
@@
 
-if(i==legend_panel){
-   legend(legend_x,
-          inset=legend_inset,
-       horiz=TRUE,bty="n",
-       legend=MPNamesSub_legtext[legtext_o],
-       col=cols[legtext_o],lty=ltys[legtext_o],lwd=lwds[legtext_o],
-       cex=legend_cex,
-       xpd=NA
-       )
-
-}
+# if(i==legend_panel){
+#    legend(legend_x,
+#           inset=legend_inset,
+#        horiz=TRUE,bty="n",
+#        legend=MPNamesSub_legtext[legtext_o],
+#        col=cols[legtext_o],lty=ltys[legtext_o],lwd=lwds[legtext_o],
+#        cex=legend_cex,
+#        xpd=NA
+#        ) 
+# 
+# }
 }
@@
 mtext(ylabel,side=2,line=1.5,outer=TRUE)
-mtext(xlabel,side=1,line= par("mgp")[1],outer=TRUE)
+mtext(xlabel,side=1,line=xlabel_line,outer=TRUE)
 
+}
+```
+
+```{r function PMsummary}
+# compute and plot summary statistics
+
+PMsummary <- function(myMPName,OMNames=OMNames_user,scenNames=scenNames_user){
+myMP <- get(myMPName)
+out_list <- list()
+
+par(mfrow=c(length(OMNames),1),mar=c(2,2,2,1),oma=c(0,2,0,0),mgp=c(0.8,0.2,0),tck=-0.01)
+
+for (OMNames_i in OMNames){
+Names_i <- gsub("^OM_","",OMNames_i)
+MSEoutNames_i = paste0(rep(gsub("OM","MSE",OMNames_i),each=length(scenNames)),
+                     "_",
+                     rep(scenNames,length(OMNames_i))
+                     )
+    Prob_list_i <- list()
+    for(MSEoutNames_ij in MSEoutNames_i){
+      scenNames_j <- str_extract(MSEoutNames_ij,"[a-z]+$")
+      MSEout_ij <- get(MSEoutNames_ij)
+      PMout_ij <- myMP(MSEout_ij)
+      MPs_ij <- PMout_ij@MPs
+      Prob_ij <- PMout_ij@Prob
+      dimnames(Prob_ij) <- list("sim"=seq(1:dim(Prob_ij)[1]), "MPs"=MPs_ij)
+      Prob_ij <- cbind("scen"=scenNames_j,as.data.frame(Prob_ij))
+      Prob_list_i[[MSEoutNames_ij]] <- Prob_ij
+
+    }
+    # Combine scenario outputs into large data frame with scen column indicating scenario
+    Prob_df_i <- do.call(rbind,Prob_list_i)
+    out_list[[paste0("Prob_df_",Names_i,"_",myMPName)]] <- Prob_df_i
+
+    # Plot stuff
+    boxplot(Prob_df_i[,-1],ylab=myMPName,main=Names_i)
+    }
+
+invisible(out_list)
 }
@@
 for(file.i in list.files("MSE_obj")){
+  out_i <- readRDS(file.path("MSE_obj",file.i))
+  names(out_i@PPD) <- out_i@MPs
   assign(gsub(".rds","",file.i),readRDS(file.path("MSE_obj",file.i)))
@@
 
-```{r,eval=TRUE}
-OMNames <- c("OM_BlackSeaBass","OM_VermilionSnapper","OM_RedPorgy")
+```{r OMNames set 1,eval=TRUE}
+OMNames <- OMNames_user#[1:3]
 speciesNames <- gsub("OM_","",OMNames)
+speciesNames_huynh <- gsub("OM_","",OMNames_huynh)
+MSEoutNames_user <- paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames_user)),
+                     "_",
+                     rep(scenNames_user,length(OMNames))
+                     )
+
 ```
 
-```{r plot data1, fig.cap=paste0("\\label{fig:lifeHist} Life history (growth and maturity) and vulnerability schedules at age used in the operating models for ",combine_words(speciesNames),".
-Growth is expressed as mean length-at-age relative to that at the maximum age.
-Compare with Huynh et al (2020) Figure 1."),eval=TRUE}
+```{r plot data1, fig.cap=paste0("\\label{fig:lifeHist} Life history (growth and maturity) and vulnerability schedules at age used in the operating models during the projection period ",combine_words(speciesNames),".
+Growth is expressed as mean length-at-age relative to that at the maximum age."),eval=TRUE}
 # Figure 1 from Huynh et al (2020)
@@
 
-```{r plot results1,eval=TRUE}
+```{r plot selectivities,fig.cap=paste0("\\label{fig:selex} Vulnerability schedules at age used in the operating models during the historical period (colored lines in rainbow order) and projection period (black lines)",combine_words(speciesNames),".
+Growth is expressed as mean length-at-age relative to that at the maximum age.")}
+par(mfrow=c(length(OMNames),1),mgp=c(1,0.2,0),mar=c(3,2,1.5,1),oma=c(1,2,1,1),tck=-0.01)
+for(OMName_i in paste0(OMNames,"_base")){
+OM_i <- get(OMName_i)
+V_i <- OM_i@cpars$V
+nyears_i <- OM_i@nyears
+proyears_i <- OM_i@proyears
+cols_i <- rainbow(nyears_i)
+matplot(V_i[1,,1:nyears_i],type="l",lty=1,col=cols_i,main=OMName_i,xlab="age",ylab="V")
+matpoints(V_i[1,,nyears_i+(1:proyears_i)],type="l",lty=1,col="black",lwd=2)
+}
+
+```
+
+```{r plot selectivities huynh,fig.cap=paste0("\\label{fig:selexhuynh} Vulnerability schedules at age used in the operating models during the historical period (colored lines in rainbow order) and projection period (black lines)",combine_words(speciesNames_huynh),".
+Growth is expressed as mean length-at-age relative to that at the maximum age.")}
+par(mfrow=c(length(OMNames_huynh),1),mgp=c(1,0.2,0),mar=c(3,2,1.5,1),oma=c(1,2,1,1),tck=-0.01)
+for(OMName_i in OMNames_huynh){
+OM_i <- get(OMName_i)
+V_i <- OM_i@cpars$V
+nyears_i <- OM_i@nyears
+proyears_i <- OM_i@proyears
+cols_i <- rainbow(nyears_i)
+matplot(V_i[1,,1:nyears_i],type="l",lty=1,col=cols_i,main=OMName_i,xlab="age",ylab="V")
+matpoints(V_i[1,,nyears_i+(1:proyears_i)],type="l",lty=1,col="black",lwd=2)
+}
+
+```
+
+```{r plot indices, eval=TRUE}
+# This code is set up to make each set of plots for each MP, but the indices are basically the same
+
+for(MP_name_i in MPNamesAll){
+    # Ind
+    # MSE_i <- get(MSE_name_j)
+    plot_MSE_ts(
+      OMNames= OMNames, scenNames=scenNames_user,
+      myvarName = expression(slot(out_i@PPD[[MP_name_i]],"Ind")),
+      plot_type = "boot",
+      FUN = mean_noNA,
+      ylabel = "index of abundance",
+      MPNamesSub = MPNamesSub_user,
+      MPNamesSub_legtext=MPNamesSub_user_legtext,
+      rowLabs=scenNames_key[scenNames_user],
+      oma=c(3,4,5,3),
+      ylim=c(0,4)
+    )
+  title(main=MP_name_i,outer=TRUE)
+}
+```
+
+```{r plot addindices, eval=FALSE}
+# This code is set up to make each set of plots for each MP, but the indices are basically the same
+
+for(MP_name_i in MPNamesAll){
+    # Ind
+    # MSE_i <- get(MSE_name_j)
+    plot_MSE_ts(
+      OMNames= OMNames, scenNames="addind",
+      myvarName = expression(slot(out_i@PPD[[MP_name_i]],"AddInd")),
+      plot_type = "addind",
+      ylabel = "index of abundance",
+      FUN=mean_noNA,
+      MPNamesSub = MPNamesSub_user,
+      MPNamesSub_legtext=MPNamesSub_user_legtext,
+      rowLabs=scenNames_key["addind"],
+      oma=c(3,4,5,3),
+      ylim=c(0,4)
+    )
+  title(main=MP_name_i,outer=TRUE)
+}
+```
+
+```{r summary plots}
+P75_out <- PMsummary("P75")
+mtext("P(B > 0.75 BMSY)",2,outer=TRUE,font=2)
+
+PNOF_out <- PMsummary("PNOF")
+mtext("P(F < FMSY)",2,outer=TRUE,font=2)
+
+AAVY_out <- PMsummary("AAVY")
+mtext("P(AAVY < 0.2) (Average Annual Variability in Yield)",2,outer=TRUE,font=2)
+
+## Which is the best MP?
+
+### Highest yield
+
+### Most consistent yield
+
+### Lowest probability of overfishing
+```
+
+```{r plot time series,eval=TRUE}
+# # VB
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user,
+# myvarName = "VB",
+# ylabel = expression(mean~(VB)),
+# FUN = mean,
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user]
+# )
+
+# SSB
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user,
+  myvarName = "SSB",
+  ylabel = expression(mean~(SSB)),
+  FUN = mean,
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user]
+)
+# 
+# # F
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user,  
+# myvarName = "FM",
+# ylabel = expression(mean~(F)),
+# FUN = mean,
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user]
+# )
+# 
+# # TAC
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user,  
+# myvarName = "TAC",
+# ylabel = expression(mean~(TAC)),
+# FUN = mean,
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user] 
+# )
+
+# Catch
+plot_MSE_ts(
+OMNames= OMNames, scenNames=scenNames_user,  
+myvarName = "Catch",
+ylabel = expression(mean~(Catch)),
+FUN = mean,
+MPNamesSub = MPNamesSub_user,
+MPNamesSub_legtext=MPNamesSub_user_legtext,
+rowLabs=scenNames_key[scenNames_user]
+)
 
 # SSB/SSBmsy
-plot_MSE_ts_Huynh(
+plot_MSE_ts(
   OMNames= OMNames, scenNames=scenNames_user,
   myvarName = "SB_SBMSY",
-  ylabel = expression(mean~~SSB/SSBmsy),
+  ylabel = expression(mean~(SSB/SSBmsy)),
   FUN = mean,
@@
 # F/Fmsy
-plot_MSE_ts_Huynh(
+plot_MSE_ts(
   OMNames= OMNames, scenNames=scenNames_user,
   myvarName = "F_FMSY",
-  ylabel = expression(mean~~F/Fmsy),
+  ylabel = expression(mean~(F/Fmsy)),
   FUN = mean,
@@
 # C/MSY
-plot_MSE_ts_Huynh(
+plot_MSE_ts(
   OMNames= OMNames, scenNames=scenNames_user,
@@
   myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
-  ylabel = expression(mean~~Catch/MSY),
+  ylabel = expression(mean~(Catch/MSY)),
   FUN = mean,
@@
 )
+# 
+# # TAC/MSY
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user,
+#   myvarName = "TAC",
+#   myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+#   ylabel = expression(mean~(TAC/MSY)),
+#   FUN = mean,
+#   ylim=c(0,2),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user]
+# )
+# 
+# # C/TAC
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user,  
+#   myvarName = "Catch",
+#   myvarDenomExpr = expression(slot(out_i,"TAC")),
+#   ylabel = expression(mean~(C/TAC)),
+#   FUN = mean,
+#   ylim=c(0,1.1),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user]
+# )
+# 
+# # MSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user,
+# myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+# FUN = mean,
+# ylabel= expression(mean~(MSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user]
+# )
+# 
+# # SSBMSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user,
+# myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears)]),
+# FUN = mean,
+# ylabel= expression(mean~(SSBMSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user]
+# )
+# 
+# # FMSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user,
+# myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)]),
+# FUN = mean,
+# ylabel= expression(mean~(FMSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user]
+# )
+# 
+# # UMSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user,
+# myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)])),
+# FUN = mean,
+# ylabel= expression(mean~(UMSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user]
+# )
+```
 
-# TAC/MSY
-plot_MSE_ts_Huynh(
+```{r plot time series RE,eval=TRUE}
+# # VB
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user,
+# myvarName = "VB",
+# ylabel = expression(RE~(mean~(VB))),
+# FUN = mean, MPNamesRef = "SCA_1",
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user]
+# )
+
+# SSB
+plot_MSE_ts(
   OMNames= OMNames, scenNames=scenNames_user,
-  myvarName = "TAC",
-  myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
-  ylabel = "TAC/MSY",
-  FUN = mean,
-  ylim=c(0,4),
+  myvarName = "SSB",
+  ylabel = expression(RE~(mean~(SBB))),
+  FUN = mean, MPNamesRef = "SCA_1",
   MPNamesSub = MPNamesSub_user,
   MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user],
+  ylim=c(-0.5,0.5)
+)
+# 
+# # F
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user,  
+# myvarName = "FM",
+# ylabel = expression(RE~(mean~(F))),
+# FUN = mean, MPNamesRef = "SCA_1",
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user]
+# )
+# 
+# # TAC
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user,  
+# myvarName = "TAC",
+# ylabel = expression(RE~(mean~(TAC))),
+# FUN = mean, MPNamesRef = "SCA_1",
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user] 
+# )
+
+# Catch
+plot_MSE_ts(
+OMNames= OMNames, scenNames=scenNames_user,  
+myvarName = "Catch",
+ylabel = expression(RE~(mean~(Catch))),
+FUN = mean, MPNamesRef = "SCA_1",
+MPNamesSub = MPNamesSub_user,
+MPNamesSub_legtext=MPNamesSub_user_legtext,
+rowLabs=scenNames_key[scenNames_user],
+ylim=c(-0.5,0.5)
+)
+
+# SSB/SSBmsy
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user,
+  myvarName = "SB_SBMSY",
+  ylabel = expression(RE~(mean~(SSB/SSBmsy))),
+  FUN = mean, MPNamesRef = "SCA_1",
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user],
+  ylim=c(-0.5,0.5),
+  hline=NA
+)
+
+# F/Fmsy
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user,
+  myvarName = "F_FMSY",
+  ylabel = expression(RE~(mean~(F/Fmsy))),
+  FUN = mean, MPNamesRef = "SCA_1",
+  MPNamesSub = MPNamesSub_user,
+  rowLabs=scenNames_key[scenNames_user],
+  ylim=c(-1,1.5),
+  hline=NA
+)
+
+# C/MSY
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user,
+  myvarName = "Catch",
+  myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+  ylabel = expression(RE~(mean~(Catch/MSY))),
+  FUN = mean, MPNamesRef = "SCA_1",
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user],
+  ylim=c(-0.5,0.5)
+)
+
+# 
+# # TAC/MSY
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user,
+#   myvarName = "TAC",
+#   myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+#   ylabel = expression(RE~(mean~(TAC/MSY))),
+#   FUN = mean, MPNamesRef = "SCA_1",
+#   ylim=c(0,2),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user],
+#   ylim=c(-0.5,0.5),
+#   hline=NA
+# )
+# 
+# # C/TAC
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user,  
+#   myvarName = "Catch",
+#   myvarDenomExpr = expression(slot(out_i,"TAC")),
+#   ylabel = expression(RE~(mean~(C/TAC))),
+#   FUN = mean, MPNamesRef = "SCA_1",
+#   ylim=c(0,1.1),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user],
+#   ylim=c(-0.5,0.5),
+#   hline=NA
+# )
+# 
+# # MSY
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user,
+#   myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+#   FUN = mean, MPNamesRef = "SCA_1",
+#   ylabel= expression(RE~(mean~(MSY))),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user],
+#   ylim=c(-0.5,0.5),
+#   hline=NA
+# )
+# 
+# # SSBMSY
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user,
+#   myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears)]),
+#   FUN = mean, MPNamesRef = "SCA_1",
+#   ylabel= expression(RE~(mean~(SSBMSY))),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user],
+#   ylim=c(-0.5,0.5),
+#   hline=NA
+# )
+# 
+# # FMSY
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user,
+#   myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)]),
+#   FUN = mean, MPNamesRef = "SCA_1",
+#   ylabel= expression(RE~(mean~(FMSY))),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user],
+#   ylim=c(-0.5,0.5),
+#   hline=NA
+# )
+# 
+# # UMSY
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user,
+#   myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)])),
+#   FUN = mean, MPNamesRef = "SCA_1",
+#   ylabel= expression(RE~(mean~(UMSY))),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user],
+#   ylim=c(-0.5,0.5),
+#   hline=NA
+# )
+```
+
+```{r plot dot and whiskers, eval=TRUE}
+plot_MSE_dw(
+    OMNames= OMNames, scenNames=scenNames_user,
+    myvarName = "SSB",
+    ylabel = expression(cv~(SSB)),
+    FUN = cv,
+    MPNamesSub = MPNamesAll,
+    MPNamesSub_legtext=MPNamesAll_legtext,
     rowLabs=scenNames_key[scenNames_user]
@@
 
-# C/TAC
-plot_MSE_ts_Huynh(
+plot_MSE_dw(
     OMNames= OMNames, scenNames=scenNames_user,
     myvarName = "Catch",
-  myvarDenomExpr = expression(slot(out_i,"TAC")),
-  ylabel = expression(mean~~C/TAC),
-  FUN = mean,
-  ylim=c(0,1.1),
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user]
-)
-
-# SSB
-plot_MSE_ts_Huynh(
-  OMNames= OMNames, scenNames=scenNames_user,
-  myvarName = "SSB",
-  ylabel = expression(mean~~SSB),
-  FUN = mean,
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user]
-)
-
-# VB
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,
-myvarName = "VB",
-ylabel = expression(mean~~VB),
-FUN = mean,
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user]
-)
-
-# F
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,  
-myvarName = "FM",
-ylabel = expression(mean~~F),
-FUN = mean,
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user]
-)
-
-# Catch
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,  
-myvarName = "Catch",
-ylabel = expression(mean~~Catch),
-FUN = mean,
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user]
-)
-
-# TAC
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,  
-myvarName = "TAC",
-FUN = mean,
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user] 
-)
-
-# MSY
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,
-myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
-FUN = mean,
-ylabel="MSY",
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user]
-)
-
-# SSBMSY
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,
-myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears)]),
-FUN = mean,
-ylabel="SSBMSY",
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user]
-)
-
-# FMSY
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,
-myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)]),
-FUN = mean,
-ylabel="FMSY",
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user]
-)
-
-# UMSY
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,
-myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)])),
-FUN = mean,
-ylabel="UMSY",
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user]
+    myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+    ylabel = expression(geomean~(Catch/MSY)),
+    FUN = geomean,
+    MPNamesSub = MPNamesAll,
+    MPNamesSub_legtext=MPNamesAll_legtext,
+    rowLabs=scenNames_key[scenNames_user],
+    ylim = c(0,1)
 )
@@
 ```
+
+```{r MSEtool tradeoff plots, eval=FALSE}
+# MSEtool Tradeoff plots
+for(outName_i in MSEoutNames_user){
+out_i <- get(outName_i)  
+par(oma=c(1,1,2,1))  
+MSEtool::TradePlot(out_i)
+}
+```
+
+\clearpage
+
+# Tradeoff plots
+
+```{r manual tradeoff plots, eval=TRUE}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user,
+  # MPNamesRef = "SCA_1",
+  plot_type = "tradeoff",
+  PMx = Yield,
+  MPNamesSub = MPNamesAll,
+  MPNamesSub_legtext=MPNamesAll,
+  rowLabs=scenNames_key[scenNames_user],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,1.1),ylim=c(0,1.1),
+  hline=NA
+)
+```
+
+\clearpage
+
+```{r}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user,
+  # MPNamesRef = "SCA_1",
+  plot_type = "tradeoff",
+  PMx = PNOF,
+  #proyear_phase=20,
+  MPNamesSub = MPNamesAll,
+  MPNamesSub_legtext=MPNamesAll,
+  rowLabs=scenNames_key[scenNames_user],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,1.1),ylim=c(0,1.1),
+  hline=NA
+)
+
+```
+\clearpage
+
+```{r}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user,
+  # MPNamesRef = "SCA_1",
+  plot_type = "tradeoff",
+  PMx = AAVY10,
+  #proyear_phase=20,
+  MPNamesSub = MPNamesAll,
+  MPNamesSub_legtext=MPNamesAll,
+  rowLabs=scenNames_key[scenNames_user],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,1.1),ylim=c(0,1.1),
+  hline=NA
+)
+
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user,
+  # MPNamesRef = "SCA_1",
+  plot_type = "tradeoff",
+  PMx = AAVY10,
+  PMy = PNOF,
+  #proyear_phase=20,
+  MPNamesSub = MPNamesAll,
+  MPNamesSub_legtext=MPNamesAll,
+  rowLabs=scenNames_key[scenNames_user],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,1.1),ylim=c(0,1.1),
+  hline=NA
+)
+
+```
+
+\clearpage
+
+# Phase plots
+
+```{r phase plots}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user,
+  MPNamesRef = "SCA_1",
+  plot_type = "phase",
+  #proyear_phase=20,
+  MPNamesSub = c(MPNamesSub_user),
+  MPNamesSub_legtext=c(MPNamesSub_user_legtext),
+  rowLabs=scenNames_key[scenNames_user],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,3),ylim=c(0,3),
+  hline=NA
+)
+```

### 2022-03-07 BuildOM/2022-02-14/rdat_to_Data_input_tmp.R

@@ -1,0 +1,153 @@
+rdat=rdat_BlackSeaBass
+length_sc = length_sc
+Data = new('Data')
+herm = NULL
+nsim=48
+genus_species=NULL
+Region="Southeast US Atlantic"
+Fref_name = "Fmsy"
+Rec="bam_recruits"
+CAA_abb="all"
+CAL_abb="all"
+Ind_abb="all"
+CV_vbK=0.001
+CV_vbLinf=0.001
+CV_vbt0=0.001
+CV_Cat=NULL
+Mat_age1_max=Mat_age1_max
+length_sc=length_sc
+wla_sc=NULL
+wla_unit="lbs"
+wla_unit_mult=1000
+catch_sc=1
+
+
+# Begin function
+
+rdat <- standardize_rdat(rdat)
+
+info <- rdat$info
+parms <- rdat$parms
+parm.cons <- rdat$parm.cons
+parm.tvec <- rdat$parm.tvec
+a.series <- rdat$a.series
+t.series <- rdat$t.series
+comp.mats <- rdat$comp.mats
+styr <- parms$styr
+endyr <- parms$endyr
+
+Name <- gsub(" ","",str_to_title(info$species))
+
+# MSEtool expects age-based data to begin with age 0
+if(min(a.series$age)>0){
+  warning(paste(Name,": Minimum age > 0. Age-based data extrapolated to age-0"))
+  a.series <- data_polate(a.series,xout=0:max(a.series$age))
+  a.series <- data_lim(a.series,xlim=c(0,Inf))
+  a.series <- data_lim(a.series,xname=c("prop.female","prop.male","mat.female","mat.male"),xlim=c(0,1))
+  a.series <- as.data.frame(a.series)
+  rownames(a.series) <- a.series$age
+}
+age <- a.series$age
+
+t.series <- t.series[paste(styr:endyr),]
+
+Common_Name <- str_replace_all(Name,"(?<=[a-z])(?=[A-Z])"," ")
+if(is.null(genus_species)){genus_species <- bamStockMisc[Name,"Species"]}
+if(is.null(herm)){herm <- bamStockMisc[Name,"herm"]}
+
+B.to.klb <- local({
+  if(info$units.biomass%in%c("mt","metric tons")){
+    out <- 2.204624}else{
+      warning("units.biomass not equal to metric tons")
+    }
+  return(out)
+})
+
+catch.raw <- t.series$total.L.klb*catch_sc
[…]

### 2022-03-07 BuildOM/rdat_to_Data_input_tmp.R

@@ -1,0 +1,154 @@
+rdat = rdat_BlackSeaBass
+Data = NULL
+herm = NULL
+nsim=2
+genus_species=NULL
+Region="Southeast US Atlantic"
+Fref_name = "Fmsy"
+Rec="bam_recruits"
+CAA_abb="all"
+CAL_abb="all"
+Ind_abb="all"
+CV_vbK=0.001
+CV_vbLinf=0.001
+CV_vbt0=0.001
+CV_Cat=NULL
+Mat_age1_max = 0.49
+length_sc=0.1
+wla_sc=NULL
+wla_unit="lbs"
+wla_unit_mult=1000
+catch_sc=1
+combine_indices=FALSE
+fleet_sel_abb_key=data.frame("U"=c("sTV","rHB","rGN"),"sel"=c("sCT","rGN","rHB"))
+AddInd_order = c("sTV","sCT","sVD","sBL","sVL","sBT","sFT","rHB","rHB.D","cDV","cHL","cLL","cOT","cPT","cGN","rGN")
+
+# Begin function
+
+rdat <- standardize_rdat(rdat)
+
+info <- rdat$info
+parms <- rdat$parms
+parm.cons <- rdat$parm.cons
+parm.tvec <- rdat$parm.tvec
+a.series <- rdat$a.series
+t.series <- rdat$t.series
+comp.mats <- rdat$comp.mats
+styr <- parms$styr
+endyr <- parms$endyr
+
+Name <- gsub(" ","",str_to_title(info$species))
+
+# MSEtool expects age-based data to begin with age 0
+if(min(a.series$age)>0){
+  warning(paste(Name,": Minimum age > 0. Age-based data extrapolated to age-0"))
+  a.series <- data_polate(a.series,xout=0:max(a.series$age))
+  a.series <- data_lim(a.series,xlim=c(0,Inf))
+  a.series <- data_lim(a.series,xname=c("prop.female","prop.male","mat.female","mat.male"),xlim=c(0,1))
+  a.series <- as.data.frame(a.series)
+  rownames(a.series) <- a.series$age
+}
+age <- a.series$age
+
+t.series <- t.series[paste(styr:endyr),]
+
+Common_Name <- str_replace_all(Name,"(?<=[a-z])(?=[A-Z])"," ")
+if(is.null(genus_species)){genus_species <- bamStockMisc[Name,"Species"]}
+if(is.null(herm)){herm <- bamStockMisc[Name,"herm"]}
+
+B.to.klb <- local({
[…]

### 2022-03-07 RunMSE/HCR_MSY/fn/iMP_NK.R

@@ -1,237 +1,0 @@
-# "perfect" MP suggested by Quang Huynh to investigate deviation of HCR_MSY from MSY reference points
-MP_PerfectMSY <- make_MP(Perfect, HCR_MSY)
-
-# Averaged Index and Buffered Index MPs with (numbers indicate assessment interval)
-iMP_avg_5 <- make_interim_MP(.Assess = "SCA_Pope", .HCR = "HCR_MSY", MSY_frac = 1,
-                             assessment_interval = 5,
-                             type = "mean", type_par = 3)
-iMP_avg_10 <- make_interim_MP(SCA_Pope, .HCR = "HCR_MSY", MSY_frac = 1,
-                              assessment_interval = 10,
-                              type = "mean", type_par = 3)
-
-iMP_buffer_5 <- make_interim_MP(.Assess = "SCA_Pope", .HCR = "HCR_MSY", MSY_frac = 1,
-                                assessment_interval = 5,
-                                type = "buffer", type_par = 1)
-iMP_buffer_10 <- make_interim_MP(.Assess = "SCA_Pope", .HCR = "HCR_MSY", MSY_frac = 1,
-                                 assessment_interval = 10,
-                                 type = "buffer", type_par = 1)
-
-# Fixed TAC MPs (numbers indicate assessment interval) and annual assessment MPs
-SCA_5 <- SCA_10 <- SCA_1 <- make_MP(.Assess = "SCA_Pope", .HCR = "HCR_MSY", MSY_frac = 1,
-                                    diagnostic = "min")
-
-# # Merge batches of MSE output (modified for newer version of SAMtool by Nikolai)
-merge_MSE <- function(...) {
-  dots <- list(...)
-
-  slots_identical <- function(slotname, x = dots, is_logical = FALSE) {
-    res <- lapply(x, getElement, slotname)
-    is_identical <- all(vapply(res[-1], identical, logical(1), res[[1]]))
-    if(is_logical) {
-      return(is_identical)
-    } else return(unique(do.call(c, res)))
-  }
-
-  slots_identical("Name")
-  nyears <- slots_identical("nyears")
-  proyears <- slots_identical("proyears")
-  nsim <- slots_identical("nsim")
[…]

### 2022-03-07 RunMSE/HCR_MSY/run_script_NK_HCR_MSY.R

@@ -1,135 +1,0 @@
-library(openMSE)
-library(TMB)
-
-rm(list=ls())
-t_list <- Sys.time()
-set.seed(1358)
-
-nsim <- 48
-runScenarios <- TRUE # Run scenarios to do MSE or just generate historical data?
-runParallel <- TRUE
-ObsUser <- "Perfect_Info" # Set to NULL to avoid replacing Obs
-ImpUser <- "Perfect_Imp"  # Set to NULL to avoid replacing Imp
-
-OM_name_scen_complete <- local({
-  a <- gsub(".rds","",list.files("MSE_obj"))
-  b <- gsub("MSE","OM",a)
-  b
-})
-
-OM_name_all <- gsub(".rds","",list.files("OM"))
-OM_name <- OM_name_all#[!OM_name_all%in%OM_name_complete]
-OM_name <- c("OM_BlackSeaBass","OM_RedPorgy","OM_VermilionSnapper"
-              #,"OM_RedGrouper", "OM_GagGrouper", "OM_GrayTriggerfish"
-             )
-
-# Setup loops
-scenario <- c("base", "nr" #"hs", "hd",
-              #"lf","dep",
-              # "epiM"
-)
-
-seeds <- setNames(sample(1:10000,length(OM_name),replace = FALSE),OM_name)
-
-MSEtool::setup(12) # Run in parallel over 12 cores
-
-for(OM_name_k in OM_name) { ######### Loop over operating model
-  source('fn/iMP_NK.R')
-
-  MSE_name_k <- gsub("OM","MSE",OM_name_k)
-
-  myOM_init <- readRDS(paste0("OM/", OM_name_k, ".rds"))
-
-  if(runScenarios){
-    for(scenario_i in scenario) { ######### Loop over scenario
-      # All scenarios
-      OM_name_scen <- paste0(OM_name_k, "_", scenario_i)
-      if(!OM_name_scen%in%OM_name_scen_complete){
-      myOM <- myOM_init
-      myOM <- SubCpars(myOM, sims = 1:nsim) # Limit number of simulations
-      if(!is.null(ObsUser)) myOM <- Replace(myOM, get(ObsUser))
-      if(!is.null(ImpUser)) myOM <- Replace(myOM, get(ImpUser))
-
-      # No recruitment process error scenario
-      if(scenario_i == "nr") {
-        myOM@cpars$Perr_y[] <- 1
-      }
-
-      # Hyperstable scenario
[…]

### 2022-03-07 RunMSE/RunMSE_SCAconvIssue/Huynh_plots_args_temp.R

@@ -1,32 +1,0 @@
-myvarName = "Catch"
-myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears),drop=FALSE])
-ylabel = expression(mean~~Catch/MSY)
-FUN = mean_noNA
-scenNames=scenNames_user
-OMNames= OMNames
-MPNamesSub = MPNamesSub_user
-MPNamesSub_legtext=MPNamesSub_user_legtext
-legtext_o = 1 # order for plotting legend text
-MSEoutNames = gsub("OM","MSE",OMNames)
-colLabs = str_replace_all(gsub("OM_","",OMNames),"(?<=[a-z])(?=[A-Z])"," ")
-rowLabs=scenNames_key[scenNames_user]
-
-mar=c(1,1,1,1)
-cols = setNames(c("red","black","deepskyblue2","deepskyblue2"),MPNamesSub)
-ltys = setNames(c(1,1,1,2),MPNamesSub)
-lwds = setNames(c(3,3,3,3),MPNamesSub)
-types = setNames(c("l","l","l","l"),MPNamesSub)
-xlabel = "Management year"
-xlim = NULL
-ylim=c(0,2)
-assessmentYears = seq(10,40,by=10)
-x.at = NULL
-y.at = NULL
-# leg.x=NULL
-# leg.y =NULL
-legend_panel=NULL
-legend_cex= 1
-legend_x="bottomleft"
-legend_inset=c(0,-0.6)
-label_axes="all" # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
-hline=1 # values to pass into abline(h=hline)

### 2022-03-07 RunMSE/RunMSE_SCAconvIssue/Project_NK.R

@@ -1,553 +1,0 @@
-Project_NK <- function (Hist = NULL, MPs = NA, parallel = FALSE, silent = FALSE, 
-                        extended = FALSE, checkMPs = TRUE) 
-{
-  popdynOneTScpp <- MSEtool:::popdynOneTScpp
-  calcRecruitment <- MSEtool:::calcRecruitment
-  tiny <- MSEtool:::tiny
-  CalcMPDynamics <- MSEtool:::CalcMPDynamics
-  updateData <- MSEtool:::updateData
-  CheckMPs <- MSEtool:::CheckMPs
-  # readline("press any key to continue")
-  if (class(Hist) != "Hist") 
-    stop("Must provide an object of class `Hist`")
-  OM <- Hist@OM
-  set.seed(OM@seed)
-  nsim <- OM@nsim
-  nyears <- OM@nyears
-  proyears <- OM@proyears
-  interval <- OM@interval
-  maxF <- OM@maxF
-  pstar <- OM@pstar
-  reps <- OM@reps
-  control <- OM@cpars$control
-  OM@cpars$control <- NULL
-  if (checkMPs) 
-    MPs <- CheckMPs(MPs = MPs, silent = silent)
-  nMP <- length(MPs)
-  if (nMP < 1) 
-    stop("No valid MPs found", call. = FALSE)
-  isrunning <- snowfall::sfIsRunning()
-  if (!parallel & isrunning) 
-    snowfall::sfStop()
-  if (parallel) {
-    if (!isrunning) 
-      setup()
-    Export_customMPs(MPs)
-  }
-  if (length(interval) != nMP) 
-    interval <- rep(interval, nMP)[1:nMP]
-  if (!all(interval == interval[1])) {
-    if (!silent) 
-      message("Variable management intervals:")
-    df <- data.frame(MP = MPs, interval = interval)
-    for (i in 1:nrow(df)) {
-      message(df$MP[i], "has management interval:", df$interval[i])
-    }
-  }
-  MSY_y <- Hist@Ref$ByYear$MSY
-  FMSY_y <- Hist@Ref$ByYear$FMSY
-  SSBMSY_y <- Hist@Ref$ByYear$SSBMSY
-  BMSY_y <- Hist@Ref$ByYear$BMSY
-  VBMSY_y <- Hist@Ref$ByYear$VBMSY
-  F01_YPR_y <- Hist@Ref$ByYear$F01_YPR
[…]

### 2022-03-07 RunMSE/RunMSE_SCAconvIssue/SCA_NK.R

@@ -1,584 +1,0 @@
-SCA_NK <- function (x = 1, Data, AddInd = "B", SR = c("BH", "Ricker", 
-                                            "none"), vulnerability = c("logistic", "dome"), catch_eq = c("Baranov", 
-                                                                                                         "Pope"), comp = c("age", "length"), comp_dist = c("multinomial", 
-                                                                                                                                                           "lognormal"), comp_multiplier = c(50, 50), rescale = "mean1", 
-          max_age = Data@MaxAge, start = NULL, prior = list(), fix_h = TRUE, 
-          fix_F_equilibrium = TRUE, fix_omega = TRUE, fix_tau = TRUE, 
-          tv_M = c("none", "walk", "DD"), M_bounds = NULL, refyear = 1, 
-          LWT = list(), early_dev = c("comp_onegen", "comp", "all"), 
-          late_dev = "comp50", integrate = FALSE, silent = TRUE, opt_hess = FALSE, 
-          n_restart = ifelse(opt_hess, 0, 1), control = list(iter.max = 2e+05, 
-                                                             eval.max = 4e+05), inner.control = list(), ...) 
-{
-  print("running SCA_NK")
-  Assess_I_hist <- SAMtool:::Assess_I_hist
-  make_prior <- SAMtool:::make_prior
-  tiny_comp <- SAMtool:::tiny_comp
-  logit <- SAMtool:::logit
-  optimize_TMB_model <- SAMtool:::optimize_TMB_model
-  SCA_dynamic_SSB0 <- SAMtool:::SCA_dynamic_SSB0
-  ref_pt_SCA <- SAMtool:::ref_pt_SCA
-
-  dependencies <- "Data@Cat, Data@Ind, Data@Mort, Data@L50, Data@L95, Data@CAA, Data@vbK, Data@vbLinf, Data@vbt0, Data@wla, Data@wlb, Data@MaxAge"
-  dots <- list(...)
-  start <- lapply(start, eval, envir = environment())
-  max_age <- as.integer(min(max_age, Data@MaxAge))
-  n_age <- max_age + 1
-  vulnerability <- match.arg(vulnerability)
-  catch_eq <- match.arg(catch_eq)
-  comp <- match.arg(comp, several.ok = TRUE)
[…]

### 2022-03-07 RunMSE/RunMSE_SCAconvIssue/SCA_Pope_NK.R

@@ -1,22 +1,0 @@
-SCA_Pope_NK <- function (x = 1, Data, AddInd = "B", SR = c("BH", "Ricker", 
-                                            "none"), vulnerability = c("logistic", "dome"), CAA_dist = c("multinomial", 
-                                                                                                         "lognormal"), CAA_multiplier = 50, rescale = "mean1", max_age = Data@MaxAge, 
-          start = NULL, prior = list(), fix_h = TRUE, fix_U_equilibrium = TRUE, 
-          fix_tau = TRUE, LWT = list(), early_dev = c("comp_onegen", 
-                                                      "comp", "all"), late_dev = "comp50", integrate = FALSE, 
-          silent = TRUE, opt_hess = FALSE, n_restart = ifelse(opt_hess, 
-                                                              0, 1), control = list(iter.max = 2e+05, eval.max = 4e+05), 
-          inner.control = list(), ...) 
-{
-  print("running SCA_Pope_NK")
-  out <- SCA_NK(x = x, Data = Data, AddInd = AddInd, SR = SR, 
-              vulnerability = vulnerability, catch_eq = "Pope", comp = "age", 
-              comp_dist = CAA_dist, comp_multiplier = CAA_multiplier, 
-              rescale = rescale, max_age = max_age, start = start, 
-              prior = prior, fix_h = fix_h, fix_F_equilibrium = fix_U_equilibrium, 
-              fix_omega = TRUE, fix_tau, LWT = LWT, early_dev = early_dev, 
-              late_dev = late_dev, integrate = integrate, silent = silent, 
-              opt_hess = opt_hess, n_restart = n_restart, control = control, 
-              inner.control = inner.control, ...)
-  return(out)
-}

### 2022-03-07 RunMSE/RunMSE_SCAconvIssue/applyMP_NK.R

@@ -1,95 +1,0 @@
-applyMP_NK <- function (Data, MPs = NA, reps = 100, nsims = NA, silent = FALSE) 
-{
-  print("applyMP_NK: running applyMP_NK")
-  if (class(Data) != "Data") 
-    stop("First argument must be object of class 'Data'", 
-         call. = FALSE)
-  Dataout <- Data
-  if (is.na(nsims)) 
-    nsims <- nrow(Data@Cat)
-  nMPs <- length(MPs)
-  if (.hasSlot(Data, "nareas")) {
-    nareas <- Data@nareas
-  }
-  else {
-    nareas <- 2
-  }
-  returnList <- list()
-  recList <- list()
-  TACout <- array(NA, dim = c(nMPs, reps, nsims))
-  refMPs <- c("FMSYref", "FMSYref50", "FMSYref75", "NFref")
-  runParallel <- snowfall::sfIsRunning()
-  if (!silent) 
-    message("Attempting to run ", length(MPs), " MPs:")
-  for (mp in 1:nMPs) {
-    if (!silent) 
-      message(MPs[mp])
-    mp_ns <- find(MPs[mp])
-    dlmmp <- grepl("DLMtool", mp_ns)
-    if (length(dlmmp) < 1) 
-      dlmmp <- FALSE
-    msemmp <- grepl("MSEtool", mp_ns)
-    if (length(msemmp) < 1) 
-      msemmp <- FALSE
-    if (MPs[mp] %in% c("LBSPR", "LBSPR_MLL")) 
-      dlmmp <- FALSE
-    if (dlmmp | msemmp) 
-      runParallel <- FALSE
-    print("applyMP_NK: Made it here")
-    if (runParallel) {
-      temp <- try(snowfall::sfLapply(1:nsims, MPs[mp], 
-                                     Data = Data, reps = reps), silent = TRUE)
-    }
-    else {
-      temp <- try(lapply(1:nsims, MPs[mp], Data = Data, 
-                         reps = reps), silent = TRUE)
-    }
-    mytemp <<-temp
-    myrecList <<- recList
-    mynsims <<- nsims
-    myDataout <<- Dataout
-    mynareas <<- nareas
-    myTACout<<-TACout
-    if (class(temp) == "try-error") {
-      warning("Method ", MPs[mp], " failed with error: ", 
-              temp)
-    }
-    else {
-      slots <- slotNames(temp[[1]])
-      for (X in slots) {
[…]

### 2022-03-07 RunMSE/RunMSE_SCAconvIssue/iMP_avg_10_NK.R

@@ -1,98 +1,0 @@
-iMP_avg_10_NK <- function (x = 1, Data, reps = 1, assessment_interval = 10, AddInd = "VB", 
-          type = "mean", type_par = 3, diagnostic = "min") 
-{
-  dependencies <- "Data@Cat, Data@Ind, Data@Mort, Data@L50, Data@L95, Data@CAA, Data@vbK, Data@vbLinf, Data@vbt0, Data@wla, Data@wlb, Data@MaxAge, Data@steep, Data@CV_Ind, Data@sigmaR, Data@CV_Cat, Data@Mort, Data@CV_Mort, Data@steep, Data@CV_steep, Data@vbLinf, Data@vbK, Data@vbt0, Data@wla, Data@wlb, Data@MaxAge, Data@L50, Data@L95"
-  interim_get_index <- SAMtool:::interim_get_index
-  Assess_diagnostic <- SAMtool:::Assess_diagnostic
-  
-  
-  ny <- length(Data@Year)
-  Current_Yr <- Data@Year[ny]
-  first_assess_yr <- Current_Yr == Data@LHYear
-  run_assessment <- first_assess_yr || Current_Yr == Data@Misc[[x]]$interim$next_assess_yr
-  run_interim <- !run_assessment
-  print(paste("iMP_avg_10_NK: Current_Yr=",Current_Yr))
-  print(paste("iMP_avg_10_NK: run_assessment=",run_assessment))
-  if (run_assessment) {
-    do_Assessment <- SCA_Pope_NK(x = x, Data = Data, AddInd = "VB")
-    if (diagnostic != "none") {
-      Assess_diag_output <- Assess_diagnostic(x, Data, 
-                                              do_Assessment, include_assessment = FALSE)
-    }
-    if (do_Assessment@conv) {
-      Rec <- HCR_MSY(Assessment = do_Assessment, reps = reps, 
-                     MSY_frac = 1)
-      if (diagnostic != "none") 
-        Rec@Misc$diagnostic <- Assess_diag_output$diagnostic
-      if (!is.null(do_Assessment@info$Misc)) 
-        Rec@Misc <- c(Rec@Misc, do_Assessment@info$Misc)
-      Rec@Misc$interim <- list(Cref = Rec@TAC, Iref = do_Assessment@Index[ny, 
-                                                                          1], next_assess_yr = Current_Yr + assessment_interval)
-      if (type == "buffer") {
-        Rec@Misc$interim$s <- log(do_Assessment@Obs_Index[, 
[…]

### 2022-03-07 RunMSE/RunMSE_SCAconvIssue/runMSE_NK.R

@@ -1,42 +1,0 @@
-runMSE_NK <- function (OM = MSEtool::testOM, MPs = NA, Hist = FALSE, silent = FALSE,
-                       parallel = FALSE, extended = FALSE, checkMPs = TRUE)
-{
-  CheckMPs <- MSEtool:::CheckMPs
-  if (class(OM) == "OM") {
-    if (OM@nsim <= 1)
-      stop("OM@nsim must be > 1", call. = FALSE)
-  }
-  else if (class(OM) == "Hist") {
-    if (!silent)
-      message("Using `Hist` object to reproduce historical dynamics")
-  }
-  else {
-    stop("You must specify an operating model")
-  }
-  if (checkMPs & !Hist)
-    MPs <- CheckMPs(MPs = MPs, silent = silent)
-  if (class(OM) == "OM") {
-    HistSims <- Simulate(OM, parallel, silent)
-  }
-  else {
-    HistSims <- OM
-  }
-  if (Hist) {
-    if (!silent)
-      message("Returning historical simulations")
-    return(HistSims)
-  }
-  myHistSims <<- HistSims
-  if (!silent)
-    message("Running forward projections")
-  MSEout <- try(Project_NK(Hist = HistSims, MPs, parallel, silent,
-                        extended = extended, checkMPs = FALSE), silent = TRUE)
-  if (class(MSEout) == "try-error") {
-    message("The following error occured when running the forward projections: ",
-            crayon::red(attributes(MSEout)$condition))
-    message("Returning the historical simulations (class `Hist`). To avoid re-running spool up, ",
-            "the forward projections can be run with ", "`runMSE(Hist, MPs, ...)`")
-    return(HistSims)
-  }
-  MSEout
-}

### 2022-03-07 RunMSE/RunMSE_SCAconvIssue/run_script_MSEfails.R

@@ -1,61 +1,0 @@
-library(openMSE)
-library(TMB)
-
-rm(list=ls())
-t_list <- Sys.time()
-set.seed(1358)
-
-nsim <- 48
-runParallel <- TRUE
-ObsUser <- "Perfect_Info" # Set to NULL to avoid replacing Obs
-ImpUser <- "Perfect_Imp"  # Set to NULL to avoid replacing Imp
-
-OM_name <- "OM_RedGrouper"
-
-# Setup loops
-scenario <- "base"
-
-seeds <- setNames(sample(1:10000,length(OM_name),replace = FALSE),OM_name)
-
-MSEtool::setup(12) # Run in parallel over 12 cores
-
-iMP_avg_10 <- make_interim_MP(SCA_Pope, .HCR = "HCR_MSY", MSY_frac = 1,
-                              assessment_interval = 10,
-                              type = "mean", type_par = 3)
-
-for(OM_name_k in OM_name) { ######### Loop over operating model
-  MSE_name_k <- gsub("OM","MSE",OM_name_k)
-
-  myOM_init <- readRDS(paste0(OM_name_k, ".rds"))
-
-
-    for(scenario_i in scenario) { ######### Loop over scenario
-      # All scenarios
-      OM_name_scen <- paste0(OM_name_k, "_", scenario_i)
-      myOM <- myOM_init
-      myOM <- SubCpars(myOM, sims = 1:nsim) # Limit number of simulations
-      if(!is.null(ObsUser)) myOM <- Replace(myOM, get(ObsUser))
-      if(!is.null(ImpUser)) myOM <- Replace(myOM, get(ImpUser))
-
-      # # Save OM to object
-      OM_name_ki <- paste0(OM_name_k, "_", scenario_i)
-
-      ######## Fixed TAC MPs and Averaged Index MPs
-      myOM@interval <- 1
-
-      message(paste("Fixed TAC and Averaged MPs for:", OM_name_ki))
-      t_list <- c(t_list,Sys.time())
-      message(paste0("at: ",tail(t_list,1),".(",round(diff(tail(t_list,2)),2)," since start)"))
-
-      MSE_batch_1 <- runMSE(myOM, MPs = "iMP_avg_10", parallel = TRUE)
-      message(paste0("batch 1 finished at ",tail(t_list,1),".(",round(diff(tail(t_list,2)),2)," duration"))
-
-      ######## Merge MSE and save output
[…]

### 2022-03-07 RunMSE/RunMSE_SCAconvIssue/tmpCrap.R

@@ -1,45 +1,0 @@
-myvarName = "SB_SBMSY"
-myvarDenomExpr = NULL
-ylabel = myvarName
-FUN = mean_noNA
-OMNames=OMNames_user
-scenNames=scenNames_user
-# MSEoutNames = gsub("OM","MSE",OMNames)
-MPNamesSub = c("SCA_10","SCA_1","iMP_avg_10","iMP_buffer_10")
-MPNamesSub_legtext=MPNamesSub
-legtext_o = c(2,3,4,1) # order for plotting legend text
-MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
-                     "_",
-                     rep(scenNames,length(OMNames))
-)
-colLabs = NULL
-rowLabs = scenNames
-
-mar=c(1,1,1,1)
-cols = setNames(c("red","black","deepskyblue2","deepskyblue2"),MPNamesSub)
-ltys = setNames(c(1,1,1,2),MPNamesSub)
-lwds = setNames(c(3,3,3,3),MPNamesSub)
-types = setNames(c("l","l","l","l"),MPNamesSub)
-xlabel = "Management year"
-xlim = NULL
-ylim = NULL
-assessmentYears = seq(10,40,by=10)
-x.at = NULL
-y.at = NULL
-# leg.x=NULL
-# leg.y =NULL
-legend_panel=NULL
-legend_cex= 1
-legend_x="bottomleft"
-legend_inset=c(0,-0.2)
-label_axes="all" # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
-hline=1 # values to pass into abline(h=hline)
-
-
-
-ylabel = expression(mean~~SSB/SSBmsy)
-FUN = mean
-ylim=c(0,2)
-MPNamesSub = MPNamesSub_user
-MPNamesSub_legtext=MPNamesSub_user_legtext
-rowLabs=scenNames_key[scenNames_user]

### 2022-03-07 RunMSE/SEFSC/fn/MP_wrapper.R

@@ -1,0 +1,29 @@
+# Script copied 2022-02-25 from: https://github.com/Blue-Matter/WSKJ/blob/master/03a_MPs.R#L6
+# Author: Quang Huynh
+
+# MP wrapper that puts the BB fleet in Data@Ind
+MP_wrapper <- function(MP, delay = 2, ...) {
+  MP <- substitute(MP)
+  MP_call <- as.call(c(MP, x = quote(x), Data = quote(Data), reps = quote(reps), list(...)))
+  force(delay)
+
+  MP_body <- bquote({
+    Data@Ind <- Data@AddInd[, 1, ]
+    Data@CV_Ind <- Data@CV_AddInd[, 1, ]
+    if(delay > 0) {
+      delay_ind <- seq(ncol(Data@Cat) - delay + 1, ncol(Data@Cat), 1)
+      Data@Ind <- Data@Ind[, -delay_ind]
+      Data@CV_Ind <- Data@CV_Ind[, -delay_ind]
+      Data@Cat <- Data@Cat[, -delay_ind, drop = FALSE]
+      Data@CV_Cat <- Data@CV_Cat[, -delay_ind, drop = FALSE]
+      Data@Year <- Data@Year[-delay_ind]
+    }
+    Rec <- .(MP_call)
+    return(Rec)
+  })
+
+  MP_out <- eval(call("function", as.pairlist(alist(x = 1, Data = , reps = 1)), MP_body))
+  class(MP_out) <- "MP"
+  return(MP_out)
+}
+

### 2022-03-07 RunMSE/SEFSC/fn/MP_wrapper_development.R

@@ -1,0 +1,48 @@
+
+MP=SCA; lag = 2; Data <- rdat_to_Data(rdat_BlackSeaBass)
+
+# MP wrapper that puts the BB fleet in Data@Ind
+MP_wrapper <- function(MP, lag = 2, ...) {
+  MP <- substitute(MP)
+  MP_call <- as.call(c(MP, x = quote(x), Data = quote(Data), reps = quote(reps), list(...)
+                       )
+                     )
+  force(lag)
+
+  MP_body <- bquote({
+    Data@Ind <- Data@AddInd[, 1, ]
+    Data@CV_Ind <- Data@CV_AddInd[, 1, ]
+    if(lag > 0) {
+      lag_ind <- seq(ncol(Data@Cat) - lag + 1, ncol(Data@Cat), 1)
+      Data@Ind <- Data@Ind[, -lag_ind]
+      Data@CV_Ind <- Data@CV_Ind[, -lag_ind]
+      Data@Cat <- Data@Cat[, -lag_ind, drop = FALSE]
+      Data@CV_Cat <- Data@CV_Cat[, -lag_ind, drop = FALSE]
+      Data@Year <- Data@Year[-lag_ind]
+    }
+    Rec <- .(MP_call)
+    return(Rec)
+  })
+
+  MP_out <- eval(call("function", as.pairlist(alist(x = 1, Data = , reps = 1)), MP_body))
+  class(MP_out) <- "MP"
+  return(MP_out)
+}
+
+MP_wrapper2 <- function(MP, lag = 3, ...) {
+  MP <- substitute(MP)
+  MP_call <- as.call(c(MP, x = quote(x), Data = quote(Data), reps = quote(reps), list(...)
+  )
+  )
+  force(lag)
+
+  MP_body <- bquote({
+    Data <- Data_sub_dim(Data,nyr_rm=lag)
+    Rec <- .(MP_call)
+    return(Rec)
+  })
+
+  MP_out <- eval(call("function", as.pairlist(alist(x = 1, Data = , reps = 1)), MP_body))
+  class(MP_out) <- "MP"
+  return(MP_out)
+}

### 2022-03-07 RunMSE/SEFSC/fn/SCA_lag.R

@@ -1,0 +1,29 @@
+SCA_lag <- function (x = 1, Data, lag=0,
+                     AddInd = "B", SR = c("BH", "Ricker", "none"),
+                     vulnerability = c("logistic", "dome"),
+                     catch_eq = c("Baranov", "Pope"),
+                     CAA_dist = c("multinomial", "lognormal"), CAA_multiplier = 50,
+                     rescale = "mean1", max_age = Data@MaxAge, start = NULL,
+                     prior = list(), fix_h = TRUE, fix_F_equilibrium = TRUE,
+                     fix_omega = TRUE, fix_tau = TRUE, LWT = list(),
+                     early_dev = c("comp_onegen","comp", "all"), late_dev = "comp50",
+                     integrate = FALSE, silent = TRUE, opt_hess = FALSE,
+                     n_restart = ifelse(opt_hess, 0, 1),
+                     control = list(iter.max = 2e+05, eval.max = 4e+05),
+                     inner.control = list(), ...)
+{
+  
+  Data <- bamExtras::Data_sub_dim(Data,nyr_rm=lag) # Trim temporally explicit slots based on lag
+  
+  out <- SAMtool:::SCA_(x = x, Data = Data, AddInd = AddInd, SR = SR,
+                        vulnerability = vulnerability, catch_eq = catch_eq,
+                        comp = "age", comp_dist = CAA_dist, comp_multiplier = CAA_multiplier,
+                        rescale = rescale, max_age = max_age, start = start,
+                        prior = prior, fix_h = fix_h, fix_F_equilibrium = fix_F_equilibrium,
+                        fix_omega = fix_omega, fix_tau = fix_tau, LWT = LWT,
+                        early_dev = early_dev, late_dev = late_dev, integrate = integrate,
+                        silent = silent, opt_hess = opt_hess, n_restart = n_restart,
+                        control = control, inner.control = inner.control, ...)
+  return(out)
+}
+class(SCA_lag) <- "Assess"

### 2022-03-07 RunMSE/SEFSC/fn/iMP.R

@@ -1,0 +1,38 @@
+# Define custom stock assessment function
+MP_args <- list(.Assess = "SCA_lag", .HCR = "HCR_MSY", MSY_frac = 1, AddInd = 1)
+BAM_SCA_args <- list(SR="BH",
+                     vulnerability = "logistic",
+                     early_dev = "comp_onegen",
+                     late_dev = "comp50",
+                     CAA_dist = "multinomial",
+                     lag=lag)
+
+# Averaged Index and Buffered Index MPs with (numbers indicate assessment interval)
+iMP_avg_5 <- do.call(make_interim_MP_lag,
+                     c(list(assessment_interval = 5,type = "mean", type_par = 3),
+                       MP_args, BAM_SCA_args)
+                     )
+
+iMP_avg_10 <- do.call(make_interim_MP_lag,
+                      c(list(assessment_interval = 10,type = "mean", type_par = 3),
+                        MP_args, BAM_SCA_args)
+                      )
+
+iMP_buffer_5 <-  do.call(make_interim_MP_lag,
+                         c(list(assessment_interval = 5, type = "buffer", type_par = 1),
+                           MP_args, BAM_SCA_args)
+                         )
+
+iMP_buffer_10 <-  do.call(make_interim_MP_lag,
+                           c(list(assessment_interval = 10, type = "buffer", type_par = 1),
+                             MP_args, BAM_SCA_args)
+)
+
+# Fixed TAC MPs (numbers indicate assessment interval) and annual assessment MPs
+SCA_5 <- SCA_10 <- SCA_1 <- do.call(make_MP,
+                                    c(list(diagnostic = "min"),
+                                      MP_args, BAM_SCA_args)
+                                    )
+# Projection MPs
+# pMP_5 <- make_projection_MP(assessment_interval = 5)
+# pMP_10 <- make_projection_MP(assessment_interval = 10)

### 2022-03-07 RunMSE/SEFSC/fn/iMP_NK.R

@@ -1,234 +1,0 @@
-# Averaged Index and Buffered Index MPs with (numbers indicate assessment interval)
-iMP_avg_5 <- make_interim_MP(.Assess = "SCA_Pope", .HCR = "HCR_MSY", MSY_frac = 1,
-                             assessment_interval = 5,
-                             type = "mean", type_par = 3)
-iMP_avg_10 <- make_interim_MP(SCA_Pope, .HCR = "HCR_MSY", MSY_frac = 1,
-                              assessment_interval = 10,
-                              type = "mean", type_par = 3)
-
-iMP_buffer_5 <- make_interim_MP(.Assess = "SCA_Pope", .HCR = "HCR_MSY", MSY_frac = 1,
-                                assessment_interval = 5,
-                                type = "buffer", type_par = 1)
-iMP_buffer_10 <- make_interim_MP(.Assess = "SCA_Pope", .HCR = "HCR_MSY", MSY_frac = 1,
-                                 assessment_interval = 10,
-                                 type = "buffer", type_par = 1)
-
-# Fixed TAC MPs (numbers indicate assessment interval) and annual assessment MPs
-SCA_5 <- SCA_10 <- SCA_1 <- make_MP(.Assess = "SCA_Pope", .HCR = "HCR_MSY", MSY_frac = 1,
-                                    diagnostic = "min")
-
-# # Merge batches of MSE output (modified for newer version of SAMtool by Nikolai)
-merge_MSE <- function(...) {
-  dots <- list(...)
-
-  slots_identical <- function(slotname, x = dots, is_logical = FALSE) {
-    res <- lapply(x, getElement, slotname)
-    is_identical <- all(vapply(res[-1], identical, logical(1), res[[1]]))
-    if(is_logical) {
-      return(is_identical)
-    } else return(unique(do.call(c, res)))
-  }
-
-  slots_identical("Name")
-  nyears <- slots_identical("nyears")
-  proyears <- slots_identical("proyears")
-  nsim <- slots_identical("nsim")
-  nallyears <- nyears+proyears
-
-  stopifnot(slots_identical("OM", is_logical = TRUE))
-  stopifnot(slots_identical("Obs", is_logical = TRUE))
[…]

### 2022-03-07 RunMSE/SEFSC/fn/iMP_addind.R

@@ -1,0 +1,37 @@
+# Redefine MPs to use all additional indices in stock assessments
+
+# Define custom stock assessment function
+BAM_SCA_args <- list(SR="BH",
+                     vulnerability = "logistic",
+                     early_dev = "comp_onegen",
+                     late_dev = "comp50",
+                     CAA_dist = "multinomial",
+                     AddInd = AddInd_colnums,
+                     lag=2)
+
+# Averaged Index and Buffered Index MPs with (numbers indicate assessment interval)
+iMP_avg_5 <- do.call(make_interim_MP_lag,
+                     c(list(assessment_interval = 5,type = "mean", type_par = 3),
+                       MP_args, BAM_SCA_args)
+                     )
+
+iMP_avg_10 <- do.call(make_interim_MP_lag,
+                      c(list(assessment_interval = 10,type = "mean", type_par = 3),
+                        MP_args, BAM_SCA_args)
+                      )
+
+iMP_buffer_5 <-  do.call(make_interim_MP_lag,
+                         c(list(assessment_interval = 5, type = "buffer", type_par = 1),
+                           MP_args, BAM_SCA_args)
+                         )
+
+iMP_buffer_10 <-  do.call(make_interim_MP_lag,
+                           c(list(assessment_interval = 10, type = "buffer", type_par = 1),
+                             MP_args, BAM_SCA_args)
+)
+
+# Fixed TAC MPs (numbers indicate assessment interval) and annual assessment MPs
+SCA_5 <- SCA_10 <- SCA_1 <- do.call(make_MP,
+                                    c(list(diagnostic = "min"),
+                                      MP_args, BAM_SCA_args)
+                                    )

### 2022-03-07 RunMSE/SEFSC/fn/make_interim_MP_lag.R

@@ -1,0 +1,158 @@
+
+
+
+make_interim_MP_lag <- function (.Assess = "SCA",
+                                 .HCR = "HCR_MSY",
+                                 AddInd = "VB",
+                                 assessment_interval = 5,
+                                 type = c("buffer", "mean", "loess", "none"),
+                                 type_par = NULL,
+                                 diagnostic = c("min", "full","none"),
+                                 ...)
+{
+  type <- match.arg(type)
+  diagnostic <- match.arg(diagnostic)
+  if (is.character(.Assess)) {
+    Assess_char <- .Assess
+    .Assess <- as.symbol(.Assess)
+  }
+  else {
+    .Assess <- substitute(.Assess)
+    Assess_char <- as.character(.Assess)
+  }
+  if (is.character(.HCR)) {
+    .HCR <- as.symbol(.HCR)
+  }
+  else {
+    .HCR <- substitute(.HCR)
+  }
+  if (!inherits(eval(.Assess), "Assess")) {
+    stop(paste(.Assess, "does not belong to class 'Assess'. Use: avail('Assess') to find eligible objects."))
+  }
+  if (!inherits(eval(.HCR), "HCR")) {
+    stop(paste(.HCR, "does not belong to class 'HCR.' Use: avail('HCR') to find eligible objects."))
+  }
+  dots <- list(...)
+  dots$AddInd <- AddInd
+
+  if(!is.null(dots$lag)){
+    lag <- dots$lag
+  }else{
+    lag <- 0
+  }
+
+  dots_in_Assess <- dots[match(names(formals(eval(.Assess))),
+                               names(dots), nomatch = 0)]
+  dots_in_HCR <- dots[match(names(formals(eval(.HCR))), names(dots),
+                            nomatch = 0)]
+  Assess_call <- as.call(c(.Assess, x = quote(x), Data = quote(Data),
+                           dots_in_Assess))
+  HCR_call <- as.call(c(.HCR, Assessment = quote(do_Assessment),
+                        reps = quote(reps), dots_in_HCR))
+  MP_body <- bquote({
+    dependencies <- .(SAMtool:::get_dependencies(Assess_char, dots))
+    ny <- length(Data@Year)      # Number of years in available Data object
+    ny_Assess <- ny- .(lag)           # Number of year of Data available for assessment
+    Current_Yr <- Data@Year[ny]  # Current year
[…]

### 2022-03-07 RunMSE/SEFSC/fn/make_projection_MP.R

@@ -1,0 +1,10 @@
+# Author: Quang Huynh
+
+make_projection_MP <- function(...) {
+  fn <- projection_MP
+  dots <- list(...)
+  arg_ind <- pmatch(names(dots), names(formals(fn)))
+  formals(fn)[arg_ind] <- dots
+  class(fn) <- "MP"
+  return(fn)
+}

### 2022-03-07 RunMSE/SEFSC/fn/make_projection_MP_NK.R

@@ -1,0 +1,143 @@
+# Author: Quang Huynh
+# Modified and totally wrecked: Nikolai Klibansky
+# I was trying to modify this code to make it usable with the current version of openMSE, but there are some settings
+# I don't readily understand and Quang says he can probably code it up pretty quickly. So I'm giving up
+
+
+make_projection_MP <- function (.Assess = "SCA",
+                                .HCR = "HCR_MSY",
+                                AddInd = 1,
+                                assessment_interval = 5,
+                                diagnostic = c("min", "full","none"),
+                                ...) {
+  diagnostic <- match.arg(diagnostic)
+  if (is.character(.Assess)) {
+    Assess_char <- .Assess
+    .Assess <- as.symbol(.Assess)
+  }
+  else {
+    .Assess <- substitute(.Assess)
+    Assess_char <- as.character(.Assess)
+  }
+  if (is.character(.HCR)) {
+    .HCR <- as.symbol(.HCR)
+  }
+  else {
+    .HCR <- substitute(.HCR)
+  }
+  if (!inherits(eval(.Assess), "Assess")) {
+    stop(paste(.Assess, "does not belong to class 'Assess'. Use: avail('Assess') to find eligible objects."))
+  }
+  if (!inherits(eval(.HCR), "HCR")) {
+    stop(paste(.HCR, "does not belong to class 'HCR.' Use: avail('HCR') to find eligible objects."))
+  }
+  dots <- list(...)
+  dots$AddInd <- AddInd
+
+  if(!is.null(dots$lag)){
+    lag <- dots$lag
+  }else{
+    lag <- 0
+  }
+
+  dots_in_Assess <- dots[match(names(formals(eval(.Assess))),
+                               names(dots), nomatch = 0)]
+  dots_in_HCR <- dots[match(names(formals(eval(.HCR))), names(dots),
+                            nomatch = 0)]
+  Assess_call <- as.call(c(.Assess, x = quote(x), Data = quote(Data),
+                           dots_in_Assess))
+  HCR_call <- as.call(c(.HCR, Assessment = quote(do_Assessment),
+                        reps = quote(reps), dots_in_HCR))
+  MP_body <- bquote({
+    dependencies <- .(SAMtool:::get_dependencies(Assess_char, dots))
+    ny <- length(Data@Year)      # Number of years in available Data object
[…]

### 2022-03-07 RunMSE/SEFSC/fn/projection_MP.R

@@ -1,0 +1,61 @@
+# Author: Quang Huynh
+
+projection_MP <- eval(bquote(function(x, Data, reps = 1, assessment_interval, HCR = HCR_MSY, SCA_arg = list(I_type = "VB", CAA_multiplier = 20)) {
+  dependencies <- .(SAMtool:::get_dependencies("SCA_Pope"))
+
+  current_yr <- Data@Year[length(Data@Year)]
+  run_SCA <- current_yr == Data@LHYear
+  if (current_yr > Data@LHYear) {
+    run_SCA <- current_yr == Data@Misc[[x]]$next_assess_yr
+  }
+  if (!run_SCA) get_projected_TAC <- TRUE else get_projected_TAC <- FALSE
+
+  if (run_SCA) {
+    # Return TAC = UMSY * VB_current when run_SCA = TRUE
+    SCA_formals <- list(x = x, Data = Data)
+    do_Assessment <- do.call(SCA_Pope, c(SCA_formals, SCA_arg))
+    Assess_output <- Assess_diagnostic(x, Data, do_Assessment, include_assessment = FALSE)
+
+    if (do_Assessment@conv) {
+      Rec <- do.call(match.fun(HCR), list(Assessment = do_Assessment, reps = reps))
+      pro <- projection(do_Assessment, FMort = do_Assessment@UMSY, p_years = 52, p_sim = 1, obs_error = c(0, 0), process_error = 0)
+      Rec@Misc <- c(list(project_catch = pro@Catch[1, ], last_assess_yr = current_yr, next_assess_yr = current_yr + assessment_interval), Assess_output)
+
+      get_projected_TAC <- FALSE
+
+    } else {
+ 
+      if (current_yr == Data@LHYear || length(Data@Misc[[x]]) == 2) {
+        Rec <- new("Rec")
+        Rec@TAC <- TACfilter(rep(NA, reps))
+        Rec@Misc <- c(list(next_assess_yr = current_yr + 1), Assess_output)
+
+        get_projected_TAC <- FALSE
+      } else {
+        get_projected_TAC <- TRUE
+        next_assess_yr <- current_yr + 1
+      }
+    }
+  }
+
+  if (get_projected_TAC) {
+    Rec <- new("Rec")
+    TAC_used <- Data@Misc[[x]]$project_catch[current_yr - Data@Misc[[x]]$last_assess_yr + 1]
[…]

### 2022-03-07 RunMSE/SEFSC/run_script_NK.R

@@ -1,115 +1,316 @@
+library(abind)
+library(bamExtras)
 library(openMSE)
+library(magrittr)
 
 rm(list=ls())
-t1 <- Sys.time()
-set.seed(1358)
+t_list <- Sys.time()
+myseed <- 8675309
 
+source("fn/make_interim_MP_lag.R")
+source("fn/SCA_lag.R")
+
+nsim <- 48 #250
 runScenarios <- TRUE # Run scenarios to do MSE or just generate historical data?
+runMSE_args <- list("parallel"=TRUE,"extended"=TRUE,"silent"=FALSE)
+lag_init <- 2 # Number of years between terminal year of assessment and first year of management. May be modified in scenarios
 
-# assessment_type <-  "SCA_Pope"
-# HCR_type <-  "HCR_MSY"
-# MSY_frac <- 0.75 # Passed to HCR_MSY and multiplied by Fmsy
+OM_name_scen_complete <- NA
+#   local({
+#   a <- gsub(".rds","",list.files("MSE_obj"))
+#   b <- gsub("MSE","OM",a)
+#   b
+# })
+
+OM_name_all <- gsub(".rds","",list.files("OM"))
+OM_name <- OM_name_all#[!OM_name_all%in%OM_name_complete]
+OM_name <- c("OM_RedPorgy"#, # Runs,
+             ,"OM_BlackSeaBass" # Runs
+             ,"OM_VermilionSnapper" # Runs
+             ,"OM_SnowyGrouper" # Runs 2022-1-20 batch 1 for base took only 25 min
+             #"OM_RedGrouper", # 2022-1-19 This took 7 hours just to run the base scenario batch 1 so I interrupted it
+             ,"OM_GagGrouper"#, # Runs
+             #,"OM_GrayTriggerfish" # Problems with lightly fished scenario where "More than 5 % of simulations can't get to the specified level of depletion with these Operating Model parameters"
+             #"OM_RedSnapper" # Seems to run but takes a long time
+)
 
 # Setup loops
-scenario <- c("base"#, #"hs", "hd",
-              #"lf","dep",
-              # "epiM"
-               )
- OM_name <- c(
-   "OM_RedPorgy"#,
-   #"OM_BlackSeaBass",
-   #"OM_VermilionSnapper"#,
-   #"OM_RedGrouper",
-   # "OM_RedSnapper",
-   # "OM_SnowyGrouper"
-             )
[…]

### 2022-03-10 RunMSE/SEFSC/fn/NEW_make_interim_MP.R
Create NEW_make_interim_MP

@@ -1,0 +1,149 @@
+NEW_make_interim_MP<-function (.Assess = "SCA", .HCR = "HCR_MSY", AddInd = "VB", 
+                              assessment_interval = 5, type = c("buffer", "mean", "loess", "none"), 
+                              type_par = NULL, diagnostic = c("min", "full", "none"), 
+                              const=1, eq="default", ...) 
+{
+  
+  type <- match.arg(type)
+  diagnostic <- match.arg(diagnostic)
+  if (is.character(.Assess)) {
+    Assess_char <- .Assess
+    .Assess <- as.symbol(.Assess)
+  }
+  else {
+    .Assess <- substitute(.Assess)
+    Assess_char <- as.character(.Assess)
+  }
+  if (is.character(.HCR)) {
+    .HCR <- as.symbol(.HCR)
+  }
+  else {
+    .HCR <- substitute(.HCR)
+  }
+  if (!inherits(eval(.Assess), "Assess")) {
+    stop(paste(.Assess, "does not belong to class 'Assess'. Use: avail('Assess') to find eligible objects."))
+  }
+  if (!inherits(eval(.HCR), "HCR")) {
+    stop(paste(.HCR, "does not belong to class 'HCR.' Use: avail('HCR') to find eligible objects."))
+  }
+  dots <- list(...)
+  dots$AddInd <- AddInd
+  dots_in_Assess <- dots[match(names(formals(eval(.Assess))), 
+                               names(dots), nomatch = 0)]
+  dots_in_HCR <- dots[match(names(formals(eval(.HCR))), names(dots), 
+                            nomatch = 0)]
+  Assess_call <- as.call(c(.Assess, x = quote(x), Data = quote(Data), 
+                           dots_in_Assess))
+  HCR_call <- as.call(c(.HCR, Assessment = quote(do_Assessment), 
+                        reps = quote(reps), dots_in_HCR))
+  MP_body <- bquote({
+    dependencies <- .(get_dependencies(Assess_char, dots))
+    ny <- length(Data@Year)
+    Current_Yr <- Data@Year[ny]
+    first_assess_yr <- Current_Yr == Data@LHYear
+    run_assessment <- first_assess_yr || Current_Yr == Data@Misc[[x]]$interim$next_assess_yr
+    run_interim <- !run_assessment
+    if (run_assessment) {
+      do_Assessment <- .(Assess_call)
+      if (diagnostic != "none") {
+        Assess_diag_output <- Assess_diagnostic(x, Data, 
[…]

### 2022-03-16 BuildOM/BuildOMAssess2OM.Rmd
updated rds files

--- 2022-03-07 BuildOM/BuildOMVPA2OM.Rmd
@@
 library(bamExtras) # Nikolai's package
+library(bamMSE) # Nikolai's package
 
@@
 Mat_age1_max <- 0.49
+
+# Indicate if operating models should only include indices that were available in the final year of the assessment. logical
+AddInd_endyr_only <- TRUE
 
@@
 
+```{r}
+# create completely empty Data object
+Data_empty <- local({
+  dat <- new("Data")
+  for(slotName_i in slotNames(dat)){
+    slot_i <- slot(dat,slotName_i)
+    if(length(slot_i)>0&is.numeric(slot_i)){
+      slot(dat,slotName_i) <- slot_i*NA
+    }
+  }
+  dat
+})
+```
+
 ```{r build Data, eval=TRUE}
@@
 
-```{r build OM VPA2OM, eval=TRUE}
-list_Nage_F0_pr_sc <- list() # List for storing values of Nage_F0_pr_sc
+```{r build OM Assess2OM, eval=TRUE}
+list_Nage_F0_pr_sc <- list() # List for storing values of Nage_F0_pr_sc (for plotting hist compared to BAM)
 vec_to_mat <- function(vec){
@@
   Name_i <- gsub("rdat_","",rdat_name_i)
+  DataName_i <- gsub("rdat_","Data_",rdat_name_i)
+  Data_i <- get(DataName_i)
+  Obs_i <- rdat_to_Obs(rdat_i)
+
   herm_i <- bamStockMisc[Name_i, "herm"]
@@
   # NOTE: this will have no effect in ageinitmin_i=0 
-  Nage_F0_pr <- expDecay(age=age_i,Z=a.series_i$M,N0=1)                  # Unfished N-at-age per recruit
+  Nage_F0_pr <- exp_decay(age=age_i,Z=a.series_i$M,N0=1)                  # Unfished N-at-age per recruit
   Nage_F0_pr_sc <- (Nage_F0_pr/Nage_F0_pr[[paste(ageinitmin_i)]])[["0"]] # Scaling factor for computing unfished numbers at age-0
@@
                             Obs=ObsUser,
-                            Ind_abb=c("sCT","sTV","sVD"),
-                            CAA_abb=c("sCT","sTV","sVD"),
-                            CAL_abb=c("sCT","sTV","sVD")
+                            Ind_abb=c("sTV", "sCT", "sVD", "sBL", "sVL", "sBT", "sFT"),
+                            CAA_abb=c("sTV", "sCT", "sVD", "sBL", "sVL", "sBT", "sFT"),
+                            CAL_abb=c("sTV", "sCT", "sVD", "sBL", "sVL", "sBT", "sFT")
                             )
@@
 
- OM_i <- VPA2OM(Name=Name_i,
+ OM_i <- Assess2OM(Name=Name_i,
                 proyears = proyears,
@@
         )
+
+ # Add indices observed in the assessment, their CVs, and their selectivities
+ AddInd <- slot(Data_i,"AddInd")
+ CV_AddInd <- slot(Data_i,"CV_AddInd")
+ AddIndV <- slot(Data_i,"AddIndV")
+ AddIndType <- slot(Data_i,"AddIndType")
+ AddIunits <- slot(Data_i,"AddIunits")
+
+ if(AddInd_endyr_only){
+   # Identify which indices are available (not NA) in the terminal year of the assessment
+   AddInd_endyr_ix <- which(!is.na(AddInd[1,,dim(AddInd)[3]])) # Just uses the first sim!!
+   AddInd <- AddInd[,AddInd_endyr_ix,,drop=FALSE]
+   CV_AddInd <- CV_AddInd[,AddInd_endyr_ix,,drop=FALSE]
+   AddIndV <- AddIndV[,AddInd_endyr_ix,,drop=FALSE]
+   AddIndType <- AddIndType[AddInd_endyr_ix]
+   AddIunits <- AddIunits[AddInd_endyr_ix]
+ }
+
+ Data2_i <- Data_empty
+ slot(Data2_i,"AddInd") <- AddInd
+ slot(Data2_i,"CV_AddInd") <- CV_AddInd
+ slot(Data2_i,"AddIndV") <- AddIndV
+ slot(Data2_i,"AddIndType") <- AddIndType
+ slot(Data2_i,"AddIunits") <- AddIunits
+
+ OM_i@cpars$Data <- Data2_i
 

### 2022-03-16 RunMSE/SEFSC/MSEPlots.Rmd
updated rds files

--- 2022-01-07 RunMSE/SEFSC/MSEPlots.Rmd
@@
 rm(list=ls())
-knitr::opts_chunk$set(comment=NA,echo=FALSE,message=FALSE,warning=FALSE,fig.height=7,fig.width=6)
+knitr::opts_chunk$set(comment=NA,echo=FALSE,message=FALSE,warning=FALSE,fig.width=8,fig.height=10)
 
@@
 ```{r user}
-OMNames_user <- c("OM_BlackSeaBass","OM_VermilionSnapper","OM_RedPorgy")#,
-                   #"OM_Tilefish","OM_Cobia","OM_SnowyGrouper",
+# Should individual PDFs be produced (or just plot in Rmd output)
+plot_pdf <- TRUE
+
+OMNames_user <- c("OM_BlackSeaBass",
+                  "OM_VermilionSnapper",
+                  "OM_RedPorgy",
+                   #"OM_Tilefish","OM_Cobia",
+                  "OM_SnowyGrouper"#,
+                  #"OM_GagGrouper")#,
                    #"OM_capelin", "OM_POP", "OM_vs"
-                   #)
-scenNames_user <-  c("base",#"hs","hd",
-                     "dep","lf",
-                     "epiM"
                    )
-scenNames_key <- c("base"="Base","hs"="Hyper-stable","hd"="Hyper-deplete",
-                   "dep"="Depleted","lf"="Lightly fished","epiM"="Episodic M")
-MPNamesSub_user <- c("SCA_10","SCA_1","iMP_avg_10","iMP_buffer_10")
-MPNamesSub_user_legtext <- c("Fixed TAC (10)","Annual assessment","Averaged Index (10)","Buffered Index (10)")
+OMNames_huynh <- c("OM_CapelinHuynh", "OM_PacificOceanPerchHuynh", "OM_VermilionSnapperHuynh")
+
+scenNames_user1 <-  c("base","dep","lf","epiM","ubias","tachi","rc")
+scenNames_user2 <-  c("base","nolag","minerr","minrecdev","perfobs","ucvhi","ucvlo","vtiv"
+                        )
+
+# All scenarios
+scenNames_user <- unique(c(scenNames_user1,scenNames_user2))
+
+# Alternative realities
+# These scenarios are considered equally plausible, for the purposes of
+# averaging results together. Most other scenarios could be considered sensitivities.
+scenNames_user_alt <- c("base","dep","lf","epiM","ubias","tachi","rc")
+
+scenNames_key <- c("base"="Base",
+                   "nolag"="No data lag",
+                   "hs"="Hyper-stable","hd"="Hyper-deplete",
+                   "dep"="Depleted","lf"="Lightly fished","epiM"="Episodic M",
+                   "rc"="Regime\nchange", "ubias"="Index\nbiased","ucvhi"="Index\nHigh CV",
+                   "ucvlo"="Index\nLow CV",
+                   "perfobs"="Perfect observation",
+                   "minerr"="Minimal error",
+                   "minrecdev"="Minimal rec devs",
+                   "tachi"="TAC 1.25MSY",
+                   "vtiv"="V time invariant"
+                   )
+
+MPNamesAll <-         c(#"AvC",
+                        "CC1",
+                        #"DCAC","DBSRA","SPMSY",
+                        "SCA_1","SCA_5","SCA_10",
+                        "iMP_avg_5","iMP_avg_10",
+                        "iMP_buffer_5","iMP_buffer_10",
+                        "pMP_5","pMP_10"
+                        )
+
+MPNamesAll_key <- c("AvC"="average catch",
+                    "CC1"="average catch (last 5 yr)",
+                    "DCAC"= "depletion corrected average catch",
+                    "DBSRA" = "depletion based stock reduction analysis",
+                    "SPMSY" = "surplus production model",
+                    "SCA_1" = "SCA 1 yr",
+                    "SCA_5" = "SCA 5 yr",
+                    "SCA_10"= "SCA 10 yr",
+                    "iMP_avg_5" = "avg. index (5 yr)",
+                    "iMP_avg_10" = "avg. index (10 yr)",
+                    "iMP_buffer_5" = "buffer index (5 yr)",
+                    "iMP_buffer_10" = "buffer index (10 yr)",
+                    "pMP_5" = "projection (5 yr)",
+                    "pMP_10" = "projection (10 yr)"
+                        )
+MPNamesAll_legtext <- MPNamesAll
+
+MPNamesSub_user <- c("SCA_10","SCA_5","SCA_1","iMP_avg_10"#,"iMP_buffer_10"
+                     )
+MPNamesSub_user_legtext <- c("Fixed TAC (10)","Fixed TAC (5)","Annual assessment","Averaged Index (10)"#,"Buffered Index (10)"
+                             )
 
@@
 # OMNames_user <- c("OM_RedPorgy","OM_Tilefish","OM_Cobia")
+```
+
+## Built in performance metrics (PMs)
+
+* `P10`	  Probability B > 0.1 BMSY
+* `P50`	  Probability B > 0.5 BMSY
+* `P100`  Probability B > BMSY
+* `PNOF`  Probability F < FMSY
+* `LTY`	  Probability Long-Term Yield > 0.5 Relative Yield
+* `STY`	  Probability Short-Term Yield > 0.5 Relative Yield
+* `AAVY`	Probability AAVY < 0.2 (Average Annual Variability in Yield)
+* `AAVE`	Probability AAVE < 0.2 (Average Annual Variability in Effort)
+* `Yield`	Average Yield (relative to Reference Yield)
+
+- can easily vary reference values and years
+- PMs compute probabilities across years for each simulation and return mean values across simulations (but we could recompute them however we want from the raw MSE objects)
+
+```{r functions}
+# color function like rainbow() but without yellow (or indigo)
+ROGBP <- colorRampPalette(c("red","orange","green","blue","purple"))
+# Makes an ROGBP function with an alpha channel
+ROGBP_alpha <- function(alpha){
+  x <- colorRampPalette(c(
+    rgb(1,0,0,alpha), # red
+    rgb(1,0.5,0.25,alpha), # orange
+    rgb(0,1,0,alpha), # green 
+    rgb(0,0,1,alpha), # blue
+    rgb(0.5,0,0.5,alpha)), # purple
+    alpha=TRUE)
+  return(x)
+}
+
+# Turn hexadecimal color opaque
+makeOpaque <-      function(hexcolor){gsub(".{2}$","FF",hexcolor)}
+
+P75 <- function(...,Ref=0.75){P50(...,Ref=Ref)}
+
+AAVY10 <- function(MSEobj = NULL, Ref = 0.1, Yrs = NULL){AAVY(MSEobj = MSEobj, Ref = Ref, Yrs = Yrs)}
+
 ```
@@
 
-```{r plot_MSE_ts_Huynh function}
+```{r plot_MSE_ts function}
+# Time series plots
 
-plot_MSE_ts_Huynh <- function(
+plot_MSE_ts <- function(
+myvarName="SSB",
+myvarDenomExpr = NULL,
+ylabel = myvarName,
+FUN = mean,
+scenNames,
+OMNames,
+MPNamesSub = NULL,
+MPNamesSub_legtext=MPNamesSub,
+MPNamesRef = NULL, # Name of reference MP
+FUNRef = function(myvarsubStat,MPNamesRef){ # Function for comparing MPs with reference MP
+  (myvarsubStat-myvarsubStat[,MPNamesRef])/myvarsubStat[,MPNamesRef]},
+legtext_o = NULL, # order for plotting legend text
+MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
+                     "_",
+                     rep(scenNames,length(OMNames))
+                     ),
+colLabs = str_replace_all(gsub("OM_","",OMNames),"(?<=[a-z])(?=[A-Z])"," "),
+rowLabs = scenNames,
+sims = NULL, # which simulation runs should be used to generate the plot when plot_type="sims"?
+plot_type="huynh", # "huynh" plots time series by MP like in the Huynh et al paper
+                   # "boot" plots times series of bootstrapped data  with bamExtras::plot_boot_vec
+                   # "phase" plots phase plots of F/Fmsy versus SSB/SSBmsy
+                   # "tradeoff" plots tradeoff plots by MP
+                   # "addind" plot additional indices from AddInd
+                   # "sims" plot time series for individual sim runs
+proyear_phase=NULL,
+PMx = Yield, # Performance metric function x (x-axis) for tradeoff plots)
+PMy = P75, # Performance metric function y (y-axis) for tradeoff plots)
+mar=c(1,1,1,1),
+oma=c(6,4,3,3),
+mgp=c(1.5,0.2,0),
+cols = setNames(ROGBP_alpha(0.5)(length(MPNamesSub)),MPNamesSub),
+ltys = setNames(rep(1,length(MPNamesSub)),MPNamesSub),
+pchs = setNames(rep(16,length(MPNamesSub)),MPNamesSub),
+lwds = setNames(rep(3,length(MPNamesSub)),MPNamesSub),
+types = setNames(rep("l",length(MPNamesSub)),MPNamesSub),
+xlabel = "Management year",
+main_line = 1, # Line for main column labels
+xlim = NULL,
+ylim = NULL,
+assessmentYears=NULL,
+x.at = NULL,
+y.at = NULL,
+# leg.x=NULL,
+# leg.y =NULL,
+legend_panel=NULL,
+legend_cex= 1,
+legend_x="bottomleft",
+legend_inset=c(0,-0.5),
+label_axes="all", # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
+hline=1 # values to pass into abline(h=hline)
+){
+if(is.null(legtext_o)){
+  legtext_o <- seq_along(MPNamesSub)
+}
+
+xlim_user <- xlim
+ylim_user <- ylim
+x.at_user <- x.at
+y.at_user <- y.at
+
+colLabsAll = as.character(matrix(c(colLabs,rep("",length(MSEoutNames)-length(colLabs))),ncol=length(colLabs),byrow=TRUE))
+rowLabsAll = as.character(matrix(c(rep("",length(MSEoutNames)-length(rowLabs)),rowLabs),nrow=length(rowLabs),byrow=FALSE))
+
+dim1 <- length(rowLabs)
+dim2 <- length(colLabs)
+
+if(plot_type=="addind"){
+  mfcol <- c(dim2,dim1)}else{
+  mfcol <- c(dim1,dim2)
+}
+
+par(mfcol=mfcol,mgp=mgp,mar=mar,oma=oma,tck=-0.01,xpd=FALSE,xaxs="r",yaxs="r")
+
+### LOOP THROUGH MSE OBJECTS
+for(outName_i in MSEoutNames){
+topPanels <- (length(scenNames)*(seq_along(OMNames)-1)+1)
+bottomPanels <- length(scenNames)*seq_along(OMNames)
+leftPanels <- seq_along(scenNames)
+rightPanels <- tail(seq_along(MSEoutNames),length(scenNames))
+
+i <- which(MSEoutNames==outName_i)
+out_i <- get(outName_i)
+MPNames <- out_i@MPs
+
+if(is.null(sims)){
+  sims <- 1:out_i@nsim
+}
+if(!is.expression(myvarName)){
+  myvar <- slot(out_i,myvarName)  
+}else{
+  myvar <- eval(myvarName) 
+}
+
+nyears_i <- out_i@nyears
+proyears_i <- out_i@proyears
+LHyear_i <- out_i@Hist@Data@LHYear # Last historic year
+histYears <- sort(LHyear_i - ((1:nyears_i)-1))
+projYears_i <- LHyear_i+1:proyears_i
+
+legend_panel <- bottomPanels[1]
+
+if(!is.null(myvarDenomExpr)){
+myvarDenom <- eval(myvarDenomExpr)
+myvar <- myvar/myvarDenom # Scale myvar
+}
+
+xaxt_i <- ifelse(i%in%bottomPanels,"n","n")
+yaxt_i <- ifelse(i%in%leftPanels,"n","n")
+
+MPNamesSubix <- match(MPNamesSub,MPNames)
+
+if(plot_type=="huynh"){
+if(!is.null(dim(myvar))){
+myvarsub <- myvar[,match(MPNamesSub,MPNames),]
+myvarsubStat <- apply(myvarsub,2,function(x){apply(x,2,FUN)})
+}else{
+myvarsubStat <- matrix(rep(myvar,length(MPNamesSub)),ncol=length(MPNamesSub))  
+}
+dimnames(myvarsubStat) <- list(1:nrow(myvarsubStat),MPNamesSub)
+
+if(!is.null(MPNamesRef)){
+myvarsubStat <- FUNRef(myvarsubStat,MPNamesRef)
+}
+
+if(is.null(ylim_user)){
+  ylim <- range(myvarsubStat,na.rm=TRUE)
+}
+if(is.null(xlim_user)){
+  xlim <- range(projYears_i,na.rm=TRUE)
+}
+
+matplot(projYears_i#as.numeric(rownames(myvarsubStat))
+        ,myvarsubStat,
+        col=cols,lty=ltys,lwd=lwds,type=types,
+        xaxt=xaxt_i,yaxt=yaxt_i,
+        xlim=xlim,ylim=ylim,xlab="",ylab="")
+#title(main=colLabsAll[i],line=1)
+
+grid(nx=NA,ny=NULL)
+abline(v=assessmentYears,lty="1111",lwd=2)
+}
+    if(plot_type=="sims"){
+      cols <-  ROGBP(length(sims))
+      ltys <-  1:length(MPNamesSub)
+      pchs <-  NA
+      lwds <-  3
+      types <- "l"
+
+      myvarsub <- myvar[sims,match(MPNamesSub,MPNames),,drop=FALSE]
+      dimnames(myvarsub) <- list(sims,MPNamesSub,1:proyears_i)
+
+      if(!is.null(MPNamesRef)){
+        myvarsub <- FUNRef(myvarsub,MPNamesRef)
+      }
+
+      if(is.null(ylim_user)){
+        ylim <- range(myvarsub,na.rm=TRUE)
+      }
+      if(is.null(xlim_user)){
+        xlim <- range(projYears_i,na.rm=TRUE)
+      }
+
+      for(MP_j in MPNamesSub){
+      j <- match(MP_j,MPNamesSub)
+      myvarsub_j <- myvarsub[,j,]
+      lty <- ltys[j]
+      if(j==1){
+      matplot(projYears_i,
+              t(myvarsub_j), 
+              col=cols,lty=lty,lwd=lwds,type=types,
+              xaxt=xaxt_i,yaxt=yaxt_i,
+              xlim=xlim,ylim=ylim,xlab="",ylab="")
+      #title(main=colLabsAll[i],line=1)
+
+      grid(nx=NA,ny=NULL)
+      abline(v=assessmentYears,lty=2,lwd=1)
+      }else{
+        matpoints(t(myvarsub_j), 
+                col=cols,lty=lty,lwd=lwds,type=types
+                )        
+      }
+    }
+    }
+
+if(plot_type=="addind"){
+  PPDYears_i <- local({
+    a <- c(histYears,projYears_i)
+    a[-length(a)]
+  })
+if(is.null(assessmentYears)){
+assessmentYears <- apply(do.call(cbind,lapply(out_i@PPD[[MPNamesSub]]@Misc,FUN=function(x){x1 <- x$diagnostic; unlist(lapply(x1,FUN=function(xx){xx$Year}))})),1,median)
+}
+
+if(!is.null(dim(myvar))){
+myvarsub <- myvar
+#myvarsubStat <- apply(myvarsub,2,function(x){apply(x,2,FUN)})
+}else{
+  warning("is.null(dim(myvar) == TRUE. No option currently available for this situation.")
+}
+dimnames(myvarsub) <- list("sim"=1:dim(myvarsub)[1],"AddInd"=1:dim(myvarsub)[2],"Year"=PPDYears_i)
+if(is.null(ylim_user)){
+  ylim <- range(myvarsub,na.rm=TRUE)
+}
+if(is.null(xlim_user)){
+  xlim <- range(PPDYears_i,na.rm=TRUE)
+}
+# n_AddInd <- ncol(myvarsubStat)
+# cols <-  ROGBP_alpha(0.5)(n_AddInd)
+# matplot(PPDYears_i,myvarsubStat,
+#         col=cols,lty=ltys,lwd=lwds,type=types,
+#         xaxt=xaxt_i,yaxt=yaxt_i,
+#         xlim=xlim,ylim=ylim,xlab="",ylab="")
+#title(main=colLabsAll[i],line=1)
+n_AddInd <- dim(myvarsub)[2]
+col_AddInd <- ROGBP(n_AddInd)
+for(j in 1:n_AddInd){
+
+plot_boot_vec(myvarsub[,j,],
+              col_lines = col_AddInd[j],
+              add=ifelse(j!=1,TRUE,FALSE),
+              xlim=xlim,ylim=ylim)
+
+}
+grid(nx=NA,ny=NULL)
+abline(v=assessmentYears,lty=2,lwd=1)
+}
+
+if(plot_type=="boot"){
+  if(is.null(ylim_user)){
+  ylim <- range(myvar,na.rm=TRUE)
+}
+  bamExtras::plot_boot_vec(myvar,ylim=ylim)
+  abline(v=out_i@nyears,lwd=2,lty=2) # Plot vertical line at end of historical period
+}
+
+if(plot_type=="phase"){
+ltys <-  setNames(rep(0,length(MPNamesSub)),MPNamesSub)
+# pchs <-  setNames(rep(1,length(MPNamesSub)),MPNamesSub)
+lwds <-  setNames(rep(0,length(MPNamesSub)),MPNamesSub)
+types <- setNames(rep("p",length(MPNamesSub)),MPNamesSub)  
+xlabel <- "F/Fmsy"  
+ylabel <- "SSB/SSBmsy"
+
+if(is.null(proyear_phase)){
+  proyear_phase <- out_i@proyears
+}
+Bstatus <- out_i@SB_SBMSY[,MPNamesSubix,proyear_phase]
+Fstatus <- out_i@F_FMSY[,MPNamesSubix,proyear_phase]
+
+matplot(Fstatus,Bstatus,
+        col=cols,lty=ltys,lwd=lwds,pch=pchs,type=types,
+        xaxt=xaxt_i,yaxt=yaxt_i,
+        xlab="",ylab="",xlim=xlim,ylim=ylim
+        )
+points(apply(Fstatus,2,median),
+       apply(Bstatus,2,median),pch=21,cex=3,lwd=2,col="black",bg=makeOpaque(cols))
+
+  abline(v=1,lty=3)
+  abline(h=1,lty=3)
+
+}
+
+if(plot_type=="tradeoff"){
+  out_i <- get(outName_i)
+
+PMx_out <- PMx(out_i)
+PMy_out <- PMy(out_i)
+
+plot(PMx_out@Mean[MPNamesSubix],PMy_out@Mean[MPNamesSubix],pch=16,col=cols,
+     xaxt=xaxt_i,yaxt=yaxt_i,
+     xlab="",ylab="",
+     xlim=xlim,ylim=ylim
+     )
+
+# legend("top",legend=MPs,col=MPcols,pch=16,bty="n")
+
+ltys <-  setNames(rep(0,length(MPNamesSub)),MPNamesSub)
+lwds <-  setNames(rep(0,length(MPNamesSub)),MPNamesSub)
+types <- setNames(rep("p",length(MPNamesSub)),MPNamesSub)  
+xlabel <- PMx_out@Caption 
+ylabel <- PMy_out@Caption
+
+}
+
+if(!is.null(hline)){
+abline(h=hline)
+}
+
+if(is.null(x.at_user)){
+  x.at <- pretty(par("usr")[1:2])
+}
+if(is.null(y.at_user)){
+  y.at <- pretty(par("usr")[3:4])
+}
+
+if(i%in%topPanels){
+col.ct <- which(topPanels==i)
+mtext(colLabsAll[i],side=3,line=main_line,outer=FALSE,font=2)
+}
+
+if(i%in%rightPanels){
+row.ct <- which(rightPanels==i)
+rowcenter <-par("usr")[3]+diff(par("usr")[3:4])/2
+text(x=par("usr")[2]+diff(par("usr")[1:2])*0.1
+     ,y=rowcenter,rowLabsAll[i],
+     srt=-90,xpd=NA,font=2)
+}
+
+if(label_axes=="all"){
+  x.at.i <- x.at
+  axis(side=1,at=x.at.i)
+  y.at.i <- y.at
+  axis(side=2,at=y.at.i)
+}
+if(label_axes=="leftbottom"){
+  if(i%in%bottomPanels){
+    x.at.i <- x.at
+    if(i>bottomPanels[1]){x.at.i <- x.at[-1]}
+    axis(side=1,at=x.at.i,outer=TRUE)
+  }
+  if(i%in%leftPanels){
+    y.at.i <- y.at
+    if(i>leftPanels[1]){y.at.i <- y.at[1:(length(y.at)-1)]}
+    axis(side=2,at=y.at.i,outer=TRUE)
+  }
+}
+
+if(i==legend_panel&plot_type%in%c("huynh","phase","tradeoff")){
+   legend(legend_x,
+          inset=legend_inset,
+       horiz=TRUE,bty="n",
+       legend=MPNamesSub_legtext[legtext_o],
+       col=makeOpaque(cols)[legtext_o],lty=ltys[legtext_o],lwd=lwds[legtext_o],pch=pchs[legtext_o],
+       cex=legend_cex,
+       xpd=NA,
+       x.intersp=0.5
+       )
+
+}
+}
+
+mtext(ylabel,side=2,line=par("mgp")[1],outer=TRUE)
+mtext(xlabel,side=1,line= par("mgp")[1],outer=TRUE)
+
+}
+```
+
+```{r plot_MSE_dw function}
+# Dot and whisker plots
+
+plot_MSE_dw <- function(
 myvarName,
@@
 ylabel = myvarName,
-FUN = mean_noNA,
+FUN = cv,  # MSEtool::cv
 scenNames,
@@
 MPNamesSub_legtext=MPNamesSub,
-legtext_o = c(2,3,4,1), # order for plotting legend text
+legtext_o = c(3,2,1,4), # order for plotting legend text
 MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
@@
 
-mar=c(1,1,1,1),
-cols = setNames(c("red","black","deepskyblue2","deepskyblue2"),MPNamesSub),
-ltys = setNames(c(1,1,1,2),MPNamesSub),
-lwds = setNames(c(3,3,3,3),MPNamesSub),
-types = setNames(c("l","l","l","l"),MPNamesSub),
-xlabel = "Management year",
+mar=c(0,0,0,0),
+oma=c(10,4,3,3),
+mgp=c(1,0.3,0),
+cols = setNames(ROGBP(length(MPNamesSub)),MPNamesSub),
+ltys = setNames(rep(1,length(MPNamesSub)),MPNamesSub),
+lwds = setNames(rep(1,length(MPNamesSub)),MPNamesSub),
+pchs = setNames(rep(16,length(MPNamesSub)),MPNamesSub),
+types = setNames(rep("l",length(MPNamesSub)),MPNamesSub),
+textlabpos = rep("lo",length(MSEoutNames)),#c(rep("lo",6),rep("up",7),"lo",rep("up",4)),
+xlabel = "Management procedure",
+xlabel_line=9,
 xlim = NULL,
-ylim = NULL,
-assessmentYears = seq(10,40,by=10),
+ylim = c(0,0.6),
 x.at = NULL,
@@
 # leg.y =NULL,
-legend_panel=NULL,
-legend_cex= 1,
-legend_x="bottomleft",
-legend_inset=c(0,-0.6),
-label_axes="all", # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
+# legend_panel=NULL,
+# legend_cex= 1,
+# legend_x="bottomleft",
+# legend_inset=c(0,-0.6),
+label_axes="leftbottom", # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
 hline=1 # values to pass into abline(h=hline)
 ){
+
 xlim_user <- xlim
@@
 ncol <- length(colLabs)
-npanel <- nrow*ncol
 
-par(mfcol=c(nrow,ncol),mgp=c(1,0.2,0),mar=mar,oma=c(6,4,3,3),tck=-0.01,xpd=FALSE,xaxs="i",yaxs="i")
+par(mfcol=c(nrow,ncol),mgp=mgp,mar=mar,oma=oma,tck=-0.01,xpd=FALSE,xaxs="i",
+    yaxs="r",lend="butt")
 
@@
 
-if(i==legend_panel){
-   legend(legend_x,
-          inset=legend_inset,
-       horiz=TRUE,bty="n",
-       legend=MPNamesSub_legtext[legtext_o],
-       col=cols[legtext_o],lty=ltys[legtext_o],lwd=lwds[legtext_o],
-       cex=legend_cex,
-       xpd=NA
-       )
+# if(i==legend_panel){
+#    legend(legend_x,
+#           inset=legend_inset,
+#        horiz=TRUE,bty="n",
+#        legend=MPNamesSub_legtext[legtext_o],
+#        col=cols[legtext_o],lty=ltys[legtext_o],lwd=lwds[legtext_o],
+#        cex=legend_cex,
+#        xpd=NA
+#        ) 
+# 
+# }
+}
 
+mtext(ylabel,side=2,line=1.5,outer=TRUE)
+mtext(xlabel,side=1,line=xlabel_line,outer=TRUE)
+
+}
+```
+
+```{r plot_MSE_sims function}
+plot_MSE_sims <- function(MSE, sims=NULL, MPs=NULL, proyears_ix=NULL,
+              varNames=NULL, rec_age=0,
+              type="proj", # period to plot: "proj", or "histproj"
+              title_main = NULL,
+              vline=NULL,vline_lty=3,
+              ...){
+MSEName <- deparse(substitute(MSE))
+if(is.null(varNames)){
+  varNames <- list("proj"=    c("Catch","FM","F_FMSY","recruit","SSB","SB_SBMSY"),
+                   "histproj"=c("Catch","FM","F_FMSY","recruit","SSB","SB_SBMSY"))[[type]]
+}
+
+nyears <- MSE@nyears
+proyears <- MSE@proyears
+LHyear <- MSE@Hist@Data@LHYear # Last historic year
+histYears <- sort(LHyear - ((1:nyears)-1))
+projYears <- LHyear+1:proyears
+
+if(is.null(sims)){sims <- 1:3}  
+if(is.null(MPs)){MPs <- MSE@MPs[1]}
+if(is.null(proyears_ix))    {proyears_ix <- 1:proyears}
+
+MPn <- match(MPs,MSE@MPs)
+
+nr <- ceiling(sqrt(length(varNames)))
+nc <- ceiling(length(varNames)/nr)
+par(mfcol=c(nr,nc),mar=c(2,3,1,1),oma=c(0,0,2,0),mgp=c(1,0.2,0),tck=-0.01)
+
+for(varName_i in varNames){
+  for(MPn_j in  MPn){
+    MPn_j_ix <- match(MPn_j,MPn)
+    if(type=="proj"){
+      years_plot <- projYears
+      if(varName_i=="recruit"){
+        N <- Reduce("+",apply(MSE@Misc$extended$N,5,FUN=function(x){x},simplify = FALSE))
+        var_i <- N[,rec_age+1,,]
+        years_ix <-   tail(1:dim(var_i)[3],MSE@proyears)
+        # drop MP dimension but not sims
+        varSub_i <- var_i[sims,MPn_j,years_ix,drop=FALSE]
+        varSub_i <- matrix(varSub_i,nrow=dim(varSub_i)[1],ncol=dim(varSub_i)[3]) 
+      }else{
+        var_i <- slot(MSE,varName_i)
+        varSub_i <- var_i[sims,MPn_j,proyears_ix,drop=FALSE]
+        varSub_i <- matrix(varSub_i,nrow=dim(varSub_i)[1],ncol=dim(varSub_i)[3]) 
       }
@@
 
-mtext(ylabel,side=2,line=1.5,outer=TRUE)
-mtext(xlabel,side=1,line= par("mgp")[1],outer=TRUE)
+    if(type=="histproj"){
+      years_plot <- c(histYears, projYears)
+      if(varName_i=="recruit"){
+        N <- Reduce("+",apply(MSE@Misc$extended$N,5,FUN=function(x){x},simplify = FALSE))
+        var_i <- N[,rec_age+1,,]
+      }
+      if(varName_i%in%c("F","FM")){
+        FM <- apply(MSE@Misc$extended[["FM"]],c(1,3,4),max) # Max F over ages and areas
+        var_i <- FM
+      }
+      if(varName_i=="F_FMSY"){
+        FM <- apply(MSE@Misc$extended[["FM"]],c(1,3,4),max) # Max F over ages and areas
+        FMSY <- MSE@RefPoint$FMSY
+        var_i <- FM/FMSY
+      }
+      if(varName_i=="SB_SBMSY"){
+        SSB <- apply(MSE@Misc$extended[["SSB"]],c(1,3,4),sum) # Sum SSB over ages and areas
+        SSBMSY <- MSE@RefPoint$SSBMSY
+        var_i <- SSB/SSBMSY
+      }
+      if(!varName_i%in%c("F","FM","recruit","F_FMSY","SB_SBMSY")){
+        var_i <- Reduce("+",apply(MSE@Misc$extended[[varName_i]],5,FUN=function(x){x},simplify = FALSE))
+        var_i <- Reduce("+",apply(var_i,2,FUN=function(x){x},simplify = FALSE))
+      }
+      #varSub_i <- var_i[sims,MPn_j,] # Drops dimension to be matrix
+        varSub_i <- var_i[sims,MPn_j,,drop=FALSE]
+        varSub_i <- matrix(varSub_i,nrow=dim(varSub_i)[1],ncol=dim(varSub_i)[3]) 
+    }
+    if(match(MPn_j,MPn)==1){
+      matplot(years_plot,t(varSub_i),type="l",
+              col=ROGBP(length(sims)),xlab="",ylab=varName_i, lty=MPn_j_ix,...)
+    }else{
+      matpoints(years_plot,t(varSub_i),type="l",
+                col=ROGBP(length(sims)),lty=MPn_j_ix,...)
+    }    
+  }
+  if(match(varName_i,varNames)==1){
+    legend("topright",legend=MPs,lty=1:length(MPs),bty="n")
+  }
+  if(is.null(vline)){vline <- LHyear}
+  abline(v=vline,lty=vline_lty)
+}
+if(is.null(title_main)){
+  title_main <- paste(MSEName,MPs,sep=": ")
+}
+title(main=title_main,outer = TRUE)
+}
 
+```
+
+```{r function PMsummary}
+# compute and plot summary statistics for Performance metrics
+PMsummary <- function(PMName,OMNames=OMNames_user,scenNames,MPs=NULL,
+                      slot_to_plot="Prob", # Can be either "Prob" or "Stat"
+                      main_line=-1.5,
+                      hline=1,hline_lty=1,
+                      par_args=list(mfrow=c(length(OMNames),1), 
+                                    mar=c(0,2,0,1), oma=c(6,2,1,0),
+                                    mgp=c(0.8,0.2,0), tck=-0.01),
+                      ...){
+PM <- get(PMName)
+dots <- list(...)
+if(!"ylab"%in%names(dots)){
+  dots$ylab <- PMName
+}
+
+out_list <- list()
+
+do.call(par,par_args)
+
+for (OMNames_i in OMNames){
+Names_i <- gsub("^OM_","",OMNames_i)
+MSEoutNames_i = paste0(rep(gsub("OM","MSE",OMNames_i),each=length(scenNames)),
+                     "_",
+                     rep(scenNames,length(OMNames_i))
+                     )
+    out_list_i <- list()
+    for(MSEoutNames_ij in MSEoutNames_i){
+      scenNames_j <- str_extract(MSEoutNames_ij,"[a-z]+$")
+      MSEout_ij <- get(MSEoutNames_ij)
+      PMout_ij <- PM(MSEout_ij)
+        MPs_ij <- PMout_ij@MPs
+        out_ij <- slot(PMout_ij,slot_to_plot)
+      if(!is.null(MPs)){
+        out_ij <- out_ij[,match(MPs,MPs_ij)]
+        MPs_ij <- MPs
+      }
+      dimnames(out_ij) <- list("sim"=seq(1:dim(out_ij)[1]), "MPs"=MPs_ij)
+      out_ij <- cbind("scen"=scenNames_j,as.data.frame(out_ij))
+      out_list_i[[MSEoutNames_ij]] <- out_ij
+
+    }
+    # Combine scenario outputs into large data frame with scen column indicating scenario
+      out_df_i <- do.call(rbind,out_list_i)
+      out_list[[paste0("out_df_",Names_i,"_",PMName)]] <- out_df_i
+    # Plot stuff
+      dots$xaxt <- ifelse(match(OMNames_i,rev(OMNames))==1,"s","n")
+
+      do.call(boxplot,c(list(out_df_i[,-1],main=""),dots))
+      mtext(Names_i,side=3,line=main_line,outer=FALSE,font=2)
+      abline(h=hline,lty=hline_lty)
+    }
+
+invisible(out_list)
+}
+```
+
+```{r function MSEsummary}
+# compute and plot summary statistics for Performance metrics
+MSEsummary <- function(MSEslotName,OMNames=OMNames_user,scenNames,MPs=NULL,
+                       main_line=-1.5,
+                       hline=1,hline_lty=1,
+                      par_args=list(mfrow=c(length(OMNames),1),
+                                    mar=c(3,2,1,1), oma=c(1,2,0,0),
+                                    mgp=c(0.8,0.2,0), tck=-0.01),
+                      ...){
+dots <- list(...)
+if(!"ylab"%in%names(dots)){
+  dots$ylab <- MSEslotName
+}
+out_list <- list()
+
+do.call(par,par_args)
+
+for (OMNames_i in OMNames){
+  Names_i <- gsub("^OM_","",OMNames_i)
+  MSEoutNames_i = paste0(rep(gsub("OM","MSE",OMNames_i),each=length(scenNames)),
+                         "_",
+                         rep(scenNames,length(OMNames_i))
+  )
+  slot_list_i <- list()
+  for(MSEoutNames_ij in MSEoutNames_i){
+    scenNames_j <- str_extract(MSEoutNames_ij,"[a-z]+$")
+    MSEout_ij <- get(MSEoutNames_ij)
+    if(!is.expression(MSEslotName)){
+      slot_k <- slot(MSEout_ij,MSEslotName) %>% apply(2,as.numeric)
+    }else{
+      slot_k <- eval(MSEslotName) %>% apply(2,as.numeric)
+    }
+    slot_k <- slot(MSEout_ij,MSEslotName) %>% apply(2,as.numeric)
+    MPs_ij <- MSEout_ij@MPs
+    if(!is.null(MPs)){
+      slot_k <- slot_k[,match(MPs,MPs_ij)]
+      MPs_ij <- MPs
+    }
+    dimnames(slot_k) <- list(NULL, "MPs"=MPs_ij)
+    slot_k <- cbind("scen"=scenNames_j,as.data.frame(slot_k))
+    slot_list_i[[MSEoutNames_ij]] <- slot_k
+
+  }
+  # Combine scenario outputs into large data frame with scen column indicating scenario
+  slot_df_i <- do.call(rbind,slot_list_i)
+  out_list[[paste0("slot_df_",Names_i,"_",MSEslotName)]] <- slot_df_i
+
+  # Plot stuff
+  do.call(boxplot,c(list(slot_df_i[,-1],main=""),dots))
+  mtext(Names_i,side=3,line=main_line,outer=FALSE,font=2)
+  abline(h=hline,lty=hline_lty)
+}
+
+invisible(out_list)
 }
@@
 for(file.i in list.files("MSE_obj")){
+  out_i <- readRDS(file.path("MSE_obj",file.i))
+  names(out_i@PPD) <- out_i@MPs
   assign(gsub(".rds","",file.i),readRDS(file.path("MSE_obj",file.i)))
 }
+```
 
-# # Merge sets of MSE results
-# for(i in  OMNames_user){
-#   for(j in scenNames_user){
-#     OMscenName <- paste0(i,"_",j)
-#     MSEName <- gsub("OM","MSE",OMscenName)
-#     a <- mget(MSE_res_names[grepl(OMscenName,MSE_res_names)])
-#     b <- do.call(merge_MSE, args=a)
-#     assign(MSEName,b)
-#   }
-# }
-# 
-# rm(list=MSE_res_names)
-# MSE_res_names <- gsub("OM","MSE",apply(expand.grid(OMNames_user,scenNames_user),1,function(x){paste(x,collapse ="_")}))
+```{r OMNames set 1,eval=TRUE}
+OMNames <- OMNames_user#[1:3]
+speciesNames <- gsub("OM_","",OMNames)
+speciesNames_huynh <- gsub("OM_","",OMNames_huynh)
+MSEoutNames_user1 <- paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames_user1)),
+                     "_",
+                     rep(scenNames_user1,length(OMNames))
+                     )
 
@@
 
-```{r,eval=TRUE}
-OMNames <- c("OM_BlackSeaBass","OM_VermilionSnapper","OM_RedPorgy")
-speciesNames <- gsub("OM_","",OMNames)
-```
-
-```{r plot data1, fig.cap=paste0("\\label{fig:lifeHist} Life history (growth and maturity) and vulnerability schedules at age used in the operating models for ",combine_words(speciesNames),".
-Growth is expressed as mean length-at-age relative to that at the maximum age.
-Compare with Huynh et al (2020) Figure 1."),eval=TRUE}
+```{r plot data1, fig.cap=paste0("\\label{fig:lifeHist} Life history (growth and maturity) and vulnerability schedules at age used in the operating models during the projection period ",combine_words(speciesNames),".
+Growth is expressed as mean length-at-age relative to that at the maximum age."),eval=TRUE}
 # Figure 1 from Huynh et al (2020)
@@
 
-```{r plot results1,eval=TRUE}
+```{r plot selectivities,fig.cap=paste0("\\label{fig:selex} Vulnerability schedules at age used in the operating models during the historical period (colored lines in rainbow order) and projection period (black lines)",combine_words(speciesNames),".
+Growth is expressed as mean length-at-age relative to that at the maximum age.")}
+par(mfrow=c(length(OMNames),1),mgp=c(1,0.2,0),mar=c(3,2,1.5,1),oma=c(1,2,1,1),tck=-0.01)
+for(OMName_i in OMNames){#paste0(OMNames,"_base")){
+OM_i <- get(OMName_i)
+V_i <- OM_i@cpars$V
+nyears_i <- OM_i@nyears
+proyears_i <- OM_i@proyears
+cols_i <- rainbow(nyears_i)
+matplot(V_i[1,,1:nyears_i],type="l",lty=1,col=cols_i,main=OMName_i,xlab="age",ylab="V")
+matpoints(V_i[1,,nyears_i+(1:proyears_i)],type="l",lty=1,col="black",lwd=2)
+}
+
+```
+
+```{r plot selectivities huynh,fig.cap=paste0("\\label{fig:selexhuynh} Vulnerability schedules at age used in the operating models during the historical period (colored lines in rainbow order) and projection period (black lines)",combine_words(speciesNames_huynh),".
+Growth is expressed as mean length-at-age relative to that at the maximum age."),eval=FALSE}
+par(mfrow=c(length(OMNames_huynh),1),mgp=c(1,0.2,0),mar=c(3,2,1.5,1),oma=c(1,2,1,1),tck=-0.01)
+for(OMName_i in OMNames_huynh){
+OM_i <- get(OMName_i)
+V_i <- OM_i@cpars$V
+nyears_i <- OM_i@nyears
+proyears_i <- OM_i@proyears
+cols_i <- rainbow(nyears_i)
+matplot(V_i[1,,1:nyears_i],type="l",lty=1,col=cols_i,main=OMName_i,xlab="age",ylab="V")
+matpoints(V_i[1,,nyears_i+(1:proyears_i)],type="l",lty=1,col="black",lwd=2)
+}
+
+```
+
+```{r plot Ind, eval=FALSE}
+# This code is set up to make each set of plots for each MP, but the indices are basically the same
+
+for(MP_name_i in "SCA_5"){#MPNamesAll[1]){
+    # Ind
+    plot_MSE_ts(
+      OMNames= OMNames, scenNames=scenNames_user1,
+      myvarName = expression(slot(out_i@PPD[[MP_name_i]],"Ind")),
+      plot_type = "boot",
+      FUN = mean_noNA,
+      ylabel = "index of abundance",
+      MPNamesSub = MPNamesSub_user,
+      MPNamesSub_legtext=MPNamesSub_user_legtext,
+      rowLabs=scenNames_key[scenNames_user1],
+      oma=c(3,4,5,3),
+      ylim=c(0,4)
+    )
+  title(main=MP_name_i,outer=TRUE)
+}
+```
+
+```{r plot AddInd, eval=TRUE}
+# This code is set up to make each set of plots for each MP, but the indices are basically the same
+if(plot_pdf){pdf("Figs/AddInd.pdf")}
+for(MP_name_i in "SCA_5"){#MPNamesAll){
+    # Ind
+    # MSE_i <- get(MSE_name_j)
+    plot_MSE_ts(
+      OMNames= OMNames, scenNames="base",
+      myvarName = expression(slot(out_i@PPD[[MP_name_i]],"AddInd")),
+      plot_type = "addind",
+      ylabel = "index of abundance",
+      # FUN=mean_noNA,
+      MPNamesSub = MP_name_i,
+      # MPNamesSub_legtext=MPNamesSub_user_legtext,
+      #rowLabs=scenNames_key["addind"],
+      xlabel="year",
+      oma=c(3,4,5,3),
+      ylim=c(0,8),
+      main_line = -1.5,
+      hline=NA
+    )
+  #title(main=MP_name_i,outer=TRUE)
+}
+if(plot_pdf){dev.off()}
+```
+
+```{r plot sims proj base, eval=FALSE}
+MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
+scen <- "base"
+
+for(OMName_i in OMNames_user){
+Name_i <- gsub("^OM_","",OMName_i)
+MSEoutName_i <- paste0(gsub("^OM","MSE",OMName_i),paste0("_",scen))
+MSEOut_i <- get(MSEoutName_i)
+
+figName_ij <- paste0("sims_",MSEoutName_i,"_",scen,".pdf")
+if(plot_pdf){pdf(file.path("Figs",figName_ij))}
+plot_MSE_sims(MSEOut_i,MPs=MPs_sim,type="proj",
+              lwd=2,sims=sample(1,1:50),
+              title_main = paste0(Name_i,", ",scen),
+              varNames = c("Catch","TAC","FM","F_FMSY",#"recruit",
+                           "SSB","SB_SBMSY"))
+if(plot_pdf){dev.off()}
+}
+
+```
+
+```{r plot sims base}
+MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
+scen <- "base"
+
+for(OMName_i in OMNames_user){
+Name_i <- gsub("^OM_","",OMName_i)
+MSEoutName_i <- paste0(gsub("^OM","MSE",OMName_i),paste0("_",scen))
+MSEOut_i <- get(MSEoutName_i)
+
+figName_ij <- paste0("sims_",MSEoutName_i,"_",scen,".pdf")
+if(plot_pdf){pdf(file.path("Figs",figName_ij))}
+plot_MSE_sims(MSEOut_i,MPs=MPs_sim,type="histproj",
+              lwd=2,sims=sample(1,1:50),
+              title_main = paste0(Name_i,", ",scen))
+if(plot_pdf){dev.off()}
+}
+
+```
+
+```{r plot sims minerr, eval=TRUE}
+MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
+scen <- "minerr"
+
+for(OMName_i in OMNames_user){
+Name_i <- gsub("^OM_","",OMName_i)
+MSEoutName_i <- paste0(gsub("^OM","MSE",OMName_i),paste0("_",scen))
+MSEOut_i <- get(MSEoutName_i)
+
+figName_ij <- paste0("sims_",MSEoutName_i,"_",scen,".pdf")
+if(plot_pdf){pdf(file.path("Figs",figName_ij))}
+plot_MSE_sims(MSEOut_i,MPs=MPs_sim,type="histproj",
+              lwd=2,sims=1,
+              title_main = paste0(Name_i,", ",scen))
+if(plot_pdf){dev.off()}
+}
+```
+
+```{r plot sims minrecdev}
+MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
+scen <- "minrecdev"
+
+for(OMName_i in OMNames_user){
+Name_i <- gsub("^OM_","",OMName_i)
+MSEoutName_i <- paste0(gsub("^OM","MSE",OMName_i),paste0("_",scen))
+MSEOut_i <- get(MSEoutName_i)
+
+figName_ij <- paste0("sims_",MSEoutName_i,"_",scen,".pdf")
+if(plot_pdf){pdf(file.path("Figs",figName_ij))}
+plot_MSE_sims(MSEOut_i,MPs=MPs_sim,type="histproj",
+              lwd=2,sims=1,
+              title_main = paste0(Name_i,", ",scen))
+if(plot_pdf){dev.off()}
+}
+
+# Check if assessments are converging and hessians inverting
+# unlist(lapply(MSE_BlackSeaBass_minrecdev@PPD$SCA_1@Misc,function(i){table(unlist(lapply(i$diagnostic,function(j){j$hess})))}))
+```
+
+```{r plot sims perfobs}
+MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
+scen <- "perfobs"
+
+for(OMName_i in OMNames_user){
+Name_i <- gsub("^OM_","",OMName_i)
+MSEoutName_i <- paste0(gsub("^OM","MSE",OMName_i),paste0("_",scen))
+MSEOut_i <- get(MSEoutName_i)
+
+figName_ij <- paste0("sims_",MSEoutName_i,"_",scen,".pdf")
+if(plot_pdf){pdf(file.path("Figs",figName_ij))}
+plot_MSE_sims(MSEOut_i,MPs=MPs_sim,type="histproj",
+              lwd=2,sims=1,
+              title_main = paste0(Name_i,", ",scen))
+if(plot_pdf){dev.off()}
+}
+
+```
+
+```{r plot sims "vtiv"}
+MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
+scen <- "vtiv"
+
+for(OMName_i in OMNames_user){
+Name_i <- gsub("^OM_","",OMName_i)
+MSEoutName_i <- paste0(gsub("^OM","MSE",OMName_i),paste0("_",scen))
+MSEOut_i <- get(MSEoutName_i)
+
+figName_ij <- paste0("sims_",MSEoutName_i,"_",scen,".pdf")
+#if(plot_pdf){pdf(file.path("Figs",figName_ij))}
+plot_MSE_sims(MSEOut_i,MPs=MPs_sim,type="histproj",
+              lwd=2,sims=1,
+              title_main = paste0(Name_i,", ",scen))
+#if(plot_pdf){dev.off()}
+}
+
+```
+
+```{r summary plots, eval=TRUE}
+# Summary plots combining all years and all scenarios
+
+if(plot_pdf){pdf("Figs/boxplot_P_Bgrt75BMSY.pdf")}
+P75_out <- PMsummary("P75",scenNames=scenNames_user_alt,MPs=MPNamesAll,
+                     cex.axis=1,las=2,outline=FALSE,
+                     boxwex=0.25,ylab="",ylim=c(0,1.1),
+                     hline=NA)
+mtext("P(B > 0.75 BMSY)",2,outer=TRUE,font=2)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf("Figs/boxplot_P_BgrtBMSY.pdf")}
+P100_out <- PMsummary("P100",scenNames=scenNames_user_alt,MPs=MPNamesAll,
+                     cex.axis=1,las=2,outline=FALSE,
+                     boxwex=0.25,ylab="",ylim=c(0,1.1),
+                     hline=NA)
+mtext("P(B > BMSY)",2,outer=TRUE,font=2)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf("Figs/boxplot_P_FlssFMSY.pdf")}
+PNOF_out <- PMsummary("PNOF",scenNames=scenNames_user_alt,MPs=MPNamesAll,
+                     cex.axis=1,las=2,outline=FALSE,
+                     boxwex=0.25,ylab="",ylim=c(0,1.1),
+                     hline=NA)
+mtext("P(F < FMSY)",2,outer=TRUE,font=2)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf("Figs/boxplot_AAVY.pdf")}
+AAVY_out <- PMsummary("AAVY",scenNames=scenNames_user_alt,MPs=MPNamesAll,
+                      slot_to_plot = "Stat",
+                     cex.axis=1,las=2,outline=FALSE,
+                     boxwex=0.25,ylab="",ylim=c(0,1.1),
+                     hline=NA)
+mtext("Avg. Annual Variability in Yield",2,outer=TRUE,font=2)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf("Figs/boxplot_SB_SBMSY.pdf")}
+MSEsummary("SB_SBMSY",scenNames=scenNames_user_alt,MPs=MPNamesAll,
+           cex.axis=0.75,las=2,outline=FALSE,boxwex=0.25,ylab="")
+mtext("SSB/SSBmsy",2,outer=TRUE,font=2)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf("Figs/boxplot_F_FSY.pdf")}
+MSEsummary("F_FMSY",scenNames=scenNames_user_alt,MPs=MPNamesAll,
+           cex.axis=0.75,las=2,outline=FALSE,boxwex=0.25,ylab="")
+mtext("F/Fmsy",2,outer=TRUE,font=2)
+if(plot_pdf){dev.off()}
+
+## Which is the best MP?
+
+### Highest yield
+
+### Most consistent yield
+
+### Lowest probability of overfishing
+```
+
+```{r plot time series1,eval=FALSE}
+# # VB
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user1,
+# myvarName = "VB",
+# ylabel = expression(mean~(VB)),
+# FUN = mean,
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user1]
+# )
+
+# SSB
+if(plot_pdf){pdf("Figs/ts_SSB.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user1,
+  myvarName = "SSB",
+  ylabel = expression(mean~(SSB)),
+  FUN = mean,
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user1]
+)
+if(plot_pdf){dev.off()}
+# 
+# # F
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user1,  
+# myvarName = "FM",
+# ylabel = expression(mean~(F)),
+# FUN = mean,
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user1]
+# )
+# 
+# # TAC
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user1,  
+# myvarName = "TAC",
+# ylabel = expression(mean~(TAC)),
+# FUN = mean,
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user1] 
+# )
+
+# Catch
+if(plot_pdf){pdf("Figs/ts_Catch.pdf")}
+plot_MSE_ts(
+OMNames= OMNames, scenNames=scenNames_user1,  
+myvarName = "Catch",
+ylabel = expression(mean~(Catch)),
+FUN = mean,
+MPNamesSub = MPNamesSub_user,
+MPNamesSub_legtext=MPNamesSub_user_legtext,
+rowLabs=scenNames_key[scenNames_user1]
+)
+if(plot_pdf){dev.off()}
 
 # SSB/SSBmsy
-plot_MSE_ts_Huynh(
-  OMNames= OMNames, scenNames=scenNames_user,
+if(plot_pdf){pdf("Figs/ts_SSB_SSBmsy.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user1,
   myvarName = "SB_SBMSY",
-  ylabel = expression(mean~~SSB/SSBmsy),
+  ylabel = expression(mean~(SSB/SSBmsy)),
   FUN = mean,
-  ylim=c(0,2),
+  #ylim=c(0,2),
   MPNamesSub = MPNamesSub_user,
   MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user]
+  rowLabs=scenNames_key[scenNames_user1]
+)
+if(plot_pdf){dev.off()}
+
+# F/Fmsy
+if(plot_pdf){pdf("Figs/ts_F_Fmsy.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user1,
+  myvarName = "F_FMSY",
+  ylabel = expression(mean~(F/Fmsy)),
+  FUN = mean,
+  #ylim=c(0,2),
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user1]
+)
+if(plot_pdf){dev.off()}
+
+# C/MSY
+if(plot_pdf){pdf("Figs/ts_Catch_MSY.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user1,
+  myvarName = "Catch",
+  myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+  ylabel = expression(mean~(Catch/MSY)),
+  FUN = mean,
+  #ylim=c(0,2),
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user1]
+)
+if(plot_pdf){dev.off()}
+
+# 
+# # TAC/MSY
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user1,
+#   myvarName = "TAC",
+#   myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+#   ylabel = expression(mean~(TAC/MSY)),
+#   FUN = mean,
+#   ylim=c(0,2),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user1]
+# )
+# 
+# # C/TAC
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user1,  
+#   myvarName = "Catch",
+#   myvarDenomExpr = expression(slot(out_i,"TAC")),
+#   ylabel = expression(mean~(C/TAC)),
+#   FUN = mean,
+#   ylim=c(0,1.1),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user1]
+# )
+# 
+# # MSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user1,
+# myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+# FUN = mean,
+# ylabel= expression(mean~(MSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user1]
+# )
+# 
+# # SSBMSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user1,
+# myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears)]),
+# FUN = mean,
+# ylabel= expression(mean~(SSBMSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user1]
+# )
+# 
+# # FMSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user1,
+# myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)]),
+# FUN = mean,
+# ylabel= expression(mean~(FMSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user1]
+# )
+# 
+# # UMSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user1,
+# myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)])),
+# FUN = mean,
+# ylabel= expression(mean~(UMSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user1]
+# )
+```
+
+```{r plot time series2,eval=TRUE}
+# # VB
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user2,
+# myvarName = "VB",
+# ylabel = expression(mean~(VB)),
+# FUN = mean,
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user2]
+# )
+
+# SSB
+if(plot_pdf){pdf("Figs/ts_SSB.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user2,
+  myvarName = "SSB",
+  ylabel = expression(mean~(SSB)),
+  FUN = mean,
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user2]
+)
+if(plot_pdf){dev.off()}
+# 
+# # F
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user2,  
+# myvarName = "FM",
+# ylabel = expression(mean~(F)),
+# FUN = mean,
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user2]
+# )
+# 
+# # TAC
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user2,  
+# myvarName = "TAC",
+# ylabel = expression(mean~(TAC)),
+# FUN = mean,
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user2] 
+# )
+
+# Catch
+if(plot_pdf){pdf("Figs/ts_Catch.pdf")}
+plot_MSE_ts(
+OMNames= OMNames, scenNames=scenNames_user2,  
+myvarName = "Catch",
+ylabel = expression(mean~(Catch)),
+FUN = mean,
+MPNamesSub = MPNamesSub_user,
+MPNamesSub_legtext=MPNamesSub_user_legtext,
+rowLabs=scenNames_key[scenNames_user2]
+)
+if(plot_pdf){dev.off()}
+
+# SSB/SSBmsy
+if(plot_pdf){pdf("Figs/ts_SSB_SSBmsy.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user2,
+  myvarName = "SB_SBMSY",
+  ylabel = expression(mean~(SSB/SSBmsy)),
+  FUN = mean,
+  # ylim=c(0,2),
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user2]
+)
+if(plot_pdf){dev.off()}
+
+# F/Fmsy
+if(plot_pdf){pdf("Figs/ts_F_Fmsy.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user2,
+  myvarName = "F_FMSY",
+  ylabel = expression(mean~(F/Fmsy)),
+  FUN = mean,
+  # ylim=c(0,2),
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user2]
+)
+if(plot_pdf){dev.off()}
+
+# C/MSY
+if(plot_pdf){pdf("Figs/ts_Catch_MSY.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user2,
+  myvarName = "Catch",
+  myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+  ylabel = expression(mean~(Catch/MSY)),
+  FUN = mean,
+  # ylim=c(0,2),
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user2]
+)
+if(plot_pdf){dev.off()}
+
+# 
+# # TAC/MSY
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user2,
+#   myvarName = "TAC",
+#   myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+#   ylabel = expression(mean~(TAC/MSY)),
+#   FUN = mean,
+#   ylim=c(0,2),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user2]
+# )
+# 
+# # C/TAC
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user2,  
+#   myvarName = "Catch",
+#   myvarDenomExpr = expression(slot(out_i,"TAC")),
+#   ylabel = expression(mean~(C/TAC)),
+#   FUN = mean,
+#   ylim=c(0,1.1),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user2]
+# )
+# 
+# # MSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user2,
+# myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+# FUN = mean,
+# ylabel= expression(mean~(MSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user2]
+# )
+# 
+# # SSBMSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user2,
+# myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears)]),
+# FUN = mean,
+# ylabel= expression(mean~(SSBMSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user2]
+# )
+# 
+# # FMSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user2,
+# myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)]),
+# FUN = mean,
+# ylabel= expression(mean~(FMSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user2]
+# )
+# 
+# # UMSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user2,
+# myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)])),
+# FUN = mean,
+# ylabel= expression(mean~(UMSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user2]
+# )
+```
+
+```{r plot time series RE,eval=FALSE}
+# # VB
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user1,
+# myvarName = "VB",
+# ylabel = expression(RE~(mean~(VB))),
+# FUN = mean, MPNamesRef = "SCA_1",
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user1]
+# )
+
+# SSB
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user1,
+  myvarName = "SSB",
+  ylabel = expression(RE~(mean~(SBB))),
+  FUN = mean, MPNamesRef = "SCA_1",
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user1],
+  ylim=c(-0.5,0.5)
+)
+# 
+# # F
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user1,  
+# myvarName = "FM",
+# ylabel = expression(RE~(mean~(F))),
+# FUN = mean, MPNamesRef = "SCA_1",
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user1]
+# )
+# 
+# # TAC
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user1,  
+# myvarName = "TAC",
+# ylabel = expression(RE~(mean~(TAC))),
+# FUN = mean, MPNamesRef = "SCA_1",
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user1] 
+# )
+
+# Catch
+plot_MSE_ts(
+OMNames= OMNames, scenNames=scenNames_user1,  
+myvarName = "Catch",
+ylabel = expression(RE~(mean~(Catch))),
+FUN = mean, MPNamesRef = "SCA_1",
+MPNamesSub = MPNamesSub_user,
+MPNamesSub_legtext=MPNamesSub_user_legtext,
+rowLabs=scenNames_key[scenNames_user1],
+ylim=c(-0.5,0.5)
+)
+
+# SSB/SSBmsy
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user1,
+  myvarName = "SB_SBMSY",
+  ylabel = expression(RE~(mean~(SSB/SSBmsy))),
+  FUN = mean, MPNamesRef = "SCA_1",
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user1],
+  ylim=c(-0.5,0.5),
+  hline=NA
 )
@@
 # F/Fmsy
-plot_MSE_ts_Huynh(
-  OMNames= OMNames, scenNames=scenNames_user,
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user1,
   myvarName = "F_FMSY",
-  ylabel = expression(mean~~F/Fmsy),
-  FUN = mean,
-  ylim=c(0,2),
+  ylabel = expression(RE~(mean~(F/Fmsy))),
+  FUN = mean, MPNamesRef = "SCA_1",
   MPNamesSub = MPNamesSub_user,
-  rowLabs=scenNames_key[scenNames_user]
+  rowLabs=scenNames_key[scenNames_user1],
+  ylim=c(-1,1.5),
+  hline=NA
 )
@@
 # C/MSY
-plot_MSE_ts_Huynh(
-  OMNames= OMNames, scenNames=scenNames_user,
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user1,
   myvarName = "Catch",
   myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
-  ylabel = expression(mean~~Catch/MSY),
-  FUN = mean,
-  ylim=c(0,2),
+  ylabel = expression(RE~(mean~(Catch/MSY))),
+  FUN = mean, MPNamesRef = "SCA_1",
   MPNamesSub = MPNamesSub_user,
   MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user]
+  rowLabs=scenNames_key[scenNames_user1],
+  ylim=c(-0.5,0.5)
 )
 
-# TAC/MSY
-plot_MSE_ts_Huynh(
-  OMNames= OMNames, scenNames=scenNames_user,
-  myvarName = "TAC",
-  myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
-  ylabel = "TAC/MSY",
-  FUN = mean,
-  ylim=c(0,4),
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user]
+# 
+# # TAC/MSY
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user1,
+#   myvarName = "TAC",
+#   myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+#   ylabel = expression(RE~(mean~(TAC/MSY))),
+#   FUN = mean, MPNamesRef = "SCA_1",
+#   ylim=c(0,2),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user1],
+#   ylim=c(-0.5,0.5),
+#   hline=NA
+# )
+# 
+# # C/TAC
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user1,  
+#   myvarName = "Catch",
+#   myvarDenomExpr = expression(slot(out_i,"TAC")),
+#   ylabel = expression(RE~(mean~(C/TAC))),
+#   FUN = mean, MPNamesRef = "SCA_1",
+#   ylim=c(0,1.1),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user1],
+#   ylim=c(-0.5,0.5),
+#   hline=NA
+# )
+# 
+# # MSY
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user1,
+#   myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+#   FUN = mean, MPNamesRef = "SCA_1",
+#   ylabel= expression(RE~(mean~(MSY))),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user1],
+#   ylim=c(-0.5,0.5),
+#   hline=NA
+# )
+# 
+# # SSBMSY
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user1,
+#   myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears)]),
+#   FUN = mean, MPNamesRef = "SCA_1",
+#   ylabel= expression(RE~(mean~(SSBMSY))),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user1],
+#   ylim=c(-0.5,0.5),
+#   hline=NA
+# )
+# 
+# # FMSY
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user1,
+#   myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)]),
+#   FUN = mean, MPNamesRef = "SCA_1",
+#   ylabel= expression(RE~(mean~(FMSY))),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user1],
+#   ylim=c(-0.5,0.5),
+#   hline=NA
+# )
+# 
+# # UMSY
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user1,
+#   myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)])),
+#   FUN = mean, MPNamesRef = "SCA_1",
+#   ylabel= expression(RE~(mean~(UMSY))),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user1],
+#   ylim=c(-0.5,0.5),
+#   hline=NA
+# )
+```
+
+```{r plot dot and whiskers, eval=FALSE}
+plot_MSE_dw(
+    OMNames= OMNames, scenNames=scenNames_user1,
+    myvarName = "SSB",
+    ylabel = expression(cv~(SSB)),
+    FUN = cv,
+    MPNamesSub = MPNamesAll,
+    MPNamesSub_legtext=MPNamesAll_legtext,
+    rowLabs=scenNames_key[scenNames_user1]
 )
 
-# C/TAC
-plot_MSE_ts_Huynh(
-  OMNames= OMNames, scenNames=scenNames_user,  
+plot_MSE_dw(
+    OMNames= OMNames, scenNames=scenNames_user1,
     myvarName = "Catch",
-  myvarDenomExpr = expression(slot(out_i,"TAC")),
-  ylabel = expression(mean~~C/TAC),
-  FUN = mean,
-  ylim=c(0,1.1),
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user]
-)
-
-# SSB
-plot_MSE_ts_Huynh(
-  OMNames= OMNames, scenNames=scenNames_user,
-  myvarName = "SSB",
-  ylabel = expression(mean~~SSB),
-  FUN = mean,
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user]
-)
-
-# VB
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,
-myvarName = "VB",
-ylabel = expression(mean~~VB),
-FUN = mean,
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user]
-)
-
-# F
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,  
-myvarName = "FM",
-ylabel = expression(mean~~F),
-FUN = mean,
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user]
-)
-
-# Catch
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,  
-myvarName = "Catch",
-ylabel = expression(mean~~Catch),
-FUN = mean,
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user]
-)
-
-# TAC
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,  
-myvarName = "TAC",
-FUN = mean,
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user] 
-)
-
-# MSY
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,
-myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
-FUN = mean,
-ylabel="MSY",
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user]
-)
-
-# SSBMSY
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,
-myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears)]),
-FUN = mean,
-ylabel="SSBMSY",
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user]
-)
-
-# FMSY
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,
-myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)]),
-FUN = mean,
-ylabel="FMSY",
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user]
-)
-
-# UMSY
-plot_MSE_ts_Huynh(
-OMNames= OMNames, scenNames=scenNames_user,
-myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)])),
-FUN = mean,
-ylabel="UMSY",
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user]
+    myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+    ylabel = expression(geomean~(Catch/MSY)),
+    FUN = geomean,
+    MPNamesSub = MPNamesAll,
+    MPNamesSub_legtext=MPNamesAll_legtext,
+    rowLabs=scenNames_key[scenNames_user1],
+    ylim = c(0,1)
 )
@@
 ```
+
+```{r MSEtool tradeoff plots, eval=FALSE}
+# MSEtool Tradeoff plots
+for(outName_i in MSEoutNames_user1){
+out_i <- get(outName_i)  
+par(oma=c(1,1,2,1))  
+MSEtool::TradePlot(out_i)
+}
+```
+
+\clearpage
+
+# Tradeoff plots
+
+```{r tradeoffPlot1, eval=FALSE}
+if(plot_pdf){pdf("Figs/tradeoffPlot1.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user1,
+  # MPNamesRef = "SCA_1",
+  plot_type = "tradeoff",
+  PMx = Yield,
+  MPNamesSub = MPNamesAll,
+  MPNamesSub_legtext=MPNamesAll,
+  rowLabs=scenNames_key[scenNames_user1],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,1.1),ylim=c(0,1.1),
+  hline=NA
+)
+if(plot_pdf){dev.off()}
+```
+
+\clearpage
+
+```{r tradeoffPlot2, eval=FALSE}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user1,
+  # MPNamesRef = "SCA_1",
+  plot_type = "tradeoff",
+  PMx = PNOF,
+  #proyear_phase=20,
+  MPNamesSub = MPNamesAll,
+  MPNamesSub_legtext=MPNamesAll,
+  rowLabs=scenNames_key[scenNames_user1],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,1.1),ylim=c(0,1.1),
+  hline=NA
+)
+
+```
+\clearpage
+
+```{r tradeoffPlot3, eval=FALSE}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user1,
+  # MPNamesRef = "SCA_1",
+  plot_type = "tradeoff",
+  PMx = AAVY10,
+  #proyear_phase=20,
+  MPNamesSub = MPNamesAll,
+  MPNamesSub_legtext=MPNamesAll,
+  rowLabs=scenNames_key[scenNames_user1],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,1.1),ylim=c(0,1.1),
+  hline=NA
+)
+```
+
+```{r tradeoffPlot4, eval=FALSE}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user1,
+  # MPNamesRef = "SCA_1",
+  plot_type = "tradeoff",
+  PMx = AAVY10,
+  PMy = PNOF,
+  #proyear_phase=20,
+  MPNamesSub = MPNamesAll,
+  MPNamesSub_legtext=MPNamesAll,
+  rowLabs=scenNames_key[scenNames_user1],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,1.1),ylim=c(0,1.1),
+  hline=NA
+)
+
+```
+
+\clearpage
+
+# Phase plots
+
+```{r phase plots}
+if(plot_pdf){pdf("Figs/phasePlot1.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user1,
+  plot_type = "phase",
+  #proyear_phase=50,
+  MPNamesSub = c(MPNamesSub_user),
+  MPNamesSub_legtext=c(MPNamesSub_user_legtext),
+  rowLabs=scenNames_key[scenNames_user1],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,5),ylim=c(0,5),
+  hline=NA
+)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf("Figs/phasePlot2.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user2,
+  plot_type = "phase",
+  #proyear_phase=50,
+  MPNamesSub = c(MPNamesSub_user),
+  MPNamesSub_legtext=c(MPNamesSub_user_legtext),
+  rowLabs=scenNames_key[scenNames_user2],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,5),ylim=c(0,5),
+  hline=NA
+)
+if(plot_pdf){dev.off()}
+```

### 2022-03-16 RunMSE/SEFSC/Manuscript/MainText.Rnw
updated rds files

\documentclass[12pt,english]{article}
%%% PREAMBLE

%%% Install missing packages %%%
% tinytex::parse_install("MainText.log")

% Sometimes you have to run: tinytex::install_tinytex()
% and maybe: tlmgr_update()

\usepackage{bbding} % for checkmark symbol
\usepackage{booktabs}
%\usepackage{chngcntr} % Allows table and figure counters to be reset in Appendix
\usepackage[font=small,format=hang,justification=raggedright,labelfont=up,labelsep=space,singlelinecheck=false]{caption}
\usepackage{color} % use to color text
\usepackage[T1]{fontenc}
\usepackage{geometry} % set margins and stuff
\usepackage{graphicx}
\usepackage{lineno}
\usepackage{longtable}
\usepackage{microtype}
\usepackage{pdflscape} % Causes pages that are in landscape format to be rotated when viewing the pdf but print as usual
\usepackage{scrextend} % Allows you to change margins for section of text
\usepackage{setspace}
\usepackage{siunitx}
\usepackage{titlesec}
\usepackage[dvipsnames]{xcolor} % use to get more colors

%\DisableLigatures{encoding = *, family = *}
\DisableLigatures[f]{encoding = *, family = *} %% <- only disables f-ligatures

\PassOptionsToPackage{hyphens}{url}\usepackage[hidelinks]{hyperref} % enables hyperlinks
\urlstyle{same} % Maintains URLs in the same font as the rest of the text

% Bibliography related
\usepackage{natbib}                            % For citations
\bibpunct{(}{)}{;}{a}{}{;}
\setlength{\bibhang}{2em}

%\addbibresource{KlibanskyFishResearch_1.5}
%\graphicspath{ {images/} }
\geometry{verbose,letterpaper,tmargin=2.54cm,bmargin=2.54cm,lmargin=2.54cm,rmargin=2.54cm}
%\linenumbers

\captionsetup{figurename=Fig.}

% Define heading formatting
\titleformat{\section}
   {\small\mdseries\scshape}{\thesection}{1em}{}

\titleformat{\subsection}
   {\small\mdseries\itshape}{\thesubsection}{1em}{}

%%% Main document
% BEGIN DOCUMENT
\begin{document}
\SweaveOpts{concordance=TRUE}

<<setup, include=FALSE, cache=FALSE, echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figures/plots-', fig.align='center', fig.show='hold', eval=TRUE, echo=FALSE)
#options(replace.assign=TRUE,width=80)
Sys.setenv(TEXINPUTS=getwd(),
           BIBINPUTS=getwd(),
           BSTINPUTS=getwd())
@

<<admin, echo=FALSE,warning=FALSE,message=FALSE>>=
#load("../.RData")
library(english) # For english() function which converts numbers to words
library(Hmisc)
library(stringr)
library(tinytex)
# tinytex::tlmgr_update()
# tinytex::reinstall_tinytex()
dir_figs <- "../Figs"
@

<<latexTable, echo=FALSE>>=

@

<<parsForText, echo=FALSE>>=
# my wrapper function for formatting numbers with commas separating thousands
tn <- function(x){
  prettyNum(x,big.mark=",",scientific=FALSE)
  }

# Update these later based on saved results
n_sp <- english(3)
n_scen <- 10
n_MP <- 13

@

% Top matter
\title{Evaluating procedures for updating catch advice between stock assessments of reef fishes with management strategy evaluation}
\author{Nikolai Klibansky,  Shannon Calay, Rob Cheshire,\\
Cassidy Peterson, Kyle Shertzer, Erik Williams, and Matt Vincent\\\\
Southeast Fisheries Science Center, \\
National Marine Fisheries Service, NOAA,\\
101 Pivers Island Road, Beaufort, North Carolina, 28516, USA}
\maketitle

\begin{abstract}
We built operating models for \Sexpr{n_sp} reef fish species from the US Southeast Atlantic, based on recent stock assessments. We developed \Sexpr{n_scen} scenerios and \Sexpr{n_MP} management procedures. Management procedures varied in terms of how often stock assessments were conducted, and how catch advice was adjusted between stock assessments.

\end{abstract}

\begin{flushleft}
\begin{spacing}{1.9}
\setlength{\parindent}{1cm} % Indent paragraphs after the first one

\section*{Introduction}
We can only do stock assessments every few years. It would be nice to know if there were ways that we could adjust catch advice between stock assessments to improve.

\section*{Materials and Methods}
We used the most recent stock assessments from US Southeast US Atlantic for Red Porgy, Black Sea Bass, and Vermilion Snapper.

\subsection{Evaluating management procedures}

\section*{Results}

\section*{Discussion}

Some broad conclusions

Which factors seem to account for the most variation in results in general?
\begin{itemize}
\item Above all, results differ between operating models (i.e. species)
\item Scenario is the next most important factor, particularly depletion scenarios and regime change
\end{itemize}

\section*{Acknowledgements}
We thank everyone.

\end{spacing}
\end{flushleft}

% \printbibliography
%%% LITERATURE CITED %%%
%\printbibliography
\clearpage
\section*{Literature Cited}
\renewcommand{\refname}{}
\bibliographystyle{ecosphere} % Modified from ecology.bst
\vspace{-1cm}

\bibliography{KlibanskyFishResearch_1.5}

%% TABLES
\newpage
\section*{Tables}

%\input{../Results/biodivByArea.tex}
%\clearpage

%% FIGURES %%
\newpage
\section*{Figures}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in,height=7in]{../Figs/AddInd.pdf}
\end{center}
\begin{flushleft}
\caption{Indices derived from BAM stock assessments available during the projection period, for the SCA\_5 MP in the Base scenario. Shaded areas represent 95\% CI for indices among simulation runs.}
\label{fig:phasePlot1}
\end{flushleft}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in,height=7in]{../Figs/phasePlot1.pdf}
\end{center}
\begin{flushleft}
\caption{Phase plots for the base scenario and the first set of experimental scenarios}
\label{fig:phasePlot1}
\end{flushleft}
\end{figure}

% \begin{figure}[!ht]
% \begin{center}
% \includegraphics[width=6in,height=7in]{../Figs/phasePlot2.pdf}
% \end{center}
% \begin{flushleft}
% \caption{Phase plots for the base scenario and the second set of experimental scenarios}
% \label{fig:phasePlot2}
% \end{flushleft}
% \end{figure}

%% APPENDIX
% \begin{appendix}
%
% \clearpage
% \section*{Appendix S1}
%
% \setcounter{table}{0}
% \renewcommand{\thetable}{S\arabic{table}}
%
% \input{../Results/Appendix.tex}
%
% \input{../Results/biodivByBlock.tex}
%
% \end{appendix}

% END DOCUMENT
\end{document}

### 2022-03-16 RunMSE/SEFSC/Manuscript/MainText.tex
updated rds files

--- 2022-03-16 RunMSE/SEFSC/Manuscript/MainText.Rnw
@@
 % BEGIN DOCUMENT
+\usepackage{Sweave}
 \begin{document}
-\SweaveOpts{concordance=TRUE}
-
-<<setup, include=FALSE, cache=FALSE, echo=FALSE>>=
-library(knitr)
-opts_chunk$set(fig.path='figures/plots-', fig.align='center', fig.show='hold', eval=TRUE, echo=FALSE)
-#options(replace.assign=TRUE,width=80)
-Sys.setenv(TEXINPUTS=getwd(),
-           BIBINPUTS=getwd(),
-           BSTINPUTS=getwd())
-@
-
-<<admin, echo=FALSE,warning=FALSE,message=FALSE>>=
-#load("../.RData")
-library(english) # For english() function which converts numbers to words
-library(Hmisc)
-library(stringr)
-library(tinytex)
-# tinytex::tlmgr_update()
-# tinytex::reinstall_tinytex()
-dir_figs <- "../Figs"
-@
-
-<<latexTable, echo=FALSE>>=
-
-@
-
-<<parsForText, echo=FALSE>>=
-# my wrapper function for formatting numbers with commas separating thousands
-tn <- function(x){
-  prettyNum(x,big.mark=",",scientific=FALSE)
-  }
-
-# Update these later based on saved results
-n_sp <- english(3)
-n_scen <- 10
-n_MP <- 13
-
-@
+\input{MainText-concordance}
 
@@
 \begin{abstract}
-We built operating models for \Sexpr{n_sp} reef fish species from the US Southeast Atlantic, based on recent stock assessments.
-We developed \Sexpr{n_scen} scenerios and \Sexpr{n_MP} management procedures.
+We built operating models for three reef fish species from the US Southeast Atlantic, based on recent stock assessments.
+We developed 10 scenerios and 13 management procedures.
 Management procedures varied in terms of how often stock assessments were conducted, and how catch advice was adjusted between stock assessments.

### 2022-03-16 RunMSE/SEFSC/fn/MP_wrapper.R

@@ -1,29 +1,0 @@
-# Script copied 2022-02-25 from: https://github.com/Blue-Matter/WSKJ/blob/master/03a_MPs.R#L6
-# Author: Quang Huynh
-
-# MP wrapper that puts the BB fleet in Data@Ind
-MP_wrapper <- function(MP, delay = 2, ...) {
-  MP <- substitute(MP)
-  MP_call <- as.call(c(MP, x = quote(x), Data = quote(Data), reps = quote(reps), list(...)))
-  force(delay)
-
-  MP_body <- bquote({
-    Data@Ind <- Data@AddInd[, 1, ]
-    Data@CV_Ind <- Data@CV_AddInd[, 1, ]
-    if(delay > 0) {
-      delay_ind <- seq(ncol(Data@Cat) - delay + 1, ncol(Data@Cat), 1)
-      Data@Ind <- Data@Ind[, -delay_ind]
-      Data@CV_Ind <- Data@CV_Ind[, -delay_ind]
-      Data@Cat <- Data@Cat[, -delay_ind, drop = FALSE]
-      Data@CV_Cat <- Data@CV_Cat[, -delay_ind, drop = FALSE]
-      Data@Year <- Data@Year[-delay_ind]
-    }
-    Rec <- .(MP_call)
-    return(Rec)
-  })
-
-  MP_out <- eval(call("function", as.pairlist(alist(x = 1, Data = , reps = 1)), MP_body))
-  class(MP_out) <- "MP"
-  return(MP_out)
-}
-

### 2022-03-16 RunMSE/SEFSC/fn/MP_wrapper_development.R

@@ -1,48 +1,0 @@
-
-MP=SCA; lag = 2; Data <- rdat_to_Data(rdat_BlackSeaBass)
-
-# MP wrapper that puts the BB fleet in Data@Ind
-MP_wrapper <- function(MP, lag = 2, ...) {
-  MP <- substitute(MP)
-  MP_call <- as.call(c(MP, x = quote(x), Data = quote(Data), reps = quote(reps), list(...)
-                       )
-                     )
-  force(lag)
-
-  MP_body <- bquote({
-    Data@Ind <- Data@AddInd[, 1, ]
-    Data@CV_Ind <- Data@CV_AddInd[, 1, ]
-    if(lag > 0) {
-      lag_ind <- seq(ncol(Data@Cat) - lag + 1, ncol(Data@Cat), 1)
-      Data@Ind <- Data@Ind[, -lag_ind]
-      Data@CV_Ind <- Data@CV_Ind[, -lag_ind]
-      Data@Cat <- Data@Cat[, -lag_ind, drop = FALSE]
-      Data@CV_Cat <- Data@CV_Cat[, -lag_ind, drop = FALSE]
-      Data@Year <- Data@Year[-lag_ind]
-    }
-    Rec <- .(MP_call)
-    return(Rec)
-  })
-
-  MP_out <- eval(call("function", as.pairlist(alist(x = 1, Data = , reps = 1)), MP_body))
-  class(MP_out) <- "MP"
-  return(MP_out)
-}
-
-MP_wrapper2 <- function(MP, lag = 3, ...) {
-  MP <- substitute(MP)
-  MP_call <- as.call(c(MP, x = quote(x), Data = quote(Data), reps = quote(reps), list(...)
-  )
-  )
-  force(lag)
-
-  MP_body <- bquote({
-    Data <- Data_sub_dim(Data,nyr_rm=lag)
-    Rec <- .(MP_call)
-    return(Rec)
-  })
-
-  MP_out <- eval(call("function", as.pairlist(alist(x = 1, Data = , reps = 1)), MP_body))
-  class(MP_out) <- "MP"
-  return(MP_out)
-}

### 2022-03-16 RunMSE/SEFSC/fn/iMP.R

@@ -1,11 +1,11 @@
 # Define custom stock assessment function
-MP_args <- list(.Assess = "SCA_lag", .HCR = "HCR_MSY", MSY_frac = 1, AddInd = 1)
+MP_args <- list(.Assess = "SCA_lag", .HCR = "HCR_MSY", MSY_frac = MSY_frac, AddInd = 1)
 BAM_SCA_args <- list(SR="BH",
                      vulnerability = "logistic",
                      early_dev = "comp_onegen",
                      late_dev = "comp50",
                      CAA_dist = "multinomial",
-                     lag=lag)
+                     lag=lag_Assess)
 
 # Averaged Index and Buffered Index MPs with (numbers indicate assessment interval)
 iMP_avg_5 <- do.call(make_interim_MP_lag,
@@ -26,7 +26,7 @@ iMP_buffer_5 <-  do.call(make_interim_MP_lag,
 iMP_buffer_10 <-  do.call(make_interim_MP_lag,
                            c(list(assessment_interval = 10, type = "buffer", type_par = 1),
                              MP_args, BAM_SCA_args)
-)
+                          )
 
 # Fixed TAC MPs (numbers indicate assessment interval) and annual assessment MPs
 SCA_5 <- SCA_10 <- SCA_1 <- do.call(make_MP,
@@ -34,5 +34,11 @@ SCA_5 <- SCA_10 <- SCA_1 <- do.call(make_MP,
                                       MP_args, BAM_SCA_args)
                                     )
 # Projection MPs
-# pMP_5 <- make_projection_MP(assessment_interval = 5)
-# pMP_10 <- make_projection_MP(assessment_interval = 10)
+pMP_5 <- do.call(make_projection_MP_lag,
+                 c(list(assessment_interval = 5,process_error = NULL, p_sim = 1),
+                   MP_args, BAM_SCA_args)
+                 )
+pMP_10 <- do.call(make_projection_MP_lag,
+                 c(list(assessment_interval = 10,process_error = NULL, p_sim = 1),
+                   MP_args, BAM_SCA_args)
+)

### 2022-03-16 RunMSE/SEFSC/fn/iMP_nolag.R

@@ -1,37 +1,43 @@
-# Redefine MPs to use all additional indices in stock assessments
-
 # Define custom stock assessment function
+MP_args <- list(.Assess = "SCA", .HCR = "HCR_MSY", MSY_frac = MSY_frac, AddInd = 1)
 BAM_SCA_args <- list(SR="BH",
                      vulnerability = "logistic",
                      early_dev = "comp_onegen",
                      late_dev = "comp50",
-                     CAA_dist = "multinomial",
-                     AddInd = AddInd_colnums,
-                     lag=2)
+                     CAA_dist = "multinomial")
 
 # Averaged Index and Buffered Index MPs with (numbers indicate assessment interval)
-iMP_avg_5 <- do.call(make_interim_MP_lag,
+iMP_avg_5 <- do.call(make_interim_MP,
                      c(list(assessment_interval = 5,type = "mean", type_par = 3),
                        MP_args, BAM_SCA_args)
                      )
 
-iMP_avg_10 <- do.call(make_interim_MP_lag,
+iMP_avg_10 <- do.call(make_interim_MP,
                       c(list(assessment_interval = 10,type = "mean", type_par = 3),
                         MP_args, BAM_SCA_args)
                       )
 
-iMP_buffer_5 <-  do.call(make_interim_MP_lag,
+iMP_buffer_5 <-  do.call(make_interim_MP,
                          c(list(assessment_interval = 5, type = "buffer", type_par = 1),
                            MP_args, BAM_SCA_args)
                          )
 
-iMP_buffer_10 <-  do.call(make_interim_MP_lag,
+iMP_buffer_10 <-  do.call(make_interim_MP,
                            c(list(assessment_interval = 10, type = "buffer", type_par = 1),
                              MP_args, BAM_SCA_args)
-)
+                          )
 
 # Fixed TAC MPs (numbers indicate assessment interval) and annual assessment MPs
 SCA_5 <- SCA_10 <- SCA_1 <- do.call(make_MP,
                                     c(list(diagnostic = "min"),
                                       MP_args, BAM_SCA_args)
                                     )
+# Projection MPs
+pMP_5 <- do.call(make_projection_MP,
+                 c(list(assessment_interval = 5,process_error = NULL, p_sim = 1),
+                   MP_args, BAM_SCA_args)
+                 )
+pMP_10 <- do.call(make_projection_MP,
+                 c(list(assessment_interval = 10,process_error = NULL, p_sim = 1),
+                   MP_args, BAM_SCA_args)
+)

### 2022-03-16 RunMSE/SEFSC/fn/make_interim_MP_lag.R

@@ -1,6 +1,3 @@
-
-
-
 make_interim_MP_lag <- function (.Assess = "SCA",
                                  .HCR = "HCR_MSY",
                                  AddInd = "VB",
@@ -52,7 +49,7 @@ make_interim_MP_lag <- function (.Assess = "SCA",
   MP_body <- bquote({
     dependencies <- .(SAMtool:::get_dependencies(Assess_char, dots))
     ny <- length(Data@Year)      # Number of years in available Data object
-    ny_Assess <- ny- .(lag)           # Number of year of Data available for assessment
+    #ny_Assess <- ny- .(lag)           # Number of year of Data available for assessment
     Current_Yr <- Data@Year[ny]  # Current year
     first_assess_yr <- Current_Yr == Data@LHYear # Is the current year the last year of available data?
     run_assessment <- first_assess_yr || Current_Yr == Data@Misc[[x]]$interim$next_assess_yr # Should the assessment be run?

### 2022-03-16 RunMSE/SEFSC/fn/make_projection_MP.R

@@ -1,10 +1,0 @@
-# Author: Quang Huynh
-
-make_projection_MP <- function(...) {
-  fn <- projection_MP
-  dots <- list(...)
-  arg_ind <- pmatch(names(dots), names(formals(fn)))
-  formals(fn)[arg_ind] <- dots
-  class(fn) <- "MP"
-  return(fn)
-}

### 2022-03-16 RunMSE/SEFSC/fn/make_projection_MP_NK.R

@@ -1,143 +1,0 @@
-# Author: Quang Huynh
-# Modified and totally wrecked: Nikolai Klibansky
-# I was trying to modify this code to make it usable with the current version of openMSE, but there are some settings
-# I don't readily understand and Quang says he can probably code it up pretty quickly. So I'm giving up
-
-
-make_projection_MP <- function (.Assess = "SCA",
-                                .HCR = "HCR_MSY",
-                                AddInd = 1,
-                                assessment_interval = 5,
-                                diagnostic = c("min", "full","none"),
-                                ...) {
-  diagnostic <- match.arg(diagnostic)
-  if (is.character(.Assess)) {
-    Assess_char <- .Assess
-    .Assess <- as.symbol(.Assess)
-  }
-  else {
-    .Assess <- substitute(.Assess)
-    Assess_char <- as.character(.Assess)
-  }
-  if (is.character(.HCR)) {
-    .HCR <- as.symbol(.HCR)
-  }
-  else {
-    .HCR <- substitute(.HCR)
-  }
-  if (!inherits(eval(.Assess), "Assess")) {
-    stop(paste(.Assess, "does not belong to class 'Assess'. Use: avail('Assess') to find eligible objects."))
-  }
-  if (!inherits(eval(.HCR), "HCR")) {
-    stop(paste(.HCR, "does not belong to class 'HCR.' Use: avail('HCR') to find eligible objects."))
-  }
-  dots <- list(...)
-  dots$AddInd <- AddInd
-
-  if(!is.null(dots$lag)){
-    lag <- dots$lag
-  }else{
-    lag <- 0
-  }
-
-  dots_in_Assess <- dots[match(names(formals(eval(.Assess))),
-                               names(dots), nomatch = 0)]
-  dots_in_HCR <- dots[match(names(formals(eval(.HCR))), names(dots),
-                            nomatch = 0)]
-  Assess_call <- as.call(c(.Assess, x = quote(x), Data = quote(Data),
-                           dots_in_Assess))
-  HCR_call <- as.call(c(.HCR, Assessment = quote(do_Assessment),
-                        reps = quote(reps), dots_in_HCR))
-  MP_body <- bquote({
-    dependencies <- .(SAMtool:::get_dependencies(Assess_char, dots))
-    ny <- length(Data@Year)      # Number of years in available Data object
[…]

### 2022-03-16 RunMSE/SEFSC/fn/make_projection_MP_lag.R

@@ -1,0 +1,83 @@
+make_projection_MP_lag <- function (.Assess = "SCA",
+                                    .HCR = "HCR_MSY",
+                                    assessment_interval = 5,
+                                    Ftarget = expression(Assessment@FMSY),
+                                    proj_args = list(process_error = 1, p_sim = 1),
+                                    diagnostic = c("min", "full", "none"),
+                                    ...)
+{
+  diagnostic <- match.arg(diagnostic)
+  if (is.character(.Assess)) {
+    Assess_char <- .Assess
+    .Assess <- as.symbol(.Assess)
+  }
+  else {
+    .Assess <- substitute(.Assess)
+    Assess_char <- as.character(.Assess)
+  }
+  if (!inherits(eval(.Assess), "Assess")) {
+    stop(paste(.Assess, "does not belong to class 'Assess'. Use: avail('Assess') to find eligible objects."))
+  }
+  dots <- list(...)
+
+  if(!is.null(dots$lag)){
+    lag <- dots$lag
+  }else{
+    lag <- 0
+  }
+
+  dots_in_Assess <- dots[match(names(formals(eval(.Assess))),
+                               names(dots), nomatch = 0)]
+  Assess_call <- as.call(c(.Assess, x = quote(x), Data = quote(Data),
+                           dots_in_Assess))
+  proj_args <- proj_args[match(names(formals(projection)),
+                               names(proj_args), nomatch = 0)]
+  proj_args$p_years <- assessment_interval + 1
+  proj_call <- as.call(c(substitute(projection), Assessment = quote(Assessment),
+                         Ftarget = quote(eval(Ftarget)), proj_args))
+  MP_body <- bquote({
+    dependencies <- .(SAMtool:::get_dependencies(Assess_char, dots))
+    ny <- length(Data@Year)
+    ny_Assess <- ny- .(lag)           # Number of year of Data available for assessment
+    Current_Yr <- Data@Year[ny]
+    first_assess_yr <- Current_Yr == Data@LHYear
+    run_assessment <- first_assess_yr || Current_Yr == Data@Misc[[x]]$proj$next_assess_yr
+    get_projection <- !run_assessment
+    Rec <- new("Rec")
+    if (run_assessment) {
+      Assessment <- .(Assess_call)
+      if (diagnostic != "none") {
+        Rec@Misc <- SAMtool:::Assess_diagnostic(x, Data, Assessment,
+                                      include_assessment = .(diagnostic == "full"))
[…]

### 2022-03-16 RunMSE/SEFSC/fn/projection_MP.R

@@ -1,61 +1,0 @@
-# Author: Quang Huynh
-
-projection_MP <- eval(bquote(function(x, Data, reps = 1, assessment_interval, HCR = HCR_MSY, SCA_arg = list(I_type = "VB", CAA_multiplier = 20)) {
-  dependencies <- .(SAMtool:::get_dependencies("SCA_Pope"))
-
-  current_yr <- Data@Year[length(Data@Year)]
-  run_SCA <- current_yr == Data@LHYear
-  if (current_yr > Data@LHYear) {
-    run_SCA <- current_yr == Data@Misc[[x]]$next_assess_yr
-  }
-  if (!run_SCA) get_projected_TAC <- TRUE else get_projected_TAC <- FALSE
-
-  if (run_SCA) {
-    # Return TAC = UMSY * VB_current when run_SCA = TRUE
-    SCA_formals <- list(x = x, Data = Data)
-    do_Assessment <- do.call(SCA_Pope, c(SCA_formals, SCA_arg))
-    Assess_output <- Assess_diagnostic(x, Data, do_Assessment, include_assessment = FALSE)
-
-    if (do_Assessment@conv) {
-      Rec <- do.call(match.fun(HCR), list(Assessment = do_Assessment, reps = reps))
-      pro <- projection(do_Assessment, FMort = do_Assessment@UMSY, p_years = 52, p_sim = 1, obs_error = c(0, 0), process_error = 0)
-      Rec@Misc <- c(list(project_catch = pro@Catch[1, ], last_assess_yr = current_yr, next_assess_yr = current_yr + assessment_interval), Assess_output)
-
-      get_projected_TAC <- FALSE
-
-    } else {
- 
-      if (current_yr == Data@LHYear || length(Data@Misc[[x]]) == 2) {
-        Rec <- new("Rec")
-        Rec@TAC <- TACfilter(rep(NA, reps))
-        Rec@Misc <- c(list(next_assess_yr = current_yr + 1), Assess_output)
-
-        get_projected_TAC <- FALSE
-      } else {
-        get_projected_TAC <- TRUE
-        next_assess_yr <- current_yr + 1
-      }
-    }
-  }
-
-  if (get_projected_TAC) {
-    Rec <- new("Rec")
-    TAC_used <- Data@Misc[[x]]$project_catch[current_yr - Data@Misc[[x]]$last_assess_yr + 1]
-    if(is.infinite(TAC_used) || is.na(TAC_used)) stop("Error in TAC during interim")
[…]

### 2022-03-16 RunMSE/SEFSC/plot_MSE_ts_args_example.R

@@ -1,0 +1,321 @@
+OMNames= OMNames
+scenNames=scenNames_user
+myvarName="Catch"
+myvarDenomExpr = NULL
+ylabel = myvarName
+FUN = mean
+#sims = NULL # which simulation runs should be plotted?
+sims = 1:3
+MPNamesSub = "SCA_1"#MPNamesSub_user
+MPNamesSub_legtext="Annual assessment"#MPNamesSub_user_legtext
+rowLabs=scenNames_key[scenNames_user]
+MPNamesRef = NULL # Name of reference MP
+FUNRef = function(myvarsubStat,MPNamesRef){ # Function for comparing MPs with reference MP
+  (myvarsubStat-myvarsubStat[,MPNamesRef])/myvarsubStat[,MPNamesRef]}
+legtext_o = NULL # order for plotting legend text
+MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
+                     "_",
+                     rep(scenNames,length(OMNames))
+)
+colLabs = str_replace_all(gsub("OM_","",OMNames),"(?<=[a-z])(?=[A-Z])"," ")
+plot_type= "sims"#"huynh" # "huynh" plots time series by MP like in the Huynh et al paper
+# "boot" plots times series of bootstrapped data  with bamExtras::plot_boot_vec
+# "phase" plots phase plots of F/Fmsy versus SSB/SSBmsy
+# "tradeoff" plots tradeoff plots by MP
+# "addind" plot additional indices from AddInd
+# "sims" plot time series for individual sim runs
+proyear_phase=NULL
+PMx = Yield # Performance metric function x (x-axis) for tradeoff plots)
+PMy = P75 # Performance metric function y (y-axis) for tradeoff plots)
+mar=c(1,1,1,1)
+oma=c(6,4,3,3)
+mgp=c(1.5,0.2,0)
+cols = setNames(ROGBP(length(MPNamesSub)),MPNamesSub)
+ltys = setNames(rep(1,length(MPNamesSub)),MPNamesSub)
+pchs = setNames(rep(16,length(MPNamesSub)),MPNamesSub)
+lwds = setNames(rep(3,length(MPNamesSub)),MPNamesSub)
+types = setNames(rep("l",length(MPNamesSub)),MPNamesSub)
+xlabel = "Management year"
+xlim = NULL
+ylim = NULL
[…]

### 2022-03-16 RunMSE/SEFSC/run_script.R

@@ -8,12 +8,14 @@ t_list <- Sys.time()
 myseed <- 8675309
 
 source("fn/make_interim_MP_lag.R")
+source("fn/make_projection_MP_lag.R")
 source("fn/SCA_lag.R")
 
 nsim <- 48 #250
 runScenarios <- TRUE # Run scenarios to do MSE or just generate historical data?
 runMSE_args <- list("parallel"=TRUE,"extended"=TRUE,"silent"=FALSE)
-lag_init <- 2 # Number of years between terminal year of assessment and first year of management. May be modified in scenarios
+lag_Assess_init <- 2 # Number of years between terminal year of assessment and first year of management. May be modified in scenarios
+MSY_frac_init <- 0.75 # Fraction of MSY for setting TAC. May be modified in scenarios
 
 OM_name_scen_complete <- NA
 #   local({
@@ -24,29 +26,33 @@ OM_name_scen_complete <- NA
 
 OM_name_all <- gsub(".rds","",list.files("OM"))
 OM_name <- OM_name_all#[!OM_name_all%in%OM_name_complete]
-OM_name <- c("OM_RedPorgy"#, # Runs,
-             ,"OM_BlackSeaBass" # Runs
+OM_name <- c("OM_BlackSeaBass", # Runs
+             "OM_RedPorgy"#, # Runs
              ,"OM_VermilionSnapper" # Runs
              ,"OM_SnowyGrouper" # Runs 2022-1-20 batch 1 for base took only 25 min
              #"OM_RedGrouper", # 2022-1-19 This took 7 hours just to run the base scenario batch 1 so I interrupted it
-             ,"OM_GagGrouper"#, # Runs
+             #,"OM_GagGrouper"#, # Runs
              #,"OM_GrayTriggerfish" # Problems with lightly fished scenario where "More than 5 % of simulations can't get to the specified level of depletion with these Operating Model parameters"
              #"OM_RedSnapper" # Seems to run but takes a long time
 )
 
 # Setup loops
-scenario <- c("base", #"hs", "hd",
-              "nolag",
-              "ucvhi",
-              "ucvlo",
-              "ubias",
-              "lf",
-              "dep",
-              "epiM",
-              "rc",     # Regime change
-              "vtiv",    # Vulnerability time-invariant
-              "perfobs" # Perfect observations
[…]

### 2022-03-29 BuildOM/BuildOMAssess2OM.Rmd
newest runs

@@
 
-run_rdat_to_Obs <- TRUE   # If TRUE, OM will start with ObsUser but then run rdat_to_Obs on the appropriate
+run_rdat2Obs <- TRUE   # If TRUE, OM will start with ObsUser but then run rdat2Obs on the appropriate
                           # rdat to modify the Obs object to reflect sampling observed in data used in BAM
@@
 AddInd_endyr_only <- TRUE
+
+## Do not use age-varying M (since SCA uses constant M)
+#!! As of 2022-03-24 the run_script for the MSE is expecting OM with age-varying M.
+#!! M is then set to constant in most scenarios in the MSE
+Mconstant <- FALSE
 
@@
 
-```{r}
-# create completely empty Data object
-Data_empty <- local({
-  dat <- new("Data")
-  for(slotName_i in slotNames(dat)){
-    slot_i <- slot(dat,slotName_i)
-    if(length(slot_i)>0&is.numeric(slot_i)){
-      slot(dat,slotName_i) <- slot_i*NA
-    }
-  }
-  dat
-})
-```
-
 ```{r build Data, eval=TRUE}
@@
   Data_name_i <- gsub("rdat","Data",rdat_name_i)
-  Data_i <- rdat_to_Data(rdat_i, Mat_age1_max=Mat_age1_max, length_sc = length_sc,nsim=nsim)
-  # This is to try to solve a problem that occurs later when running Simulate on OM_GreaterAmberjack that has something to do with CAL
-  # I think it might be occurring because there are length comps in a year with no age comps. Maybe. It doesn't occur with Cobia which also
-  # has CAL with values for only a single year.
-  # if(Data_name_i=="Data_GreaterAmberjack"){
-  #   Data_i@CAL <- array(NA,c(1,1,1))
-  #   Data_i@CAL_bins <- as.numeric(NA)
-  #   Data_i@CAL_mids <- as.numeric(NA)
-  # }
-  #Data_i@wla <- Data_i@wla*0.00220462 # Convert kg to klb
+  Data_i <- rdat2Data(rdat_i, Mat_age1_max=Mat_age1_max, length_sc = length_sc,nsim=nsim)
 
@@
 list_Nage_F0_pr_sc <- list() # List for storing values of Nage_F0_pr_sc (for plotting hist compared to BAM)
-vec_to_mat <- function(vec){
+vec2mat <- function(vec){
   matrix(vec,nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
@@
 
-mat_to_array <- function(mat,nsim){
+mat2array <- function(mat,nsim){
   mat_data <- rep(as.numeric(mat),each=nsim)
@@
   Data_i <- get(DataName_i)
-  Obs_i <- rdat_to_Obs(rdat_i)
+  Obs_i <- rdat2Obs(rdat_i)
 
@@
   naa_mat2[naa_mat2<0] <- 1 # Don't let value be less than 1
-  naa <- mat_to_array(naa_mat2[,-1],nsim=nsim)
+  naa <- mat2array(naa_mat2[,-1],nsim=nsim)
 
@@
 
-  faa <- mat_to_array(faa_mat2[,-1],nsim=nsim)
+  faa <- mat2array(faa_mat2[,-1],nsim=nsim)
 
@@
                         dimnames=dimnames(naa)[2:3])
-  waa <- mat_to_array(mat_waa_klb,nsim=nsim)
+  waa <- mat2array(mat_waa_klb,nsim=nsim)
 
@@
                         dimnames=dimnames(naa)[2:3])
-  Mataa <- mat_to_array(mat_pmat,nsim=nsim)
+  Mataa <- mat2array(mat_pmat,nsim=nsim)
 
@@
                         dimnames=dimnames(naa)[2:3])
-  Maa <- mat_to_array(mat_M,nsim=nsim)
+  Maa <- mat2array(mat_M,nsim=nsim)
 
@@
                         dimnames=dimnames(naa)[2:3])
-  laa <- mat_to_array(mat_laa,nsim=nsim)
+  laa <- mat2array(mat_laa,nsim=nsim)
 
@@
           if(!is.null(ObsUser)) {
-          if(run_rdat_to_Obs){
+          if(run_rdat2Obs){
             my_rdat <- get(gsub("OM","rdat",OM_name_i))
-            ObsUser <- rdat_to_Obs(
+            ObsUser <- rdat2Obs(
                             rdat=my_rdat,
@@
                 CurrentYr = CurrentYr_i,
-                h=steep_i, R0=R0_i,
+                h=steep_i,
+                R0=R0_i,
                 Obs = ObsUser,
@@
                 altinit = 0,
-                fixq1 = TRUE,)
+                fixq1 = FALSE)
+
+ if(Mconstant){
+    OM_i@cpars$M_ageArray[] <- Data_i@Mort
+ }
 
@@
 
- Data2_i <- Data_empty
+ Data2_i <- Data_empty()
  slot(Data2_i,"AddInd") <- AddInd

### 2022-03-29 RunMSE/SEFSC/MSEPlots.Rmd
newest runs

@@
 library(latex2exp) # lets you use TeX() function to convert latex equations to R expressions for plotting
-library(SAMtool)
+library(openMSE)
 library(stringr)
 library(bamExtras)
+library(bamMSE)
 
@@
                   "OM_SnowyGrouper"#,
-                  #"OM_GagGrouper")#,
-                   #"OM_capelin", "OM_POP", "OM_vs"
-                   )
+                  #"OM_GagGrouper"
+                   )
+Names_user <- gsub("^OM_","",OMNames_user)
+
 OMNames_huynh <- c("OM_CapelinHuynh", "OM_PacificOceanPerchHuynh", "OM_VermilionSnapperHuynh")
 
-scenNames_user1 <-  c("base","dep","lf","epiM","ubias","tachi","rc")
-scenNames_user2 <-  c("base","nolag","minerr","minrecdev","perfobs","ucvhi","ucvlo","vtiv"
+scenNames_user1 <-  c("base","dep","lf","ucvhi","ubias","ucvlo")
+scenNames_user2 <-  c("base","rc","minerr","minrecdev","vtiv")
+scenNames_user3 <-  c("base","noempind",
+                      "nolag","perfobs","tachi")
+scenNames_user4 <-  c("base","lhset","Mset","steepset","agevarM"#,"epiM"
                       )
@@
 # All scenarios
-scenNames_user <- unique(c(scenNames_user1,scenNames_user2))
+scenNames_user <- unique(c(scenNames_user1,scenNames_user2,scenNames_user3,scenNames_user4))
 
@@
 # averaging results together. Most other scenarios could be considered sensitivities.
-scenNames_user_alt <- c("base","dep","lf","epiM","ubias","tachi","rc")
-
-scenNames_key <- c("base"="Base",
+# scenNames_user_alt <- scenNames_user1
+
+scenNames_key <- c("agevarM"="Age-varying M",
+                   "base"="Base",
+                   "dep"="Depleted",
+                   "epiM"="Episodic M",
+                   "hd"="Hyper-deplete",
+                   "hs"="Hyper-stable",
+                   "lf"="Lightly fished",
+                   "lhset"="Set M and steep",
+                   "mconst"="M constant",
+                   "minerr"="Minimal error",
+                   "minrecac"="Minimal rec AC",
+                   "minrecdev"="Minimal rec devs",
+                   "Mset"="Set M",
+                   "noempind"="No empirical indices",
                    "nolag"="No data lag",
-                   "hs"="Hyper-stable","hd"="Hyper-deplete",
-                   "dep"="Depleted","lf"="Lightly fished","epiM"="Episodic M",
-                   "rc"="Regime\nchange", "ubias"="Index\nbiased","ucvhi"="Index\nHigh CV",
+                   "perfobs"="Perfect observation",
+                   "rc"="Regime\nchange",
+                   "steepset"="Set steepness",
+                   "tachi"="TAC 1.25MSY",
+                   "ubias"="Index\nbiased",
+                   "ucvhi"="Index\nHigh CV",
                    "ucvlo"="Index\nLow CV",
-                   "perfobs"="Perfect observation",
-                   "minerr"="Minimal error",
-                   "minrecdev"="Minimal rec devs",
-                   "tachi"="TAC 1.25MSY",
                    "vtiv"="V time invariant"
@@
 
-MPNamesAll <-         c(#"AvC",
-                        "CC1",
-                        #"DCAC","DBSRA","SPMSY",
+MPNamesAll <-         c(#"AvC", "CC1", "DCAC","DBSRA","SPMSY",
                         "SCA_1","SCA_5","SCA_10",
+                        "pMP_5","pMP_10",                        
                         "iMP_avg_5","iMP_avg_10",
-                        "iMP_buffer_5","iMP_buffer_10",
-                        "pMP_5","pMP_10"
+                        "iMP_buffer_5","iMP_buffer_10"
                         )
@@
                     "SPMSY" = "surplus production model",
-                    "SCA_1" = "SCA 1 yr",
-                    "SCA_5" = "SCA 5 yr",
-                    "SCA_10"= "SCA 10 yr",
-                    "iMP_avg_5" = "avg. index (5 yr)",
-                    "iMP_avg_10" = "avg. index (10 yr)",
-                    "iMP_buffer_5" = "buffer index (5 yr)",
-                    "iMP_buffer_10" = "buffer index (10 yr)",
-                    "pMP_5" = "projection (5 yr)",
-                    "pMP_10" = "projection (10 yr)"
+                    "SCA_1" = "Annual assessment",
+                    "SCA_5" = "Fixed TAC (5)",
+                    "SCA_10"= "Fixed TAC (10)",
+                    "iMP_avg_5" = "Avg. index (5)",
+                    "iMP_avg_10" = "Avg. index (10)",
+                    "iMP_buffer_5" = "Buffer index (5)",
+                    "iMP_buffer_10" = "Buffer index (10)",
+                    "pMP_5" = "Projection (5)",
+                    "pMP_10" = "Projection (10)"
                         )
@@
 
-MPNamesSub_user <- c("SCA_10","SCA_5","SCA_1","iMP_avg_10"#,"iMP_buffer_10"
-                     )
-MPNamesSub_user_legtext <- c("Fixed TAC (10)","Fixed TAC (5)","Annual assessment","Averaged Index (10)"#,"Buffered Index (10)"
-                             )
-
-# OMNames_user <- c("OM_BlackSeaBass","OM_SnowyGrouper","OM_VermilionSnapper")
-# OMNames_user <- c("OM_RedPorgy","OM_Tilefish","OM_Cobia")
+MPNamesSub_user <- c("SCA_1","SCA_5","SCA_10","iMP_avg_10","iMP_buffer_10")
+MPNamesSub_user_legtext <- MPNamesAll_key[MPNamesSub_user]
 ```
@@
 proyear_phase=NULL,
+proyear_phase_FUNName="median",
 PMx = Yield, # Performance metric function x (x-axis) for tradeoff plots)
-PMy = P75, # Performance metric function y (y-axis) for tradeoff plots)
+PMy = P100, # Performance metric function y (y-axis) for tradeoff plots)
+PMx_Yrs=-10, # Defaults to the last 10 years 
+PMy_Yrs=-10, # Defaults to the last 10 years
 mar=c(1,1,1,1),
@@
 label_axes="all", # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
-hline=1 # values to pass into abline(h=hline)
+hline=NULL, # values to pass into abline(h=hline)
+vline=NULL, # values to pass into abline(v=vline)
+hline_lty=3,
+vline_lty=3,
+...
 ){
@@
         xaxt=xaxt_i,yaxt=yaxt_i,
-        xlim=xlim,ylim=ylim,xlab="",ylab="")
+        xlim=xlim,ylim=ylim,xlab="",ylab="",...)
 #title(main=colLabsAll[i],line=1)
@@
               xaxt=xaxt_i,yaxt=yaxt_i,
-              xlim=xlim,ylim=ylim,xlab="",ylab="")
+              xlim=xlim,ylim=ylim,xlab="",ylab="",...)
       #title(main=colLabsAll[i],line=1)
@@
               add=ifelse(j!=1,TRUE,FALSE),
-              xlim=xlim,ylim=ylim)
+              xlim=xlim,ylim=ylim,...)
 
@@
 }
-Bstatus <- out_i@SB_SBMSY[,MPNamesSubix,proyear_phase]
-Fstatus <- out_i@F_FMSY[,MPNamesSubix,proyear_phase]
+proyear_phase_FUN <- get(proyear_phase_FUNName)
+Bstatus <- out_i@SB_SBMSY[,MPNamesSubix,proyear_phase,drop=FALSE] %>% apply(1:2,proyear_phase_FUN)
+Fstatus <- out_i@F_FMSY[,MPNamesSubix,proyear_phase,drop=FALSE] %>% apply(1:2,proyear_phase_FUN)
 
@@
         xaxt=xaxt_i,yaxt=yaxt_i,
-        xlab="",ylab="",xlim=xlim,ylim=ylim
+        xlab="",ylab="",xlim=xlim,ylim=ylim,
+        ...
         )
@@
 
+if(i%in%topPanels&i%in%leftPanels){
+  if(length(proyear_phase)>1){
+    leg_text_phase <- paste0(proyear_phase_FUNName,"(proyears ",paste(range(proyear_phase),collapse="-"),")")
+  }else{
+    leg_text_phase <- paste0("proyear ",proyear_phase)
+  }
+  legend("topright",legend=leg_text_phase,bty="n",text.col="black",text.font = 2)
+}
+
 }
@@
 
-PMx_out <- PMx(out_i)
-PMy_out <- PMy(out_i)
+PMx_out <- PMx(out_i,Yrs=PMx_Yrs)
+PMy_out <- PMy(out_i,Yrs=PMy_Yrs)
 
@@
      xlab="",ylab="",
-     xlim=xlim,ylim=ylim
-     )
+     xlim=xlim,ylim=ylim,
+     ...)
 
@@
 if(!is.null(hline)){
-abline(h=hline)
+abline(h=hline,lty=hline_lty)
+}
+if(!is.null(vline)){
+abline(v=vline,lty=vline_lty)
 }
@@
 ```{r function PMsummary}
+
+## NEED TO MODIFY THIS SO IT GROUPS THE GROUPED BOXPLOTS VISUALLY
 # compute and plot summary statistics for Performance metrics
-PMsummary <- function(PMName,OMNames=OMNames_user,scenNames,MPs=NULL,
-                      slot_to_plot="Prob", # Can be either "Prob" or "Stat"
-                      main_line=-1.5,
-                      hline=1,hline_lty=1,
-                      par_args=list(mfrow=c(length(OMNames),1), 
-                                    mar=c(0,2,0,1), oma=c(6,2,1,0),
-                                    mgp=c(0.8,0.2,0), tck=-0.01),
+PMsummary <- function(PMName,
+                      OMNames = OMNames_user,
+                      scenNames,
+                      MPs = NULL,
+                      xaxis_label = NULL,
+                      xaxis_label_outer = "Management procedure",
+                      slot_to_plot = "Prob", # Can be either "Prob" or "Stat"
+                      main_line = -1.5,
+                      hline = 1,
+                      hline_lty = 1,
+                      par_args = list(mfrow = c(length(OMNames),1), mar = c(0,2,0,1), 
+                                      oma = c(3,2,1,0), mgp = c(0.8,0.2,0), tck = -0.01),
+                      n_yr_groups = 1, # Number of groups to split years into
+                      group_space = NULL,  # Additional spacing between groups of boxes
                       ...){
@@
   }
+  if(!"col"%in%names(dots)){
+    colorFUN = colorRampPalette(c("lightblue","darkblue"))
+    dots$col <-  colorFUN(n_yr_groups)
+  }
+  if(is.null(group_space)){
+    group_space <- (n_yr_groups-1)*.75
+  }
 
@@
       MSEout_ij <- get(MSEoutNames_ij)
-      PMout_ij <- PM(MSEout_ij)
-        MPs_ij <- PMout_ij@MPs
-        out_ij <- slot(PMout_ij,slot_to_plot)
-      if(!is.null(MPs)){
-        out_ij <- out_ij[,match(MPs,MPs_ij)]
-        MPs_ij <- MPs
-      }
-      dimnames(out_ij) <- list("sim"=seq(1:dim(out_ij)[1]), "MPs"=MPs_ij)
-      out_ij <- cbind("scen"=scenNames_j,as.data.frame(out_ij))
-      out_list_i[[MSEoutNames_ij]] <- out_ij
-
+      proyears_ij <- MSEout_ij@proyears
+      yr_ij <- 1:proyears_ij
+      breaks_ij <- round(seq(min(yr_ij),max(yr_ij),length=n_yr_groups+1))
+
+      yr_groups_ij <- as.numeric(cut(yr_ij,breaks=breaks_ij,include.lowest = TRUE))
+
+      for(k in 1:n_yr_groups){
+        MSEoutNames_ijk <- paste(MSEoutNames_ij,sprintf("%02.0f",k),sep="_")  
+        PMout_ijk <- PM(MSEout_ij,Yrs=range(yr_ij[yr_groups_ij==k]))
+        MPs_ijk <- PMout_ijk@MPs
+        out_ijk <- slot(PMout_ijk,slot_to_plot)
+        if(!is.null(MPs)){ # Possibly subset MPs
+          out_ijk <- out_ijk[,match(MPs,MPs_ijk)]
+          MPs_ijk <- MPs
+        }
+        dimnames(out_ijk) <- list("sim"=seq(1:dim(out_ijk)[1]), "MPs"=MPs_ijk)
+        out_ijk <- cbind("scen"=scenNames_j,"yr_group"=k,as.data.frame(out_ijk))
+        out_list_i[[MSEoutNames_ijk]] <- out_ijk
+
+      } # end n_yr_groups
     } 
@@
     out_df_i <- do.call(rbind,out_list_i)
+    out_df_i <- reshape2::melt(data=out_df_i,id.vars=c("scen","yr_group"))
     out_list[[paste0("out_df_",Names_i,"_",PMName)]] <- out_df_i
+
     # Plot stuff
-      dots$xaxt <- ifelse(match(OMNames_i,rev(OMNames))==1,"s","n")
-
-      do.call(boxplot,c(list(out_df_i[,-1],main=""),dots))
+    dots$xaxt <- ifelse(match(OMNames_i,rev(OMNames))==1,"n","n")
+    n_group <- length(unique(out_df_i$yr_group))
+    n_variable <- length(unique(out_df_i$variable))
+
+    group_space_add <- rep(1:n_variable,each=n_group)*group_space
+    box_at <- 1:(n_group*n_variable)+group_space_add
+
+    xaxis_label_at <- apply(matrix(box_at,nrow=n_group,ncol=n_variable),2,mean)
+
+    do.call(boxplot,c(list(formula = value ~ yr_group + variable, data = out_df_i,
+                           main = "", at = box_at),dots))
+
     mtext(Names_i,side=3,line=main_line,outer=FALSE,font=2)
@@
   }
+  if(is.null(xaxis_label)){xaxis_label <- MPs}
+
+  axis(side = 1, at = xaxis_label_at, labels = xaxis_label)
+  mtext(xaxis_label_outer,side=1,line=1.5, outer=TRUE,font=2)
 
@@
 # compute and plot summary statistics for Performance metrics
-MSEsummary <- function(MSEslotName,OMNames=OMNames_user,scenNames,MPs=NULL,
+MSEsummary <- function(MSEslotName,
+                       OMNames=OMNames_user,
+                       scenNames,
+                       MPs=NULL,
+                       xaxis_label = NULL,
+                       xaxis_label_outer = "Management procedure",
                        main_line=-1.5,
-                       hline=1,hline_lty=1,
+                       hline=1,
+                       hline_lty=1,
                       par_args=list(mfrow=c(length(OMNames),1), 
-                                    mar=c(3,2,1,1), oma=c(1,2,0,0),
+                                    mar=c(0,2,0,1), oma=c(3,2,1,0),
                                     mgp=c(0.8,0.2,0), tck=-0.01),
+                      n_yr_groups=1, # Number of groups to split years into
+                      FUN_yr_groups=NULL,
+                      group_space = NULL,  # Additional spacing between groups of boxes
                       ...){
@@
 }
+if(!"col"%in%names(dots)){
+ colorFUN = colorRampPalette(c("lightblue","darkblue"))
+ dots$col <-  colorFUN(n_yr_groups)
+}
+if(is.null(group_space)){
+  group_space <- (n_yr_groups-1)*.75
+}
+
 out_list <- list()
@@
     MSEout_ij <- get(MSEoutNames_ij)
+    MPs_ij <- MSEout_ij@MPs
+    proyears_ij <- MSEout_ij@proyears
+    yr_ij <- 1:proyears_ij
+    breaks_ij <- round(seq(min(yr_ij),max(yr_ij),length=n_yr_groups+1))
+
+    yr_groups_ij <- as.numeric(cut(yr_ij,breaks=breaks_ij,include.lowest = TRUE))
+
     if(!is.expression(MSEslotName)){
-      slot_k <- slot(MSEout_ij,MSEslotName) %>% apply(2,as.numeric)
+      slot_k <- slot(MSEout_ij,MSEslotName)
     }else{
-      slot_k <- eval(MSEslotName) %>% apply(2,as.numeric)
-    }
-    slot_k <- slot(MSEout_ij,MSEslotName) %>% apply(2,as.numeric)
-    MPs_ij <- MSEout_ij@MPs
+      slot_k <- eval(MSEslotName)
+    }
+    list_slot_km <- list()
+    for(m in 1:n_yr_groups){
+      if(is.null(FUN_yr_groups)){
+      slot_km <- slot_k[,,which(yr_groups_ij==m)] %>% apply(2,as.numeric)
+      }else{
+      slot_km <- slot_k[,,which(yr_groups_ij==m)] %>% apply(1:2,FUN_yr_groups)
+      }
     if(!is.null(MPs)){
-      slot_k <- slot_k[,match(MPs,MPs_ij)]
+      slot_km <- slot_km[,match(MPs,MPs_ij)]
       MPs_ij <- MPs
     }
-    dimnames(slot_k) <- list(NULL, "MPs"=MPs_ij)
-    slot_k <- cbind("scen"=scenNames_j,as.data.frame(slot_k))
-    slot_list_i[[MSEoutNames_ij]] <- slot_k
+      dimnames(slot_km) <- list(NULL, "MPs"=MPs_ij)
+      list_slot_km[[m]] <- cbind("yr_group"=m,as.data.frame(slot_km))
+    }
+
+    slot_df_km <- do.call(rbind,list_slot_km)
+
+    slot_df_km <- cbind("scen"=scenNames_j,as.data.frame(slot_df_km))
+    slot_list_i[[MSEoutNames_ij]] <- slot_df_km
 
@@
   slot_df_i <- do.call(rbind,slot_list_i)
+  slot_df_i <- reshape2::melt(data=slot_df_i,id.vars=c("scen","yr_group"))
   out_list[[paste0("slot_df_",Names_i,"_",MSEslotName)]] <- slot_df_i
@@
   # Plot stuff
-  do.call(boxplot,c(list(slot_df_i[,-1],main=""),dots))
+  dots$xaxt <- ifelse(match(OMNames_i,rev(OMNames))==1,"n","n")
+  n_group <- length(unique(slot_df_i$yr_group))
+  n_variable <- length(unique(slot_df_i$variable))
+
+  group_space_add <- rep(1:n_variable,each=n_group)*group_space
+  box_at <- 1:(n_group*n_variable)+group_space_add
+
+  xaxis_label_at <- apply(matrix(box_at,nrow=n_group,ncol=n_variable),2,mean)
+
+  do.call(boxplot,c(list(formula=value~yr_group+variable,data=slot_df_i,main="",at=box_at),dots))
   mtext(Names_i,side=3,line=main_line,outer=FALSE,font=2)
@@
 }
+  if(is.null(xaxis_label)){xaxis_label <- MPs}
+
+  axis(side = 1, at = xaxis_label_at, labels = xaxis_label)
+  mtext(xaxis_label_outer,side=1,line=1.5, outer=TRUE,font=2)
 
@@
 # Read in data for modified operating models
-for(file.i in list.files("OM_modified")){
-  assign(gsub(".rds","",file.i),readRDS(file.path("OM_modified",file.i)))
-}
+# for(file.i in list.files("OM_modified")){
+#   assign(gsub(".rds","",file.i),readRDS(file.path("OM_modified",file.i)))
+# }
 
@@
 
-OM_nsim <- c()
-for(OM_Name_i in OMNames){
-  i <- which(OMNames==OM_Name_i)
-  OM_i <- get(OM_Name_i)
-  nsim_i <- OM_i@nsim
-  OM_nsim <- c(OM_nsim,nsim_i)
-}
-
-nsim_text <- combine_words(unique(OM_nsim),and=" or ")
-
 # Read in MSE results
@@
 for(file.i in list.files("MSE_obj")){
+  if(file.i%in%paste0("MSE_",rep(Names_user,each=length(scenNames_user)),"_",scenNames_user,".rds")){
+
     out_i <- readRDS(file.path("MSE_obj",file.i))
@@
     assign(gsub(".rds","",file.i),readRDS(file.path("MSE_obj",file.i)))
+    rm(out_i)
+  }
 }
@@
 if(plot_pdf){pdf("Figs/AddInd.pdf")}
-for(MP_name_i in "SCA_5"){#MPNamesAll){
+for(MP_name_i in "SCA_10"){#MPNamesAll){
     # Ind
@@
 ```{r plot sims proj base, eval=FALSE}
-MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
+MPs_sim <- c("SCA_1","SCA_10","iMP_avg_10")
 scen <- "base"
@@
 
-figName_ij <- paste0("sims_",MSEoutName_i,"_",scen,".pdf")
+figName_ij <- paste0("sims",gsub("MSE|_","",MSEoutName_i),".pdf")
 if(plot_pdf){pdf(file.path("Figs",figName_ij))}
@@
 ```{r plot sims base}
-MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
+MPs_sim <- c("SCA_1","SCA_10","iMP_avg_10")
 scen <- "base"
@@
 
-```{r plot sims minerr, eval=TRUE}
-MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
+```{r plot sims minerr, eval=FALSE}
+MPs_sim <- c("SCA_1","SCA_10","iMP_avg_10")
 scen <- "minerr"
@@
 
-```{r plot sims minrecdev}
-MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
+```{r plot sims minrecdev, eval=FALSE}
+MPs_sim <- c("SCA_1","SCA_10","iMP_avg_10")
 scen <- "minrecdev"
@@
 
-```{r plot sims perfobs}
-MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
+```{r plot sims perfobs, eval=FALSE}
+MPs_sim <- c("SCA_1","SCA_10","iMP_avg_10")
 scen <- "perfobs"
@@
 
-```{r plot sims "vtiv"}
-MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
+```{r plot sims "vtiv",eval=FALSE}
+MPs_sim <- c("SCA_1","SCA_10","iMP_avg_10")
 scen <- "vtiv"
@@
 
-figName_ij <- paste0("sims_",MSEoutName_i,"_",scen,".pdf")
-#if(plot_pdf){pdf(file.path("Figs",figName_ij))}
+figName_ij <- paste0("sims",gsub("MSE|_","",MSEoutName_i),".pdf")
+if(plot_pdf){pdf(file.path("Figs",figName_ij))}
 plot_MSE_sims(MSEOut_i,MPs=MPs_sim,type="histproj",
@@
               title_main = paste0(Name_i,", ",scen))
-#if(plot_pdf){dev.off()}
+if(plot_pdf){dev.off()}
 }
@@
 
-if(plot_pdf){pdf("Figs/boxplot_P_Bgrt75BMSY.pdf")}
-P75_out <- PMsummary("P75",scenNames=scenNames_user_alt,MPs=MPNamesAll,
+if(plot_pdf){pdf("Figs/boxplotPBgrt75BMSY1.pdf")}
+P75_out <- PMsummary("P75",scenNames=scenNames_user1,MPs=MPNamesAll,
                      cex.axis=1,las=2,outline=FALSE,
-                     boxwex=0.25,ylab="",ylim=c(0,1.1),
-                     hline=NA)
-mtext("P(B > 0.75 BMSY)",2,outer=TRUE,font=2)
-if(plot_pdf){dev.off()}
-
-if(plot_pdf){pdf("Figs/boxplot_P_BgrtBMSY.pdf")}
-P100_out <- PMsummary("P100",scenNames=scenNames_user_alt,MPs=MPNamesAll,
+                     boxwex=0.5,ylab="",ylim=c(0,1.1),
+                     hline=NA,n_yr_groups=3,
+                     xaxis_label=gsub("buffer","bfr",MPNamesAll)
+                     )       
+mtext("P(B > 0.75 BMSY)",side = 2,outer=TRUE,font=2)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf("Figs/boxplotPBgrtBMSY1.pdf")}
+P100_out <- PMsummary("P100",scenNames=scenNames_user1,MPs=MPNamesAll,
                      cex.axis=1,las=2,outline=FALSE,
-                     boxwex=0.25,ylab="",ylim=c(0,1.1),
-                     hline=NA)
+                     boxwex=0.5,ylab="",ylim=c(0,1.1),
+                     hline=NA,n_yr_groups=3,
+                     xaxis_label=gsub("buffer","bfr",MPNamesAll)
+                     )
 mtext("P(B > BMSY)",2,outer=TRUE,font=2)
@@
 
-if(plot_pdf){pdf("Figs/boxplot_P_FlssFMSY.pdf")}
-PNOF_out <- PMsummary("PNOF",scenNames=scenNames_user_alt,MPs=MPNamesAll,
+if(plot_pdf){pdf("Figs/boxplotPFlssFMSY1.pdf")}
+PNOF_out <- PMsummary("PNOF",scenNames=scenNames_user1,MPs=MPNamesAll,
                      cex.axis=1,las=2,outline=FALSE,
-                     boxwex=0.25,ylab="",ylim=c(0,1.1),
-                     hline=NA)
+                     boxwex=0.5,ylab="",ylim=c(0,1.1),
+                     hline=NA,n_yr_groups=3,
+                     xaxis_label=gsub("buffer","bfr",MPNamesAll)
+                     )
 mtext("P(F < FMSY)",2,outer=TRUE,font=2)
@@
 
-if(plot_pdf){pdf("Figs/boxplot_AAVY.pdf")}
-AAVY_out <- PMsummary("AAVY",scenNames=scenNames_user_alt,MPs=MPNamesAll,
+if(plot_pdf){pdf("Figs/boxplotAAVY1.pdf")}
+AAVY_out <- PMsummary("AAVY",scenNames=scenNames_user1,MPs=MPNamesAll,
                      slot_to_plot = "Stat",
                      cex.axis=1,las=2,outline=FALSE,
-                     boxwex=0.25,ylab="",ylim=c(0,1.1),
-                     hline=NA)
+                     boxwex=0.5,ylab="",ylim=c(0,1.1),
+                     hline=0.2,n_yr_groups=3,
+                     xaxis_label=gsub("buffer","bfr",MPNamesAll)
+                     )   
 mtext("Avg. Annual Variability in Yield",2,outer=TRUE,font=2)
@@
 
-if(plot_pdf){pdf("Figs/boxplot_SB_SBMSY.pdf")}
-MSEsummary("SB_SBMSY",scenNames=scenNames_user_alt,MPs=MPNamesAll,
-           cex.axis=0.75,las=2,outline=FALSE,boxwex=0.25,ylab="")
+if(plot_pdf){pdf("Figs/boxplotSBSBMSY1.pdf")}
+MSEsummary("SB_SBMSY",scenNames=scenNames_user1,MPs=MPNamesAll,
+           cex.axis=0.75,las=2,outline=FALSE,boxwex=0.5,ylab="",
+           n_yr_groups=3,hline=1,
+           xaxis_label=gsub("buffer","bfr",MPNamesAll)
+)
 mtext("SSB/SSBmsy",2,outer=TRUE,font=2)
@@
 
-if(plot_pdf){pdf("Figs/boxplot_F_FSY.pdf")}
-MSEsummary("F_FMSY",scenNames=scenNames_user_alt,MPs=MPNamesAll,
-           cex.axis=0.75,las=2,outline=FALSE,boxwex=0.25,ylab="")
+if(plot_pdf){pdf("Figs/boxplotFFMSY1.pdf")}
+MSEsummary("F_FMSY",scenNames=scenNames_user1,MPs=MPNamesAll,
+           cex.axis=0.75,las=2,outline=FALSE,boxwex=0.5,ylab="",
+           n_yr_groups=3,hline=1,
+           xaxis_label=gsub("buffer","bfr",MPNamesAll)
+)
 mtext("F/Fmsy",2,outer=TRUE,font=2)
@@
 
+if(plot_pdf){pdf("Figs/boxplotCatch1.pdf")}
+MSEsummary("Catch",scenNames=scenNames_user1,MPs=MPNamesAll,
+           cex.axis=0.75,las=2,outline=FALSE,boxwex=0.5,ylab="",
+           n_yr_groups=3,
+           xaxis_label=gsub("buffer","bfr",MPNamesAll)
+)
+mtext("Catch",2,outer=TRUE,font=2)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf("Figs/boxplotCatchTotal1.pdf")}
+MSEsummary("Catch",scenNames=scenNames_user1,MPs=MPNamesAll,
+           cex.axis=0.75,las=2,outline=FALSE,boxwex=0.5,ylab="",
+           n_yr_groups=3,FUN_yr_groups=sum,
+           xaxis_label=gsub("buffer","bfr",MPNamesAll)
+)
+mtext("Total catch",2,outer=TRUE,font=2)
+if(plot_pdf){dev.off()}
+
 ## Which is the best MP?
@@
 
-```{r plot time series1,eval=FALSE}
+```{r plot time series1,eval=TRUE}
 # # VB
@@
 # SSB
-if(plot_pdf){pdf("Figs/ts_SSB.pdf")}
+if(plot_pdf){pdf("Figs/tsSSB1.pdf")}
 plot_MSE_ts(
@@
 # Catch
-if(plot_pdf){pdf("Figs/ts_Catch.pdf")}
+if(plot_pdf){pdf("Figs/tsCatch1.pdf")}
 plot_MSE_ts(
@@
 # SSB/SSBmsy
-if(plot_pdf){pdf("Figs/ts_SSB_SSBmsy.pdf")}
+if(plot_pdf){pdf("Figs/tsSSBSSBmsy1.pdf")}
 plot_MSE_ts(
@@
   FUN = mean,
-  #ylim=c(0,2),
+  ylim=c(0,2),
   MPNamesSub = MPNamesSub_user,
   MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user1]
+  rowLabs=scenNames_key[scenNames_user1],
+  hline=1
 )
@@
 # F/Fmsy
-if(plot_pdf){pdf("Figs/ts_F_Fmsy.pdf")}
+if(plot_pdf){pdf("Figs/tsFFmsy1.pdf")}
 plot_MSE_ts(
@@
 # C/MSY
-if(plot_pdf){pdf("Figs/ts_Catch_MSY.pdf")}
+if(plot_pdf){pdf("Figs/tsCatchMSY1.pdf")}
 plot_MSE_ts(
@@
 # SSB
-if(plot_pdf){pdf("Figs/ts_SSB.pdf")}
+if(plot_pdf){pdf("Figs/tsSSB2.pdf")}
 plot_MSE_ts(
@@
 # Catch
-if(plot_pdf){pdf("Figs/ts_Catch.pdf")}
+if(plot_pdf){pdf("Figs/tsCatch2.pdf")}
 plot_MSE_ts(
@@
 # SSB/SSBmsy
-if(plot_pdf){pdf("Figs/ts_SSB_SSBmsy.pdf")}
+if(plot_pdf){pdf("Figs/tsSSBSSBmsy2.pdf")}
 plot_MSE_ts(
@@
   FUN = mean,
-  # ylim=c(0,2),
+  ylim=c(0,2),
   MPNamesSub = MPNamesSub_user,
   MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user2]
+  rowLabs=scenNames_key[scenNames_user2],
+  hline=1
 )
@@
 # F/Fmsy
-if(plot_pdf){pdf("Figs/ts_F_Fmsy.pdf")}
+if(plot_pdf){pdf("Figs/tsFFmsy2.pdf")}
 plot_MSE_ts(
@@
 # C/MSY
-if(plot_pdf){pdf("Figs/ts_Catch_MSY.pdf")}
+if(plot_pdf){pdf("Figs/tsCatchMSY2.pdf")}
 plot_MSE_ts(
@@
 # rowLabs=scenNames_key[scenNames_user2]
+# )
+```
+
+```{r plot time series3,eval=TRUE}
+# # VB
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user3,
+# myvarName = "VB",
+# ylabel = expression(mean~(VB)),
+# FUN = mean,
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user3]
+# )
+
+# SSB
+if(plot_pdf){pdf("Figs/tsSSB3.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user3,
+  myvarName = "SSB",
+  ylabel = expression(mean~(SSB)),
+  FUN = mean,
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user3]
+)
+if(plot_pdf){dev.off()}
+# 
+# # F
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user3,  
+# myvarName = "FM",
+# ylabel = expression(mean~(F)),
+# FUN = mean,
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user3]
+# )
+# 
+# # TAC
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user3,  
+# myvarName = "TAC",
+# ylabel = expression(mean~(TAC)),
+# FUN = mean,
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user3] 
+# )
+
+# Catch
+if(plot_pdf){pdf("Figs/tsCatch3.pdf")}
+plot_MSE_ts(
+OMNames= OMNames, scenNames=scenNames_user3,  
+myvarName = "Catch",
+ylabel = expression(mean~(Catch)),
+FUN = mean,
+MPNamesSub = MPNamesSub_user,
+MPNamesSub_legtext=MPNamesSub_user_legtext,
+rowLabs=scenNames_key[scenNames_user3]
+)
+if(plot_pdf){dev.off()}
+
+# SSB/SSBmsy
+if(plot_pdf){pdf("Figs/tsSSBSSBmsy3.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user3,
+  myvarName = "SB_SBMSY",
+  ylabel = expression(mean~(SSB/SSBmsy)),
+  FUN = mean,
+  ylim=c(0,2),
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user3],
+  hline=1
+)
+if(plot_pdf){dev.off()}
+
+# F/Fmsy
+if(plot_pdf){pdf("Figs/tsFFmsy3.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user3,
+  myvarName = "F_FMSY",
+  ylabel = expression(mean~(F/Fmsy)),
+  FUN = mean,
+  ylim=c(0,2),
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user3],
+  hline=1
+)
+if(plot_pdf){dev.off()}
+
+# C/MSY
+if(plot_pdf){pdf("Figs/tsCatchMSY3.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user3,
+  myvarName = "Catch",
+  myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+  ylabel = expression(mean~(Catch/MSY)),
+  FUN = mean,
+  ylim=c(0,2),
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user3],
+  hline=1
+)
+if(plot_pdf){dev.off()}
+
+# 
+# # TAC/MSY
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user3,
+#   myvarName = "TAC",
+#   myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+#   ylabel = expression(mean~(TAC/MSY)),
+#   FUN = mean,
+#   ylim=c(0,2),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user3]
+# )
+# 
+# # C/TAC
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user3,  
+#   myvarName = "Catch",
+#   myvarDenomExpr = expression(slot(out_i,"TAC")),
+#   ylabel = expression(mean~(C/TAC)),
+#   FUN = mean,
+#   ylim=c(0,1.1),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user3]
+# )
+# 
+# # MSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user3,
+# myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+# FUN = mean,
+# ylabel= expression(mean~(MSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user3]
+# )
+# 
+# # SSBMSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user3,
+# myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears)]),
+# FUN = mean,
+# ylabel= expression(mean~(SSBMSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user3]
+# )
+# 
+# # FMSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user3,
+# myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)]),
+# FUN = mean,
+# ylabel= expression(mean~(FMSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user3]
+# )
+# 
+# # UMSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user3,
+# myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)])),
+# FUN = mean,
+# ylabel= expression(mean~(UMSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user3]
+# )
+```
+
+```{r plot time series4,eval=TRUE}
+# # VB
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user4,
+# myvarName = "VB",
+# ylabel = expression(mean~(VB)),
+# FUN = mean,
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user4]
+# )
+
+# SSB
+if(plot_pdf){pdf("Figs/tsSSB4.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user4,
+  myvarName = "SSB",
+  ylabel = expression(mean~(SSB)),
+  FUN = mean,
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user4]
+)
+if(plot_pdf){dev.off()}
+# 
+# # F
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user4,  
+# myvarName = "FM",
+# ylabel = expression(mean~(F)),
+# FUN = mean,
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user4]
+# )
+# 
+# # TAC
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user4,  
+# myvarName = "TAC",
+# ylabel = expression(mean~(TAC)),
+# FUN = mean,
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user4] 
+# )
+
+# Catch
+if(plot_pdf){pdf("Figs/tsCatch4.pdf")}
+plot_MSE_ts(
+OMNames= OMNames, scenNames=scenNames_user4,  
+myvarName = "Catch",
+ylabel = expression(mean~(Catch)),
+FUN = mean,
+MPNamesSub = MPNamesSub_user,
+MPNamesSub_legtext=MPNamesSub_user_legtext,
+rowLabs=scenNames_key[scenNames_user4]
+)
+if(plot_pdf){dev.off()}
+
+# SSB/SSBmsy
+if(plot_pdf){pdf("Figs/tsSSBSSBmsy4.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user4,
+  myvarName = "SB_SBMSY",
+  ylabel = expression(mean~(SSB/SSBmsy)),
+  FUN = mean,
+  ylim=c(0,2),
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user4],
+  hline=1
+)
+if(plot_pdf){dev.off()}
+
+# F/Fmsy
+if(plot_pdf){pdf("Figs/tsFFmsy4.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user4,
+  myvarName = "F_FMSY",
+  ylabel = expression(mean~(F/Fmsy)),
+  FUN = mean,
+  ylim=c(0,2),
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user4],
+  hline=1
+)
+if(plot_pdf){dev.off()}
+
+# C/MSY
+if(plot_pdf){pdf("Figs/tsCatchMSY4.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user4,
+  myvarName = "Catch",
+  myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+  ylabel = expression(mean~(Catch/MSY)),
+  FUN = mean,
+  ylim=c(0,2),
+  MPNamesSub = MPNamesSub_user,
+  MPNamesSub_legtext=MPNamesSub_user_legtext,
+  rowLabs=scenNames_key[scenNames_user4],
+  hline=1
+)
+if(plot_pdf){dev.off()}
+
+# 
+# # TAC/MSY
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user4,
+#   myvarName = "TAC",
+#   myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+#   ylabel = expression(mean~(TAC/MSY)),
+#   FUN = mean,
+#   ylim=c(0,2),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user4]
+# )
+# 
+# # C/TAC
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user4,  
+#   myvarName = "Catch",
+#   myvarDenomExpr = expression(slot(out_i,"TAC")),
+#   ylabel = expression(mean~(C/TAC)),
+#   FUN = mean,
+#   ylim=c(0,1.1),
+#   MPNamesSub = MPNamesSub_user,
+#   MPNamesSub_legtext=MPNamesSub_user_legtext,
+#   rowLabs=scenNames_key[scenNames_user4]
+# )
+# 
+# # MSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user4,
+# myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+# FUN = mean,
+# ylabel= expression(mean~(MSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user4]
+# )
+# 
+# # SSBMSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user4,
+# myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears)]),
+# FUN = mean,
+# ylabel= expression(mean~(SSBMSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user4]
+# )
+# 
+# # FMSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user4,
+# myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)]),
+# FUN = mean,
+# ylabel= expression(mean~(FMSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user4]
+# )
+# 
+# # UMSY
+# plot_MSE_ts(
+# OMNames= OMNames, scenNames=scenNames_user4,
+# myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)])),
+# FUN = mean,
+# ylabel= expression(mean~(UMSY)),
+# MPNamesSub = MPNamesSub_user,
+# MPNamesSub_legtext=MPNamesSub_user_legtext,
+# rowLabs=scenNames_key[scenNames_user4]
 # )
@@
 
-```{r tradeoffPlot1, eval=FALSE}
-if(plot_pdf){pdf("Figs/tradeoffPlot1.pdf")}
+```{r tr_YldP100_1, eval=TRUE}
+if(plot_pdf){pdf("Figs/tr_YldP100_1.pdf")}
 plot_MSE_ts(
   OMNames= OMNames, scenNames=scenNames_user1,
-  # MPNamesRef = "SCA_1",
   plot_type = "tradeoff",
   PMx = Yield,
+  PMy = P100,
+  MPNamesSub = MPNamesAll,
+  MPNamesSub_legtext=MPNamesAll,
+  rowLabs=scenNames_key[scenNames_user1],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,1.2),ylim=c(0,1.1),
+  hline=0.5,vline=0.5,cex=2,legend_cex = 1
+)
+if(plot_pdf){dev.off()}
+```
+
+\clearpage
+
+```{r tr_PNOFP100_1, eval=TRUE}
+if(plot_pdf){pdf("Figs/tr_PNOFP100_1.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user1,
+  plot_type = "tradeoff",
+  PMx = PNOF,
+  PMy = P100,
   MPNamesSub = MPNamesAll,
@@
   xlim=c(0,1.1),ylim=c(0,1.1),
-  hline=NA
-)
-if(plot_pdf){dev.off()}
-```
-
+  hline=0.5,vline=0.5,cex=2,legend_cex = 1
+)
+if(plot_pdf){dev.off()}
+```
 \clearpage
 
-```{r tradeoffPlot2, eval=FALSE}
+```{r tr_AAVYP100_1, eval=TRUE}
+if(plot_pdf){pdf("Figs/tr_AAVYP100_1.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames,
+  scenNames = scenNames_user1,
+  plot_type = "tradeoff",
+  PMx = AAVY,
+  PMy = P100,  
+  MPNamesSub = MPNamesAll,
+  MPNamesSub_legtext = MPNamesAll,
+  rowLabs=scenNames_key[scenNames_user1],
+  mar=c(0,0,0,0), label_axes = "leftbottom",
+  xlim=c(0,1.2), ylim=c(0,1.1),
+  hline=0.5,vline=0.5,cex=2,legend_cex = 1
+)
+if(plot_pdf){dev.off()}
+```
+
+```{r tr_AAVYPNOF_1, eval=TRUE}
+if(plot_pdf){pdf("Figs/tr_AAVYPNOF_1.pdf")}
 plot_MSE_ts(
   OMNames= OMNames, scenNames=scenNames_user1,
-  # MPNamesRef = "SCA_1",
   plot_type = "tradeoff",
-  PMx = PNOF,
-  #proyear_phase=20,
+  PMx = AAVY,
+  PMy = PNOF,
   MPNamesSub = MPNamesAll,
@@
   mar=c(0,0,0,0),label_axes="leftbottom",
-  xlim=c(0,1.1),ylim=c(0,1.1),
-  hline=NA
-)
-
-```
-\clearpage
-
-```{r tradeoffPlot3, eval=FALSE}
-plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user1,
-  # MPNamesRef = "SCA_1",
-  plot_type = "tradeoff",
-  PMx = AAVY10,
-  #proyear_phase=20,
-  MPNamesSub = MPNamesAll,
-  MPNamesSub_legtext=MPNamesAll,
-  rowLabs=scenNames_key[scenNames_user1],
-  mar=c(0,0,0,0),label_axes="leftbottom",
-  xlim=c(0,1.1),ylim=c(0,1.1),
-  hline=NA
-)
-```
-
-```{r tradeoffPlot4, eval=FALSE}
-plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user1,
-  # MPNamesRef = "SCA_1",
-  plot_type = "tradeoff",
-  PMx = AAVY10,
-  PMy = PNOF,
-  #proyear_phase=20,
-  MPNamesSub = MPNamesAll,
-  MPNamesSub_legtext=MPNamesAll,
-  rowLabs=scenNames_key[scenNames_user1],
-  mar=c(0,0,0,0),label_axes="leftbottom",
-  xlim=c(0,1.1),ylim=c(0,1.1),
-  hline=NA
-)
-
+  xlim=c(0,1.2),ylim=c(0,1.1),
+  hline=0.5,vline=0.5,cex=2,legend_cex = 1
+)
+if(plot_pdf){dev.off()}
 ```
@@
   plot_type = "phase",
-  #proyear_phase=50,
+  proyear_phase=41:50,
   MPNamesSub = c(MPNamesSub_user),
@@
 if(plot_pdf){dev.off()}
-```
+
+if(plot_pdf){pdf("Figs/phasePlot3.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user3,
+  plot_type = "phase",
+  proyear_phase=41:50,
+  MPNamesSub = c(MPNamesSub_user),
+  MPNamesSub_legtext=c(MPNamesSub_user_legtext),
+  rowLabs=scenNames_key[scenNames_user3],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,5),ylim=c(0,5),
+  hline=NA
+)
+
+if(plot_pdf){pdf("Figs/phasePlot4.pdf")}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=scenNames_user4,
+  plot_type = "phase",
+  proyear_phase=41:50,
+  MPNamesSub = c(MPNamesSub_user),
+  MPNamesSub_legtext=c(MPNamesSub_user_legtext),
+  rowLabs=scenNames_key[scenNames_user4],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,5),ylim=c(0,5),
+  hline=NA
+)
+if(plot_pdf){dev.off()}
+```

### 2022-03-29 RunMSE/SEFSC/Manuscript/MainText.Rnw
newest runs

@@
 \usepackage{color} % use to color text
+\usepackage{enumitem}
+  \setlist[enumerate]{itemsep=0mm}
 \usepackage[T1]{fontenc}
@@
 n_sp <- english(3)
-n_scen <- 10
+n_scen <- 23
 n_MP <- 13
@@
 \section*{Materials and Methods}
-We used the most recent stock assessments from US Southeast US Atlantic for Red Porgy, Black Sea Bass, and Vermilion Snapper.
 
-\subsection{Evaluating management procedures}
+\subsection*{Operating models}
+We used the most recent stock assessments from US Southeast US Atlantic for Red Porgy, Black Sea Bass, Vermilion Snapper, and Snowy Grouper (cite SEDAR reports).
+Elements of the stock assessments are stored as data sets in the R package \texttt{bamExtras} (cite Github).
+Management strategy evaluation was conducted with the R package \texttt{openMSE} (cite), which includes three sub-packages \texttt{DLMtool}, \texttt{MSEtool}, and \texttt{SAMtool} (cite).
+This package uses a set of data objects with very specific list-like structures (S4; \url{http://adv-r.had.co.nz/S4.html}), such as operating model objects (\texttt{OM}).
+Such objects are made up of a set of named 'slots', which contain specific types of information with particular dimensions, to characterize main components of an MSE.
+Input and output from the Beaufort Assessment Model (BAM) is configured as a list which has a specific structure, and is stored in an \texttt{rdat} file.
+The most recent \texttt{rdat} files are also stored in \texttt{bamExtras} as objects (e.g.
+\texttt{rdat\_BlackSeaBass}).
+In order to the transfer information from BAM \texttt{rdat} objects to \texttt{openMSE} objects, we wrote a set of functions and constructed a new R package, \texttt{bamMSE} (cite GitHub).
+
+Operating models in \texttt{openMSE} (\texttt{OM} class S4 objects) are constructed of four sub-objects: \texttt{Stock}, \texttt{Fleet}, \texttt{Obs}, and \texttt{Imp} class objects.
+Values stored in \texttt{Stock} objects describe a fish stock, \texttt{Fleet} objects characterize a fishing fleet that fishes that stock, \texttt{Obs} objects contain parameters describing how the simulated stock and fleet are observed (e.g.
+bias and error of catch or relative abundance data), and the \texttt{Imp} objects allow the user to set how well managers adhere to management recommendations (i.e.
+implementation error).
+A fifth \texttt{openMSE} object class \texttt{Data}, is used to store various types of data, including data sets typically used in fitting stock assessment models (e.g.
+indices of abundance, catch, and age-composition time series).
+Functions in \texttt{bamMSE} convert \texttt{rdat} objects to \texttt{Stock}, \texttt{Fleet}, \texttt{Obs}, and \texttt{Data} objects (\texttt{rdat2Stock}, \texttt{rdat2Fleet}, \texttt{rdat2Obs}, and \texttt{rdat2Data}).
+
+We used the function \texttt{MSEtool::Assess2OM} to convert BAM results to \texttt{OM} objects, with the help of a wrapper function \texttt{bamAssess2OM} (not yet added to \texttt{bamMSE}).
+While the values of the steepness parameter $h$, and unfished recruitment ($R_{0}$) for the Beverton-Holt stock-recruit relationship is directly passed from BAM to \texttt{Assess2OM}, most other inputs had to be modified from BAM.
+Since \texttt{openMSE} requires the first age in age-structured populations to be age-0, and most BAM assessments start with age-1, age-based data from BAM was linearly extrapolated from age-1 to age-0 before being passed to \texttt{Assess2OM}.
+Such data include several three dimensional numeric arrays with dimensions simulation, age, and year (within recent assessment period): fish weight, fish length, proportion mature, numbers of fish, total fishing mortality rate ($F$; including dead discards) , and natural mortality rate ($M$).
+
+We ran  \texttt{rdat2Data} on the \texttt{rdat} objects, and passed indices of abundance, their associated CVs, and selectivity-at-age to an \texttt{openMSE} \texttt{cpars} list object.
+In \texttt{openMSE} a \texttt{cpars} list object is used to pass custom parameters, typically time-varying, to an operating model.
+The \texttt{rdat2Data} function assumes that indices based on surveys or recreational fisheries are in numbers and indices based on commercial fisheries are in pounds.
+Only indices available in the terminal year of the assessments were passed to \texttt{cpars} and the \texttt{OM} objects (Fig.
+\ref{fig:AddInd}).
+Estimated of growth parameters ($K$, $L_{\infty}$, and $t_{0}$) from BAM were also passed to the \texttt{OM} objects.
+Selectivity-at-age of removals is estimated annually during the empirical assessment period by \texttt{Assess2OM}, and the average of the last three years of the assessment period was passed to \texttt{cpars} and the \texttt{OM} objects.
+
+\subsection*{Scenarios}
+
+\begin{enumerate}
+\setstretch{1}
+\item Base (base): Most likely scenario, described above
+
+\item Episodic $M$ (epiM): $M$ is constant in most years but is occasionally much higher
+\item Age-varying $M$ (agevarM): $M$ varies with age
+\item Set $M$ (Mset): $M$ is set to the same fixed value for all species ($M$ = 0.2)
+\item Set $h$ (steepset): $h$ is set to the same fixed value for all species ($h$ = 0.84)
+\item Set life history (lhset): $M$ and $h$ are set to the same fixed values for all species ($M$ = 0.2, $h$ = 0.84)
+\item Minimal rec. dev. (minrecdev): Recruitment deviations set to low value
+\item Vulnerability time variant (vtvar): Selectivity associated with catch (i.e. vulnerability) varies annually during the historic period
+\item Depleted (dep): Depletion of the stock is high (i.e. smaller stock size) at the beginning of the projection period
+\item Lightly fished (lf): Depletion of the stock is low (i.e. larger stock size) at the beginning of the projection period.
+\item Regime change (rc): Recruitment deviations decline over the projection period, then remain low
+
+\item No empirical indices (noempind): No empirical indices, CVs, or index selectivities are included in the \texttt{OM}
+\item Index is biased (ubias): Primary index of abundance increasingly underestimates population size (i.e. decreasing catchability)
+\item Index high CV (ucvhi): Primary index of abundance of abundance is twice as high
+\item Index low CV (ucvlo): Primary index of abundance of abundance is half as high
+\item Hyper-deplete: Primary index of abundance is hyper-deplete
+\item Hyper-stable: Primary index of abundance is hyper-stable
+\item Minimal error (minerr): Minimal (but not zero) error in all stochastic elements of the \texttt{OM}
+\item Perfect observation (perfobs): Minimal observation error and very high sample sizes in data sets
+
+\item Vulnerability dome-shaped (vdome): Selectivity associated with catch (i.e. vulnerability) is estimated with a dome-shaped function in stock assessments
+\item No data lag (nolag): Catch advice (i.e. TAC) from stock assessments is implemented the year after the terminal year of the assessment
+\item High TAC (tachi): TAC = 1.25MSY
+\item Low TAC (taclo): TAC = 0.75MSY
+\end{enumerate}
+\setstretch{2}
+
+\subsection*{Management procedures}
+
+\begin{enumerate}
+\setstretch{1}
+\item Average catch (AvC): Average catch over all years
+\item Recent catch (CC1): Average catch over the last 5 years
+\item Depletion corrected average catch (DCAC):
+\item Depletion based stock reduction analysis (DBSRA):
+\item Surplus production model (SPMSY):
+\item Statistical catch-at-age model
+\begin{enumerate}
+\item 1-year interval (SCA\_1)
+\item 5-year interval with fixed TAC between years (SCA\_5)
+\item 10-year interval with fixed TAC between years (SCA\_10)
+\item 5-year interval with projected TAC between years (pMP\_5)
+\item 10-year interval with projected TAC between years (pMP\_10)
+\item 5-year interval with TAC adjusted based on averaged recent index between years  (iMP\_avg\_5)
+\item 10-year interval with TAC adjusted based on averaged recent index between years  (iMP\_avg\_10)
+\item 5-year interval with TAC adjusted based on buffered averaged recent index between years  (iMP\_bfr\_5)
+\item 10-year interval with TAC adjusted based on buffered averaged recent index between years  (iMP\_bfr\_10)
+\end{enumerate}
+\end{enumerate}
+\setstretch{2}
+
+\subsection*{Response variables and performance metrics}
+
+(include description of stock assessments and interim approach calculations)
+
+Response variables: Catch, average annual variability in catch, $SSB/SSB_{MSY}$, $F/F_{MSY}$.
 
 \section*{Results}
+
+Response variables tended to vary among time periods over the projection years, and therefore plotted by time period.
+In general, stock status ($SSB/SSB_{MSY}$) was similar among all nine SCA-based MPs for all four species, pooling across scenarios (Fig.
+\ref{fig:boxplotSBSBMSY1}).
+However MPs that adjusted between assessments with a buffered index approach tended to show slightly higher stock status for Black Sea Bass and Vermilion Snapper.
+Fishery status ($F/F_{MSY}$) was somewhat more variable, but still largely consistent among SCA-based MPs, for all species.
+For Black Sea Bass and Vermilion Snapper, $F/F_{MSY}$ for buffered index MPs tended to be at the low end of the range of the other MPs.
+Similarly, total catch was also similar among SCA-based MPs for all species, for similar time periods.
+Average annual variability in yield (catch) showed more substantial variation among MPs.
 
@@
 
+% Indices
 \begin{figure}[!ht]
@@
 \caption{Indices derived from BAM stock assessments available during the projection period, for the SCA\_5 MP in the Base scenario. Shaded areas represent 95\% CI for indices among simulation runs.}
-\label{fig:phasePlot1}
+\label{fig:AddInd}
 \end{flushleft}
@@
 
+% Time series of SSB/SSBMSY 1
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in,height=7in]{../Figs/tsSSBSSBmsy1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of mean $\mathrm{SSB/SSB_{MSY}}$ among simulation runs for the base and alternative scenarios. }
+\label{fig:tsSSBSSBmsy1}
+\end{flushleft}
+\end{figure}
+
+% Time series of F/FMSY 1
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in,height=7in]{../Figs/tsFFmsy1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of mean $\mathrm{F/F_{MSY}}$ among simulation runs for the base and alternative scenarios. }
+\label{fig:tsFFmsy1}
+\end{flushleft}
+\end{figure}
+
+% Time series of Catch 1
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in,height=7in]{../Figs/tsCatch1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of mean $\mathrm{catch}$ among simulation runs for the base and alternative scenarios. }
+\label{fig:tsCatch1}
+\end{flushleft}
+\end{figure}
+
+% Boxplot of SSB/SSBMSY 1
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in,height=7in]{../Figs/boxplotSBSBMSY1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Box plots of $\mathrm{SSB/SSB_{MSY}}$ for the base and alternative scenarios. Grouped boxes represent sequential time periods during the projection period.}
+\label{fig:boxplotSBSBMSY1}
+\end{flushleft}
+\end{figure}
+
+% Boxplot of F/FMSY 1
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in,height=7in]{../Figs/boxplotFFMSY1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Box plots of $\mathrm{F/F_{MSY}}$ for the base and alternative scenarios. Grouped boxes represent sequential time periods during the projection period.}
+\label{fig:boxplotFFMSY1}
+\end{flushleft}
+\end{figure}
+
+% Boxplot of Catch 1
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in,height=7in]{../Figs/boxplotCatchTotal1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Box plots of total catch (annual catches summed across each time period), for the base and alternative scenarios.
+Grouped boxes represent sequential time periods during the projection period.}
+\label{fig:boxplotCatch1}
+\end{flushleft}
+\end{figure}
+
+% Boxplot of AAVY 1
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in,height=7in]{../Figs/boxplotAAVY1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Box plots of average annual variation in yield ($\mathrm{AAVY}$) for the base and alternative scenarios. Grouped boxes represent sequential time periods during the projection period.}
+\label{fig:boxplotAAVY1}
+\end{flushleft}
+\end{figure}
+
+% Phase plots
 \begin{figure}[!ht]
@@
 \begin{flushleft}
-\caption{Phase plots for the base scenario and the first set of experimental scenarios}
+\caption{Phase plots for the base and alternative scenarios.}
 \label{fig:phasePlot1}

### 2022-03-29 RunMSE/SEFSC/Manuscript/MainText.tex
newest runs

@@
 We built operating models for three reef fish species from the US Southeast Atlantic, based on recent stock assessments.
-We developed 10 scenerios and 13 management procedures.
+We developed 23 scenerios and 13 management procedures.
 Management procedures varied in terms of how often stock assessments were conducted, and how catch advice was adjusted between stock assessments.

### 2022-03-29 BuildOM/SCA_NK.R

@@ -1,0 +1,23 @@
+SCA_NK <- function (x = 1, Data, AddInd = "B", SR = c("BH", "Ricker",
+                                            "none"), vulnerability = c("logistic", "dome"), catch_eq = c("Baranov",
+                                                                                                         "Pope"), CAA_dist = c("multinomial", "lognormal"), CAA_multiplier = 50,
+          rescale = "mean1", max_age = Data@MaxAge, start = NULL,
+          prior = list(), fix_h = TRUE, fix_F_equilibrium = TRUE,
+          fix_omega = TRUE, fix_tau = TRUE, LWT = list(), early_dev = c("comp_onegen",
+                                                                        "comp", "all"), late_dev = "comp50", integrate = FALSE,
+          silent = TRUE, opt_hess = FALSE, n_restart = ifelse(opt_hess,
+                                                              0, 1), control = list(iter.max = 2e+05, eval.max = 4e+05),
+          inner.control = list(), ...)
+{
+  out <- SCA__NK(x = x, Data = Data, AddInd = AddInd, SR = SR,
+              vulnerability = vulnerability, catch_eq = catch_eq,
+              comp = "age", comp_dist = CAA_dist, comp_multiplier = CAA_multiplier,
+              rescale = rescale, max_age = max_age, start = start,
+              prior = prior, fix_h = fix_h, fix_F_equilibrium = fix_F_equilibrium,
+              fix_omega = fix_omega, fix_tau = fix_tau, LWT = LWT,
+              early_dev = early_dev, late_dev = late_dev, integrate = integrate,
+              silent = silent, opt_hess = opt_hess, n_restart = n_restart,
+              control = control, inner.control = inner.control, ...)
+  return(out)
+}
+class(SCA_NK) <- "Assess"

### 2022-03-29 BuildOM/SCA__NK.R

@@ -1,0 +1,577 @@
+SCA__NK <- function (x = 1, Data, AddInd = "B", SR = c("BH", "Ricker",
+                                            "none"), vulnerability = c("logistic", "dome"), catch_eq = c("Baranov",
+                                                                                                         "Pope"), comp = c("age", "length"), comp_dist = c("multinomial",
+                                                                                                                                                           "lognormal"), comp_multiplier = c(50, 50), rescale = "mean1",
+          max_age = Data@MaxAge, start = NULL, prior = list(), fix_h = TRUE,
+          fix_F_equilibrium = TRUE, fix_omega = TRUE, fix_tau = TRUE,
+          tv_M = c("none", "walk", "DD"), M_bounds = NULL, refyear = 1,
+          LWT = list(), early_dev = c("comp_onegen", "comp", "all"),
+          late_dev = "comp50", integrate = FALSE, silent = TRUE, opt_hess = FALSE,
+          n_restart = ifelse(opt_hess, 0, 1), control = list(iter.max = 2e+05,
+                                                             eval.max = 4e+05), inner.control = list(), ...)
+{
+  dependencies <- "Data@Cat, Data@Ind, Data@Mort, Data@L50, Data@L95, Data@CAA, Data@vbK, Data@vbLinf, Data@vbt0, Data@wla, Data@wlb, Data@MaxAge"
+  dots <- list(...)
+  start <- lapply(start, eval, envir = environment())
+  max_age <- as.integer(min(max_age, Data@MaxAge))
+  n_age <- max_age + 1
+  vulnerability <- match.arg(vulnerability)
+  catch_eq <- match.arg(catch_eq)
+  comp <- match.arg(comp, several.ok = TRUE)
+  comp_dist <- match.arg(comp_dist)
+  if (length(comp_multiplier) == 1)
+    comp_multiplier <- rep(comp_multiplier, 2)
+  SR <- match.arg(SR)
+  tv_M <- match.arg(tv_M)
+  if (is.character(early_dev))
+    early_dev <- match.arg(early_dev)
+  if (is.numeric(early_dev))
+    stopifnot(early_dev < length(Data@Year))
+  if (any(names(dots) == "yind")) {
[…]

### 2022-03-29 BuildOM/projection_SCA_NK.R

@@ -1,0 +1,85 @@
+# pmin(FMort, max_F) # Don't let me exceed max_F
+
+
+Assessment=res
+constrain = c("F", "Catch")
+Ftarget=res@FMSY
+#Catch
+p_years = 1
+p_sim = 1
+obs_error = list(array(1, c(1, 1, res@info$data$nsurvey)), matrix(1, 1, 1))
+process_error = matrix(1, 1, 1)
+max_F = 3
+seed = 499
+
+projection_SCA_NK <- function (Assessment,
+                               constrain = c("F", "Catch"),
+                               Ftarget,
+                               Catch,
+                               p_years = 50,
+                               p_sim = 200,
+                               obs_error,
+                               process_error,
+                               max_F = 3,
+                               seed = 499,
+                               ...) 
+{
+  constrain <- "F"#match.arg(constrain)
+  TMB_report <- Assessment@TMB_report
+  TMB_data <- Assessment@obj$env$data
+  Pope <- TMB_data$catch_eq == "Pope"
+  set.seed(seed)
+  if (is.matrix(process_error)) {
+    if (nrow(process_error) != p_sim) 
+      stop("Number of rows of process_error not equal to ", 
+           p_sim, call. = FALSE)
+    if (ncol(process_error) != p_years) 
+      stop("Number of columns of process_error not equal to ", 
+           p_years, call. = FALSE)
+    p_log_rec_dev <- process_error
+  } else {
+    tau <- ifelse(!is.null(process_error), process_error[1], 
+                  TMB_report$tau)
+    if (!is.null(tau) && tau > 0) 
+      p_log_rec_dev <- exp(matrix(rnorm(p_years * p_sim, 
+                                        0, tau), p_sim, p_years) - 0.5 * tau^2)
+  }
+  if (!exists("p_log_rec_dev", inherits = FALSE)) 
+    p_log_rec_dev <- matrix(1, p_sim, p_years)
+  nsurvey <- ifelse(is.matrix(Assessment@Index), Assessment@Index %>% 
+                      ncol(), 1)
+  if (is.array(obs_error[[1]])) {
+    Iobs_err <- obs_error[[1]]
+  } else {
+    samps <- rnorm(p_years * p_sim * nsurvey, 0, obs_error[[1]]) %>% 
+      array(c(nsurvey, p_sim, p_years)) %>% aperm(c(2, 
[…]

### 2022-03-29 RunMSE/SEFSC/2022-03-17/fn/SCA_lag.R

@@ -1,0 +1,37 @@
+SCA_lag <- function (x = 1, Data, lag=0,
+                     AddInd = "B", AddInd_all=TRUE,
+                     SR = c("BH", "Ricker", "none"),
+                     vulnerability = c("logistic", "dome"),
+                     catch_eq = c("Baranov", "Pope"),
+                     CAA_dist = c("multinomial", "lognormal"), CAA_multiplier = 50,
+                     rescale = "mean1", max_age = Data@MaxAge, start = NULL,
+                     prior = list(), fix_h = TRUE, fix_F_equilibrium = TRUE,
+                     fix_omega = TRUE, fix_tau = TRUE, LWT = list(),
+                     early_dev = c("comp_onegen","comp", "all"), late_dev = "comp50",
+                     integrate = FALSE, silent = TRUE, opt_hess = FALSE,
+                     n_restart = ifelse(opt_hess, 0, 1),
+                     control = list(iter.max = 2e+05, eval.max = 4e+05),
+                     inner.control = list(), ...)
+{
+
+  Data <- bamMSE::Data_sub_dim(Data,nyr_rm=lag) # Trim temporally explicit slots based on lag
+
+  # Override AddInd setting (which is also used by interim procedures) to use all available indices
+  # in the assessments.
+  if(AddInd_all){
+    if(any(!is.na(as.numeric(Data@AddInd)))){
+      AddInd <- 1:dim(Data@AddInd)[2]}
+  }
+
+  out <- SAMtool:::SCA_(x = x, Data = Data, AddInd = AddInd, SR = SR,
+                        vulnerability = vulnerability, catch_eq = catch_eq,
+                        comp = "age", comp_dist = CAA_dist, comp_multiplier = CAA_multiplier,
+                        rescale = rescale, max_age = max_age, start = start,
+                        prior = prior, fix_h = fix_h, fix_F_equilibrium = fix_F_equilibrium,
+                        fix_omega = fix_omega, fix_tau = fix_tau, LWT = LWT,
+                        early_dev = early_dev, late_dev = late_dev, integrate = integrate,
+                        silent = silent, opt_hess = opt_hess, n_restart = n_restart,
+                        control = control, inner.control = inner.control, ...)
+  return(out)
+}
+class(SCA_lag) <- "Assess"

### 2022-03-29 RunMSE/SEFSC/2022-03-17/fn/iMP.R

@@ -1,0 +1,45 @@
+# Define custom stock assessment function
+MP_args <- list(.Assess = "SCA_lag", .HCR = "HCR_MSY", MSY_frac = MSY_frac,
+                AddInd = AddInd_val, AddInd_all=AddInd_all_assess)
+BAM_SCA_args <- list(SR="BH",
+                     vulnerability = "logistic",
+                     early_dev = "comp_onegen",
+                     late_dev = "comp50",
+                     CAA_dist = "multinomial",
+                     lag=lag_Assess)
+
+# Averaged Index and Buffered Index MPs with (numbers indicate assessment interval)
+iMP_avg_5 <- do.call(make_interim_MP_lag,
+                     c(list(assessment_interval = 5,type = "mean", type_par = 3),
+                       MP_args, BAM_SCA_args)
+                     )
+
+iMP_avg_10 <- do.call(make_interim_MP_lag,
+                      c(list(assessment_interval = 10,type = "mean", type_par = 3),
+                        MP_args, BAM_SCA_args)
+                      )
+
+iMP_buffer_5 <-  do.call(make_interim_MP_lag,
+                         c(list(assessment_interval = 5, type = "buffer", type_par = 1),
+                           MP_args, BAM_SCA_args)
+                         )
+
+iMP_buffer_10 <-  do.call(make_interim_MP_lag,
+                           c(list(assessment_interval = 10, type = "buffer", type_par = 1),
+                             MP_args, BAM_SCA_args)
+                          )
+
+# Fixed TAC MPs (numbers indicate assessment interval) and annual assessment MPs
+SCA_5 <- SCA_10 <- SCA_1 <- do.call(make_MP,
+                                    c(list(diagnostic = "min"),
+                                      MP_args, BAM_SCA_args)
+                                    )
+# Projection MPs
+pMP_5 <- do.call(make_projection_MP_lag,
+                 c(list(assessment_interval = 5,process_error = NULL, p_sim = 1),
+                   MP_args, BAM_SCA_args)
+                 )
+pMP_10 <- do.call(make_projection_MP_lag,
+                 c(list(assessment_interval = 10,process_error = NULL, p_sim = 1),
+                   MP_args, BAM_SCA_args)
+)

### 2022-03-29 RunMSE/SEFSC/2022-03-17/fn/iMP_nolag.R

@@ -1,0 +1,43 @@
+# Define custom stock assessment function
+MP_args <- list(.Assess = "SCA", .HCR = "HCR_MSY", MSY_frac = MSY_frac, AddInd = 1)
+BAM_SCA_args <- list(SR="BH",
+                     vulnerability = "logistic",
+                     early_dev = "comp_onegen",
+                     late_dev = "comp50",
+                     CAA_dist = "multinomial")
+
+# Averaged Index and Buffered Index MPs with (numbers indicate assessment interval)
+iMP_avg_5 <- do.call(make_interim_MP,
+                     c(list(assessment_interval = 5,type = "mean", type_par = 3),
+                       MP_args, BAM_SCA_args)
+                     )
+
+iMP_avg_10 <- do.call(make_interim_MP,
+                      c(list(assessment_interval = 10,type = "mean", type_par = 3),
+                        MP_args, BAM_SCA_args)
+                      )
+
+iMP_buffer_5 <-  do.call(make_interim_MP,
+                         c(list(assessment_interval = 5, type = "buffer", type_par = 1),
+                           MP_args, BAM_SCA_args)
+                         )
+
+iMP_buffer_10 <-  do.call(make_interim_MP,
+                           c(list(assessment_interval = 10, type = "buffer", type_par = 1),
+                             MP_args, BAM_SCA_args)
+                          )
+
+# Fixed TAC MPs (numbers indicate assessment interval) and annual assessment MPs
+SCA_5 <- SCA_10 <- SCA_1 <- do.call(make_MP,
+                                    c(list(diagnostic = "min"),
+                                      MP_args, BAM_SCA_args)
+                                    )
+# Projection MPs
+pMP_5 <- do.call(make_projection_MP,
+                 c(list(assessment_interval = 5,process_error = NULL, p_sim = 1),
+                   MP_args, BAM_SCA_args)
+                 )
+pMP_10 <- do.call(make_projection_MP,
+                 c(list(assessment_interval = 10,process_error = NULL, p_sim = 1),
+                   MP_args, BAM_SCA_args)
+)

### 2022-03-29 RunMSE/SEFSC/2022-03-17/fn/merge_MSE.R

@@ -1,0 +1,143 @@
+# Author: Quang Huynh
+# Modified for compatability with newer version of SAMtool by Nikolai Klibansky
+
+# Merge batches of MSE output
+merge_MSE <- function(...) {
+  dots <- list(...)
+  
+  slots_identical <- function(slotname, x = dots, is_logical = FALSE) {
+    res <- lapply(x, getElement, slotname)
+    is_identical <- all(vapply(res[-1], identical, logical(1), res[[1]]))
+    if(is_logical) {
+      return(is_identical)
+    } else return(unique(do.call(c, res)))
+  }
+  
+  slots_identical("Name")
+  nyears <- slots_identical("nyears")
+  proyears <- slots_identical("proyears")
+  nsim <- slots_identical("nsim")
+  nallyears <- nyears+proyears
+  
+  stopifnot(slots_identical("OM", is_logical = TRUE))
+  stopifnot(slots_identical("Obs", is_logical = TRUE))
+  stopifnot(slots_identical("SSB_hist", is_logical = TRUE))
+  stopifnot(slots_identical("CB_hist", is_logical = TRUE))
+  stopifnot(slots_identical("FM_hist", is_logical = TRUE))
+  #stopifnot(slots_identical("Hist", is_logical = TRUE))
+  
+  nMPs <- vapply(dots, getElement, numeric(1), "nMPs")
+  
+  
+  # These objects are all arrays (nsim, nMPs, proyears)
+  slotvec <- c("SB_SBMSY", "F_FMSY", "N", "B", "SSB", "VB", "FM", "Catch", "Removals", "Effort",
+               "TAC", "TAE")
+  res <- list()
+  for(i in 1:length(slotvec)) {
+    new_mat <- array(NA, dim = c(nsim, sum(nMPs), proyears))
+    for(j in 1:length(dots)) {
+      array_ij <- getElement(dots[[j]], slotvec[i])
+      if(j == 1) new_mat[, 1:nMPs[1], ] <- array_ij
+      if(j > 1) new_mat[, (sum(nMPs[1:(j-1)]) + 1):(sum(nMPs[1:(j-1)]) + nMPs[j]), ] <- array_ij
+    }
+    res[[i]] <- new_mat
+  }
+  
+  
+  # These objects are basically lists of arrays (nlevels, nsim, nMPs, proyears)
+  slotvec2 <- c("SPR", "BioEco")
+  res2 <- list()
+  for(i in 1:length(slotvec2)) {
[…]

### 2022-03-29 RunMSE/SEFSC/2022-03-17/run_script_2022-03-17.R

@@ -1,0 +1,385 @@
+library(abind)
+library(bamExtras)
+library(bamMSE)
+library(openMSE)
+library(magrittr)
+
+rm(list=ls())
+t_list <- Sys.time()
+myseed <- 8675309
+
+source("fn/make_interim_MP_lag.R")
+source("fn/make_projection_MP_lag.R")
+source("fn/SCA_lag.R")
+
+nsim <- 48 #250
+runScenarios <- TRUE # Run scenarios to do MSE or just generate historical data?
+runMSE_args <- list("parallel"=TRUE,"extended"=TRUE,"silent"=FALSE)
+lag_Assess_Init <- 2 # Number of years between terminal year of assessment and first year of management. May be modified in scenarios
+MSY_frac_Init <- 0.75 # Fraction of MSY for setting TAC. May be modified in scenarios
+AddInd_val_Init <- 1  # Index used in interim procedures and possibly assessments. May be modified in scenarios
+AddInd_all_assess_Init <- TRUE # Should all available indices be used in assessments? Only works with SCA_lag() May be modified in scenarios
+
+OMName_scen_complete <- NA
+#   local({
+#   a <- gsub(".rds","",list.files("MSE_obj"))
+#   b <- gsub("MSE","OM",a)
+#   b
+# })
+
+OMName_all <- gsub(".rds","",list.files("OM"))
+OMName <- OMName_all#[!OMName_all%in%OMName_complete]
+OMName <- c("OM_BlackSeaBass", # Runs
+             "OM_RedPorgy"#, # Runs
+             ,"OM_VermilionSnapper" # Runs
+             #,
+             #"OM_SnowyGrouper" # Runs 2022-1-20 batch 1 for base took only 25 min
+             #"OM_RedGrouper", # 2022-1-19 This took 7 hours just to run the base scenario batch 1 so I interrupted it
+             #,"OM_GagGrouper"#, # Runs
+             #,"OM_GrayTriggerfish" # Problems with lightly fished scenario where "More than 5 % of simulations can't get to the specified level of depletion with these Operating Model parameters"
+             #"OM_RedSnapper" # Seems to run but takes a long time
+)
+
+# Setup loops
+scenario <- c(#"base", #"hs", "hd",
+              #"nolag"#,
+               "noaddind"
+              #"lf",
+              #"dep",
+              #"ucvhi",
+              #"ucvlo",
+              #"ubias"#,
[…]

### 2022-03-29 RunMSE/SEFSC/fn/Assess_diagnostic_NK.R

@@ -1,0 +1,63 @@
+Assess_diagnostic_NK <- function (x, Data, Assessment, include_assessment = TRUE)
+{
+  Year <- Data@Year[length(Data@Year)]
+  if (inherits(Assessment, "Assessment")) {
+    msg <- ifelse(is.character(Assessment@opt), Assessment@opt,
+                  Assessment@opt$message)
+    hess <- ifelse(is.character(Assessment@SD), FALSE, Assessment@SD$pdHess)
+    maxgrad <- ifelse(is.character(Assessment@SD), 1e+10,
+                      max(abs(Assessment@SD$gradient.fixed)))
+    iter <- ifelse(is.character(Assessment@opt), NA, Assessment@opt$iterations)
+    fn_eval <- ifelse(is.character(Assessment@opt), NA,
+                      Assessment@opt$evaluations[1])
+
+    # Stuff added by Nikolai Klibansky (2022-03-18)
+    conv <- slot(Assessment,"conv")
+    R0 <- slot(Assessment,"R0")
+    h <- slot(Assessment,"h")
+    MSY <- slot(Assessment,"MSY")
+    FSY <- slot(Assessment,"FMSY")
+    SSBMSY <- slot(Assessment,"SSBMSY")
+    F_FMSY <- tail(slot(Assessment,"F_FMSY"),1)
+    SSB_SSBMSY <- tail(slot(Assessment,"SSB_SSBMSY"),1)
+
+    dg <- list(hess = hess, msg = msg, maxgrad = maxgrad,
+               iter = iter, fn_eval = fn_eval, Year = Year,
+               conv = conv,
+               R0 = R0, h = h,
+               MSY = MSY, FSY = FSY, SSBMSY = SSBMSY,
+               F_FMSY = F_FMSY, SSB_SSBMSY = SSB_SSBMSY
+               )
+  }
+  else {
+    dg <- list(hess = FALSE, msg = msg, maxgrad = 1e+10,
+               iter = NA, fn_eval = NA, Year = Year,
+               conv = NA,
+               R0 = NA, h = NA,
+               MSY = NA, FSY = NA, SSBMSY = NA,
+               F_FMSY = NA, SSB_SSBMSY = NA
+    )
+  }
+  if (length(Data@Misc) == 0)
+    Data@Misc <- vector("list", length(Data@Mort))
+  diagnostic <- Data@Misc[[x]]$diagnostic
+  len_diag <- length(diagnostic)
[…]

### 2022-03-29 RunMSE/SEFSC/fn/SCA_NK.R

@@ -1,0 +1,37 @@
+SCA_NK <- function (x = 1, Data, lag=0,
+                     AddInd = "B", AddInd_all=TRUE,
+                     SR = c("BH", "Ricker", "none"),
+                     vulnerability = c("logistic", "dome"),
+                     catch_eq = c("Baranov", "Pope"),
+                     CAA_dist = c("multinomial", "lognormal"), CAA_multiplier = 50,
+                     rescale = "mean1", max_age = Data@MaxAge, start = NULL,
+                     prior = list(), fix_h = TRUE, fix_F_equilibrium = TRUE,
+                     fix_omega = TRUE, fix_tau = TRUE, LWT = list(),
+                     early_dev = c("comp_onegen","comp", "all"), late_dev = "comp50",
+                     integrate = FALSE, silent = TRUE, opt_hess = FALSE,
+                     n_restart = ifelse(opt_hess, 0, 1),
+                     control = list(iter.max = 2e+05, eval.max = 4e+05),
+                     inner.control = list(), ...)
+{
+
+  Data <- bamMSE::Data_sub_dim(Data,nyr_rm=lag) # Trim temporally explicit slots based on lag
+
+  # Override AddInd setting (which is also used by interim procedures) to use all available indices
+  # in the assessments.
+  if(AddInd_all){
+    if(any(!is.na(as.numeric(Data@AddInd)))){
+      AddInd <- 1:dim(Data@AddInd)[2]}
+  }
+
+  out <- SAMtool:::SCA_(x = x, Data = Data, AddInd = AddInd, SR = SR,
+                        vulnerability = vulnerability, catch_eq = catch_eq,
+                        comp = "age", comp_dist = CAA_dist, comp_multiplier = CAA_multiplier,
+                        rescale = rescale, max_age = max_age, start = start,
+                        prior = prior, fix_h = fix_h, fix_F_equilibrium = fix_F_equilibrium,
+                        fix_omega = fix_omega, fix_tau = fix_tau, LWT = LWT,
+                        early_dev = early_dev, late_dev = late_dev, integrate = integrate,
+                        silent = silent, opt_hess = opt_hess, n_restart = n_restart,
+                        control = control, inner.control = inner.control, ...)
+  return(out)
+}
+class(SCA_NK) <- "Assess"

### 2022-03-29 RunMSE/SEFSC/fn/SCA_lag.R

@@ -1,29 +1,0 @@
-SCA_lag <- function (x = 1, Data, lag=0,
-                     AddInd = "B", SR = c("BH", "Ricker", "none"),
-                     vulnerability = c("logistic", "dome"),
-                     catch_eq = c("Baranov", "Pope"),
-                     CAA_dist = c("multinomial", "lognormal"), CAA_multiplier = 50,
-                     rescale = "mean1", max_age = Data@MaxAge, start = NULL,
-                     prior = list(), fix_h = TRUE, fix_F_equilibrium = TRUE,
-                     fix_omega = TRUE, fix_tau = TRUE, LWT = list(),
-                     early_dev = c("comp_onegen","comp", "all"), late_dev = "comp50",
-                     integrate = FALSE, silent = TRUE, opt_hess = FALSE,
-                     n_restart = ifelse(opt_hess, 0, 1),
-                     control = list(iter.max = 2e+05, eval.max = 4e+05),
-                     inner.control = list(), ...)
-{
-  
-  Data <- bamExtras::Data_sub_dim(Data,nyr_rm=lag) # Trim temporally explicit slots based on lag
-  
-  out <- SAMtool:::SCA_(x = x, Data = Data, AddInd = AddInd, SR = SR,
-                        vulnerability = vulnerability, catch_eq = catch_eq,
-                        comp = "age", comp_dist = CAA_dist, comp_multiplier = CAA_multiplier,
-                        rescale = rescale, max_age = max_age, start = start,
-                        prior = prior, fix_h = fix_h, fix_F_equilibrium = fix_F_equilibrium,
-                        fix_omega = fix_omega, fix_tau = fix_tau, LWT = LWT,
-                        early_dev = early_dev, late_dev = late_dev, integrate = integrate,
-                        silent = silent, opt_hess = opt_hess, n_restart = n_restart,
-                        control = control, inner.control = inner.control, ...)
-  return(out)
-}
-class(SCA_lag) <- "Assess"

### 2022-03-29 RunMSE/SEFSC/fn/iMP.R

@@ -1,44 +1,44 @@
 # Define custom stock assessment function
-MP_args <- list(.Assess = "SCA_lag", .HCR = "HCR_MSY", MSY_frac = MSY_frac, AddInd = 1)
+MP_args <- list(.Assess = "SCA_NK", .HCR = "HCR_MSY", MSY_frac = MSY_frac,
+                AddInd = AddInd_val, AddInd_all=AddInd_all_assess,diagnostic=MP_diagnostic)
 BAM_SCA_args <- list(SR="BH",
-                     vulnerability = "logistic",
+                     vulnerability = vulnerability_Assess,
                      early_dev = "comp_onegen",
                      late_dev = "comp50",
                      CAA_dist = "multinomial",
                      lag=lag_Assess)
 
 # Averaged Index and Buffered Index MPs with (numbers indicate assessment interval)
-iMP_avg_5 <- do.call(make_interim_MP_lag,
+iMP_avg_5 <- do.call(make_interim_MP_NK,
                      c(list(assessment_interval = 5,type = "mean", type_par = 3),
                        MP_args, BAM_SCA_args)
                      )
 
-iMP_avg_10 <- do.call(make_interim_MP_lag,
+iMP_avg_10 <- do.call(make_interim_MP_NK,
                       c(list(assessment_interval = 10,type = "mean", type_par = 3),
                         MP_args, BAM_SCA_args)
                       )
 
-iMP_buffer_5 <-  do.call(make_interim_MP_lag,
+iMP_buffer_5 <-  do.call(make_interim_MP_NK,
                          c(list(assessment_interval = 5, type = "buffer", type_par = 1),
                            MP_args, BAM_SCA_args)
                          )
 
-iMP_buffer_10 <-  do.call(make_interim_MP_lag,
+iMP_buffer_10 <-  do.call(make_interim_MP_NK,
                            c(list(assessment_interval = 10, type = "buffer", type_par = 1),
                              MP_args, BAM_SCA_args)
                           )
 
 # Fixed TAC MPs (numbers indicate assessment interval) and annual assessment MPs
-SCA_5 <- SCA_10 <- SCA_1 <- do.call(make_MP,
-                                    c(list(diagnostic = "min"),
-                                      MP_args, BAM_SCA_args)
+SCA_5 <- SCA_10 <- SCA_1 <- do.call(make_MP_NK,
+                                    c(MP_args, BAM_SCA_args)
                                     )
[…]

### 2022-03-29 RunMSE/SEFSC/fn/make_MP_NK.R

@@ -1,0 +1,51 @@
+make_MP_NK <- function (.Assess, .HCR, diagnostic = c("min", "full", "none"),
+          ...)
+{
+  diagnostic <- match.arg(diagnostic)
+  if (is.character(.Assess)) {
+    Assess_char <- .Assess
+    .Assess <- as.symbol(.Assess)
+  }
+  else {
+    .Assess <- substitute(.Assess)
+    Assess_char <- as.character(.Assess)
+  }
+  if (is.character(.HCR)) {
+    .HCR <- as.symbol(.HCR)
+  }
+  else {
+    .HCR <- substitute(.HCR)
+  }
+  if (!inherits(eval(.Assess), "Assess")) {
+    stop(paste(.Assess, "does not belong to class 'Assess'. Use: avail('Assess') to find eligible objects."))
+  }
+  if (!inherits(eval(.HCR), "HCR")) {
+    stop(paste(.HCR, "does not belong to class 'HCR.' Use: avail('HCR') to find eligible objects."))
+  }
+  dots <- list(...)
+  dots_in_Assess <- dots[match(names(formals(eval(.Assess))),
+                               names(dots), nomatch = 0)]
+  dots_in_HCR <- dots[match(names(formals(eval(.HCR))), names(dots),
+                            nomatch = 0)]
+  Assess_call <- as.call(c(.Assess, x = quote(x), Data = quote(Data),
+                           dots_in_Assess))
+  HCR_call <- as.call(c(.HCR, Assessment = quote(do_Assessment),
+                        reps = quote(reps), dots_in_HCR))
+  MP_body <- bquote({
+    dependencies <- .(SAMtool:::get_dependencies(Assess_char, dots))
+    do_Assessment <- .(Assess_call)
+    Rec <- .(HCR_call)
+    if (diagnostic != "none")
+      Rec@Misc <- Assess_diagnostic_NK(x, Data, do_Assessment,
+                                    include_assessment = .(diagnostic == "full"))
+    # # Add other assessment outputs to Rec@Misc$diagnostic
+    # Rec@Misc$diagnostic[[1]]$MSY <- do_Assessment@MSY
+    if (!is.null(do_Assessment@info$Misc))
+      Rec@Misc <- c(Rec@Misc, do_Assessment@info$Misc)
+    return(Rec)
+  })
+  custom_MP <- eval(call("function", as.pairlist(alist(x = ,
[…]

### 2022-03-29 RunMSE/SEFSC/fn/make_interim_MP_NK.R

@@ -1,0 +1,155 @@
+make_interim_MP_NK <- function (.Assess = "SCA",
+                                 .HCR = "HCR_MSY",
+                                 AddInd = "VB",
+                                 assessment_interval = 5,
+                                 type = c("buffer", "mean", "loess", "none"),
+                                 type_par = NULL,
+                                 diagnostic = c("min", "full","none"),
+                                 ...)
+{
+  type <- match.arg(type)
+  diagnostic <- match.arg(diagnostic)
+  if (is.character(.Assess)) {
+    Assess_char <- .Assess
+    .Assess <- as.symbol(.Assess)
+  }
+  else {
+    .Assess <- substitute(.Assess)
+    Assess_char <- as.character(.Assess)
+  }
+  if (is.character(.HCR)) {
+    .HCR <- as.symbol(.HCR)
+  }
+  else {
+    .HCR <- substitute(.HCR)
+  }
+  if (!inherits(eval(.Assess), "Assess")) {
+    stop(paste(.Assess, "does not belong to class 'Assess'. Use: avail('Assess') to find eligible objects."))
+  }
+  if (!inherits(eval(.HCR), "HCR")) {
+    stop(paste(.HCR, "does not belong to class 'HCR.' Use: avail('HCR') to find eligible objects."))
+  }
+  dots <- list(...)
+  dots$AddInd <- AddInd
+
+  if(!is.null(dots$lag)){
+    lag <- dots$lag
+  }else{
+    lag <- 0
+  }
+
+  dots_in_Assess <- dots[match(names(formals(eval(.Assess))),
+                               names(dots), nomatch = 0)]
+  dots_in_HCR <- dots[match(names(formals(eval(.HCR))), names(dots),
+                            nomatch = 0)]
+  Assess_call <- as.call(c(.Assess, x = quote(x), Data = quote(Data),
+                           dots_in_Assess))
+  HCR_call <- as.call(c(.HCR, Assessment = quote(do_Assessment),
+                        reps = quote(reps), dots_in_HCR))
+  MP_body <- bquote({
+    dependencies <- .(SAMtool:::get_dependencies(Assess_char, dots))
+    ny <- length(Data@Year)      # Number of years in available Data object
+    #ny_Assess <- ny- .(lag)           # Number of year of Data available for assessment
+    Current_Yr <- Data@Year[ny]  # Current year
[…]

### 2022-03-29 RunMSE/SEFSC/fn/make_projection_MP_NK.R

@@ -1,0 +1,83 @@
+make_projection_MP_NK <- function (.Assess = "SCA",
+                                    .HCR = "HCR_MSY",
+                                    assessment_interval = 5,
+                                    Ftarget = expression(Assessment@FMSY),
+                                    proj_args = list(process_error = 1, p_sim = 1),
+                                    diagnostic = c("min", "full", "none"),
+                                    ...)
+{
+  diagnostic <- match.arg(diagnostic)
+  if (is.character(.Assess)) {
+    Assess_char <- .Assess
+    .Assess <- as.symbol(.Assess)
+  }
+  else {
+    .Assess <- substitute(.Assess)
+    Assess_char <- as.character(.Assess)
+  }
+  if (!inherits(eval(.Assess), "Assess")) {
+    stop(paste(.Assess, "does not belong to class 'Assess'. Use: avail('Assess') to find eligible objects."))
+  }
+  dots <- list(...)
+
+  if(!is.null(dots$lag)){
+    lag <- dots$lag
+  }else{
+    lag <- 0
+  }
+
+  dots_in_Assess <- dots[match(names(formals(eval(.Assess))),
+                               names(dots), nomatch = 0)]
+  Assess_call <- as.call(c(.Assess, x = quote(x), Data = quote(Data),
+                           dots_in_Assess))
+  proj_args <- proj_args[match(names(formals(projection)),
+                               names(proj_args), nomatch = 0)]
+  proj_args$p_years <- assessment_interval + 1
+  proj_call <- as.call(c(substitute(projection), Assessment = quote(Assessment),
+                         Ftarget = quote(eval(Ftarget)), proj_args))
+  MP_body <- bquote({
+    dependencies <- .(SAMtool:::get_dependencies(Assess_char, dots))
+    ny <- length(Data@Year)
+    ny_Assess <- ny- .(lag)           # Number of year of Data available for assessment
+    Current_Yr <- Data@Year[ny]
+    first_assess_yr <- Current_Yr == Data@LHYear
+    run_assessment <- first_assess_yr || Current_Yr == Data@Misc[[x]]$proj$next_assess_yr
+    get_projection <- !run_assessment
+    Rec <- new("Rec")
+    if (run_assessment) {
+      Assessment <- .(Assess_call)
+      if (diagnostic != "none") {
+        Rec@Misc <- Assess_diagnostic_NK(x, Data, Assessment,
+                                      include_assessment = .(diagnostic == "full"))
+      }
[…]

### 2022-03-29 RunMSE/SEFSC/run_script.R

@@ -1,5 +1,6 @@
 library(abind)
 library(bamExtras)
+library(bamMSE)
 library(openMSE)
 library(magrittr)
 
@@ -7,59 +8,86 @@ rm(list=ls())
 t_list <- Sys.time()
 myseed <- 8675309
 
-source("fn/make_interim_MP_lag.R")
-source("fn/make_projection_MP_lag.R")
-source("fn/SCA_lag.R")
+source("fn/Assess_diagnostic_NK.R")
+source("fn/make_MP_NK.R")
+source("fn/make_interim_MP_NK.R")
+source("fn/make_projection_MP_NK.R")
+source("fn/SCA_NK.R")
 
 nsim <- 48 #250
 runScenarios <- TRUE # Run scenarios to do MSE or just generate historical data?
 runMSE_args <- list("parallel"=TRUE,"extended"=TRUE,"silent"=FALSE)
-lag_Assess_init <- 2 # Number of years between terminal year of assessment and first year of management. May be modified in scenarios
-MSY_frac_init <- 0.75 # Fraction of MSY for setting TAC. May be modified in scenarios
+lag_Assess_Init <- 2 # Number of years between terminal year of assessment and first year of management. May be modified in scenarios
+vulnerability_Assess_Init <- "logistic" # Functional form of vulnerability of catch used in assessments
+MSY_frac_Init <- 1 # Fraction of MSY for setting TAC. May be modified in scenarios
+AddInd_val_Init <- 1  # Index used in interim procedures and possibly assessments. May be modified in scenarios
+AddInd_all_assess_Init <- TRUE # Should all available indices be used in assessments? Only works with SCA_NK() May be modified in scenarios
+MP_diagnostic <- "min"
+#M_OM_agevariant <- FALSE # Should M be age-variant in the operating model? Note that the SCA function currently treats M as a constant
 
-OM_name_scen_complete <- NA
-#   local({
-#   a <- gsub(".rds","",list.files("MSE_obj"))
-#   b <- gsub("MSE","OM",a)
-#   b
-# })
 
-OM_name_all <- gsub(".rds","",list.files("OM"))
-OM_name <- OM_name_all#[!OM_name_all%in%OM_name_complete]
-OM_name <- c("OM_BlackSeaBass", # Runs
-             "OM_RedPorgy"#, # Runs
-             ,"OM_VermilionSnapper" # Runs
-             ,"OM_SnowyGrouper" # Runs 2022-1-20 batch 1 for base took only 25 min
[…]

### 2022-03-30 RunMSE/SEFSC/MSEPlots.Rmd
recent runs

@@
 scenNames_user1 <-  c("base","dep","lf","ucvhi","ubias","ucvlo")
-scenNames_user2 <-  c("base","rc","minerr","minrecdev","vtiv")
-scenNames_user3 <-  c("base","noempind",
-                      "nolag","perfobs","tachi")
-scenNames_user4 <-  c("base","lhset","Mset","steepset","agevarM"#,"epiM"
-                      )
+scenNames_user2 <-  c("base","rc","minerr","minrecdev","recns","vtiv")
+scenNames_user3 <-  c("base","noempind","catcvlo","nolag","perfobs","tachi")
+scenNames_user4 <-  c("base","lhset","Mset","steepset","agevarM","epiM")
 
 # All scenarios
-scenNames_user <- unique(c(scenNames_user1,scenNames_user2,scenNames_user3,scenNames_user4))
+scenNames_user <- unique(c(scenNames_user1
+                           ,scenNames_user2
+                           ,scenNames_user3
+                           #,scenNames_user4
+                           ))
 
@@
                    "base"="Base",
+                   "catcvlo"="Catch CV 0.05",
                    "dep"="Depleted",
@@
                    "rc"="Regime\nchange",
+                   "recns"="Recruitment\nnonstationary",
                    "steepset"="Set steepness",
@@
 
-```{r plot time series4,eval=TRUE}
+```{r plot time series4,eval=FALSE}
 # # VB
@@
 
-if(plot_pdf){pdf("Figs/phasePlot4.pdf")}
-plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user4,
-  plot_type = "phase",
-  proyear_phase=41:50,
-  MPNamesSub = c(MPNamesSub_user),
-  MPNamesSub_legtext=c(MPNamesSub_user_legtext),
-  rowLabs=scenNames_key[scenNames_user4],
-  mar=c(0,0,0,0),label_axes="leftbottom",
-  xlim=c(0,5),ylim=c(0,5),
-  hline=NA
-)
-if(plot_pdf){dev.off()}
-```
+# if(plot_pdf){pdf("Figs/phasePlot4.pdf")}
+# plot_MSE_ts(
+#   OMNames= OMNames, scenNames=scenNames_user4,
+#   plot_type = "phase",
+#   proyear_phase=41:50,
+#   MPNamesSub = c(MPNamesSub_user),
+#   MPNamesSub_legtext=c(MPNamesSub_user_legtext),
+#   rowLabs=scenNames_key[scenNames_user4],
+#   mar=c(0,0,0,0),label_axes="leftbottom",
+#   xlim=c(0,5),ylim=c(0,5),
+#   hline=NA
+# )
+# if(plot_pdf){dev.off()}
+```

### 2022-03-30 RunMSE/SEFSC/Manuscript/MainText.Rnw
recent runs

@@
 
-Response variables tended to vary among time periods over the projection years, and therefore plotted by time period.
+Response variables tended to vary among time periods over the projection years, and are therefore plotted by time period.
 In general, stock status ($SSB/SSB_{MSY}$) was similar among all nine SCA-based MPs for all four species, pooling across scenarios (Fig.
@@
 \begin{flushleft}
-\caption{Indices derived from BAM stock assessments available during the projection period, for the SCA\_5 MP in the Base scenario. Shaded areas represent 95\% CI for indices among simulation runs.}
+\caption{Indices derived from BAM stock assessments available during the projection period, for the SCA\_10 MP in the Base scenario, where stock assessments are conducted every 10 years during the projection period (dashed vertical lines).
+Shaded areas represent 95\% CI for indices among simulation runs.}
 \label{fig:AddInd}
-\end{flushleft}
-\end{figure}
-
-% Time series of SSB/SSBMSY 1
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[width=6in,height=7in]{../Figs/tsSSBSSBmsy1.pdf}
-\end{center}
-\begin{flushleft}
-\caption{Time series of mean $\mathrm{SSB/SSB_{MSY}}$ among simulation runs for the base and alternative scenarios. }
-\label{fig:tsSSBSSBmsy1}
-\end{flushleft}
-\end{figure}
-
-% Time series of F/FMSY 1
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[width=6in,height=7in]{../Figs/tsFFmsy1.pdf}
-\end{center}
-\begin{flushleft}
-\caption{Time series of mean $\mathrm{F/F_{MSY}}$ among simulation runs for the base and alternative scenarios. }
-\label{fig:tsFFmsy1}
-\end{flushleft}
-\end{figure}
-
-% Time series of Catch 1
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[width=6in,height=7in]{../Figs/tsCatch1.pdf}
-\end{center}
-\begin{flushleft}
-\caption{Time series of mean $\mathrm{catch}$ among simulation runs for the base and alternative scenarios. }
-\label{fig:tsCatch1}
 \end{flushleft}
@@
 
+% Time series of SSB/SSBMSY 1
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in,height=7in]{../Figs/tsSSBSSBmsy1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of mean $\mathrm{SSB/SSB_{MSY}}$ among simulation runs for the base and alternative scenarios. }
+\label{fig:tsSSBSSBmsy1}
+\end{flushleft}
+\end{figure}
+
+% Time series of F/FMSY 1
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in,height=7in]{../Figs/tsFFmsy1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of mean $\mathrm{F/F_{MSY}}$ among simulation runs for the base and alternative scenarios. }
+\label{fig:tsFFmsy1}
+\end{flushleft}
+\end{figure}
+
+% Time series of Catch 1
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in,height=7in]{../Figs/tsCatch1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of mean $\mathrm{catch}$ among simulation runs for the base and alternative scenarios. }
+\label{fig:tsCatch1}
+\end{flushleft}
+\end{figure}
+
 % Phase plots

### 2022-03-30 RunMSE/SEFSC/fn/iMP.R

@@ -1,13 +1,3 @@
-# Define custom stock assessment function
-MP_args <- list(.Assess = "SCA_NK", .HCR = "HCR_MSY", MSY_frac = MSY_frac,
-                AddInd = AddInd_val, AddInd_all=AddInd_all_assess,diagnostic=MP_diagnostic)
-BAM_SCA_args <- list(SR="BH",
-                     vulnerability = vulnerability_Assess,
-                     early_dev = "comp_onegen",
-                     late_dev = "comp50",
-                     CAA_dist = "multinomial",
-                     lag=lag_Assess)
-
 # Averaged Index and Buffered Index MPs with (numbers indicate assessment interval)
 iMP_avg_5 <- do.call(make_interim_MP_NK,
                      c(list(assessment_interval = 5,type = "mean", type_par = 3),

### 2022-03-30 RunMSE/SEFSC/run_script.R

@@ -46,33 +46,41 @@ OMName <- c("OM_RedPorgy" # Runs,
 )
 
 # Setup loops
-scenario <- c(
-              "hs"
-              ,"hd"
-              ,"vdome" # Assume dome-shaped selectivity of catch in assessments
-              ,"agevarM"  # M is age varying in the operating model
-              ,"base"
-              ,"dep"
-              #,"epiM"  # Red Porgy sometimes has problems getting down to the specified level of depletion
-              ,"lf"
-              ,"lhset"    # set certain life history parameters
-              ,"minerr"   # Minimize error and variation in operating model
-              ,"minrecdev"  # Minimize recruitment deviations
-              ,"Mset"     # set M
-              ,"noempind"
-              ,"nolag"
-              ,"perfobs" # Perfect observations
-              ,"rc"     # Regime change
-              ,"steepset"  # set steepness
-              ,"tachi"
-              ,"taclo"
-              ,"ucvhi"
-              ,"ucvlo"
-              ,"ubias"
-              ,"vtiv"    # Vulnerability time-invariant in historic period
+scenario <- c("recns",
+              "catcvlo",
+              #"hs"
+              #,"hd"
+              #,"vdome" # Assume dome-shaped selectivity of catch in assessments
+              #,"agevarM"  # M is age varying in the operating model
+              #,"base"
+              #,"dep"
+              "epiM"  # Red Porgy sometimes has problems getting down to the specified level of depletion
+              #,"lf"
+              #,"lhset"    # set certain life history parameters
+              #,"minerr"   # Minimize error and variation in operating model
+              #,"minrecdev"  # Minimize recruitment deviations
+              #,"Mset"     # set M
+              #,"noempind"
+              #,"nolag"
+              #,"perfobs" # Perfect observations
+              #,"rc"     # Regime change
+              #,"steepset"  # set steepness
+              #,"tachi"
+              #,"taclo"
+              #,"ucvhi"
+              #,"ucvlo"
+              #,"ubias"
[…]

### 2022-06-02 BuildOM/BuildOMAssess2OM.Rmd
move large files out of repo

@@
 plot_Hist <- TRUE # Plot hist objects
+plot_pdf <- TRUE
 
@@
 
+```{r functions}
+# color function like rainbow() but without yellow (or indigo)
+blues <- colorRampPalette(c("darkblue","lightblue"))
+grays <- colorRampPalette(c("black","lightgray"))
+```
+
 ```{r build Data, eval=TRUE}
@@
   Data_name_i <- gsub("rdat","Data",rdat_name_i)
-  Data_i <- rdat2Data(rdat_i, Mat_age1_max=Mat_age1_max, length_sc = length_sc,nsim=nsim)
+  Data_i <- rdat2Data(rdat_i, Mat_age1_max=Mat_age1_max, length_sc = length_sc,nsim=nsim, AddInd_order = "CVlo")
 
@@
 ```{r build OM Assess2OM, eval=TRUE}
+rdatmods <- list() # List for saving rdat modifications used when plotting bam results compared with Hist objects
 list_Nage_F0_pr_sc <- list() # List for storing values of Nage_F0_pr_sc (for plotting hist compared to BAM)
@@
  rdatmods_name_i <- gsub("rdat","rdatmods",rdat_name_i)
- assign(rdatmods_name_i,
-        list(
+ rdatmods_i <- list(
           "Name"=Name_i,
@@
           "B.age" = t(naa_mat2[,-1])*t(mat_waa_klb)
-
           )
-        )
+ assign(rdatmods_name_i,rdatmods_i)
+ rdatmods[[Name_i]] <- rdatmods_i
 
@@
 
+ # # Determine the order of indices from most precise to least precise, and sort the corresponding slots
+ # # This will ensure the the most precise index is in the first column, and will therefore be used 
+ # # for interim analysis based on an index.
+ # o_CV_AddInd <- order(apply(CV_AddInd,2,function(x){mean(x,na.rm=TRUE)}))
+ # 
+ # AddInd <- AddInd[,o_CV_AddInd,,drop=FALSE]
+ # CV_AddInd <- CV_AddInd[,o_CV_AddInd,,drop=FALSE]
+ # AddIndV <- AddIndV[,o_CV_AddInd,,drop=FALSE]
+ # AddIndType <- AddIndType[o_CV_AddInd]
+ # AddIunits <- AddIunits[o_CV_AddInd]
+
  if(AddInd_endyr_only){
    # Identify which indices are available (not NA) in the terminal year of the assessment
-   AddInd_endyr_ix <- which(!is.na(AddInd[1,,dim(AddInd)[3]])) # Just uses the first sim!!
+   AddInd_endyr_NA <- is.na(AddInd[1,,dim(AddInd)[3]])
+   if(any(!AddInd_endyr_NA)){
+     AddInd_endyr_ix <- which(!AddInd_endyr_NA) # Just uses the first sim, but that should be fine
+   }else{
+     message(paste(Name_i,": No indices available in the terminal year of the assessment. Using the latest index available for AddInd."))
+     AddInd_LastYearAvail <- apply(AddInd[1,,,drop=FALSE],2,function(x){max(which(!is.na(x)))})
+     AddInd_endyr_ix <- AddInd_LastYearAvail==max(AddInd_LastYearAvail)
+   }
    AddInd <- AddInd[,AddInd_endyr_ix,,drop=FALSE]
@@
 }
+save(rdatmods,file="rdatmods.RData")
 ```
@@
 
-```{r generate Hist}
+```{r generate Hist, eval=TRUE}
 if(generate_Hist){
@@
 
-```{r plot Hist with bam  results, eval=TRUE}
+```{r plot Hist with bam  results, eval=FALSE}
 if(plot_Hist){
@@
 ```
+
+```{r plot Hist with bam  results, eval=TRUE}
+if(plot_Hist){
+CIpct  <-  95
+
+#commonNames <- gsub(".*_(.+)_.*","\\1",OMNames_base)
+commonNames <- bam_common_name_sub
+lty <- c(1,2)
+
+for(i in commonNames){
+if(plot_pdf){pdf(paste0("Figs/Hist_",i,".pdf"))}  
+rdat_name_i <- paste0("rdat_",i)
+
+OM_i <- get(paste0("OM_",i))
+# Data_i <- get(paste0("Data_",i))
+Hist_i <- get(paste0("Hist_",i))
+rdat_i <- standardize_rdat(get(rdat_name_i))
+rdatmods_i <- rdatmods[[i]]
+
+parms_i <- rdat_i$parms
+years_i <- paste(parms_i$styr:parms_i$endyr)
+t.series_i <- rdat_i$t.series[years_i,]
+
+Nage_F0_pr_sc_i <- rdatmods_i$Nage_F0_pr_sc
+
+par(mfrow=c(3,2),mgp=c(0.9,0.1,0),tck=-0.01,mar=c(2,2.5,1,1),oma=c(0,0,1.5,1))
+
+Fmatrix <- Hist_i@TSdata$Find
+
+# Landings
+Lmatrix <- Hist_i@TSdata$Landings[,,1]+Hist_i@TSdata$Landings[,,2]
+dimnames(Lmatrix) <- dimnames(Fmatrix)
+Lbam <- t.series_i$total.L.klb
+Dbam <- t.series_i$total.D.klb
+if(!is.null(Dbam)){
+  Lbam <- Lbam+Dbam
+}
+Lylim <- range(c(0,as.numeric(Lmatrix),Lbam))
+plot_boot_vec(Lmatrix,CIpct=CIpct,xlab="year",ylab="Landings + Discards (1000 lb)",ylim=Lylim,lty=lty[1])
+points(years_i,Lbam,type="o",#axes=FALSE,xlab="",ylab="",
+     col="blue",lty=lty[2])
+
+legend("bottomleft",
+       legend=c("sim","BAM"),
+       lty=lty,
+       pch=c(NA,1),
+       col=c("black","blue"),
+       bg=rgb(1,1,1,0.5),
+       inset=0.05
+       )
+
+# Indices
+AddIndArray <- Hist_i@Data@AddInd
+dimnames(AddIndArray) <- dimnames(OM_i@cpars$Data@AddInd)
+nAddInd <- dim(AddIndArray)[2]
+AddInd_col_sim <- grays(nAddInd)
+AddInd_col_bam <- blues(nAddInd)
+
+#U.names.ob <- names(t.series_i)[grepl("^U..*.ob$",names(t.series_i))]
+bam.U.ob <- t.series_i[,paste0("U.",dimnames(AddIndArray)[[2]],".ob"),drop=FALSE]
+for(j in 1:nAddInd){
+AddIndmatrix_j <- AddIndArray[,j,]
+dimnames(AddIndmatrix_j) <- dimnames(Fmatrix)  
+plot_boot_vec(AddIndmatrix_j,add=ifelse(j!=1,TRUE,FALSE),
+              CIpct=CIpct,xlab="year",ylab="AddInd",
+              col_lines=AddInd_col_sim[j],lty=lty[1]
+              )
+points(as.numeric(rownames(bam.U.ob)),bam.U.ob[,j],type="o", col=AddInd_col_bam[j],lty=lty[2])
+
+}
+# Recruitment
+Rmatrix <- Hist_i@AtAge$Number[,1,,1]+Hist_i@AtAge$Number[,1,,2]
+dimnames(Rmatrix) <- dimnames(Fmatrix)
+plot_boot_vec(Rmatrix,CIpct=CIpct,xlab="year",ylab="recruits",lty=lty[1])
+points(years_i,t.series_i$recruits*Nage_F0_pr_sc_i,type="o", col="blue",lty=lty[2])
+
+# N
+Nmatrix <- Hist_i@TSdata$Number[,,1]+Hist_i@TSdata$Number[,,2]
+dimnames(Nmatrix) <- dimnames(Fmatrix)
+bam.N <- rowSums(rdatmods_i$N.age)
+plot_boot_vec(Nmatrix,CIpct=CIpct,xlab="year",ylab="N",lty=lty[1])
+points(years_i,bam.N,type="o",col="blue",lty=lty[2])
+
+# F
+# Fmatrix <- Hist_i@TSdata$Find
+plot_boot_vec(Fmatrix,CIpct=CIpct,xlab="year",ylab="F",lty=lty[1])
+ points(years_i,t.series_i$F.full,type="o",
+     col="blue",lty=lty[2])
+
+# B
+Bmatrix <- Hist_i@TSdata$Biomass[,,1]+Hist_i@TSdata$Biomass[,,2]
+dimnames(Bmatrix) <- dimnames(Fmatrix)
+bam.Bklb <- rowSums(rdatmods_i$B.age)
+plot_boot_vec(Bmatrix,CIpct=CIpct,xlab="year",ylab="Biomass (1000 lb)",lty=lty[1])
+# par(new=TRUE)
+points(years_i,bam.Bklb,type="o", #axes=FALSE,xlab="",ylab="",
+     col="blue",lty=lty[1])
+
+mtext(i,side=3,line=0,outer=TRUE)
+
+if(plot_pdf){dev.off()}
+}
+}
+```

### 2022-06-02 RunMSE/SEFSC/MSEPlots.Rmd
move large files out of repo

--- 2022-03-16 RunMSE/SEFSC/MSEPlots.Rmd
@@
 rm(list=ls())
-knitr::opts_chunk$set(comment=NA,echo=FALSE,message=FALSE,warning=FALSE,fig.width=8,fig.height=10)
+knitr::opts_chunk$set(comment=NA,echo=FALSE,message=FALSE,warning=FALSE,fig.width=9,fig.height=11)
 
@@
 library(latex2exp) # lets you use TeX() function to convert latex equations to R expressions for plotting
-library(SAMtool)
+library(openMSE)
 library(stringr)
 library(bamExtras)
+library(bamMSE)
+library(zoo)
 
@@
 median_noNA <- function(x){median(x,na.rm=TRUE)}
+
+# ts_reldiff()
+# Compute relative absolute differences in time series values
+ts_reldiff <- function(x,denom_type="x2", # "rollmean" can also be used for the denominator for scaling the diffs
+                       lag=1,type="absreldiff",
+                       rollmean_args=list(k=11,fill="extend")
+                       ){
+  Yrs <- c(1,length(x))
+  y1 <- Yrs[1]:(Yrs[2] - lag)
+  y2 <- (Yrs[1] + lag):Yrs[2]
+  x1 <- x[y1]
+  x2 <- x[y2]
+  rollmeanx2 <- do.call(rollmean,c(list(x=x),rollmean_args))[y2]
+
+  diff <-   x1-x2
+  denom <- switch(denom_type,
+                  x2=x2,
+                  rollmean=  rollmeanx2
+                  )
+  reldiff <- diff/denom
+  absreldiff <- (reldiff^2)^0.5
+  out <- switch(type,
+                diff=diff,
+                reldiff=reldiff,
+                absreldiff=absreldiff
+                )
+  return(out)
+}
 ```
@@
 plot_pdf <- TRUE
+generate_Hist <- FALSE
+plot_Hist <- TRUE
+
+boxplot_outline <- FALSE # Should outliers be plotted in boxplots?
+boxplot_range <- 1.5 # Set range of whiskers in boxplots. A value of zero plots whiskers to data extremes.
 
@@
                   "OM_SnowyGrouper"#,
-                  #"OM_GagGrouper")#,
-                   #"OM_capelin", "OM_POP", "OM_vs"
-                   )
+                  #"OM_GagGrouper"
+                   )
+Names_user <- gsub("^OM_","",OMNames_user)
+
 OMNames_huynh <- c("OM_CapelinHuynh", "OM_PacificOceanPerchHuynh", "OM_VermilionSnapperHuynh")
 
-scenNames_user1 <-  c("base","dep","lf","epiM","ubias","tachi","rc")
-scenNames_user2 <-  c("base","nolag","minerr","minrecdev","perfobs","ucvhi","ucvlo","vtiv"
+# Sets of scenarios
+sN1 <- "base"
+sN2 <-  c("base","ucvhi","ucvlo","ubias","tachi","taclo")
+sN3 <-  c("base","rc","minerr","minrecdev","recns","vtiv","vdome")
+sN4 <-  c("base","noempind","catcvlo","nolag","perfobs","dep","lf")
+sN5 <-  c("base","lhset","Mset","steepset","constM","epiM")
+
+sN_all <- c("sN1","sN2","sN3","sN4","sN5")
+
+# Run these sets
+sN_run <- c("sN1"
+            ,"sN2"
+            #"sN3"
+            #,"sN4"
+            #,"sN5"
             )
@@
 # All scenarios
-scenNames_user <- unique(c(scenNames_user1,scenNames_user2))
+sN <- unique(as.character(unlist(sapply(sN_run,get))))
+
+sN_plot <- sN_run
 
@@
 # averaging results together. Most other scenarios could be considered sensitivities.
-scenNames_user_alt <- c("base","dep","lf","epiM","ubias","tachi","rc")
+# sN_alt <- sN1
 
 scenNames_key <- c("base"="Base",
+                   "catcvlo"="Catch CV 0.05",
+                   "constM"="Constant M",
+                   "dep"="More depleted",
+                   "epiM"="Episodic M",
+                   "hd"="Hyper-deplete",
+                   "hs"="Hyper-stable",
+                   "lf"="Less depleted",
+                   "lhset"="Set M and steep",
+                   "mconst"="M constant",
+                   "minerr"="Minimal error",
+                   "minrecac"="Minimal rec AC",
+                   "minrecdev"="Minimal rec devs",
+                   "Mset"="Set M",
+                   "noempind"="No empirical indices",
                    "nolag"="No data lag",
-                   "hs"="Hyper-stable","hd"="Hyper-deplete",
-                   "dep"="Depleted","lf"="Lightly fished","epiM"="Episodic M",
-                   "rc"="Regime\nchange", "ubias"="Index\nbiased","ucvhi"="Index\nHigh CV",
+                   "perfobs"="Perfect observation",
+                   "rc"="Regime\nchange",
+                   "recns"="Recruitment\nnonstationary",
+                   "steepset"="Set steepness",
+                   "tachi"="TAC 1.25MSY",
+                   "taclo"="TAC 0.75MSY",
+                   "ubias"="Index\nbiased",
+                   "ucvhi"="Index\nHigh CV",
                    "ucvlo"="Index\nLow CV",
-                   "perfobs"="Perfect observation",
-                   "minerr"="Minimal error",
-                   "minrecdev"="Minimal rec devs",
-                   "tachi"="TAC 1.25MSY",
+                   "vdome"="V dome-shaped",
                    "vtiv"="V time invariant"
@@
 MPNamesAll <-         c(#"AvC",
-                        "CC1",
-                        #"DCAC","DBSRA","SPMSY",
+                        #"CC1", #"DCAC","DBSRA",
+                        #"SPMSY",
                         "SCA_1","SCA_5","SCA_10",
+                        "pMP_5","pMP_10",                        
                         "iMP_avg_5","iMP_avg_10",
-                        "iMP_buffer_5","iMP_buffer_10",
-                        "pMP_5","pMP_10"
+                        "iMP_buffer_5","iMP_buffer_10"
                         )
@@
                     "SPMSY" = "surplus production model",
-                    "SCA_1" = "SCA 1 yr",
-                    "SCA_5" = "SCA 5 yr",
-                    "SCA_10"= "SCA 10 yr",
-                    "iMP_avg_5" = "avg. index (5 yr)",
-                    "iMP_avg_10" = "avg. index (10 yr)",
-                    "iMP_buffer_5" = "buffer index (5 yr)",
-                    "iMP_buffer_10" = "buffer index (10 yr)",
-                    "pMP_5" = "projection (5 yr)",
-                    "pMP_10" = "projection (10 yr)"
+                    "SCA_1" = "Annual SCA",
+                    "SCA_5" = "Fixed TAC (5)",
+                    "SCA_10"= "Fixed TAC (10)",
+                    "iMP_avg_5" = "Avg Index (5)",
+                    "iMP_avg_10" = "Avg Index (10)",
+                    "iMP_buffer_5" = "Buffer Index (5)",
+                    "iMP_buffer_10" = "Buffer Index (10)",
+                    "pMP_5" = "Projection (5)",
+                    "pMP_10" = "Projection (10)"
                         )
@@
 
-MPNamesSub_user <- c("SCA_10","SCA_5","SCA_1","iMP_avg_10"#,"iMP_buffer_10"
-                     )
-MPNamesSub_user_legtext <- c("Fixed TAC (10)","Fixed TAC (5)","Annual assessment","Averaged Index (10)"#,"Buffered Index (10)"
-                             )
-
-# OMNames_user <- c("OM_BlackSeaBass","OM_SnowyGrouper","OM_VermilionSnapper")
-# OMNames_user <- c("OM_RedPorgy","OM_Tilefish","OM_Cobia")
+MPNamesSub_userB <- c("SCA_1","SCA_5","pMP_5","iMP_avg_5","iMP_buffer_5")
+MPNamesSub_userB_legtext <- MPNamesAll_key[MPNamesSub_userB]
+
+MPNamesSub_userA <- c("SCA_1","SCA_10","pMP_10","iMP_avg_10","iMP_buffer_10")
+MPNamesSub_userA_legtext <- MPNamesAll_key[MPNamesSub_userA]
+
+MPNamesAll_abb <- local({
+  a <- MPNamesAll
+  a <- gsub("iMP_buffer","Bfr I",a)
+  a <- gsub("iMP_avg","Avg I",a)
+  a <- gsub("pMP","Proj",a)
+  a <- gsub("iMP_","I",a)
+  a <- gsub("_([0-9]+)$"," (\\1)",a)
+  a
+  #parse(text=a)
+  })
 ```
@@
 # color function like rainbow() but without yellow (or indigo)
+blues <- colorRampPalette(c("darkblue","lightblue"))
+grays <- colorRampPalette(c("black","lightgray"))
+
 ROGBP <- colorRampPalette(c("red","orange","green","blue","purple"))
@@
 
+YieldLT <- function(...,Ref=1,Yrs=-10){Yield(...,Ref=Ref,Yrs=Yrs)}
+
 ```
@@
 ylabel = myvarName,
-FUN = mean,
+FUN = median,
 scenNames,
@@
 mgp=c(1.5,0.2,0),
+cex.axis=1.2,
+plot_format="landscape", # "portrait" or "landscape". Are species plots next to each other or stacked vertically?
 cols = setNames(ROGBP_alpha(0.5)(length(MPNamesSub)),MPNamesSub),
@@
 assessmentYears=NULL,
+assessmentYears_MP="SCA_10",
 x.at = NULL,
@@
 legend_inset=c(0,-0.5),
+legend_x.intersp = 1,
+legend_xjust=0,
+legend_ncol=1,
+legend_horiz=TRUE,
 label_axes="all", # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
-hline=1 # values to pass into abline(h=hline)
+hline=NULL, # values to pass into abline(h=hline)
+vline=NULL, # values to pass into abline(v=vline)
+hline_lty=3,
+vline_lty=3,
+...
 ){
@@
 
-if(plot_type=="addind"){
-  mfcol <- c(dim2,dim1)}else{
-  mfcol <- c(dim1,dim2)
-}
-
-par(mfcol=mfcol,mgp=mgp,mar=mar,oma=oma,tck=-0.01,xpd=FALSE,xaxs="r",yaxs="r")
-
-### LOOP THROUGH MSE OBJECTS
-for(outName_i in MSEoutNames){
+if(plot_type=="addind"){plot_format <- "portrait"}
+if(plot_format=="landscape"){
+  mfcol <- c(dim1,dim2)}else{
+  mfcol <- c(dim2,dim1)
+  }
+
+par(mfcol=mfcol,mgp=mgp,mar=mar,oma=oma,tck=-0.01,xpd=FALSE,xaxs="r",yaxs="r",cex.axis=cex.axis)
+
 topPanels <- (length(scenNames)*(seq_along(OMNames)-1)+1)
@@
 rightPanels <- tail(seq_along(MSEoutNames),length(scenNames))
+if(is.null(legend_panel)){
+legend_panel <- bottomPanels[1]
+}
+
+### LOOP THROUGH MSE OBJECTS
+for(outName_i in MSEoutNames){
 
@@
 projYears_i <- LHyear_i+1:proyears_i
-
-legend_panel <- bottomPanels[1]
 
@@
 grid(nx=NA,ny=NULL)
-abline(v=assessmentYears,lty="1111",lwd=2)
+if(is.null(assessmentYears)){
+assessmentYears_i <- apply(do.call(cbind,lapply(out_i@PPD[[assessmentYears_MP]]@Misc,FUN=function(x){x1 <- x$diagnostic; unlist(lapply(x1,FUN=function(xx){xx$Year}))})),1,median)
+}else{
+assessmentYears_i <- assessmentYears  
+}
+abline(v=assessmentYears_i,lty="1111",lwd=2)
 }
@@
       grid(nx=NA,ny=NULL)
-      abline(v=assessmentYears,lty=2,lwd=1)
+      abline(v=assessmentYears_i,lty=2,lwd=1)
       }else{
@@
 if(is.null(assessmentYears)){
-assessmentYears <- apply(do.call(cbind,lapply(out_i@PPD[[MPNamesSub]]@Misc,FUN=function(x){x1 <- x$diagnostic; unlist(lapply(x1,FUN=function(xx){xx$Year}))})),1,median)
+assessmentYears_i <- apply(do.call(cbind,lapply(out_i@PPD[[MPNamesSub]]@Misc,FUN=function(x){x1 <- x$diagnostic; unlist(lapply(x1,FUN=function(xx){xx$Year}))})),1,median)
+}else{
+  assessmentYears_i <- assessmentYears
 }
@@
 grid(nx=NA,ny=NULL)
-abline(v=assessmentYears,lty=2,lwd=1)
+abline(v=assessmentYears_i,lty=2,lwd=1)
 }
@@
         xaxt=xaxt_i,yaxt=yaxt_i,
-        xlab="",ylab="",xlim=xlim,ylim=ylim
-        )
-points(apply(Fstatus,2,median),
-       apply(Bstatus,2,median),pch=21,cex=3,lwd=2,col="black",bg=makeOpaque(cols))
+        xlab="",ylab="",xlim=xlim,ylim=ylim,
+        ...
+        )
+points(apply(Fstatus,2,proyear_phase_FUN),
+       apply(Bstatus,2,proyear_phase_FUN),pch=21,cex=3,lwd=2,col="black",bg=makeOpaque(cols))
 
@@
 
+if(i%in%topPanels&i%in%leftPanels){
+  if(length(proyear_phase)>1){
+    leg_text_phase <- paste0(proyear_phase_FUNName,"(proyears ",paste(range(proyear_phase),collapse="-"),")")
+  }else{
+    leg_text_phase <- paste0("proyear ",proyear_phase)
+  }
+  legend("topright",legend=leg_text_phase,bty="n",text.col="black",text.font = 2,x.intersp = legend_x.intersp)
+}
+
 }
@@
      ,y=rowcenter,rowLabsAll[i],
-     srt=-90,xpd=NA,font=2)
+     srt=-90,xpd=NA,font=1)
 }
@@
           inset=legend_inset,
-       horiz=TRUE,bty="n",
+       horiz=legend_horiz,bty="n",
        legend=MPNamesSub_legtext[legtext_o],
@@
        xpd=NA,
-       x.intersp=0.5
+       x.intersp = legend_x.intersp,
+       xjust=legend_xjust,
+       ncol=legend_ncol
        )
@@
 
-if(textlabpos[i]=="lo"){text(x=x,y=rep(par("usr")[3]),labels=Statmedtext,srt=90,adj=c(-0.1,0.5),font=2)}
-if(textlabpos[i]=="up"){text(x=x,y=rep(par("usr")[4]),labels=Statmedtext,srt=90,adj=c(1.2,0.5),font=2)}
+if(textlabpos[i]=="lo"){text(x=x,y=rep(par("usr")[3]),labels=Statmedtext,srt=90,adj=c(-0.1,0.5),font=1)}
+if(textlabpos[i]=="up"){text(x=x,y=rep(par("usr")[4]),labels=Statmedtext,srt=90,adj=c(1.2,0.5),font=1)}
 
@@
 text(x=par("usr")[2]*1.05,y=rowcenter,rowLabsAll[i],
-     srt=-90,xpd=NA,font=2)
+     srt=-90,xpd=NA,font=1)
 }
@@
 ```{r function PMsummary}
+
 # compute and plot summary statistics for Performance metrics
-PMsummary <- function(PMName,OMNames=OMNames_user,scenNames,MPs=NULL,
-                      slot_to_plot="Prob", # Can be either "Prob" or "Stat"
-                      main_line=-1.5,
-                      hline=1,hline_lty=1,
-                      par_args=list(mfrow=c(length(OMNames),1), 
-                                    mar=c(0,2,0,1), oma=c(6,2,1,0),
-                                    mgp=c(0.8,0.2,0), tck=-0.01),
+PMsummary <- function(PMName,
+                      OMNames = OMNames_user,
+                      scenNames,
+                      MPs = NULL,
+                      xaxis_label = NULL,
+                      xaxis_label_outer = "Management procedure",
+                      slot_to_plot = "Prob", # Can be either "Prob" or "Stat"
+                      main_line = -1.5,
+                      hline = NULL,
+                      hline_lty = 3,
+                      par_args = list(mfrow = c(length(OMNames),1), mar = c(0,2,0,1), 
+                                      oma = c(3,3,1,0), mgp = c(0.8,0.2,0), tck = -0.01, cex.axis=1.0),
+                      y.cex.axis=1.2,
+                      n_yr_groups = 1, # Number of groups to split years into
+                      group_space = NULL,  # Additional spacing between groups of boxes
                       ...){
@@
   }
+  if(!"col"%in%names(dots)){
+    colorFUN = colorRampPalette(c("lightblue","darkblue"))
+    dots$col <-  colorFUN(n_yr_groups)
+  }
+  if(!"outcol"%in%names(dots)){
+    dots$outcol <- dots$col
+  }
+  if(!"outpch"%in%names(dots)){
+    dots$outpch <- 16
+  }
+  if(is.null(group_space)){
+    group_space <- (n_yr_groups-1)*.75
+  }
 
@@
       MSEout_ij <- get(MSEoutNames_ij)
-      PMout_ij <- PM(MSEout_ij)
-        MPs_ij <- PMout_ij@MPs
-        out_ij <- slot(PMout_ij,slot_to_plot)
-      if(!is.null(MPs)){
-        out_ij <- out_ij[,match(MPs,MPs_ij)]
-        MPs_ij <- MPs
-      }
-      dimnames(out_ij) <- list("sim"=seq(1:dim(out_ij)[1]), "MPs"=MPs_ij)
-      out_ij <- cbind("scen"=scenNames_j,as.data.frame(out_ij))
-      out_list_i[[MSEoutNames_ij]] <- out_ij
-
+      proyears_ij <- MSEout_ij@proyears
+      yr_ij <- 1:proyears_ij
+      breaks_ij <- round(seq(min(yr_ij),max(yr_ij),length=n_yr_groups+1))
+
+      yr_groups_ij <- as.numeric(cut(yr_ij,breaks=breaks_ij,include.lowest = TRUE))
+
+      for(k in 1:n_yr_groups){
+        MSEoutNames_ijk <- paste(MSEoutNames_ij,sprintf("%02.0f",k),sep="_")  
+        PMout_ijk <- PM(MSEout_ij,Yrs=range(yr_ij[yr_groups_ij==k]))
+        MPs_ijk <- PMout_ijk@MPs
+        out_ijk <- slot(PMout_ijk,slot_to_plot)
+        if(!is.null(MPs)){ # Possibly subset MPs
+          out_ijk <- out_ijk[,match(MPs,MPs_ijk)]
+          MPs_ijk <- MPs
+        }
+        dimnames(out_ijk) <- list("sim"=1:dim(out_ijk)[1], "MPs"=MPs_ijk)
+        out_ijk <- cbind("scen"=scenNames_j,"yr_group"=k,as.data.frame(out_ijk))
+        out_list_i[[MSEoutNames_ijk]] <- out_ijk
+
+      } # end n_yr_groups
     } 
@@
     out_df_i <- do.call(rbind,out_list_i)
+    out_df_i <- reshape2::melt(data=out_df_i,id.vars=c("scen","yr_group"))
     out_list[[paste0("out_df_",Names_i,"_",PMName)]] <- out_df_i
+
     # Plot stuff
-      dots$xaxt <- ifelse(match(OMNames_i,rev(OMNames))==1,"s","n")
-
-      do.call(boxplot,c(list(out_df_i[,-1],main=""),dots))
+    dots$xaxt <- ifelse(match(OMNames_i,rev(OMNames))==1,"n","n")
+    n_group <- length(unique(out_df_i$yr_group))
+    n_variable <- length(unique(out_df_i$variable))
+
+    group_space_add <- rep(1:n_variable,each=n_group)*group_space
+    box_at <- 1:(n_group*n_variable)+group_space_add
+
+    dots$cex.axis <- y.cex.axis
+
+    do.call(boxplot,c(list(formula = value ~ yr_group + variable, data = out_df_i,
+                           main = "", at = box_at),dots))
+
     mtext(Names_i,side=3,line=main_line,outer=FALSE,font=2)
+
+    if(!is.null(hline)){
       abline(h=hline,lty=hline_lty)
     }
+  }
+  if(is.null(xaxis_label)){xaxis_label <- MPs}
+  xaxis_label_at <- apply(matrix(box_at,nrow=n_group,ncol=length(xaxis_label)),2,mean)
+
+  axis(side = 1, at = xaxis_label_at, labels = xaxis_label)
+  mtext(xaxis_label_outer,side=1,line=1.5, outer=TRUE,font=1)
 
@@
 # compute and plot summary statistics for Performance metrics
-MSEsummary <- function(MSEslotName,OMNames=OMNames_user,scenNames,MPs=NULL,
+MSEsummary <- function(MSEslotName,
+                       OMNames=OMNames_user,
+                       scenNames,
+                       MPs=NULL,
+                       xaxis_label = NULL,
+                       xaxis_label_outer = "Management procedure",
                        main_line=-1.5,
-                       hline=1,hline_lty=1,
+                       hline=NULL,
+                       hline_lty=3,
                       par_args=list(mfrow=c(length(OMNames),1), 
-                                    mar=c(3,2,1,1), oma=c(1,2,0,0),
-                                    mgp=c(0.8,0.2,0), tck=-0.01),
+                                    mar=c(0,2,0,1), oma=c(3,3,1,0),
+                                    mgp=c(0.8,0.2,0), tck=-0.01, cex.axis=1.0),
+                      y.cex.axis=1.2,
+                      n_yr_groups=1, # Number of groups to split years into
+                      FUN_yr_groups=NULL,
+                      #scale_by_nsim=FALSE,
+                      group_space = NULL,  # Additional spacing between groups of boxes
                       ...){
@@
 }
+if(!"col"%in%names(dots)){
+ colorFUN = colorRampPalette(c("lightblue","darkblue"))
+ dots$col <-  colorFUN(n_yr_groups)
+}
+if(!"outcol"%in%names(dots)){
+ dots$outcol <- dots$col
+}
+if(!"outpch"%in%names(dots)){
+ dots$outpch <- 16
+}
+
+if(is.null(group_space)){
+  group_space <- (n_yr_groups-1)*.75
+}
+
 out_list <- list()
@@
     MSEout_ij <- get(MSEoutNames_ij)
+    proyears_ij <- MSEout_ij@proyears
+    nsim_ij <- MSEout_ij@nsim
+    yr_ij <- 1:proyears_ij
+    breaks_ij <- round(seq(min(yr_ij),max(yr_ij),length=n_yr_groups+1))
+
+    yr_groups_ij <- as.numeric(cut(yr_ij,breaks=breaks_ij,include.lowest = TRUE))
+
     if(!is.expression(MSEslotName)){
-      slot_k <- slot(MSEout_ij,MSEslotName) %>% apply(2,as.numeric)
+      slot_k <- slot(MSEout_ij,MSEslotName)
     }else{
-      slot_k <- eval(MSEslotName) %>% apply(2,as.numeric)
-    }
-    slot_k <- slot(MSEout_ij,MSEslotName) %>% apply(2,as.numeric)
-    MPs_ij <- MSEout_ij@MPs
+      slot_k <- eval(MSEslotName)
+    }
+    list_slot_km <- list()
+    for(m in 1:n_yr_groups){
+      MPs_ijm <- MSEout_ij@MPs
+      if(is.null(FUN_yr_groups)){
+      slot_km <- slot_k[,,which(yr_groups_ij==m)] %>% apply(2,as.numeric)
+      }else{
+      slot_km <- slot_k[,,which(yr_groups_ij==m)] %>% apply(1:2,FUN_yr_groups)
+      # if(scale_by_nsim){
+      #   slot_km <- slot_km/nsim_ij
+      # }
+      }
     if(!is.null(MPs)){
-      slot_k <- slot_k[,match(MPs,MPs_ij)]
-      MPs_ij <- MPs
-    }
-    dimnames(slot_k) <- list(NULL, "MPs"=MPs_ij)
-    slot_k <- cbind("scen"=scenNames_j,as.data.frame(slot_k))
-    slot_list_i[[MSEoutNames_ij]] <- slot_k
+      slot_km <- slot_km[,match(MPs,MPs_ijm)]
+      MPs_ijm <- MPs
+    }
+      dimnames(slot_km) <- list("sim"=1:dim(slot_km)[1], "MPs"=MPs_ijm)
+      list_slot_km[[m]] <- cbind("yr_group"=m,as.data.frame(slot_km))
+    }
+
+    slot_df_km <- do.call(rbind,list_slot_km)
+
+    slot_df_km <- cbind("scen"=scenNames_j,as.data.frame(slot_df_km))
+    slot_list_i[[MSEoutNames_ij]] <- slot_df_km
 
@@
   # Plot stuff
-  do.call(boxplot,c(list(slot_df_i[,-1],main=""),dots))
+  dots$xaxt <- ifelse(match(OMNames_i,rev(OMNames))==1,"n","n")
+  n_group <- length(unique(slot_df_i$yr_group))
+  n_variable <- length(unique(slot_df_i$variable))
+
+  group_space_add <- rep(1:n_variable,each=n_group)*group_space
+  box_at <- 1:(n_group*n_variable)+group_space_add
+
+  dots$cex.axis <- y.cex.axis
+
+  do.call(boxplot,c(list(formula=value~yr_group+variable,data=slot_df_i,main="",at=box_at),dots))
   mtext(Names_i,side=3,line=main_line,outer=FALSE,font=2)
+    if(!is.null(hline)){
       abline(h=hline,lty=hline_lty)
     }
+}
+  if(is.null(xaxis_label)){xaxis_label <- MPs}
+  xaxis_label_at <- apply(matrix(box_at,nrow=n_group,ncol=length(xaxis_label)),2,mean)
+
+  axis(side = 1, at = xaxis_label_at, labels = xaxis_label)
+  mtext(xaxis_label_outer,side=1,line=1.5, outer=TRUE,font=1)
 
@@
 ```{r data}
+# Read in list of rdat modifications used when plotting bam results compared with Hist objects
+load("rdatmods.RData")
+
 # Read in data for original operating models
@@
 # Read in data for modified operating models
-for(file.i in list.files("OM_modified")){
+file_OMNames_base <- list.files("OM_modified")[grepl("base.rds$",list.files("OM_modified"))]
+OMNames_base <- gsub(".rds$","",file_OMNames_base)
+for(file.i in file_OMNames_base){
   assign(gsub(".rds","",file.i),readRDS(file.path("OM_modified",file.i)))
@@
 for(file.i in list.files("MSE_obj")){
+  if(file.i%in%paste0("MSE_",rep(Names_user,each=length(sN)),"_",sN,".rds")){
+
     out_i <- readRDS(file.path("MSE_obj",file.i))
@@
 speciesNames_huynh <- gsub("OM_","",OMNames_huynh)
-MSEoutNames_user1 <- paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames_user1)),
+MSEoutNames_user1 <- paste0(rep(gsub("OM","MSE",OMNames),each=length(get(sN_run[1]))),
                      "_",
-                     rep(scenNames_user1,length(OMNames))
-                     )
+                     rep(get(sN_run[1]),length(OMNames))
+                     )
+
+```
+
+```{r OM summary table}
+# Get values from base model OMs
+for(OMNames_i in OMNames_user){
+MSE_i <- get(paste0(gsub("^OM_","MSE_",OMNames_i),"_base"))
+MSEOM_i <- MSE_i@OM
+steep <- range(MSEOM_i$hs)
+Linf <- range(MSEOM_i$Linf)
+}
 
@@
     plot_MSE_ts(
-      OMNames= OMNames, scenNames=scenNames_user1,
+      OMNames= OMNames, scenNames=get(sN[1]),
       myvarName = expression(slot(out_i@PPD[[MP_name_i]],"Ind")),
@@
       ylabel = "index of abundance",
-      MPNamesSub = MPNamesSub_user,
-      MPNamesSub_legtext=MPNamesSub_user_legtext,
-      rowLabs=scenNames_key[scenNames_user1],
+      MPNamesSub = MPNamesSub_userA,
+      MPNamesSub_legtext=MPNamesSub_userA_legtext,
+      rowLabs=scenNames_key[get(sN[1])],
       oma=c(3,4,5,3),
@@
 
-```{r plot AddInd, eval=TRUE}
+```{r plot AddIndbase, eval=TRUE}
 # This code is set up to make each set of plots for each MP, but the indices are basically the same
 if(plot_pdf){pdf("Figs/AddInd.pdf")}
-for(MP_name_i in "SCA_5"){#MPNamesAll){
+for(MP_name_i in "SCA_10"){#MPNamesAll){
     # Ind
@@
       MPNamesSub = MP_name_i,
-      # MPNamesSub_legtext=MPNamesSub_user_legtext,
+      # MPNamesSub_legtext=MPNamesSub_userA_legtext,
       #rowLabs=scenNames_key["addind"],
@@
 
-```{r plot sims proj base, eval=FALSE}
-MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
-scen <- "base"
-
+```{r plot AddInducvlo, eval=FALSE}
+# This code is set up to make each set of plots for each MP, but the indices are basically the same
+# if(plot_pdf){pdf("Figs/AddInd.pdf")}
+for(MP_name_i in "SCA_10"){#MPNamesAll){
+    # Ind
+    # MSE_i <- get(MSE_name_j)
+    plot_MSE_ts(
+      OMNames= OMNames, scenNames="ucvlo",
+      myvarName = expression(slot(out_i@PPD[[MP_name_i]],"AddInd")),
+      plot_type = "addind",
+      ylabel = "index of abundance",
+      # FUN=mean_noNA,
+      MPNamesSub = MP_name_i,
+      # MPNamesSub_legtext=MPNamesSub_userA_legtext,
+      #rowLabs=scenNames_key["addind"],
+      assessmentYears=1,
+      xlabel="year",
+      oma=c(3,4,5,3),
+      ylim=c(0,12 ),
+      main_line = -1.5,
+      hline=NA
+    )
+  #title(main=MP_name_i,outer=TRUE)
+}
+# if(plot_pdf){dev.off()}
+```
+
+```{r plot sims}
+MPs_sim <- c("SCA_1","SCA_10","iMP_avg_10","pMP_10")
+scen <- c("base")
+
+for(scen_i in scen){
 for(OMName_i in OMNames_user){
 Name_i <- gsub("^OM_","",OMName_i)
-MSEoutName_i <- paste0(gsub("^OM","MSE",OMName_i),paste0("_",scen))
+MSEoutName_i <- paste0(gsub("^OM","MSE",OMName_i),paste0("_",scen_i))
 MSEOut_i <- get(MSEoutName_i)
 
-figName_ij <- paste0("sims_",MSEoutName_i,"_",scen,".pdf")
-if(plot_pdf){pdf(file.path("Figs",figName_ij))}
-plot_MSE_sims(MSEOut_i,MPs=MPs_sim,type="proj",
-              lwd=2,sims=sample(1,1:50),
-              title_main = paste0(Name_i,", ",scen),
-              varNames = c("Catch","TAC","FM","F_FMSY",#"recruit",
-                           "SSB","SB_SBMSY"))
-if(plot_pdf){dev.off()}
-}
-
-```
-
-```{r plot sims base}
-MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
-scen <- "base"
-
-for(OMName_i in OMNames_user){
-Name_i <- gsub("^OM_","",OMName_i)
-MSEoutName_i <- paste0(gsub("^OM","MSE",OMName_i),paste0("_",scen))
-MSEOut_i <- get(MSEoutName_i)
-
-figName_ij <- paste0("sims_",MSEoutName_i,"_",scen,".pdf")
+figName_ij <- paste0("sims",gsub("MSE|_","",MSEoutName_i),".pdf")
 if(plot_pdf){pdf(file.path("Figs",figName_ij))}
@@
               lwd=2,sims=sample(1,1:50),
-              title_main = paste0(Name_i,", ",scen))
-if(plot_pdf){dev.off()}
-}
-
-```
-
-```{r plot sims minerr, eval=TRUE}
-MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
-scen <- "minerr"
-
-for(OMName_i in OMNames_user){
-Name_i <- gsub("^OM_","",OMName_i)
-MSEoutName_i <- paste0(gsub("^OM","MSE",OMName_i),paste0("_",scen))
-MSEOut_i <- get(MSEoutName_i)
-
-figName_ij <- paste0("sims_",MSEoutName_i,"_",scen,".pdf")
-if(plot_pdf){pdf(file.path("Figs",figName_ij))}
-plot_MSE_sims(MSEOut_i,MPs=MPs_sim,type="histproj",
-              lwd=2,sims=1,
-              title_main = paste0(Name_i,", ",scen))
-if(plot_pdf){dev.off()}
-}
-```
-
-```{r plot sims minrecdev}
-MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
-scen <- "minrecdev"
-
-for(OMName_i in OMNames_user){
-Name_i <- gsub("^OM_","",OMName_i)
-MSEoutName_i <- paste0(gsub("^OM","MSE",OMName_i),paste0("_",scen))
-MSEOut_i <- get(MSEoutName_i)
-
-figName_ij <- paste0("sims_",MSEoutName_i,"_",scen,".pdf")
-if(plot_pdf){pdf(file.path("Figs",figName_ij))}
-plot_MSE_sims(MSEOut_i,MPs=MPs_sim,type="histproj",
-              lwd=2,sims=1,
-              title_main = paste0(Name_i,", ",scen))
-if(plot_pdf){dev.off()}
-}
-
-# Check if assessments are converging and hessians inverting
-# unlist(lapply(MSE_BlackSeaBass_minrecdev@PPD$SCA_1@Misc,function(i){table(unlist(lapply(i$diagnostic,function(j){j$hess})))}))
-```
-
-```{r plot sims perfobs}
-MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
-scen <- "perfobs"
-
-for(OMName_i in OMNames_user){
-Name_i <- gsub("^OM_","",OMName_i)
-MSEoutName_i <- paste0(gsub("^OM","MSE",OMName_i),paste0("_",scen))
-MSEOut_i <- get(MSEoutName_i)
-
-figName_ij <- paste0("sims_",MSEoutName_i,"_",scen,".pdf")
-if(plot_pdf){pdf(file.path("Figs",figName_ij))}
-plot_MSE_sims(MSEOut_i,MPs=MPs_sim,type="histproj",
-              lwd=2,sims=1,
-              title_main = paste0(Name_i,", ",scen))
-if(plot_pdf){dev.off()}
-}
-
-```
-
-```{r plot sims "vtiv"}
-MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
-scen <- "vtiv"
-
-for(OMName_i in OMNames_user){
-Name_i <- gsub("^OM_","",OMName_i)
-MSEoutName_i <- paste0(gsub("^OM","MSE",OMName_i),paste0("_",scen))
-MSEOut_i <- get(MSEoutName_i)
-
-figName_ij <- paste0("sims_",MSEoutName_i,"_",scen,".pdf")
-#if(plot_pdf){pdf(file.path("Figs",figName_ij))}
-plot_MSE_sims(MSEOut_i,MPs=MPs_sim,type="histproj",
-              lwd=2,sims=1,
-              title_main = paste0(Name_i,", ",scen))
-#if(plot_pdf){dev.off()}
-}
-
-```
-
-```{r summary plots, eval=TRUE}
+              title_main = paste0(Name_i,", ",scen_i))
+if(plot_pdf){dev.off()}
+}
+}
+
+```
+
+```{r boxplots plots combining multiple scenarios, eval=TRUE}
 # Summary plots combining all years and all scenarios
-
-if(plot_pdf){pdf("Figs/boxplot_P_Bgrt75BMSY.pdf")}
-P75_out <- PMsummary("P75",scenNames=scenNames_user_alt,MPs=MPNamesAll,
-                     cex.axis=1,las=2,outline=FALSE,
-                     boxwex=0.25,ylab="",ylim=c(0,1.1),
-                     hline=NA)
-mtext("P(B > 0.75 BMSY)",2,outer=TRUE,font=2)
-if(plot_pdf){dev.off()}
-
-if(plot_pdf){pdf("Figs/boxplot_P_BgrtBMSY.pdf")}
-P100_out <- PMsummary("P100",scenNames=scenNames_user_alt,MPs=MPNamesAll,
-                     cex.axis=1,las=2,outline=FALSE,
-                     boxwex=0.25,ylab="",ylim=c(0,1.1),
-                     hline=NA)
-mtext("P(B > BMSY)",2,outer=TRUE,font=2)
-if(plot_pdf){dev.off()}
-
-if(plot_pdf){pdf("Figs/boxplot_P_FlssFMSY.pdf")}
-PNOF_out <- PMsummary("PNOF",scenNames=scenNames_user_alt,MPs=MPNamesAll,
-                     cex.axis=1,las=2,outline=FALSE,
-                     boxwex=0.25,ylab="",ylim=c(0,1.1),
-                     hline=NA)
-mtext("P(F < FMSY)",2,outer=TRUE,font=2)
-if(plot_pdf){dev.off()}
-
-if(plot_pdf){pdf("Figs/boxplot_AAVY.pdf")}
-AAVY_out <- PMsummary("AAVY",scenNames=scenNames_user_alt,MPs=MPNamesAll,
+for(i in match(sN_plot,sN_all)){
+
+sN_i <- get(sN_all[i])
+
+if(plot_pdf){pdf(paste0("Figs/boxplot","PBgrt75BMSY",i,".pdf"))}
+P75_out <- PMsummary("P75",scenNames=sN_i,MPs=MPNamesAll,
+                     las=2,outline=boxplot_outline,range=boxplot_range,
+                     boxwex=0.5,ylab="",ylim=c(0,1.1),
+                     hline=NA,n_yr_groups=3,
+                     xaxis_label=MPNamesAll_abb
+                     )       
+mtext("P(B > 0.75 BMSY)",side = 2,outer=TRUE,font=1)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf(paste0("Figs/boxplot","PBgrtBMSY",i,".pdf"))}
+P100_out <- PMsummary("P100",scenNames=sN_i,MPs=MPNamesAll,
+                     las=2,outline=boxplot_outline,range=boxplot_range,
+                     boxwex=0.5,ylab="",ylim=c(0,1.1),
+                     hline=NA,n_yr_groups=3,
+                     xaxis_label=MPNamesAll_abb
+                     )
+mtext("P(B > BMSY)",2,outer=TRUE,font=1)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf(paste0("Figs/boxplot","PFlssFMSY",i,".pdf"))}
+PNOF_out <- PMsummary("PNOF",scenNames=sN_i,MPs=MPNamesAll,
+                     las=2,outline=boxplot_outline,range=boxplot_range,
+                     boxwex=0.5,ylab="",ylim=c(0,1.1),
+                     hline=NA,n_yr_groups=3,
+                     xaxis_label=MPNamesAll_abb
+                     )
+mtext("P(F < FMSY)",2,outer=TRUE,font=1)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf(paste0("Figs/boxplot","AAVY",i,".pdf"))}
+AAVY_out <- PMsummary("AAVY",OMNames = OMNames_user,
+                      scenNames=sN_i,MPs=MPNamesAll,
                      slot_to_plot = "Stat",
-                     cex.axis=1,las=2,outline=FALSE,
-                     boxwex=0.25,ylab="",ylim=c(0,1.1),
-                     hline=NA)
-mtext("Avg. Annual Variability in Yield",2,outer=TRUE,font=2)
-if(plot_pdf){dev.off()}
-
-if(plot_pdf){pdf("Figs/boxplot_SB_SBMSY.pdf")}
-MSEsummary("SB_SBMSY",scenNames=scenNames_user_alt,MPs=MPNamesAll,
-           cex.axis=0.75,las=2,outline=FALSE,boxwex=0.25,ylab="")
-mtext("SSB/SSBmsy",2,outer=TRUE,font=2)
-if(plot_pdf){dev.off()}
-
-if(plot_pdf){pdf("Figs/boxplot_F_FSY.pdf")}
-MSEsummary("F_FMSY",scenNames=scenNames_user_alt,MPs=MPNamesAll,
-           cex.axis=0.75,las=2,outline=FALSE,boxwex=0.25,ylab="")
-mtext("F/Fmsy",2,outer=TRUE,font=2)
-if(plot_pdf){dev.off()}
-
-## Which is the best MP?
-
-### Highest yield
-
-### Most consistent yield
-
-### Lowest probability of overfishing
-```
-
-```{r plot time series1,eval=FALSE}
+                     las=2,outline=boxplot_outline,range=boxplot_range,
+                     boxwex=0.5,ylab="",ylim=c(0,1.0),
+                     hline=0.2,n_yr_groups=3,
+                     xaxis_label=MPNamesAll_abb
+                     )   
+mtext("Avg. Annual Variability in Yield",2,outer=TRUE,font=1)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf(paste0("Figs/boxplot","SBSBMSY",i,".pdf"))}
+MSEsummary("SB_SBMSY",scenNames=sN_i,MPs=MPNamesAll,
+           las=2,outline=boxplot_outline,range=boxplot_range,boxwex=0.5,ylab="",
+           n_yr_groups=3,hline=1,ylim=c(0,5),
+           xaxis_label=MPNamesAll_abb
+)
+mtext("SSB/SSBmsy",2,outer=TRUE,font=1)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf(paste0("Figs/boxplot","FFMSY",i,".pdf"))}
+MSEsummary("F_FMSY",scenNames=sN_i,MPs=MPNamesAll,
+           las=2,outline=boxplot_outline,range=boxplot_range,boxwex=0.5,ylab="",
+           n_yr_groups=3,hline=1,ylim=c(0,5),
+           xaxis_label=MPNamesAll_abb
+)
+mtext("F/Fmsy",2,outer=TRUE,font=1)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf(paste0("Figs/boxplot","CatchTotal",i,".pdf"))}
+MSEsummary("Catch",scenNames=sN_i,MPs=MPNamesAll,
+           las=2,outline=boxplot_outline,range=boxplot_range,boxwex=0.5,ylab="",
+           n_yr_groups=3,FUN_yr_groups=sum,
+           xaxis_label=MPNamesAll_abb
+)
+mtext("Total catch (1000 lb)",2,outer=TRUE,line=1.2,font=1)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf(paste0("Figs/boxplot","CatchTotalMSY",i,".pdf"))}
+MSEsummary(expression(MSEout_ij@Catch/
+                        (MSEout_ij@RefPoint$MSY[,,-(1:MSEout_ij@nyears)]*MSE_BlackSeaBass_base@proyears)),
+           scenNames=sN_i,MPs=MPNamesAll,
+           las=2,outline=boxplot_outline,range=boxplot_range,boxwex=0.5,ylab="",
+           n_yr_groups=3,FUN_yr_groups=sum,
+           xaxis_label=MPNamesAll_abb,
+           ylim=c(0,1)
+)
+mtext("Total catch/(MSY*proyears)",2,outer=TRUE,font=1)
+if(plot_pdf){dev.off()}
+
+# My version of AAVY, to compare with the openMSE function used in PMsummary
+if(plot_pdf){pdf(paste0("Figs/boxplot","AAVYNK",i,".pdf"))}
+AAVYNK_out <- MSEsummary("Catch",scenNames=sN_i,MPs=MPNamesAll,
+                         OMNames = OMNames_user,
+           las=2,outline=boxplot_outline,range=boxplot_range,boxwex=0.5,ylab="",
+           n_yr_groups=3,FUN_yr_groups=function(x){mean(ts_reldiff(x,lag=1))},
+           xaxis_label=MPNamesAll_abb,hline=0.2,ylim=c(0,1)
+)
+mtext("Avg. Annual Variability in Yield",2,outer=TRUE,font=1)
+if(plot_pdf){dev.off()}
+
+# My version of AAVY with a lag of 2
+if(plot_pdf){pdf(paste0("Figs/boxplot","AAVYNKlag2yr",i,".pdf"))}
+AAVYNK_out <- MSEsummary("Catch",scenNames=sN_i,MPs=MPNamesAll,
+                         OMNames = OMNames_user,
+           las=2,outline=boxplot_outline,range=boxplot_range,boxwex=0.5,ylab="",
+           n_yr_groups=3,FUN_yr_groups=function(x){mean(ts_reldiff(x,lag=2))},
+           xaxis_label=MPNamesAll_abb,hline=0.2,ylim=c(0,1)
+)
+mtext("Avg. Annual Variability in Yield (lag 2 yr)",2,outer=TRUE,font=1)
+if(plot_pdf){dev.off()}
+
+# 75th percentile of interannual variation in catch
+if(plot_pdf){pdf(paste0("Figs/boxplot","75pctAVY",i,".pdf"))}
+boxplot75pctAVY1_out <- MSEsummary("Catch",scenNames=sN_i,MPs=MPNamesAll,
+                         OMNames = OMNames_user,
+           las=2,outline=boxplot_outline,range=boxplot_range,boxwex=0.5,ylab="",
+           n_yr_groups=3,
+           FUN_yr_groups=function(x){as.numeric(quantile(ts_reldiff(x,lag=1),probs=0.75))},
+           xaxis_label=MPNamesAll_abb,hline=0.2,ylim=c(0,1)
+)
+mtext("75th percentile Annual Variability in Yield",2,outer=TRUE,font=1)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf(paste0("Figs/boxplot","CatchCV",i,".pdf"))}
+MSEsummary("Catch",scenNames=sN_i,MPs=MPNamesAll,
+           las=2,outline=boxplot_outline,range=boxplot_range,boxwex=0.5,ylab="",
+           n_yr_groups=3,FUN_yr_groups=cv,hline=NA,
+           xaxis_label=MPNamesAll_abb,
+                            ylim=c(0,2)
+)
+mtext("cv catch",2,outer=TRUE,font=1)
+if(plot_pdf){dev.off()}
+
+}
+```
+
+```{r plot time series A,eval=TRUE}
+legend_inset_1 <- c(0,-0.5)
+legend_inset <- c(0,-0.8)
+
+pdf_wid <- 8
+pdf_hgt_1 <- 8
+pdf_hgt <- 8
+
+FUN_tmp <- median
+for(i in match(sN_plot,sN_all)){
+if(i==1){
+  legend_inset_i<-legend_inset_1
+  pdf_hgt_i <- pdf_hgt_1
+}else{
+  legend_inset_i<-legend_inset
+  pdf_hgt_i <- pdf_hgt
+}
+
+sN_i <- get(sN_all[i])
+
+if(length(sN_i)==1){
+  add_args <- list(plot_format = "portrait",
+                   main_line = -1.5,
+                   legend_panel = 4,
+                   mgp=c(1,0.2,0),
+                   legend_cex=1.2,
+                   legend_inset=legend_inset_i)
+}else{
+  add_args <- list(legend_cex=1.2,
+                   legend_inset=legend_inset_i)
+}
+
+# # VB
+# do.call(plot_MSE_ts,
+#  c(list(
+# OMNames= OMNames, scenNames=sN_i,
+# myvarName = "VB",
+# ylabel = expression(median~(VB)),
+# FUN = FUN_tmp,
+# MPNamesSub = MPNamesSub_userA,
+# MPNamesSub_legtext=MPNamesSub_userA_legtext,
+# rowLabs=scenNames_key[sN_i]
+# ),add_args))
+
+# SSB
+if(plot_pdf){pdf(paste0("Figs/ts","SSB",i,".pdf"), width=pdf_wid, height=pdf_hgt_i)}
+do.call(plot_MSE_ts,
+  c(list(
+  OMNames= OMNames, scenNames=sN_i,
+  myvarName = "SSB",
+  ylabel = expression(median~(SSB)),
+  FUN = FUN_tmp,
+  MPNamesSub = MPNamesSub_userA,
+  MPNamesSub_legtext=MPNamesSub_userA_legtext,
+  rowLabs=scenNames_key[sN_i]
+  ),add_args))
+if(plot_pdf){dev.off()}
+
+# F
+if(plot_pdf){pdf(paste0("Figs/ts","F",i,".pdf"), width=pdf_wid, height=pdf_hgt_i)}
+do.call(plot_MSE_ts,
+  c(list(
+OMNames= OMNames, scenNames=sN_i,
+myvarName = "FM",
+ylabel = expression(median~(F)),
+FUN = FUN_tmp,
+MPNamesSub = MPNamesSub_userA,
+MPNamesSub_legtext=MPNamesSub_userA_legtext,
+rowLabs=scenNames_key[sN_i]
+),add_args))
+if(plot_pdf){dev.off()}
+
+# # TAC
+# do.call(plot_MSE_ts,
+#  c(list(
+# OMNames= OMNames, scenNames=sN_i,  
+# myvarName = "TAC",
+# ylabel = expression(median~(TAC)),
+# FUN = FUN_tmp,
+# MPNamesSub = MPNamesSub_userA,
+# MPNamesSub_legtext=MPNamesSub_userA_legtext,
+# rowLabs=scenNames_key[sN_i] 
+# ),add_args))
+
+# Catch
+if(plot_pdf){pdf(paste0("Figs/ts","Catch",i,".pdf"), width=pdf_wid, height=pdf_hgt_i)}
+do.call(plot_MSE_ts,
+  c(list(
+OMNames= OMNames, scenNames=sN_i,  
+myvarName = "Catch",
+ylabel = expression(median~(Catch)),
+FUN = FUN_tmp,
+MPNamesSub = MPNamesSub_userA,
+MPNamesSub_legtext=MPNamesSub_userA_legtext,
+rowLabs=scenNames_key[sN_i]
+),add_args))
+if(plot_pdf){dev.off()}
+
+# SSB/SSBmsy
+if(plot_pdf){pdf(paste0("Figs/ts","SSBSSBmsy",i,".pdf"), width=pdf_wid, height=pdf_hgt_i)}
+do.call(plot_MSE_ts,
+  c(list(
+  OMNames= OMNames, scenNames=sN_i,
+  myvarName = "SB_SBMSY",
+  ylabel = expression(median~(SSB/SSBmsy)),
+  FUN = FUN_tmp,
+  ylim=c(0,2.5),
+  MPNamesSub = MPNamesSub_userA,
+  MPNamesSub_legtext=MPNamesSub_userA_legtext,
+  rowLabs=scenNames_key[sN_i],
+  hline=1, hline_lty=1
+),add_args))
+if(plot_pdf){dev.off()}
+
+# F/Fmsy
+if(plot_pdf){pdf(paste0("Figs/ts","FFmsy",i,".pdf"), width=pdf_wid, height=pdf_hgt_i)}
+do.call(plot_MSE_ts,
+  c(list(
+  OMNames= OMNames, scenNames=sN_i,
+  myvarName = "F_FMSY",
+  ylabel = expression(median~(F/Fmsy)),
+  FUN = FUN_tmp,
+  ylim=c(0,4.5),
+  MPNamesSub = MPNamesSub_userA,
+  MPNamesSub_legtext=MPNamesSub_userA_legtext,
+  rowLabs=scenNames_key[sN_i],
+  hline=1, hline_lty=1
+),add_args))
+if(plot_pdf){dev.off()}
+
+# C/MSY
+if(plot_pdf){pdf(paste0("Figs/ts","CatchMSY",i,".pdf"), width=pdf_wid, height=pdf_hgt_i)}
+do.call(plot_MSE_ts,
+  c(list(
+  OMNames= OMNames, scenNames=sN_i,
+  myvarName = "Catch",
+  myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+  ylabel = expression(median~(Catch/MSY)),
+  FUN = FUN_tmp,
+  ylim=c(0,2.5),
+  MPNamesSub = MPNamesSub_userA,
+  MPNamesSub_legtext=MPNamesSub_userA_legtext,
+  rowLabs=scenNames_key[sN_i],
+  hline=1, hline_lty=1
+),add_args))
+if(plot_pdf){dev.off()}
+
+# 
+# # TAC/MSY
+# do.call(plot_MSE_ts,
+#  c(list(
+#   OMNames= OMNames, scenNames=sN_i,
+#   myvarName = "TAC",
+#   myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+#   ylabel = expression(median~(TAC/MSY)),
+#   FUN = FUN_tmp,
+#   ylim=c(0,2),
+#   MPNamesSub = MPNamesSub_userA,
+#   MPNamesSub_legtext=MPNamesSub_userA_legtext,
+#   rowLabs=scenNames_key[sN_i]
+# ),add_args))
+# 
+# # C/TAC
+# do.call(plot_MSE_ts,
+#  c(list(
+#   OMNames= OMNames, scenNames=sN_i,  
+#   myvarName = "Catch",
+#   myvarDenomExpr = expression(slot(out_i,"TAC")),
+#   ylabel = expression(median~(C/TAC)),
+#   FUN = FUN_tmp,
+#   ylim=c(0,1.1),
+#   MPNamesSub = MPNamesSub_userA,
+#   MPNamesSub_legtext=MPNamesSub_userA_legtext,
+#   rowLabs=scenNames_key[sN_i]
+# ),add_args))
+
+# MSY
+# do.call(plot_MSE_ts,
+#   c(list(
+# OMNames= OMNames, scenNames=sN_i,
+# myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+# FUN = FUN_tmp,
+# ylabel= expression(median~(MSY)),
+# MPNamesSub = MPNamesSub_userA,
+# MPNamesSub_legtext=MPNamesSub_userA_legtext,
+# rowLabs=scenNames_key[sN_i]
+# ),add_args))
+
+# # SSBMSY
+# do.call(plot_MSE_ts,
+#  c(list(
+# OMNames= OMNames, scenNames=sN_i,
+# myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears)]),
+# FUN = FUN_tmp,
+# ylabel= expression(median~(SSBMSY)),
+# MPNamesSub = MPNamesSub_userA,
+# MPNamesSub_legtext=MPNamesSub_userA_legtext,
+# rowLabs=scenNames_key[sN_i]
+# ),add_args))
+# FMSY
+# do.call(plot_MSE_ts,
+#   c(list(
+# OMNames= OMNames, scenNames=sN_i,
+# myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)]),
+# FUN = FUN_tmp,
+# ylabel= expression(median~(FMSY)),
+# MPNamesSub = MPNamesSub_userA,
+# MPNamesSub_legtext=MPNamesSub_userA_legtext,
+# rowLabs=scenNames_key[sN_i]
+# ),add_args))
+
+# # UMSY
+# do.call(plot_MSE_ts,
+#  c(list(
+# OMNames= OMNames, scenNames=sN_i,
+# myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)])),
+# FUN = FUN_tmp,
+# ylabel= expression(median~(UMSY)),
+# MPNamesSub = MPNamesSub_userA,
+# MPNamesSub_legtext=MPNamesSub_userA_legtext,
+# rowLabs=scenNames_key[sN_i]
+# ),add_args))
+}
+```
+
+```{r plot time series B,eval=TRUE}
+legend_inset_1 <- c(0,-0.5)
+legend_inset <- c(0,-0.8)
+
+pdf_wid <- 8
+pdf_hgt_1 <- 8
+pdf_hgt <- 8
+
+FUN_tmp <- median
+for(i in match(sN_plot,sN_all)){
+if(i==1){
+  legend_inset_i<-legend_inset_1
+  pdf_hgt_i <- pdf_hgt_1
+}else{
+  legend_inset_i<-legend_inset
+  pdf_hgt_i <- pdf_hgt
+}
+
+sN_i <- get(sN_all[i])
+
+if(length(sN_i)==1){
+  add_args <- list(plot_format = "portrait",
+                   main_line = -1.5,
+                   legend_panel = 4,
+                   mgp=c(1,0.2,0),
+                   legend_cex=1.2,
+                   legend_inset=legend_inset_i)
+}else{
+  add_args <- list(legend_cex=1.2,
+                   legend_inset=legend_inset_i)
+}
+
+# # VB
+# do.call(plot_MSE_ts,
+#  c(list(
+# OMNames= OMNames, scenNames=sN_i,
+# myvarName = "VB",
+# ylabel = expression(median~(VB)),
+# FUN = FUN_tmp,
+# MPNamesSub = MPNamesSub_userB,
+# MPNamesSub_legtext=MPNamesSub_userB_legtext,
+# rowLabs=scenNames_key[sN_i],
+#  assessmentYears_MP="SCA_5"
+# ),add_args))
+
+# SSB
+if(plot_pdf){pdf(paste0("Figs/ts","SSB",i,"B.pdf"), width=pdf_wid, height=pdf_hgt_i)}
+do.call(plot_MSE_ts,
+  c(list(
+  OMNames= OMNames, scenNames=sN_i,
+  myvarName = "SSB",
+  ylabel = expression(median~(SSB)),
+  FUN = FUN_tmp,
+  MPNamesSub = MPNamesSub_userB,
+  MPNamesSub_legtext=MPNamesSub_userB_legtext,
+  rowLabs=scenNames_key[sN_i],
+  assessmentYears_MP="SCA_5"
+  ),add_args))
+if(plot_pdf){dev.off()}
+
+# F
+if(plot_pdf){pdf(paste0("Figs/ts","F",i,"B.pdf"), width=pdf_wid, height=pdf_hgt_i)}
+do.call(plot_MSE_ts,
+  c(list(
+OMNames= OMNames, scenNames=sN_i,
+myvarName = "FM",
+ylabel = expression(median~(F)),
+FUN = FUN_tmp,
+MPNamesSub = MPNamesSub_userB,
+MPNamesSub_legtext=MPNamesSub_userB_legtext,
+rowLabs=scenNames_key[sN_i],
+  assessmentYears_MP="SCA_5"
+),add_args))
+if(plot_pdf){dev.off()}
+
+# # TAC
+# do.call(plot_MSE_ts,
+#  c(list(
+# OMNames= OMNames, scenNames=sN_i,  
+# myvarName = "TAC",
+# ylabel = expression(median~(TAC)),
+# FUN = FUN_tmp,
+# MPNamesSub = MPNamesSub_userB,
+# MPNamesSub_legtext=MPNamesSub_userB_legtext,
+# rowLabs=scenNames_key[sN_i],
+#  assessmentYears_MP="SCA_5" 
+# ),add_args))
+
+# Catch
+if(plot_pdf){pdf(paste0("Figs/ts","Catch",i,"B.pdf"), width=pdf_wid, height=pdf_hgt_i)}
+do.call(plot_MSE_ts,
+  c(list(
+OMNames= OMNames, scenNames=sN_i,  
+myvarName = "Catch",
+ylabel = expression(median~(Catch)),
+FUN = FUN_tmp,
+MPNamesSub = MPNamesSub_userB,
+MPNamesSub_legtext=MPNamesSub_userB_legtext,
+rowLabs=scenNames_key[sN_i],
+  assessmentYears_MP="SCA_5"
+),add_args))
+if(plot_pdf){dev.off()}
+
+# SSB/SSBmsy
+if(plot_pdf){pdf(paste0("Figs/ts","SSBSSBmsy",i,"B.pdf"), width=pdf_wid, height=pdf_hgt_i)}
+do.call(plot_MSE_ts,
+  c(list(
+  OMNames= OMNames, scenNames=sN_i,
+  myvarName = "SB_SBMSY",
+  ylabel = expression(median~(SSB/SSBmsy)),
+  FUN = FUN_tmp,
+  ylim=c(0,2.5),
+  MPNamesSub = MPNamesSub_userB,
+  MPNamesSub_legtext=MPNamesSub_userB_legtext,
+  rowLabs=scenNames_key[sN_i],
+  assessmentYears_MP="SCA_5",
+  hline=1, hline_lty=1
+),add_args))
+if(plot_pdf){dev.off()}
+
+# F/Fmsy
+if(plot_pdf){pdf(paste0("Figs/ts","FFmsy",i,"B.pdf"), width=pdf_wid, height=pdf_hgt_i)}
+do.call(plot_MSE_ts,
+  c(list(
+  OMNames= OMNames, scenNames=sN_i,
+  myvarName = "F_FMSY",
+  ylabel = expression(median~(F/Fmsy)),
+  FUN = FUN_tmp,
+  ylim=c(0,4.5),
+  MPNamesSub = MPNamesSub_userB,
+  MPNamesSub_legtext=MPNamesSub_userB_legtext,
+  rowLabs=scenNames_key[sN_i],
+  assessmentYears_MP="SCA_5",
+  hline=1, hline_lty=1
+),add_args))
+if(plot_pdf){dev.off()}
+
+# C/MSY
+if(plot_pdf){pdf(paste0("Figs/ts","CatchMSY",i,"B.pdf"), width=pdf_wid, height=pdf_hgt_i)}
+do.call(plot_MSE_ts,
+  c(list(
+  OMNames= OMNames, scenNames=sN_i,
+  myvarName = "Catch",
+  myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+  ylabel = expression(median~(Catch/MSY)),
+  FUN = FUN_tmp,
+  ylim=c(0,2.5),
+  MPNamesSub = MPNamesSub_userB,
+  MPNamesSub_legtext=MPNamesSub_userB_legtext,
+  rowLabs=scenNames_key[sN_i],
+  assessmentYears_MP="SCA_5",
+  hline=1, hline_lty=1
+),add_args))
+if(plot_pdf){dev.off()}
+
+# 
+# # TAC/MSY
+# do.call(plot_MSE_ts,
+#  c(list(
+#   OMNames= OMNames, scenNames=sN_i,
+#   myvarName = "TAC",
+#   myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+#   ylabel = expression(median~(TAC/MSY)),
+#   FUN = FUN_tmp,
+#   ylim=c(0,2),
+#   MPNamesSub = MPNamesSub_userB,
+#   MPNamesSub_legtext=MPNamesSub_userB_legtext,
+#   rowLabs=scenNames_key[sN_i],
+#  assessmentYears_MP="SCA_5"
+# ),add_args))
+# 
+# # C/TAC
+# do.call(plot_MSE_ts,
+#  c(list(
+#   OMNames= OMNames, scenNames=sN_i,  
+#   myvarName = "Catch",
+#   myvarDenomExpr = expression(slot(out_i,"TAC")),
+#   ylabel = expression(median~(C/TAC)),
+#   FUN = FUN_tmp,
+#   ylim=c(0,1.1),
+#   MPNamesSub = MPNamesSub_userB,
+#   MPNamesSub_legtext=MPNamesSub_userB_legtext,
+#   rowLabs=scenNames_key[sN_i],
+#  assessmentYears_MP="SCA_5"
+# ),add_args))
+
+# MSY
+# do.call(plot_MSE_ts,
+#   c(list(
+# OMNames= OMNames, scenNames=sN_i,
+# myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
+# FUN = FUN_tmp,
+# ylabel= expression(median~(MSY)),
+# MPNamesSub = MPNamesSub_userB,
+# MPNamesSub_legtext=MPNamesSub_userB_legtext,
+# rowLabs=scenNames_key[sN_i],
+#  assessmentYears_MP="SCA_5"
+# ),add_args))
+
+# # SSBMSY
+# do.call(plot_MSE_ts,
+#  c(list(
+# OMNames= OMNames, scenNames=sN_i,
+# myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears)]),
+# FUN = FUN_tmp,
+# ylabel= expression(median~(SSBMSY)),
+# MPNamesSub = MPNamesSub_userB,
+# MPNamesSub_legtext=MPNamesSub_userB_legtext,
+# rowLabs=scenNames_key[sN_i],
+#  assessmentYears_MP="SCA_5"
+# ),add_args))
+# FMSY
+# do.call(plot_MSE_ts,
+#   c(list(
+# OMNames= OMNames, scenNames=sN_i,
+# myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)]),
+# FUN = FUN_tmp,
+# ylabel= expression(median~(FMSY)),
+# MPNamesSub = MPNamesSub_userB,
+# MPNamesSub_legtext=MPNamesSub_userB_legtext,
+# rowLabs=scenNames_key[sN_i],
+#  assessmentYears_MP="SCA_5"
+# ),add_args))
+
+# # UMSY
+# do.call(plot_MSE_ts,
+#  c(list(
+# OMNames= OMNames, scenNames=sN_i,
+# myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)])),
+# FUN = FUN_tmp,
+# ylabel= expression(median~(UMSY)),
+# MPNamesSub = MPNamesSub_userB,
+# MPNamesSub_legtext=MPNamesSub_userB_legtext,
+# rowLabs=scenNames_key[sN_i],
+#  assessmentYears_MP="SCA_5"
+# ),add_args))
+}
+```
+
+```{r plot time series RE,eval=FALSE}
+for(i in 1:length(sN_plot)){
+
+sN_i <- get(sN_plot[i])
 # # VB
 # plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user1,
+# OMNames= OMNames, scenNames=sN_i,
 # myvarName = "VB",
-# ylabel = expression(mean~(VB)),
-# FUN = mean,
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user1]
+# ylabel = expression(RE~(mean~(VB))),
+# FUN = FUN_tmp, MPNamesRef = "SCA_1",
+# MPNamesSub = MPNamesSub_userA,
+# MPNamesSub_legtext=MPNamesSub_userA_legtext,
+# rowLabs=scenNames_key[sN_i]
 # )
@@
 # SSB
-if(plot_pdf){pdf("Figs/ts_SSB.pdf")}
+if(plot_pdf){pdf(paste0("Figs/tsRE","SSB",i,".pdf"))}
 plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user1,
+  OMNames= OMNames, scenNames=sN_i,
   myvarName = "SSB",
-  ylabel = expression(mean~(SSB)),
-  FUN = mean,
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user1]
+  ylabel = expression(RE~(mean~(SBB))),
+  FUN = FUN_tmp, MPNamesRef = "SCA_1",
+  MPNamesSub = MPNamesSub_userA,
+  MPNamesSub_legtext=MPNamesSub_userA_legtext,
+  rowLabs=scenNames_key[sN_i],
+  ylim=c(-0.5,0.5)
 )
@@
 # plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user1,  
+# OMNames= OMNames, scenNames=sN_i,  
 # myvarName = "FM",
-# ylabel = expression(mean~(F)),
-# FUN = mean,
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user1]
+# ylabel = expression(RE~(mean~(F))),
+# FUN = FUN_tmp, MPNamesRef = "SCA_1",
+# MPNamesSub = MPNamesSub_userA,
+# MPNamesSub_legtext=MPNamesSub_userA_legtext,
+# rowLabs=scenNames_key[sN_i]
 # )
@@
 # plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user1,  
+# OMNames= OMNames, scenNames=sN_i,  
 # myvarName = "TAC",
-# ylabel = expression(mean~(TAC)),
-# FUN = mean,
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user1] 
+# ylabel = expression(RE~(mean~(TAC))),
+# FUN = FUN_tmp, MPNamesRef = "SCA_1",
+# MPNamesSub = MPNamesSub_userA,
+# MPNamesSub_legtext=MPNamesSub_userA_legtext,
+# rowLabs=scenNames_key[sN_i] 
 # )
@@
 # Catch
-if(plot_pdf){pdf("Figs/ts_Catch.pdf")}
+if(plot_pdf){pdf(paste0("Figs/tsRE","Catch",i,".pdf"))}
+
 plot_MSE_ts(
-OMNames= OMNames, scenNames=scenNames_user1,  
+OMNames= OMNames, scenNames=sN_i,  
 myvarName = "Catch",
-ylabel = expression(mean~(Catch)),
-FUN = mean,
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user1]
+ylabel = expression(RE~(mean~(Catch))),
+FUN = FUN_tmp, MPNamesRef = "SCA_1",
+MPNamesSub = MPNamesSub_userA,
+MPNamesSub_legtext=MPNamesSub_userA_legtext,
+rowLabs=scenNames_key[sN_i],
+ylim=c(-0.5,0.5)
 )
@@
 # SSB/SSBmsy
-if(plot_pdf){pdf("Figs/ts_SSB_SSBmsy.pdf")}
+if(plot_pdf){pdf(paste0("Figs/tsRE","SSBSSBMSY",i,".pdf"))}
 plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user1,
+  OMNames= OMNames, scenNames=sN_i,
   myvarName = "SB_SBMSY",
-  ylabel = expression(mean~(SSB/SSBmsy)),
-  FUN = mean,
-  #ylim=c(0,2),
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user1]
+  ylabel = expression(RE~(mean~(SSB/SSBmsy))),
+  FUN = FUN_tmp, MPNamesRef = "SCA_1",
+  MPNamesSub = MPNamesSub_userA,
+  MPNamesSub_legtext=MPNamesSub_userA_legtext,
+  rowLabs=scenNames_key[sN_i],
+  ylim=c(-0.5,0.5),
+  hline=NA
 )
@@
 # F/Fmsy
-if(plot_pdf){pdf("Figs/ts_F_Fmsy.pdf")}
+if(plot_pdf){pdf(paste0("Figs/tsRE","FFMSY",i,".pdf"))}
+
 plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user1,
+  OMNames= OMNames, scenNames=sN_i,
   myvarName = "F_FMSY",
-  ylabel = expression(mean~(F/Fmsy)),
-  FUN = mean,
-  #ylim=c(0,2),
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user1]
-)
-if(plot_pdf){dev.off()}
+  ylabel = expression(RE~(mean~(F/Fmsy))),
+  FUN = FUN_tmp, MPNamesRef = "SCA_1",
+  MPNamesSub = MPNamesSub_userA,
+  rowLabs=scenNames_key[sN_i],
+  ylim=c(-1,1.5),
+  hline=NA
+)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf(paste0("Figs/tsRE","CatchMSY",i,".pdf"))}
 
 # C/MSY
-if(plot_pdf){pdf("Figs/ts_Catch_MSY.pdf")}
 plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user1,
+  OMNames= OMNames, scenNames=sN_i,
   myvarName = "Catch",
   myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
-  ylabel = expression(mean~(Catch/MSY)),
-  FUN = mean,
-  #ylim=c(0,2),
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user1]
-)
-if(plot_pdf){dev.off()}
-
+  ylabel = expression(RE~(mean~(Catch/MSY))),
+  FUN = FUN_tmp, MPNamesRef = "SCA_1",
+  MPNamesSub = MPNamesSub_userA,
+  MPNamesSub_legtext=MPNamesSub_userA_legtext,
+  rowLabs=scenNames_key[sN_i],
+  ylim=c(-0.5,0.5)
+)
+if(plot_pdf){dev.off()}
 # 
@@
 # plot_MSE_ts(
-#   OMNames= OMNames, scenNames=scenNames_user1,
-#   myvarName = "TAC",
-#   myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
-#   ylabel = expression(mean~(TAC/MSY)),
-#   FUN = mean,
-#   ylim=c(0,2),
-#   MPNamesSub = MPNamesSub_user,
-#   MPNamesSub_legtext=MPNamesSub_user_legtext,
-#   rowLabs=scenNames_key[scenNames_user1]
-# )
-# 
-# # C/TAC
-# plot_MSE_ts(
-#   OMNames= OMNames, scenNames=scenNames_user1,  
-#   myvarName = "Catch",
-#   myvarDenomExpr = expression(slot(out_i,"TAC")),
-#   ylabel = expression(mean~(C/TAC)),
-#   FUN = mean,
-#   ylim=c(0,1.1),
-#   MPNamesSub = MPNamesSub_user,
-#   MPNamesSub_legtext=MPNamesSub_user_legtext,
-#   rowLabs=scenNames_key[scenNames_user1]
-# )
-# 
-# # MSY
-# plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user1,
-# myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
-# FUN = mean,
-# ylabel= expression(mean~(MSY)),
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user1]
-# )
-# 
-# # SSBMSY
-# plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user1,
-# myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears)]),
-# FUN = mean,
-# ylabel= expression(mean~(SSBMSY)),
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user1]
-# )
-# 
-# # FMSY
-# plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user1,
-# myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)]),
-# FUN = mean,
-# ylabel= expression(mean~(FMSY)),
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user1]
-# )
-# 
-# # UMSY
-# plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user1,
-# myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)])),
-# FUN = mean,
-# ylabel= expression(mean~(UMSY)),
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user1]
-# )
-```
-
-```{r plot time series2,eval=TRUE}
-# # VB
-# plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user2,
-# myvarName = "VB",
-# ylabel = expression(mean~(VB)),
-# FUN = mean,
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user2]
-# )
-
-# SSB
-if(plot_pdf){pdf("Figs/ts_SSB.pdf")}
-plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user2,
-  myvarName = "SSB",
-  ylabel = expression(mean~(SSB)),
-  FUN = mean,
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user2]
-)
-if(plot_pdf){dev.off()}
-# 
-# # F
-# plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user2,  
-# myvarName = "FM",
-# ylabel = expression(mean~(F)),
-# FUN = mean,
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user2]
-# )
-# 
-# # TAC
-# plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user2,  
-# myvarName = "TAC",
-# ylabel = expression(mean~(TAC)),
-# FUN = mean,
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user2] 
-# )
-
-# Catch
-if(plot_pdf){pdf("Figs/ts_Catch.pdf")}
-plot_MSE_ts(
-OMNames= OMNames, scenNames=scenNames_user2,  
-myvarName = "Catch",
-ylabel = expression(mean~(Catch)),
-FUN = mean,
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user2]
-)
-if(plot_pdf){dev.off()}
-
-# SSB/SSBmsy
-if(plot_pdf){pdf("Figs/ts_SSB_SSBmsy.pdf")}
-plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user2,
-  myvarName = "SB_SBMSY",
-  ylabel = expression(mean~(SSB/SSBmsy)),
-  FUN = mean,
-  # ylim=c(0,2),
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user2]
-)
-if(plot_pdf){dev.off()}
-
-# F/Fmsy
-if(plot_pdf){pdf("Figs/ts_F_Fmsy.pdf")}
-plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user2,
-  myvarName = "F_FMSY",
-  ylabel = expression(mean~(F/Fmsy)),
-  FUN = mean,
-  # ylim=c(0,2),
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user2]
-)
-if(plot_pdf){dev.off()}
-
-# C/MSY
-if(plot_pdf){pdf("Figs/ts_Catch_MSY.pdf")}
-plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user2,
-  myvarName = "Catch",
-  myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
-  ylabel = expression(mean~(Catch/MSY)),
-  FUN = mean,
-  # ylim=c(0,2),
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user2]
-)
-if(plot_pdf){dev.off()}
-
-# 
-# # TAC/MSY
-# plot_MSE_ts(
-#   OMNames= OMNames, scenNames=scenNames_user2,
-#   myvarName = "TAC",
-#   myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
-#   ylabel = expression(mean~(TAC/MSY)),
-#   FUN = mean,
-#   ylim=c(0,2),
-#   MPNamesSub = MPNamesSub_user,
-#   MPNamesSub_legtext=MPNamesSub_user_legtext,
-#   rowLabs=scenNames_key[scenNames_user2]
-# )
-# 
-# # C/TAC
-# plot_MSE_ts(
-#   OMNames= OMNames, scenNames=scenNames_user2,  
-#   myvarName = "Catch",
-#   myvarDenomExpr = expression(slot(out_i,"TAC")),
-#   ylabel = expression(mean~(C/TAC)),
-#   FUN = mean,
-#   ylim=c(0,1.1),
-#   MPNamesSub = MPNamesSub_user,
-#   MPNamesSub_legtext=MPNamesSub_user_legtext,
-#   rowLabs=scenNames_key[scenNames_user2]
-# )
-# 
-# # MSY
-# plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user2,
-# myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
-# FUN = mean,
-# ylabel= expression(mean~(MSY)),
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user2]
-# )
-# 
-# # SSBMSY
-# plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user2,
-# myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears)]),
-# FUN = mean,
-# ylabel= expression(mean~(SSBMSY)),
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user2]
-# )
-# 
-# # FMSY
-# plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user2,
-# myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)]),
-# FUN = mean,
-# ylabel= expression(mean~(FMSY)),
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user2]
-# )
-# 
-# # UMSY
-# plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user2,
-# myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)])),
-# FUN = mean,
-# ylabel= expression(mean~(UMSY)),
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user2]
-# )
-```
-
-```{r plot time series RE,eval=FALSE}
-# # VB
-# plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user1,
-# myvarName = "VB",
-# ylabel = expression(RE~(mean~(VB))),
-# FUN = mean, MPNamesRef = "SCA_1",
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user1]
-# )
-
-# SSB
-plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user1,
-  myvarName = "SSB",
-  ylabel = expression(RE~(mean~(SBB))),
-  FUN = mean, MPNamesRef = "SCA_1",
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user1],
-  ylim=c(-0.5,0.5)
-)
-# 
-# # F
-# plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user1,  
-# myvarName = "FM",
-# ylabel = expression(RE~(mean~(F))),
-# FUN = mean, MPNamesRef = "SCA_1",
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user1]
-# )
-# 
-# # TAC
-# plot_MSE_ts(
-# OMNames= OMNames, scenNames=scenNames_user1,  
-# myvarName = "TAC",
-# ylabel = expression(RE~(mean~(TAC))),
-# FUN = mean, MPNamesRef = "SCA_1",
-# MPNamesSub = MPNamesSub_user,
-# MPNamesSub_legtext=MPNamesSub_user_legtext,
-# rowLabs=scenNames_key[scenNames_user1] 
-# )
-
-# Catch
-plot_MSE_ts(
-OMNames= OMNames, scenNames=scenNames_user1,  
-myvarName = "Catch",
-ylabel = expression(RE~(mean~(Catch))),
-FUN = mean, MPNamesRef = "SCA_1",
-MPNamesSub = MPNamesSub_user,
-MPNamesSub_legtext=MPNamesSub_user_legtext,
-rowLabs=scenNames_key[scenNames_user1],
-ylim=c(-0.5,0.5)
-)
-
-# SSB/SSBmsy
-plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user1,
-  myvarName = "SB_SBMSY",
-  ylabel = expression(RE~(mean~(SSB/SSBmsy))),
-  FUN = mean, MPNamesRef = "SCA_1",
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user1],
-  ylim=c(-0.5,0.5),
-  hline=NA
-)
-
-# F/Fmsy
-plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user1,
-  myvarName = "F_FMSY",
-  ylabel = expression(RE~(mean~(F/Fmsy))),
-  FUN = mean, MPNamesRef = "SCA_1",
-  MPNamesSub = MPNamesSub_user,
-  rowLabs=scenNames_key[scenNames_user1],
-  ylim=c(-1,1.5),
-  hline=NA
-)
-
-# C/MSY
-plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user1,
-  myvarName = "Catch",
-  myvarDenomExpr = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
-  ylabel = expression(RE~(mean~(Catch/MSY))),
-  FUN = mean, MPNamesRef = "SCA_1",
-  MPNamesSub = MPNamesSub_user,
-  MPNamesSub_legtext=MPNamesSub_user_legtext,
-  rowLabs=scenNames_key[scenNames_user1],
-  ylim=c(-0.5,0.5)
-)
-
-# 
-# # TAC/MSY
-# plot_MSE_ts(
-#   OMNames= OMNames, scenNames=scenNames_user1,
+#   OMNames= OMNames, scenNames=sN_i,
 #   myvarName = "TAC",
@@
 #   ylabel = expression(RE~(mean~(TAC/MSY))),
-#   FUN = mean, MPNamesRef = "SCA_1",
+#   FUN = FUN_tmp, MPNamesRef = "SCA_1",
 #   ylim=c(0,2),
-#   MPNamesSub = MPNamesSub_user,
-#   MPNamesSub_legtext=MPNamesSub_user_legtext,
-#   rowLabs=scenNames_key[scenNames_user1],
+#   MPNamesSub = MPNamesSub_userA,
+#   MPNamesSub_legtext=MPNamesSub_userA_legtext,
+#   rowLabs=scenNames_key[sN_i],
 #   ylim=c(-0.5,0.5),
@@
 # plot_MSE_ts(
-#   OMNames= OMNames, scenNames=scenNames_user1,  
+#   OMNames= OMNames, scenNames=sN_i,  
 #   myvarName = "Catch",
@@
 #   ylabel = expression(RE~(mean~(C/TAC))),
-#   FUN = mean, MPNamesRef = "SCA_1",
+#   FUN = FUN_tmp, MPNamesRef = "SCA_1",
 #   ylim=c(0,1.1),
-#   MPNamesSub = MPNamesSub_user,
-#   MPNamesSub_legtext=MPNamesSub_user_legtext,
-#   rowLabs=scenNames_key[scenNames_user1],
+#   MPNamesSub = MPNamesSub_userA,
+#   MPNamesSub_legtext=MPNamesSub_userA_legtext,
+#   rowLabs=scenNames_key[sN_i],
 #   ylim=c(-0.5,0.5),
@@
 # plot_MSE_ts(
-#   OMNames= OMNames, scenNames=scenNames_user1,
+#   OMNames= OMNames, scenNames=sN_i,
 #   myvarName = expression(slot(out_i,"RefPoint")$MSY[,,-(1:out_i@nyears)]),
-#   FUN = mean, MPNamesRef = "SCA_1",
+#   FUN = FUN_tmp, MPNamesRef = "SCA_1",
 #   ylabel= expression(RE~(mean~(MSY))),
-#   MPNamesSub = MPNamesSub_user,
-#   MPNamesSub_legtext=MPNamesSub_user_legtext,
-#   rowLabs=scenNames_key[scenNames_user1],
+#   MPNamesSub = MPNamesSub_userA,
+#   MPNamesSub_legtext=MPNamesSub_userA_legtext,
+#   rowLabs=scenNames_key[sN_i],
 #   ylim=c(-0.5,0.5),
@@
 # plot_MSE_ts(
-#   OMNames= OMNames, scenNames=scenNames_user1,
+#   OMNames= OMNames, scenNames=sN_i,
 #   myvarName = expression(slot(out_i,"RefPoint")$SSBMSY[,,-(1:out_i@nyears)]),
-#   FUN = mean, MPNamesRef = "SCA_1",
+#   FUN = FUN_tmp, MPNamesRef = "SCA_1",
 #   ylabel= expression(RE~(mean~(SSBMSY))),
-#   MPNamesSub = MPNamesSub_user,
-#   MPNamesSub_legtext=MPNamesSub_user_legtext,
-#   rowLabs=scenNames_key[scenNames_user1],
+#   MPNamesSub = MPNamesSub_userA,
+#   MPNamesSub_legtext=MPNamesSub_userA_legtext,
+#   rowLabs=scenNames_key[sN_i],
 #   ylim=c(-0.5,0.5),
@@
 # plot_MSE_ts(
-#   OMNames= OMNames, scenNames=scenNames_user1,
+#   OMNames= OMNames, scenNames=sN_i,
 #   myvarName = expression(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)]),
-#   FUN = mean, MPNamesRef = "SCA_1",
+#   FUN = FUN_tmp, MPNamesRef = "SCA_1",
 #   ylabel= expression(RE~(mean~(FMSY))),
-#   MPNamesSub = MPNamesSub_user,
-#   MPNamesSub_legtext=MPNamesSub_user_legtext,
-#   rowLabs=scenNames_key[scenNames_user1],
+#   MPNamesSub = MPNamesSub_userA,
+#   MPNamesSub_legtext=MPNamesSub_userA_legtext,
+#   rowLabs=scenNames_key[sN_i],
 #   ylim=c(-0.5,0.5),
@@
 # plot_MSE_ts(
-#   OMNames= OMNames, scenNames=scenNames_user1,
+#   OMNames= OMNames, scenNames=sN_i,
 #   myvarName = expression(F2U(slot(out_i,"RefPoint")$FMSY[,,-(1:out_i@nyears)])),
-#   FUN = mean, MPNamesRef = "SCA_1",
+#   FUN = FUN_tmp, MPNamesRef = "SCA_1",
 #   ylabel= expression(RE~(mean~(UMSY))),
-#   MPNamesSub = MPNamesSub_user,
-#   MPNamesSub_legtext=MPNamesSub_user_legtext,
-#   rowLabs=scenNames_key[scenNames_user1],
+#   MPNamesSub = MPNamesSub_userA,
+#   MPNamesSub_legtext=MPNamesSub_userA_legtext,
+#   rowLabs=scenNames_key[sN_i],
 #   ylim=c(-0.5,0.5),
@@
 # )
+}
 ```
@@
 ```{r plot dot and whiskers, eval=FALSE}
+for(i in match(sN_plot,sN_all)){
+
+sN_i <- get(sN_all[i])
+
+if(plot_pdf){pdf(paste0("Figs/dw","SSB",i,".pdf"))}
 plot_MSE_dw(
-    OMNames= OMNames, scenNames=scenNames_user1,
+    OMNames= OMNames, scenNames=sN_i,
     myvarName = "SSB",
@@
     MPNamesSub_legtext=MPNamesAll_legtext,
-    rowLabs=scenNames_key[scenNames_user1]
-)
-
+    rowLabs=scenNames_key[sN_i]
+)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf(paste0("Figs/dw","Catch",i,".pdf"))}
 plot_MSE_dw(
-    OMNames= OMNames, scenNames=scenNames_user1,
+    OMNames= OMNames, scenNames=sN_i,
     myvarName = "Catch",
@@
     MPNamesSub_legtext=MPNamesAll_legtext,
-    rowLabs=scenNames_key[scenNames_user1],
+    rowLabs=scenNames_key[sN_i],
     ylim = c(0,1)
 )
-
-```
-
-```{r MSEtool tradeoff plots, eval=FALSE}
-# MSEtool Tradeoff plots
-for(outName_i in MSEoutNames_user1){
-out_i <- get(outName_i)  
-par(oma=c(1,1,2,1))  
-MSEtool::TradePlot(out_i)
-}
-```
-
+if(plot_pdf){dev.off()}
+
+}
+```
 \clearpage
@@
 
-```{r tradeoffPlot1, eval=FALSE}
-if(plot_pdf){pdf("Figs/tradeoffPlot1.pdf")}
+```{r tradeoff 1, eval=TRUE)}
+pdf_wid <- 8
+pdf_hgt_1 <- 4
+pdf_hgt <- 8
+
+cex.axis <- 1
+
+legend_inset_1 <- c(0.7,-0.27)
+legend_inset <- c(0.7,-0.7)
+legend_cex <- 1.2
+legend_ncol <- ceiling(length(MPNamesAll)/2)
+legend_horiz <- FALSE
+legend_x <- "bottomleft"
+legend_xjust <- 0.5
+
+for(i in match(sN_plot,sN_all)){
+if(i==1){
+  legend_inset_i<-legend_inset_1
+  pdf_hgt_i <- pdf_hgt_1
+}else{
+  legend_inset_i<-legend_inset
+  pdf_hgt_i <- pdf_hgt
+}
+
+sN_i <- get(sN_all[i])
+
+if(plot_pdf){pdf(paste0("Figs/tr","YldP100",i,".pdf"), width=pdf_wid, height=pdf_hgt_i)}
 plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user1,
-  # MPNamesRef = "SCA_1",
+  OMNames= OMNames, scenNames=sN_i,
   plot_type = "tradeoff",
   PMx = Yield,
+  PMy = P100,
   MPNamesSub = MPNamesAll,
-  MPNamesSub_legtext=MPNamesAll,
-  rowLabs=scenNames_key[scenNames_user1],
+  MPNamesSub_legtext=MPNamesAll_abb,
+  rowLabs=scenNames_key[sN_i],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,1.2),ylim=c(0,1.1),
+  hline=0.5,vline=0.5,cex=2,legend_cex = legend_cex, legend_x.intersp=0.1,
+  legend_inset=legend_inset_i,
+  legend_horiz=legend_horiz,
+  legend_ncol=legend_ncol,
+  legend_x=legend_x,
+  legend_xjust=legend_xjust,
+  cex.axis=cex.axis
+)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf(paste0("Figs/tr","PNOFP100",i,".pdf"), width=pdf_wid, height=pdf_hgt_i)}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=sN_i,
+  plot_type = "tradeoff",
+  PMx = PNOF,
+  PMy = P100,
+  MPNamesSub = MPNamesAll,
+  MPNamesSub_legtext=MPNamesAll_abb,
+  rowLabs=scenNames_key[sN_i],
   mar=c(0,0,0,0),label_axes="leftbottom",
   xlim=c(0,1.1),ylim=c(0,1.1),
-  hline=NA
-)
-if(plot_pdf){dev.off()}
+  hline=0.5,vline=0.5,cex=2,legend_cex = legend_cex,legend_x.intersp=0.1,
+  legend_inset=legend_inset_i,
+  legend_horiz=legend_horiz,
+  legend_ncol=legend_ncol,
+  legend_x=legend_x,
+  legend_xjust=legend_xjust,
+  cex.axis=cex.axis
+)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf(paste0("Figs/tr","AAVYP100",i,".pdf"), width=pdf_wid, height=pdf_hgt_i)}
+plot_MSE_ts(
+  OMNames= OMNames,
+  scenNames = sN_i,
+  plot_type = "tradeoff",
+  PMx = AAVY,
+  PMy = P100,  
+  MPNamesSub = MPNamesAll,
+  MPNamesSub_legtext=MPNamesAll_abb,
+  rowLabs=scenNames_key[sN_i],
+  mar=c(0,0,0,0), label_axes = "leftbottom",
+  xlim=c(0,1.2), ylim=c(0,1.1),
+  hline=0.5,vline=0.5,cex=2,legend_cex = legend_cex,legend_x.intersp=0.1,
+  legend_inset=legend_inset_i,
+  legend_horiz=legend_horiz,
+  legend_ncol=legend_ncol,
+  legend_x=legend_x,
+  legend_xjust=legend_xjust,  
+  cex.axis=cex.axis
+)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf(paste0("Figs/tr","AAVYPNOF",i,".pdf"), width=pdf_wid, height=pdf_hgt_i)}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=sN_i,
+  plot_type = "tradeoff",
+  PMx = AAVY,
+  PMy = PNOF,
+  MPNamesSub = MPNamesAll,
+  MPNamesSub_legtext=MPNamesAll_abb,
+  rowLabs=scenNames_key[sN_i],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,1.2),ylim=c(0,1.1),
+  hline=0.5,vline=0.5,cex=2,legend_cex = legend_cex,legend_x.intersp=0.1,
+  legend_inset=legend_inset_i,
+  legend_horiz=legend_horiz,
+  legend_ncol=legend_ncol,
+  legend_x=legend_x,
+  legend_xjust=legend_xjust,  
+  cex.axis=cex.axis
+)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf(paste0("Figs/tr","AAVYYldLT",i,".pdf"), width=pdf_wid, height=pdf_hgt_i)}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=sN_i,
+  plot_type = "tradeoff",
+  PMx = AAVY,
+  PMy = YieldLT,
+  MPNamesSub = MPNamesAll,
+  MPNamesSub_legtext=MPNamesAll_abb,
+  rowLabs=scenNames_key[sN_i],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,1.2),ylim=c(0,1.1),
+  hline=0.5,vline=0.5,cex=2,legend_cex = legend_cex,legend_x.intersp=0.1,
+  legend_inset=legend_inset_i,
+  legend_horiz=legend_horiz,
+  legend_ncol=legend_ncol,
+  legend_x=legend_x,
+  legend_xjust=legend_xjust,  
+  cex.axis=cex.axis
+)
+if(plot_pdf){dev.off()}
+
+if(plot_pdf){pdf(paste0("Figs/tr","P100YldLT",i,".pdf"), width=pdf_wid, height=pdf_hgt_i)}
+plot_MSE_ts(
+  OMNames= OMNames, scenNames=sN_i,
+  plot_type = "tradeoff",
+  PMx = P100,
+  PMy = YieldLT,
+  MPNamesSub = MPNamesAll,
+  MPNamesSub_legtext=MPNamesAll_abb,
+  rowLabs=scenNames_key[sN_i],
+  mar=c(0,0,0,0),label_axes="leftbottom",
+  xlim=c(0,1.2),ylim=c(0,1.1),
+  hline=0.5,vline=0.5,cex=2,legend_cex = legend_cex,legend_x.intersp=0.1,
+  legend_inset=legend_inset_i,
+  legend_horiz=legend_horiz,
+  legend_ncol=legend_ncol,
+  legend_x=legend_x,
+  legend_xjust=legend_xjust,  
+  cex.axis=cex.axis
+)
+if(plot_pdf){dev.off()}
+}
+
 ```
@@
 
-```{r tradeoffPlot2, eval=FALSE}
+# Phase plots
+
+```{r phase plots}
+pdf_wid <- 8
+pdf_hgt_1 <- 4
+pdf_hgt <- 8
+
+legend_inset_1 <- c(0,-0.2)
+legend_inset <- c(0,-0.6)
+
+for(i in match(sN_plot,sN_all)){
+if(i==1){
+  legend_inset_i<-legend_inset_1
+  pdf_hgt_i <- pdf_hgt_1
+}else{
+  legend_inset_i<-legend_inset
+  pdf_hgt_i <- pdf_hgt
+}  
+sN_i <- get(sN_all[i])
+
+if(plot_pdf){pdf(paste0("Figs/phasePlot",i,".pdf"), width=pdf_wid, height=pdf_hgt_i)}
 plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user1,
-  # MPNamesRef = "SCA_1",
-  plot_type = "tradeoff",
-  PMx = PNOF,
-  #proyear_phase=20,
-  MPNamesSub = MPNamesAll,
-  MPNamesSub_legtext=MPNamesAll,
-  rowLabs=scenNames_key[scenNames_user1],
+  OMNames= OMNames, scenNames=sN_i,
+  plot_type = "phase",
+  proyear_phase=41:50,
+  MPNamesSub = c(MPNamesSub_userA),
+  MPNamesSub_legtext=c(MPNamesSub_userA_legtext),
+  rowLabs=scenNames_key[sN_i],
   mar=c(0,0,0,0),label_axes="leftbottom",
-  xlim=c(0,1.1),ylim=c(0,1.1),
-  hline=NA
-)
-
-```
-\clearpage
-
-```{r tradeoffPlot3, eval=FALSE}
-plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user1,
-  # MPNamesRef = "SCA_1",
-  plot_type = "tradeoff",
-  PMx = AAVY10,
-  #proyear_phase=20,
-  MPNamesSub = MPNamesAll,
-  MPNamesSub_legtext=MPNamesAll,
-  rowLabs=scenNames_key[scenNames_user1],
-  mar=c(0,0,0,0),label_axes="leftbottom",
-  xlim=c(0,1.1),ylim=c(0,1.1),
-  hline=NA
-)
-```
-
-```{r tradeoffPlot4, eval=FALSE}
-plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user1,
-  # MPNamesRef = "SCA_1",
-  plot_type = "tradeoff",
-  PMx = AAVY10,
-  PMy = PNOF,
-  #proyear_phase=20,
-  MPNamesSub = MPNamesAll,
-  MPNamesSub_legtext=MPNamesAll,
-  rowLabs=scenNames_key[scenNames_user1],
-  mar=c(0,0,0,0),label_axes="leftbottom",
-  xlim=c(0,1.1),ylim=c(0,1.1),
-  hline=NA
-)
-
-```
-
-\clearpage
-
-# Phase plots
-
-```{r phase plots}
-if(plot_pdf){pdf("Figs/phasePlot1.pdf")}
-plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user1,
-  plot_type = "phase",
-  #proyear_phase=50,
-  MPNamesSub = c(MPNamesSub_user),
-  MPNamesSub_legtext=c(MPNamesSub_user_legtext),
-  rowLabs=scenNames_key[scenNames_user1],
-  mar=c(0,0,0,0),label_axes="leftbottom",
-  xlim=c(0,5),ylim=c(0,5),
-  hline=NA
-)
-if(plot_pdf){dev.off()}
-
-if(plot_pdf){pdf("Figs/phasePlot2.pdf")}
-plot_MSE_ts(
-  OMNames= OMNames, scenNames=scenNames_user2,
-  plot_type = "phase",
-  #proyear_phase=50,
-  MPNamesSub = c(MPNamesSub_user),
-  MPNamesSub_legtext=c(MPNamesSub_user_legtext),
-  rowLabs=scenNames_key[scenNames_user2],
-  mar=c(0,0,0,0),label_axes="leftbottom",
-  xlim=c(0,5),ylim=c(0,5),
-  hline=NA
-)
-if(plot_pdf){dev.off()}
-```
+  xlim=c(0,3),ylim=c(0,3),
+  hline=NA,
+  legend_inset=legend_inset_i,
+  legend_cex = 1.2
+)
+if(plot_pdf){dev.off()}
+}
+```
+
+```{r generate Hist, eval=TRUE}
+if(generate_Hist){
+
+for(OMName_base_i in OMNames_base){
+  OM_base_i <- get(OMName_base_i)
+
+  cat(paste0("\n\nWorking on ",OMName_base_i,"\n"))
+  Hist_i <- MSEtool::Simulate(OM_base_i) # Generate historical data
+
+  if(OMName_i%in%OMNames){
+  Hist_name_i <- gsub("OM","Hist",OMName_base_i)
+  assign(Hist_name_i,Hist_i)
+  saveRDS(Hist_i, file = file.path("Hist",paste0(Hist_name_i,".rds")))
+  }
+
+}
+}else{
+for(OMName_base_i in OMNames_base){
+  Hist_name_i <- gsub("OM","Hist",OMName_base_i)
+  Hist_i <- readRDS(file = file.path("Hist",paste0(Hist_name_i,".rds")))
+  assign(Hist_name_i,Hist_i)
+}
+}
+```
+
+```{r plot Hist with bam  results, eval=FALSE}
+if(plot_Hist){
+CIpct  <-  95
+
+commonNames <- gsub(".*_(.+)_.*","\\1",OMNames_base)
+lty <- c(1,2)
+
+for(i in commonNames){
+if(plot_pdf){pdf(paste0("Figs/Hist_",i,"_base.pdf"))}  
+rdat_name_i <- paste0("rdat_",i)
+
+OM_base_i <- get(paste0("OM_",i,"_base"))
+# Data_i <- get(paste0("Data_",i))
+Hist_i <- get(paste0("Hist_",i,"_base"))
+rdat_i <- get(rdat_name_i)
+rdatmods_i <- rdatmods[[i]]
+
+parms_i <- rdat_i$parms
+years_i <- paste(parms_i$styr:parms_i$endyr)
+t.series_i <- rdat_i$t.series[years_i,]
+
+Nage_F0_pr_sc_i <- rdatmods_i$Nage_F0_pr_sc
+
+par(mfrow=c(3,2),mgp=c(0.9,0.1,0),tck=-0.01,mar=c(2,2.5,1,1),oma=c(0,0,1.5,1))
+
+Fmatrix <- Hist_i@TSdata$Find
+
+# Landings
+Lmatrix <- Hist_i@TSdata$Landings[,,1]+Hist_i@TSdata$Landings[,,2]
+dimnames(Lmatrix) <- dimnames(Fmatrix)
+Lbam <- t.series_i$total.L.klb
+Dbam <- t.series_i$total.D.klb
+if(!is.null(Dbam)){
+  Lbam <- Lbam+Dbam
+}
+Lylim <- range(c(0,as.numeric(Lmatrix),Lbam))
+plot_boot_vec(Lmatrix,CIpct=CIpct,xlab="year",ylab="Landings + Discards (1000 lb)",ylim=Lylim,lty=lty[1])
+points(years_i,Lbam,type="o",#axes=FALSE,xlab="",ylab="",
+     col="blue",lty=lty[2])
+
+legend("bottomleft",
+       legend=c("sim","BAM"),
+       lty=lty,
+       pch=c(NA,1),
+       col=c("black","blue"),
+       bg=rgb(1,1,1,0.5),
+       inset=0.05
+       )
+
+# Indices
+AddIndArray <- Hist_i@Data@AddInd
+nAddInd <- dim(AddIndArray)[2]
+AddInd_col_sim <- grays(nAddInd)
+AddInd_col_bam <- blues(nAddInd)
+
+U.names.ob <- names(t.series_i)[grepl("^U..*.ob$",names(t.series_i))]
+bam.U.ob <- t.series_i[,U.names.ob[which(!is.na(tail(t.series_i[,U.names.ob],1)))],drop=FALSE]
+for(j in 1:nAddInd){
+AddIndmatrix_j <- AddIndArray[,j,]
+dimnames(AddIndmatrix_j) <- dimnames(Fmatrix)  
+plot_boot_vec(AddIndmatrix_j,add=ifelse(j!=1,TRUE,FALSE),
+              CIpct=CIpct,xlab="year",ylab="AddInd",
+              ,col_lines=AddInd_col_sim[j],lty=lty[1]
+              )
+points(as.numeric(rownames(bam.U.ob)),bam.U.ob[,j],type="o", col=AddInd_col_bam[j],lty=lty[2])
+
+}
+# Recruitment
+Rmatrix <- Hist_i@AtAge$Number[,1,,1]+Hist_i@AtAge$Number[,1,,2]
+dimnames(Rmatrix) <- dimnames(Fmatrix)
+plot_boot_vec(Rmatrix,CIpct=CIpct,xlab="year",ylab="recruits",lty=lty[1])
+points(years_i,t.series_i$recruits*Nage_F0_pr_sc_i,type="o", col="blue",lty=lty[2])
+
+# N
+Nmatrix <- Hist_i@TSdata$Number[,,1]+Hist_i@TSdata$Number[,,2]
+dimnames(Nmatrix) <- dimnames(Fmatrix)
+bam.N <- rowSums(rdatmods_i$N.age)
+plot_boot_vec(Nmatrix,CIpct=CIpct,xlab="year",ylab="N",lty=lty[1])
+points(years_i,bam.N,type="o",col="blue",lty=lty[2])
+
+# F
+# Fmatrix <- Hist_i@TSdata$Find
+plot_boot_vec(Fmatrix,CIpct=CIpct,xlab="year",ylab="F",lty=lty[1])
+ points(years_i,t.series_i$F.full,type="o",
+     col="blue",lty=lty[2])
+
+# B
+Bmatrix <- Hist_i@TSdata$Biomass[,,1]+Hist_i@TSdata$Biomass[,,2]
+dimnames(Bmatrix) <- dimnames(Fmatrix)
+bam.Bklb <- rowSums(rdatmods_i$B.age)
+plot_boot_vec(Bmatrix,CIpct=CIpct,xlab="year",ylab="Biomass (1000 lb)",lty=lty[1])
+# par(new=TRUE)
+points(years_i,bam.Bklb,type="o", #axes=FALSE,xlab="",ylab="",
+     col="blue",lty=lty[1])
+
+mtext(i,side=3,line=0,outer=TRUE)
+
+if(plot_pdf){dev.off()}
+}
+}
+```

### 2022-06-02 RunMSE/SEFSC/Manuscript/MainText.Rnw
move large files out of repo

--- 2022-03-16 RunMSE/SEFSC/Manuscript/MainText.Rnw
@@
 
+\titleformat{\subsubsection}
+   {\small\mdseries}{\thesubsubsection}{1em}{}
+
 %%% Main document
@@
 
+<<functions, echo=FALSE>>=
+texfig <- function(pdf_path="../Figs/myfigure.pdf",
+                   caption_text="This is a caption.",
+                   label="fig:myfigure",
+                   width="6in",
+                   height="7in"
+                   ){
+out <- paste0("\\begin{figure}[!ht]
+\\begin{center}
+\\includegraphics[width=",width,", height=",height,"]{",
+pdf_path,
+"}
+\\end{center}
+\\begin{flushleft}
+\\caption{",
+caption_text,
+"}
+\\label{",
+label
+,"}
+\\end{flushleft}
+\\end{figure}
+\\clearpage")
+
+cat(out)
+}
+@
+
 <<latexTable, echo=FALSE>>=
@@
 \begin{abstract}
-We built operating models for \Sexpr{n_sp} reef fish species from the US Southeast Atlantic, based on recent stock assessments.
-We developed \Sexpr{n_scen} scenerios and \Sexpr{n_MP} management procedures.
-Management procedures varied in terms of how often stock assessments were conducted, and how catch advice was adjusted between stock assessments.
+We conducted a management strategy evaluation (MSE) to investigate how management procedures that adjust catch advice between stock assessments performed compared with existing management procedures.
+We built operating models (OM) for four reef fish species from the US Southeast Atlantic, based on recent stock assessments including Black Sea Bass, Red Porgy, Snowy Grouper, and Vermilion Snapper.
+These OM contained parameters and data specific to each stock, associated fisheries, and the sampling programs that monitor them.
+The analysis assumed efficient implementation of management, such that observed catch was equal to total allowable catch (TAC).
+Our analysis focused on a base scenario intended to most closely characterize the reality of each stock.
+We also developed multiple alternative scenarios to investigate the sensitivity of the analysis to deviations from the base configuration.
+A set of management procedures (MP) was applied independently in closed loop simulation for each species and scenario, with many replicate runs.
+The MP varied in terms of how often stock assessments were conducted (every 1, 5, or 10 years), and how catch advice (i.e.
+TAC) was adjusted between stock assessments.
+Between assessments, TACs were either fixed, adjusted based on projections, or adjusted based on a reference index of abundance.
+Results varied among species and scenarios, but generally showed that healthy stock and fishery status ($\mathrm{SSB>SSB_{MSY}}$ and $F<F_{\mathrm{MSY}}$) and comparable levels of total catch could be maintained with stock assessments conducted every 1, 5 or 10 years, whether TACs were fixed, projected, or adjusted based on indices of abundance.
+But these management procedures vary in terms of average annual variability in yield (AAVY) which was highest when TACs were adjusted based on indices of abundance and lowest when TACs were fixed between assessments.
 
@@
 \section*{Introduction}
-We can only do stock assessments every few years. It would be nice to know if there were ways that we could adjust catch advice between stock assessments to improve.
+
+\subsection*{Motivation}
+Stock assessments are highly resource intensive processes.
+Recent NMFS guidance has prioritized increasing assessment throughput and reducing assessment frequency where appropriate for managed species (\citealt{ICES2012}; \citealt{Methot2015}; \citealt{LynchEtAl2018}).
+Reduced stock assessment frequency would free up assessment scientists to conduct research to advance fisheries management and prioritize unassessed stocks.
+
+One such mechanism of allowing reduced stock assessment frequency while still providing continuous adaptive management is through the use of interim assessment approaches \citep[e.g., ][]{HuynhEtAl2020}.
+Interim assessment approaches use an indicator of stock abundance (e.g., index of abundance) to adjust total allowable catch (TAC) between full stock assessments.
+Interim assessments would still require updated data and analytical input from assessment scientists, but the computational load and time commitment would be substantially diminished.
+Interim assessments have been found to be conceptually sound (Huynh et al.
+2020), and here we seek to identify whether these methods are suitable for stocks in the South Atlantic.
+
+\subsection*{MSE Background}
+The current stock assessment paradigm and the interim assessment approach are each examples of a management procedure.
+A management procedure, or management strategy, is a formal rule that defines how fisheries are managed and includes (1) a clearly defined data-generating protocol, (2) an estimating model that describes the current state or condition of the stock (e.g., stock assessment), (3) a predefined catch (harvest) control rule that describes how catch advice should be adjusted given the state of the stock, and (4) an implementation rule which describes how the catch advice will be applied (\citealt{SainsburyEtAl2000}; \citealt{Punt2010}).
+Management procedures are designed to be adaptive to changes in stock biomass or trajectory (e.g., as estimated biomass declines, allowable catch declines; \citealt{Edwards2016}).
+Consider how the current assessment paradigm can be presented within the management procedure framework, for example, as it includes: (1) a data-collection enterprise to collect abundance, biological, and catch information from the stock; (2) the stock assessment, or estimating, model which uses scientifically collected data to provide an estimate of stock status and biological reference points, (3) catch control rule, which varies with each FMC, but examples include the $P*$ approach \citep{ShertzerEtAl2008} or the 40-10 rule \citep{PFMC2020}, and (4) the implementation of the catch control rule-defined management action, often in the form of TACs.
+
+Because in situ scientific testing of alternate management procedures is logistically unfeasible in practice, we test management procedures using management strategy evaluation (\citealt{ButterworthPunt1999}; \citealt{DeOliveiraEtAl2008}).
+MSE is a framework for testing candidate management procedures across a range of uncertainties using closed-loop simulation (Fig.
+\ref{fig:diagram}; \citealt{Holland2010}; \citealt{PuntEtAl2016}).
+
+Management procedure performance is measured based on pre-specified performance metrics, which are designed to reflect the management objectives of the system.
+Typically management objectives include increasing total allowable catch and reducing risk to the resource.
+When management objectives are not already defined, as in a Fishery Management Plan, stakeholder involvement is often necessary to clarify the goals of the fishery.
+Understandably, not all performance metrics can be simultaneously maximized (e.g., increasing TAC increases risk to the resource).
+MSE therefore serves to lay bare the societal trade offs associated with fisheries management \citep{Punt2017}.
+
+An operating model is created that represents the 'true' system dynamics, and the full management procedure is applied to the stock(s) of interest simulated in the operating model.
+However, there are many assumptions that must be made when generating a simulation of a stock and fishery.
+To ensure that none of these assumptions or decision-points impact the results, particularly those that are most uncertain, multiple operating models can be generated representing different scenarios (\citealt{ButterworthPunt1999}; \citealt{DeOliveiraEtAl2008}; \citealt{PuntEtAl2016}).
+For example, if natural mortality is uncertain, multiple scenarios can be built with different realistic assumptions of natural mortality (high, medium, and low).
+
+We then measure the effects of the management procedure on the 'true' populations simulated by the operating models.
+If the management procedure cannot perform well across all operating models (e.g., natural mortality scenarios), then it likely is not a good candidate for implementation, because we are unlikely to know the real natural mortality rate in practice.
+The presence of multiple operating models serves as a test of the management procedure against many possible realities, ensuring that the chosen management procedure is robust to the uncertainties that we have in the system (\citealt{ButterworthPunt1999}; \citealt{RademeyerEtAl2007}; \citealt{PuntEtAl2016}).
+These uncertainties can extend to future projections, accordingly monitoring how management procedures would perform in the face of nonstationarity.
+
+\subsection*{Interim assessment approach}
+	While setting interim-period catches based on assessment model forecasts can yield improved performance over fixed catches, \citet{HuynhEtAl2020} noted that forecasts are made under assumptions of future stock dynamics and are not responding to true observed changes in stock size.
+The interim approach is a modification of an empirical, indicator-based management procedure, in which catch advice is adjusted based on an indicator of stock abundance (e.g., index of abundance; \cite{GeromontButterworth2015}; \cite{CarruthersEtAl2016}).
+Within the interim approach, TACs set by the stock assessment model are adjusted in interim years based on the behavior of the stock indicator.
+Unlike traditional stock assessment-based TACs, interim assessment TAC adjustments may be implemented immediately with no time-lag \citep{HuynhEtAl2020}.
+
+\citet{HuynhEtAl2020} used MSE to test the interim assessment approach across 3 species of differing life histories (short-, moderate-, long-lived), each with 6 unique operating model scenarios (Base, Hyperstable, Hyperdeplete, Depleted, Lightly fished, Episodic M), using the openMSE software suite [openMSE, \cite{openMSE}; DLMtool, \cite{DLMtool}; MSEtool, \cite{MSEtool}; SAMtool, \cite{SAMtool}].
+Authors found that the use of an interim assessment approach markedly improved management performance over using a fixed TAC between assessments and more closely approximated the management performance of using assessment projections to specify interim period catches.
+Furthermore, management resulting from the interim assessment approach was not adversely impacted by increased interim period length and hyperstable/deplete scenarios in which the assumption that the relative abundance index is proportional to stock biomass is violated.
+Ultimately, the interim approach reduced the need for frequent stock assessments, potentially freeing up resources to focus on other stocks or research questions.
+
+\subsection*{Study Objectives}
+In this study, we sought to replicate the \citet{HuynhEtAl2020} approach by applying it specifically to South Atlantic fishes based on information from the most recent stock assessments.
+Representative species analyzed include Black Sea Bass, Red Porgy, Vermillion Snapper, and Snowy Grouper.
+We used species-specific biological parameters and were able to more accurately describe the data-generating, fishery, and stock assessment dynamics for these species within the openMSE framework, including delays in data collection and management implementation \citep{ShertzerPrager2007} and specification of different selectivity functions for catch and abundance indices.
+Simulations were further specified with empirically estimated levels of observation and process uncertainty.
+The purpose of this study was to explore whether interim assessment approaches would be suitable for South Atlantic fishes.
 
 \section*{Materials and Methods}
-We used the most recent stock assessments from US Southeast US Atlantic for Red Porgy, Black Sea Bass, and Vermilion Snapper.
 
-\subsection{Evaluating management procedures}
+\subsection*{Operating models}
+We used the most recent stock assessments from US Southeast US Atlantic for Red Porgy \citep{SEDAR60}, Black Sea Bass \citep{SEDAR56}, Vermilion Snapper \citep{SEDAR55}, and Snowy Grouper \citep{SEDAR36Update}.
+Elements of the stock assessments are stored as data sets in the R package \texttt{bamExtras} (\url{https://github.com/nikolaifish/bamExtras}).
+Management strategy evaluation was conducted with the R package \texttt{openMSE} \citep{openMSE}, which includes three sub-packages \texttt{DLMtool}, \texttt{MSEtool}, and \texttt{SAMtool} (\citealt{DLMtool}; \citealt{MSEtool}; \citealt{SAMtool}).
+This package uses a set of data objects with very specific list-like structures (S4; \url{http://adv-r.had.co.nz/S4.html}), such as operating model objects (\texttt{OM}).
+Such objects are made up of a set of named 'slots', which contain specific types of information with particular dimensions, to characterize main components of an MSE.
+Input and output from the Beaufort Assessment Model (BAM) is configured as a list which has a specific structure, and is stored in an \texttt{rdat} file.
+The most recent \texttt{rdat} files are also stored in \texttt{bamExtras} as objects (e.g.
+\texttt{rdat\_BlackSeaBass}).
+In order to the transfer information from BAM \texttt{rdat} objects to \texttt{openMSE} objects, we wrote a set of functions and constructed a new R package, \texttt{bamMSE} (\url{https://github.com/nikolaifish/bamMSE}).
+
+Operating models in \texttt{openMSE} (\texttt{OM} class S4 objects) are constructed of four sub-objects: \texttt{Stock}, \texttt{Fleet}, \texttt{Obs}, and \texttt{Imp} class objects.
+Values stored in \texttt{Stock} objects describe a fish stock, \texttt{Fleet} objects characterize a fishing fleet that fishes that stock, \texttt{Obs} objects contain parameters describing how the simulated stock and fleet are observed (e.g.
+bias and error of catch or relative abundance data), and the \texttt{Imp} objects allow the user to set how well managers adhere to management recommendations (i.e.
+implementation error).
+A fifth \texttt{openMSE} object class \texttt{Data}, is used to store various types of data, including data sets typically used in fitting stock assessment models (e.g.
+indices of abundance, catch, and age-composition time series).
+Functions in \texttt{bamMSE} convert \texttt{rdat} objects to \texttt{Stock}, \texttt{Fleet}, \texttt{Obs}, and \texttt{Data} objects (\texttt{rdat2Stock}, \texttt{rdat2Fleet}, \texttt{rdat2Obs}, and \texttt{rdat2Data}).
+
+We used the function \texttt{MSEtool::Assess2OM} to convert BAM results to \texttt{OM} objects, with the help of a wrapper function \texttt{bamAssess2OM} (not yet added to \texttt{bamMSE}).
+While the values of the steepness parameter $h$, and unfished recruitment ($R_{0}$) for the Beverton-Holt stock-recruit relationship are directly passed from BAM to \texttt{Assess2OM}, most other inputs had to be modified from BAM.
+Since \texttt{openMSE} requires the first age in age-structured populations to be age-0 and most BAM assessments start with age-1, age-based data from BAM was linearly extrapolated from age-1 to age-0 before being passed to \texttt{Assess2OM}.
+Such data include several three dimensional numeric arrays with dimensions simulation, age, and year (within recent assessment period): fish weight, fish length, proportion mature, numbers of fish, total fishing mortality rate ($F$; including dead discards) , and natural mortality rate ($M$).
+
+Maturity-at-age is used to compute spawner biomass using methods followed in BAM assessments.
+For gonochoristic species (separate male and female sexes; Vermilion Snapper) maturity-at-age was based on females.
+For protogynous hermaphrodite species (females transition to male as they age; Black Sea Bass, Red Porgy, and Snowy Grouper) maturity-at-age was based on the proportion of fish of either sex mature-at-age.
+
+We ran  \texttt{rdat2Data} on the \texttt{rdat} objects, and passed indices of abundance, their associated CVs, and selectivity-at-age to an \texttt{openMSE} \texttt{cpars} list object.
+In \texttt{openMSE} a \texttt{cpars} list object is used to pass custom parameters, typically time-varying, to an operating model.
+The \texttt{rdat2Data} function assumes that indices based on surveys or recreational fisheries are in numbers and indices based on commercial fisheries are in pounds.
+Only indices available in the terminal year of the assessments were passed to \texttt{cpars} and the \texttt{OM} objects (Fig.
+\ref{fig:AddInd}).
+Estimates of growth parameters ($K$, $L_{\infty}$, and $t_{0}$) from BAM were also passed to the \texttt{OM} objects.
+Selectivity-at-age of removals is estimated annually during the empirical assessment period by \texttt{Assess2OM}, and the average of the last three years of the assessment period was passed to \texttt{cpars} and the \texttt{OM} objects to be used in the projection years.
+
+In most cases, empirical values provided to the \texttt{OM} objects are used to determine distributions of parameters, data, or residuals.
+These distributions are then used by \texttt{openMSE} when simulating values in the projection years.
+For example, the number of age samples (numbers of otoliths) available to management procedures during the projection period are determined by drawing from a distribution based on how many age samples were actually available in the most recent SEDAR assessment of that species.
+However, the time series of residuals for indices of abundance, were generated ahead of time and added to the \texttt{OM} objects.
+Residuals were sampled from a lognormal distribution based on index CVs from the most recent SEDAR assessment.
+In the base and most other scenarios, life history parameters were constant over time in the simulated populations.
+Maximum $F$ was limited in the simulations by rounding the maximum observed $F$ up to the next integer value.
+This limit prevents catch limits from being set unreasonably high.
+
+\subsection*{Management procedures}
+
+The entire MSE was run repeatedly and independently, applying one of nine different management procedures (MP).
+In all of these MP, age-structured stock assessments were conducted at a frequency of every 1, 5, or 10 yr.
+For all MPs, in an assessment year, reference points were estimated (e.g.
+$\mathrm{MSY}$, $F_{\mathrm{MSY}}$), and a simple harvest control rule was applied to determine the TAC for the following year.
+The TACs were computed from the assessment output using the \texttt{SAMtool::HCR\_MSY} function which projects abundance one year beyond the terminal year of the assessment, and applies the catch equation used in the assessment and the target level of fishing mortality ($F_{\mathrm{target}}$).
+In the base scenario, $F_{\mathrm{target}}$ was set equal to $F_{\mathrm{MSY}}$ from the simulated assessment.
+We also limited the maximum $F$ to $F_{\mathrm{max}}=3$ to avoid simulating unreasonably high catch levels.
+Between assessments, catch was set in different ways.
+
+In the fixed TAC MPs [SCA (1), SCA (5), and SCA (10)] stock assessments were conducted every 1, 5, or 10 yr respectively, and the harvest control rule was applied to determine the TAC.
+Between assessments, the TAC was fixed.
+
+In the projection MPs, [Projection (5) and Projection (10)], stock assessments were conducted every 5 or 10 yr, respectively.
+In these MPs a projection analysis is simulated in order to set the TACs for the interval between assessments.
+The population is projected forward for the interval between assessments $F_{\mathrm{target}}$ is applied to compute catch.
+These catches are then used as TACs in the simulated management during the interval.
+These TACs will tend to exhibit a temporal trend since projected abundance is not usually constant.
+
+In the average index interim MPs [Average Index (5) and Average Index (10)] stock assessments were conducted every 5, or 10 yr respectively.
+In an assessment year, the TAC is computed as in other MPs, and is treated as a reference catch ($C_{\mathrm{ref}}$) in the interim procedure.
+The value of a selected index of abundance is also recorded and treated as a reference value ($I_{\mathrm{ref}}$).
+Between assessments, a TAC in year $y+1$ is set by  according to Eq.
+\ref{eq:iMPavg}:
+
+\begin{equation}
+\mathrm{TAC}_{y+1} = C_{\mathrm{ref}}\frac{\tilde{I}_{\mathrm{recent}}}{I_{\mathrm{ref}}}
+\label{eq:iMPavg}
+\end{equation}
+
+This calculation scales $C_{\mathrm{ref}}$ by the ratio of an average of the three most recent years of the abundance index ($\tilde{I}_{\mathrm{recent}}$) and the reference year ($I_{\mathrm{ref}}$).
+Using the average of recent years of the index instead of a single recent value effectively smooths the index.
+This serves to avoid a noisy index leading to highly varying TACs.
+
+In the buffered index interim MPs, Buffered Index (5) and Buffered Index (10), stock assessments were conducted every 5, or 10 yr respectively.
+Between assessments, a TAC in year $y+1$ is set by  according to Eq.
+\ref{eq:iMPbfr}:
+
+\begin{equation}
+\mathrm{TAC}_{y+1} = C_{\mathrm{ref}} \frac{I_{y} + \hat{\sigma}}{I_{\mathrm{ref}} + \hat{\sigma}}
+\label{eq:iMPbfr}
+\end{equation}
+
+where $I_{y}$ is the value of the index in the most recent year and $\hat{\sigma}$ is the standard deviation of the index.
+Including $\hat{\sigma}$ in this calculation assures that the noisier the index, the smaller the adjustment to the TAC, limiting variation in TACs.
+
+% \begin{enumerate}
+% \setstretch{1}
+% \item Average catch (AvC): Average catch over all years
+% \item Recent catch (CC1): Average catch over the last 5 years
+% \item Depletion corrected average catch (DCAC):
+% \item Depletion based stock reduction analysis (DBSRA):
+% \item Surplus production model (SPMSY):
+% \item Statistical catch-at-age model
+% \begin{enumerate}
+% \item 1-year interval (SCA (1))
+% \item 5-year interval with fixed TAC between years (SCA (5))
+% \item 10-year interval with fixed TAC between years (SCA (10))
+% \item 5-year interval with projected TAC between years (Projection (5))
+% \item 10-year interval with projected TAC between years (Projection (10))
+% \item 5-year interval with TAC adjusted based on averaged recent index between years  (Average Index (5))
+% \item 10-year interval with TAC adjusted based on averaged recent index between years  (Average Index (10))
+% \item 5-year interval with TAC adjusted based on buffered averaged recent index between years  (Buffered Index (5))
+% \item 10-year interval with TAC adjusted based on buffered averaged recent index between years  (Buffered Index (10))
+% \end{enumerate}
+% \end{enumerate}
+% \setstretch{2}
+
+\subsubsection*{Statistical catch-at-age model configuration}
+
+Management procedures that ran statistical catch-at-age models utilized the \texttt{SAMtool::SCA} function.
+The model run in this function was configured as similar to BAM as the function would allow.
+The configuration was specific to each species' operating model where applicable.
+% Data structure
+
+The range of ages modeled in the assessments is from age-0 to the maximum age modeled in the BAM assessment for each species.
+Life history is age-structured such that, length, weight, maturity, and natural mortality vary with age.
+Years of data included in the time series span from the earliest historical year to two years prior to the current year (i.e.
+assessment year).
+Management changes go into effect the year following the assessment.
+Effectively, the last two years of available data are excluded from the stock assessment, to simulate a typical data lag observed in SEDAR assessments.
+For interim procedures, we assumed that management would be put in place the next year, and therefore did not impose any additional data lag.
+Applying data lags is not a standard option in \texttt{openMSE} so the lag option was written into wrapper functions for \texttt{SAMtool} functions \texttt{SCA}, \texttt{make\_MP}, \texttt{make\_interim\_MP}, and \texttt{make\_projection\_MP}, for this project.
+
+The \texttt{SCA} models included one combined set of removals (landings and discards).
+Although most of the empirical BAM assessments include multiple fleets of removals with landings and discards separate, this is not an option when using \texttt{runMSE}\footnote{The flexibility to add multiple landings fleets has recently been added to \texttt{openMSE} using the \texttt{multiMSE} function, but would require a nontrivial amount of coding to incorporate into the current analysis.}.
+The model also fits to one or more indices of abundance, depending on the species, and one set of simulated catch-at-age data corresponding to the landings.
+
+% Selectivity
+Selectivity-at-age associated with removals was estimated within \texttt{SCA} with a logistic selectivity function. Selectivity of the indices was provided to \texttt{SCA} as fixed information.
+
+The \texttt{SCA} model used a Beverton-Holt stock-recruit function, the Baranov catch equation, and a multinomial distribution for fitting catch-at-age information.
+Several parameters are fixed by default in \texttt{SCA} including Beverton-Holt steepness, equilibrium $F$, CV associated with catch, and the standard deviation of recruitment residuals (i.e.
+"rec sigma").
+Recruitment deviations were estimated for one generation prior to the first year that age-composition data were available.
+Toward the end of each assessment, recruitment deviations were not estimated for several years and recruitment was predicted from the mean value of the stock-recruit relationship.
+The number of years for which recruitment deviations were not estimated was based on an option within the \texttt{SCA} function (\texttt{late\_dev="comp50"}) which specifies it as the: ``number of ages (smaller than the mode) for which the catch-at-age matrix has less than half the abundance than that at the mode'' (\texttt{SAMtool::SCA} help file).
+
+\subsection*{Scenarios}
+
+The configuration of the MSE described above was considered the base scenario.
+Various modifications to the configuration were made to create other scenarios described below.
+Many other scenarios were explored but did not change the conclusions of our analysis, so they are not included in the current report.
+
+\begin{enumerate}
+\setstretch{1}
+\item Index high CV (ucvhi): Uncertainty (coefficient of variation; CV) in primary index of abundance of abundance is twice the CV of the base scenario
+\item Index low CV (ucvlo): Uncertainty (CV) in primary index of abundance of abundance is half the CV of the base scenario
+\item Index is biased (ubias): Primary index of abundance increasingly underestimates population size (i.e. decreasing catchability)
+\item High TAC (tachi): TAC = 1.25MSY ($F_{\mathrm{target}} = 1.25F_{\mathrm{MSY}}$ in harvest control rule)
+\item Low TAC (taclo): TAC = 0.75MSY ($F_{\mathrm{target}} = 0.75F_{\mathrm{MSY}}$ in harvest control rule)
+
+% \item Base (base): Most likely scenario, described above
+% \item Depleted (dep): Depletion of the stock is high (i.e. smaller stock size) at the beginning of the projection period
+% \item Lightly fished (lf): Depletion of the stock is low (i.e. larger stock size) at the beginning of the
+% \item Regime change (rc): Recruitment deviations decline over the projection period, then remain low
+% \item Minimal error (minerr): Minimal (but not zero) error in all stochastic elements of the \texttt{OM}
+% \item Minimal rec. dev. (minrecdev): Recruitment deviations set to low value
+% \item Non-stationary recruitment (recns)
+% \item Vulnerability time invariant (vtiv): Selectivity associated with catch (i.e. vulnerability) does not vary annually during the historic period.
+%
+% \item No empirical indices (noempind): No empirical indices, CVs, or index selectivities are included in the \texttt{OM}
+% \item Catch CV 0.05 (catcvlo): CV of catch is set to 0.05 when fitting to catch in stock assessments.
+% \item No data lag (nolag): Catch advice (i.e. TAC) from stock assessments is implemented the year after the terminal year of the assessment
+% \item Perfect observation (perfobs): Minimal observation error and very high sample sizes in data sets
+%
+% \item Set life history (lhset): $M$ and $h$ are set to the same fixed values for all species ($M$ = 0.2, $h$ = 0.84)
+% \item Set $M$ (Mset): $M$ is set to the same fixed value for all species ($M$ = 0.2)
+% \item Set $h$ (steepset): $h$ is set to the same fixed value for all species ($h$ = 0.84)
+% \item Age-varying $M$ (agevarM): $M$ varies with age
+% \item Episodic $M$ (epiM): $M$ is constant in most years but is occasionally much higher
+
+% \item Hyper-deplete: Primary index of abundance is hyper-deplete
+% \item Hyper-stable: Primary index of abundance is hyper-stable
+% \item Vulnerability dome-shaped (vdome): Selectivity associated with catch (i.e. vulnerability) is estimated with a dome-shaped function in stock assessments
+
+\end{enumerate}
+\setstretch{2}
+
+For each management procedure, we ran the replicate simulations 250 times for the base scenario and 50 times for each alternative scenario.
+In preliminary analysis of the base scenario, we found that results were approximately the same with 50 runs as 250 runs, although output plots were smoother when more runs were completed.
+However, output objects from 250 are rather large (200-400 Mb) and become cumbersome to work with.
+
+\subsection*{Evaluating performance}
+To evaluate the relative performance of the MPs, we consider a set of reference points and performance metrics.
+We computed total catch, relative catch ($C/\mathrm{MSY}$), stock status ($\mathrm{SSB/SSB_{MSY}}$), fishery status ($F/F_{\mathrm{MSY}}$), and the average annual variability in yield (AAVY).
+The AAVY is the absoluted relative difference in catch between two consecutive years, calculated as in Eq.
+\ref{eq:AAVY}:
+\begin{equation}
+\mathrm{AAVY} = \frac{\sum_{y=1}^{Y}\sqrt{(\frac{C_{y}-C_{y+1}}{C_{y+1}})^{2}}}{Y}
+\label{eq:AAVY}
+\end{equation}
+where $C_{y}$ and $C_{y+1}$ are catches in years $y$ and $y+1$, and $Y$ is the total number of years in the projection period.
+
+We also computed several performance metrics, focusing on long term values, measured during the last 10 years of the projection period.
+These included average long term yield, the probability [$\mathrm{P()}$] of healthy stock status $\mathrm{P(SSB>SSB_{MSY})}$, the probability of not overfishing $\mathrm{P}(F<F_{\mathrm{MSY}})$, and the probability of stable yield $\mathrm{P(AAVY<20\%)}$.
 
@@
 
+\subsection*{Base scenario}
+
+% Boxplots
+Response variables for the base scenario varied among time periods over the projection years for all metrics.
+Stock status ($\mathrm{SSB/SSB_{MSY}}$) increased over time among all nine SCA-based MPs for all four species, but was similar between MPs during the same time interval (Fig.
+\ref{fig:boxplotSBSBMSY1}).
+Fishery status ($F/F_{\mathrm{MSY}}$) was somewhat more  variable within and between MPs, but still largely consistent among SCA-based MPs, for all species (Fig.
+\ref{fig:boxplotFFMSY1}).
+Total catch was also similar among SCA-based MPs for all species, for similar time periods (Fig.
+\ref{fig:boxplotCatchTotal1}).
+It was relatively less consistent for Black Sea Bass, but variability in total catch within MPs was also more variable for that stock.
+Average annual variability in yield (AAVY) showed more substantial variation among MPs (Fig.
+\ref{fig:boxplotAAVY1}).
+For Vermilion Snapper and Snowy Grouper, the fixed TAC and projection MPs showed substantially lower AAVY than the interim MPs.
+Red Porgy showed a similar pattern, although AAVY for the Average Index (5) and Average Index (10) was relatively lower.
+For Black Sea Bass, there was relatively little difference in AAVY among MPs compared to the other species.
+
+% Time series plots
+Time series of relative catch (catch/MSY), averaged across simulation runs, are generally most stable when assessments are run annually, and show the largest interannual variations when projection MPs are used (Figs.
+\ref{fig:tsCatchMSY1} and \ref{fig:tsCatchMSY1B}).
+For the projection MPs, the difference in catch between consecutive years is actually modest for most years, but tends to be very large between a stock assessment year and the next year, leading to periodic spikes.
+For Black Sea Bass, the fixed TAC MP was often well above or below the other MPs with a 10 yr assessment interval, but catches were otherwise very steady because TACs were fixed during the intervals.
+The index-based approaches tended to produce similar catches which were more consistent than the projection and fixed TAC MPs.
+Relative catches were all more similar to the annual assessment MP when the assessment interval was 5 yrs.
+Patterns in $F/F_{\mathrm{MSY}}$ time series reflected dynamics similar to the catch.
+However the fluctuations in the projection MP were less pronounced (Figs.
+\ref{fig:tsFFmsy1} and \ref{fig:tsFFmsy1B}) and tended to be lower than other MPs, representing a more conservative strategy.
+Despite differences in catch and relative $F$ among MPs, trends in $\mathrm{SSB/SSB_{MSY}}$ were similar among all MPs for Red Porgy and Snowy Grouper.
+For Vermilion Snapper only the projection MP deviated from the others, with $\mathrm{SSB/SSB_{MSY}}$ tending to be slightly higher (Figs.
+\ref{fig:tsSSBSSBmsy1} and \ref{fig:tsSSBSSBmsy1B}).
+Trends in $\mathrm{SSB/SSB_{MSY}}$ for Black Sea Bass varied among MPs with a 10 yr assessment interval, with the Fixed TAC MP showing the widest fluctuations.
+But with a 5 year assessment interval, $\mathrm{SSB/SSB_{MSY}}$ trends were fairly similar among MPs for all species including Black Sea Bass.
+
+% Trade off plots
+Trade off plots display bivariate relationship between two performance metrics for multiple management procedures, to identify differences between MPs in performance-metric space.
+We considered several important trade offs to look for differences in performance among MPs, plotting mean values across simulation runs, for each MP.
+In particular we looked at trade offs between yield (catch), variability in yield, or fishery status, versus stock status.
+We limited data used to produce these plots to the final 10 years of the projection, to look at long term values.
+
+Trade off plots of probability that AAVY < 20\% versus the probability that $\mathrm{SSB>SSB_{MSY}}$ (Fig.
+\ref{fig:trAAVYP1001}), the probability that $F<F_{\mathrm{MSY}}$ (Fig.
+\ref{fig:trAAVYPNOF1}), and mean relative long term yield (Fig.
+\ref{fig:trAAVYYldLT1}), show little differentiation among MPs along the vertical axis.
+The MPs mostly differ in the probability of that AAVY < 20\%.
+As suggested in other plots, SCA (5), and SCA (10) produce more consistent yields, which is indicated in trade off plots as having higher probabilities that AAVY < 20\%.
+Performance of other MPs in terms of probability of AAVY < 20\% varied by species.
+Trade off plots of mean relative long term yield versus the probability that $\mathrm{SSB>SSB_{MSY}}$ (Fig.
+\ref{fig:trP100YldLT1}) and probability that $F<F_{\mathrm{MSY}}$ versus probability that $\mathrm{SSB>SSB_{MSY}}$ (Fig.
+\ref{fig:trPNOFP1001}) do not indicate any consistent differentiation among MPs.
+
+% Phase plots
+We also produced phase plots of $F/F_{\mathrm{MSY}}$ versus $\mathrm{SSB/SSB_{MSY}}$ (Fig.
+\ref{fig:phasePlot1}) including median values among all simulation runs, as well as points for each run.
+Again we limited data to the final 10 years of the projection periods.
+Phase plots also do not indicate any consistent differentiation among MPs.
+However the projection MP resulted in slightly higher stock status for Vermilion Snapper and Red Porgy and the fixed TAC MP resulted in slightly higher $F$-status in Black Sea Bass.
+
+\subsection*{Alternative scenarios}
+Although results for alternative scenarios differed from the base in various ways, the overall results are the same (Figs.
+\ref{fig:boxplotSBSBMSY2}-\ref{fig:phasePlot2}).
+Management procedures perform similarly except for variation in variability of catch.
+One exception to this generality is for Red Porgy in the scenario where the harvest control rule set the TAC to $1.25\times\mathrm{MSY}$.
+Under this scenario, the Red Porgy could not recover from its already depleted state and only the annual assessment MP was able to keep the stock from going completely crashing in more than 50\% of simulation runs (Fig.
+\ref{fig:phasePlot2}).
+
 \section*{Discussion}
 
-Some broad conclusions
+Overall, our analysis suggested that all of the management procedures we considered resulted in similar trends in $\mathrm{SSB/SSB_{MSY}}$ for a given stock and scenario.
+With a 10 yr assessment interval the Black Sea Bass stock, showed the most variability among MPs, and only the annual assessment MP produced stable $\mathrm{SSB/SSB_{MSY}}$ until late in the projection period; but with 5 yr assessment intervals, all MPs produced similar results.
+In this stock the projection MP tended to be a bit conservative, resulting in fairly high $\mathrm{SSB/SSB_{MSY}}$, but even this MP could be tuned by applying a more aggressive harvest control rule if that was desired.
 
-Which factors seem to account for the most variation in results in general?
-\begin{itemize}
-\item Above all, results differ between operating models (i.e. species)
-\item Scenario is the next most important factor, particularly depletion scenarios and regime change
-\end{itemize}
+Even this variation in $\mathrm{SSB/SSB_{MSY}}$, evident in the central tendency of the time series, is less apparent when comparing distributions in boxplots by time period.
+This is generally true for $F/F_{\mathrm{MSY}}$ as well.
+Distributions of total catch are also similar among MPs, comparing the same time periods.
+
+The performance metric that really separates the MPs is variability in yield.
+The simplest, fixed TAC, MPs correspond to the lowest variability in yield, followed by the projection MPs which set TACs that change between assessments but follow a simple trajectory.
+For the index-based approaches, TACs vary in more complex ways between assessments based on changes in abundance, leading to greater variability in catch.
+
+An ideal interim management procedure would allow for stock assessments to be conducted less frequently while still achieving management goals.
+While we found index-based interim MPs performed somewhat better than fixed TAC MPs when comparing time series of $\mathrm{SSB/SSB_{MSY}}$ at the assessment frequency, there is no clear improvement when comparing interim procedures conducted with an assessment frequency of 10 yrs and fixed TAC MPs with a assessment frequency of 5 yrs.
+
+It may be possible to improve upon the index-based MPs, although we did not investigate this.
+In particular, the computation used to adjust the TACs can be easily modified to decrease variation in TACs and presumably catch.
+But it's likely that this modification would trade off with the ability of the MP to maintain desirable stock status.
+Such an MP might be expected to occupy a location in performance space intermediate between the current index-based MPs and the fixed TAC MPs.
+
+In order for a new MP to be favored over and existing one, it would likely need to exhibit a more favorable ratio of performance to effort.
+We have focused on assessing performance, but can make some basic conjectures about effort that might be useful to guiding decisions about whether or not interim procedures are favorable.
+If we assign 1 unit of scientific effort to conducting a stock assessment (including analysis and process; e.g.
+SEDAR), then conducting one assessment every 5 years would be 0.2 units per year (upy) and every 10 years would be 0.1 upy.
+If an index-based TAC adjustment were to be applied every year, it would be completed nine times in 10 years.
+Therefore the relative effort of completing such an analysis was equal to 0.1/9 upy, it would take just as much effort as doing one additional assessment, and therefore the effort would be equivalent to doing assessments every 5 years.
+It is likely that the analytical effort of updating an index of abundance and applying the adjustment procedure is substantially less than the effort that goes into an entire assessment, and presumably the assessment process would be simpler.
+But it seems less clear that the effort would be less than $\frac{1}{9}^{\mathrm{th}}$ as much.
+
+In addition, we should consider the management effort required to review and adjust catch advice, similarly assigning 1 unit of management effort per assessment and 0.2 upy when conducting assessments every 5 years.
+But in this case, the management effort required to review and adjust catch advice based on an updated index is probably similar to the management effort of a full assessment.
+Therefore the management effort of applying an index-based MP with an assessment interval of 10 years would be about 1 upy, or about $5\times$ the management effort of applying a fixed TAC or projection MP with an assessment interval of 5 years.
+
+This consideration of effort is clearly hypothetical, but attempts to outline some of the costs that an index-based MP might have to overcome to be preferred over the status quo approach.
+In the present analysis we found limited improvement of the index-based MPs over status quo approaches in terms of maintaining healthy stocks, and poorer performance in terms of more variable catches.
+So if the net performance of the index-based MPs could even be considered similar to the status quo, the actual effort associated with conducting and implementing an index-based MP will have to be very low for the approach to be preferred.
+
+% Potential discussion materials from Quang's paper:
+% Areas of future interim MP research:
+% - Can tune interim MP to meet specific performance objectives
+% - Future case-studies can evaluate how interim MPs perform if survey and fishery vulnerability are substantially different
+% - Changes in environmental conditions may require revision of reference points
+% - Model misspecification
+% - Further evaluation of the interim MPs will need to account for the time lags in the management system.
+
+% Which factors seem to account for the most variation in results in general?
+% \begin{itemize}
+% \item Above all, results differ between operating models (i.e. species)
+% \item Scenario is the next most important factor, particularly depletion scenarios and regime change
+% \end{itemize}
 
 \section*{Acknowledgements}
-We thank everyone.
+We extend special thanks to Quang Huynh for answering many questions about the \texttt{openMSE} software and writing new features and functions into the software in response to our inquiries.
+Thanks also to Adrian Hordyk and Tom Carruthers at Blue Matter for additional help with \texttt{openMSE}.
+Thank you to Kate Siegfried and Lew Coggins for thoughtful suggestions.
+Thanks to the Fischmeister 5000 uber computer for running computations day and night, without complaint.
 
@@
 %% TABLES
-\newpage
-\section*{Tables}
+% \newpage
+% \section*{Tables}
 
@@
 
+% Indices
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in,height=5.25in]{../Figs/MSEDiagram.png}
+\end{center}
+\begin{flushleft}
+\caption{Diagram of the MSE process.
+The operating model is the simulated "true" dynamics of the system; the observation, or data-generating, model simulates the process of scientific data collection from the stock and fishery; the estimating model is used to estimate the status of the stock; the catch control rule is a pre-defined decision rule that adaptively adjusts management measures based on the status of the stock; the implementation model implements the management recommendations from the catch control rule back into the operating model with implementation and management uncertainty.
+Note that all model components highlighted in gray comprise the management procedure and performance metrics (or management procedure performance) is measured from the operating model.}
+\label{fig:diagram}
+\end{flushleft}
+\end{figure}
+
+% Indices
 \begin{figure}[!ht]
@@
 \begin{flushleft}
-\caption{Indices derived from BAM stock assessments available during the projection period, for the SCA\_5 MP in the Base scenario. Shaded areas represent 95\% CI for indices among simulation runs.}
-\label{fig:phasePlot1}
+\caption{Indices derived from BAM stock assessments available during the projection period, for the SCA (10) MP in the Base scenario, where stock assessments are conducted every 10 years during the projection period (dashed vertical lines).
+Shaded areas represent 95\% CI for indices among simulation runs.}
+\label{fig:AddInd}
 \end{flushleft}
@@
 
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[width=6in,height=7in]{../Figs/phasePlot1.pdf}
-\end{center}
-\begin{flushleft}
-\caption{Phase plots for the base scenario and the first set of experimental scenarios}
-\label{fig:phasePlot1}
-\end{flushleft}
-\end{figure}
+<<boxplots base,results=tex,echo=FALSE>>=
+box_caption <- function(...){
+  dots <- list(...)
+  paste0("Box plots of ",
+         dots[[1]],
+         " for the base ",
+         dots[[2]],
+         " Grouped boxes represent sequential time periods during the projection period. Boxes represent interquartile range (IQR). Whiskers are drawn to $1.5\\times\\mathrm{IQR}$."
+  )
+  }
 
-% \begin{figure}[!ht]
-% \begin{center}
-% \includegraphics[width=6in,height=7in]{../Figs/phasePlot2.pdf}
-% \end{center}
-% \begin{flushleft}
-% \caption{Phase plots for the base scenario and the second set of experimental scenarios}
-% \label{fig:phasePlot2}
-% \end{flushleft}
-% \end{figure}
+texfig("../Figs/boxplotSBSBMSY1.pdf",
+       box_caption("$\\mathrm{SSB/SSB_{MSY}}$","scenario."),
+       "fig:boxplotSBSBMSY1")
+
+texfig("../Figs/boxplotFFMSY1.pdf",
+       box_caption("$\\mathrm{F/F_{MSY}}$","scenario."),
+       "fig:boxplotFFMSY1")
+
+texfig("../Figs/boxplotCatchTotal1.pdf",
+       box_caption("total catch (annual catches summed across each time period)","scenario."),
+       "fig:boxplotCatchTotal1")
+
+texfig("../Figs/boxplotAAVY1.pdf",
+       box_caption("average annual variation in yield ($\\mathrm{AAVY}$)","scenario."),
+       "fig:boxplotAAVY1")
+@
+
+<<tsplots base A and B,results=tex,echo=FALSE>>=
+ts_caption <- function(...){
+  dots <- list(...)
+  paste0("Time series of ",
+         dots[[1]],
+         " among simulation runs for the base ",
+         dots[[2]],
+         "Vertical dotted lines indicate assessment years at ",
+         dots[[3]]
+         ," yr intervals."
+  )
+  }
+
+for(i in 1){
+# texfig(paste0("../Figs/tsCatch",i,".pdf"),
+#        ts_caption("median $\\mathrm{catch}$","scenario.","10"),
+#        paste0("fig:tsCatch",i))
+# texfig(paste0("../Figs/tsCatch",i,"B.pdf"),
+#        ts_caption("median $\\mathrm{catch}$","scenario.","5),
+#        paste0("fig:tsCatch",i,"B"))
+
+texfig(paste0("../Figs/tsCatchMSY",i,".pdf"),
+       ts_caption("median $\\mathrm{catch/MSY}$","scenario.","10"),
+       paste0("fig:tsCatchMSY",i)
+       )
+
+texfig(paste0("../Figs/tsCatchMSY",i,"B.pdf"),
+       ts_caption("median $\\mathrm{catch/MSY}$","scenario.","5"),
+       paste0("fig:tsCatchMSY",i,"B"))
+
+texfig(paste0("../Figs/tsFFmsy",i,".pdf"),
+       ts_caption("median $\\mathrm{F/F_{MSY}}$","scenario.","10"),
+       paste0("fig:tsFFmsy",i)
+       )
+
+texfig(paste0("../Figs/tsFFmsy",i,"B.pdf"),
+       ts_caption("median $\\mathrm{F/F_{MSY}}$","scenario.", "5"),
+       paste0("fig:tsFFmsy",i,"B"))
+
+texfig(paste0("../Figs/tsSSBSSBmsy",i,".pdf"),
+       ts_caption("median $\\mathrm{SSB/SSB_{MSY}}$","scenario.","10"),
+       paste0("fig:tsSSBSSBmsy",i)
+       )
+
+texfig(paste0("../Figs/tsSSBSSBmsy",i,"B.pdf"),
+       ts_caption("median $\\mathrm{SSB/SSB_{MSY}}$","scenario.","5"),
+       paste0("fig:tsSSBSSBmsy",i,"B"))
+}
+@
+
+<<trplots base,results=tex,echo=FALSE>>=
+tr_caption <- function(...){
+  dots <- list(...)
+  paste0("Trade off plots of",
+         dots[[1]],
+         " versus ",
+         dots[[2]],
+         " among simulation runs for the base ",
+         dots[[3]],
+         " Plots are based on data for the last 10 years of the projection period."
+  )
+  }
+
+for(i in 1){
+texfig(paste0("../Figs/trAAVYP100",i,".pdf"),
+       tr_caption(" the probability that average annual variability in yield (AAVY) <20\\%,",
+                  " the probability that $\\mathrm{SSB > SSB_{MSY}}$",
+                  "scenario."),
+       paste0("fig:trAAVYP100",i),
+       width="7in",
+       height="3.5in")
+
+texfig(paste0("../Figs/trAAVYPNOF",i,".pdf"),
+       tr_caption(" the probability that average annual variability in yield (AAVY) <20\\%,",
+                  " the probability that $\\mathrm{F < F_{MSY}}$",
+                  "scenario."),
+       paste0("fig:trAAVYPNOF",i),
+       width="7in",
+       height="3.5in")
+
+texfig(paste0("../Figs/trAAVYYldLT",i,".pdf"),
+       tr_caption(" the probability that average annual variability in yield (AAVY) <20\\%,",
+                  " longterm yield",
+                  "scenario."),
+       paste0("fig:trAAVYYldLT",i),
+       width="7in",
+       height="3.5in")
+
+texfig(paste0("../Figs/trP100YldLT",i,".pdf"),
+       tr_caption(" the probability that $\\mathrm{SSB > SSB_{MSY}}$",
+                  " longterm yield",
+                  "scenario."),
+       paste0("fig:trP100YldLT",i),
+       width="7in",
+       height="3.5in")
+
+texfig(paste0("../Figs/trPNOFP100",i,".pdf"),
+       tr_caption(" the probability that $\\mathrm{F < F_{MSY}}$ ",
+                  " the probability that $\\mathrm{SSB > SSB_{MSY}}$",
+                  "scenario."),
+       paste0("fig:trPNOFP100",i),
+       width="7in",
+       height="3.5in")
+
+}
+@
+
+<<phaseplots base,results=tex,echo=FALSE>>=
+ph_caption <- function(...){
+  dots <- list(...)
+  paste0("Phase plots of",
+         dots[[1]],
+         " versus ",
+         dots[[2]],
+         " among simulation runs for the base ",
+         dots[[3]]
+  )
+  }
+for(i in 1){
+texfig(paste0("../Figs/phasePlot",i,".pdf"),
+       ph_caption(" the probability that $\\mathrm{F > F_{MSY}}$ ",
+                  " the probability that $\\mathrm{SSB > SSB_{MSY}}$",
+                  "scenario."),
+       paste0("fig:phasePlot",i),
+       width="7in",
+       height="3.5in")
+}
+@
 
 %% APPENDIX
-% \begin{appendix}
-%
-% \clearpage
-% \section*{Appendix S1}
-%
+\begin{appendix}
+
+\clearpage
+\section*{Appendix}
+
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{S\arabic{figure}}
+
 % \setcounter{table}{0}
@@
 %
-% \end{appendix}
+
+<<boxplots appendix,results=tex,echo=FALSE>>=
+#caption_expr <- expression(paste("scenario and group", i, "alternative scenarios."))
+caption_expr <- expression(paste("and alternative scenarios."))
+
+for(i in 2){
+texfig(paste0("../Figs/boxplotSBSBMSY",i,".pdf"),
+       box_caption("$\\mathrm{SSB/SSB_{MSY}}$",
+                   eval(caption_expr)),
+
+       paste0("fig:boxplotSBSBMSY",i))
+
+texfig(paste0("../Figs/boxplotFFMSY",i,".pdf"),
+       box_caption("$\\mathrm{F/F_{MSY}}$",
+                   eval(caption_expr)),
+       paste0("fig:boxplotFFMSY",i))
+
+texfig(paste0("../Figs/boxplotCatchTotal",i,".pdf"),
+       box_caption("total catch (annual catches summed across each time period)",
+                   eval(caption_expr)),
+       paste0("fig:boxplotCatchTotal",i))
+
+texfig(paste0("../Figs/boxplotAAVY",i,".pdf"),
+       box_caption("average annual variation in yield ($\\mathrm{AAVY}$)",
+                   eval(caption_expr)),
+       paste0("fig:boxplotAAVY",i))
+}
+@
+
+<<tsplots appendix A and B,results=tex,echo=FALSE>>=
+for(i in 2){
+# texfig(paste0("../Figs/tsCatch",i,".pdf"),
+#        ts_caption("median $\\mathrm{catch}$","scenario.","10"),
+#        paste0("fig:tsCatch",i))
+# texfig(paste0("../Figs/tsCatch",i,"B.pdf"),
+#        ts_caption("median $\\mathrm{catch}$","scenario.","5),
+#        paste0("fig:tsCatch",i,"B"))
+
+texfig(paste0("../Figs/tsCatchMSY",i,".pdf"),
+       ts_caption("median $\\mathrm{catch/MSY}$","scenario.","10"),
+       paste0("fig:tsCatchMSY",i)
+       )
+
+texfig(paste0("../Figs/tsCatchMSY",i,"B.pdf"),
+       ts_caption("median $\\mathrm{catch/MSY}$","scenario.","5"),
+       paste0("fig:tsCatchMSY",i,"B"))
+
+texfig(paste0("../Figs/tsFFmsy",i,".pdf"),
+       ts_caption("median $\\mathrm{F/F_{MSY}}$","scenario.","10"),
+       paste0("fig:tsFFmsy",i)
+       )
+
+texfig(paste0("../Figs/tsFFmsy",i,"B.pdf"),
+       ts_caption("median $\\mathrm{F/F_{MSY}}$","scenario.", "5"),
+       paste0("fig:tsFFmsy",i,"B"))
+
+texfig(paste0("../Figs/tsSSBSSBmsy",i,".pdf"),
+       ts_caption("median $\\mathrm{SSB/SSB_{MSY}}$","scenario.","10"),
+       paste0("fig:tsSSBSSBmsy",i)
+       )
+
+texfig(paste0("../Figs/tsSSBSSBmsy",i,"B.pdf"),
+       ts_caption("median $\\mathrm{SSB/SSB_{MSY}}$","scenario.","5"),
+       paste0("fig:tsSSBSSBmsy",i,"B"))
+}
+@
+
+<<trplots appendix,results=tex,echo=FALSE>>=
+for(i in 2){
+texfig(paste0("../Figs/trAAVYP100",i,".pdf"),
+       tr_caption(" the probability that average annual variability in yield (AAVY) <20\\%,",
+                  " the probability that $\\mathrm{SSB > SSB_{MSY}}$",
+                  eval(caption_expr)),
+       paste0("fig:trAAVYP100",i),
+       width="7in",
+       height="8in")
+
+texfig(paste0("../Figs/trAAVYPNOF",i,".pdf"),
+       tr_caption(" the probability that average annual variability in yield (AAVY) <20\\%,",
+                  " the probability that $\\mathrm{F > F_{MSY}}$",
+                  eval(caption_expr)),
+       paste0("fig:trAAVYPNOF",i),
+       width="7in",
+       height="8in")
+
+texfig(paste0("../Figs/trAAVYYldLT",i,".pdf"),
+       tr_caption(" the probability that average annual variability in yield (AAVY) <20\\%,",
+                  " longterm yield",
+                  eval(caption_expr)),
+       paste0("fig:trAAVYYldLT",i),
+       width="7in",
+       height="8in")
+
+texfig(paste0("../Figs/trPNOFP100",i,".pdf"),
+       tr_caption(" the probability that $\\mathrm{F > F_{MSY}}$ ",
+                  " the probability that $\\mathrm{SSB > SSB_{MSY}}$",
+                  eval(caption_expr)),
+       paste0("fig:trPNOFP100",i),
+       width="7in",
+       height="8in")
+
+}
+@
+
+<<phaseplots appendix,results=tex,echo=FALSE>>=
+for(i in 2){
+texfig(paste0("../Figs/phasePlot",i,".pdf"),
+       ph_caption(" the probability that $\\mathrm{F > F_{MSY}}$ ",
+                  " the probability that $\\mathrm{SSB > SSB_{MSY}}$",
+                  eval(caption_expr)),
+       paste0("fig:phasePlot",i),
+       width="7in",
+       height="8in")
+}
+@
+
+\end{appendix}
 

### 2022-06-02 RunMSE/SEFSC/Manuscript/MainText.tex
move large files out of repo

--- 2022-03-16 RunMSE/SEFSC/Manuscript/MainText.tex
@@
 \begin{abstract}
-We built operating models for three reef fish species from the US Southeast Atlantic, based on recent stock assessments.
-We developed 10 scenerios and 13 management procedures.
-Management procedures varied in terms of how often stock assessments were conducted, and how catch advice was adjusted between stock assessments.
+We conducted a management strategy evaluation (MSE) to investigate how management procedures that adjust catch advice between stock assessments performed compared with existing management procedures.
+We built operating models (OM) for four reef fish species from the US Southeast Atlantic, based on recent stock assessments including Black Sea Bass, Red Porgy, Snowy Grouper, and Vermilion Snapper.
+These OM contained parameters and data specific to each stock, associated fisheries, and the sampling programs that monitor them.
+The analysis assumed efficient implementation of management, such that observed catch was equal to total allowable catch (TAC).
+Our analysis focused on a base scenario intended to most closely characterize the reality of each stock.
+We also developed multiple alternative scenarios to investigate the sensitivity of the analysis to deviations from the base configuration.
+A set of management procedures (MP) was applied independently in closed loop simulation for each species and scenario, with many replicate runs.
+The MP varied in terms of how often stock assessments were conducted (every 1, 5, or 10 years), and how catch advice (i.e.
+TAC) was adjusted between stock assessments.
+Between assessments, TACs were either fixed, adjusted based on projections, or adjusted based on a reference index of abundance.
+Results varied among species and scenarios, but generally showed that healthy stock and fishery status ($\mathrm{SSB>SSB_{MSY}}$ and $F<F_{\mathrm{MSY}}$) and comparable levels of total catch could be maintained with stock assessments conducted every 1, 5 or 10 years, whether TACs were fixed, projected, or adjusted based on indices of abundance.
+But these management procedures vary in terms of average annual variability in yield (AAVY) which was highest when TACs were adjusted based on indices of abundance and lowest when TACs were fixed between assessments.
 
@@
 \begin{center}
-\includegraphics[width=6in,height=7in]{../Figs/phasePlot1.pdf}
+\includegraphics[width=6in, height=7in]{../Figs/boxplotSBSBMSY1.pdf}
 \end{center}
 \begin{flushleft}
-\caption{Phase plots for the base scenario and the first set of experimental scenarios}
+\caption{Box plots of $\mathrm{SSB/SSB_{MSY}}$ for the base scenario.
+Grouped boxes represent sequential time periods during the projection period.
+Boxes represent interquartile range (IQR).
+Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
+\label{fig:boxplotSBSBMSY1}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/boxplotFFMSY1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Box plots of $\mathrm{F/F_{MSY}}$ for the base scenario.
+Grouped boxes represent sequential time periods during the projection period.
+Boxes represent interquartile range (IQR).
+Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
+\label{fig:boxplotFFMSY1}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/boxplotCatchTotal1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Box plots of total catch (annual catches summed across each time period) for the base scenario.
+Grouped boxes represent sequential time periods during the projection period.
+Boxes represent interquartile range (IQR).
+Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
+\label{fig:boxplotCatchTotal1}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/boxplotAAVY1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Box plots of average annual variation in yield ($\mathrm{AAVY}$) for the base scenario.
+Grouped boxes represent sequential time periods during the projection period.
+Boxes represent interquartile range (IQR).
+Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
+\label{fig:boxplotAAVY1}
+\end{flushleft}
+\end{figure}
+\clearpage
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/tsCatchMSY1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of median $\mathrm{catch/MSY}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 10 yr intervals.}
+\label{fig:tsCatchMSY1}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/tsCatchMSY1B.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of median $\mathrm{catch/MSY}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 5 yr intervals.}
+\label{fig:tsCatchMSY1B}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/tsFFmsy1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of median $\mathrm{F/F_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 10 yr intervals.}
+\label{fig:tsFFmsy1}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/tsFFmsy1B.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of median $\mathrm{F/F_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 5 yr intervals.}
+\label{fig:tsFFmsy1B}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/tsSSBSSBmsy1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of median $\mathrm{SSB/SSB_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 10 yr intervals.}
+\label{fig:tsSSBSSBmsy1}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/tsSSBSSBmsy1B.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of median $\mathrm{SSB/SSB_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 5 yr intervals.}
+\label{fig:tsSSBSSBmsy1B}
+\end{flushleft}
+\end{figure}
+\clearpage
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=7in, height=3.5in]{../Figs/trAAVYP1001.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Trade off plots of the probability that average annual variability in yield (AAVY) <20\%, versus  the probability that $\mathrm{SSB > SSB_{MSY}}$ among simulation runs for the base scenario.
+Plots are based on data for the last 10 years of the projection period.}
+\label{fig:trAAVYP1001}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=7in, height=3.5in]{../Figs/trAAVYPNOF1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Trade off plots of the probability that average annual variability in yield (AAVY) <20\%, versus  the probability that $\mathrm{F < F_{MSY}}$ among simulation runs for the base scenario.
+Plots are based on data for the last 10 years of the projection period.}
+\label{fig:trAAVYPNOF1}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=7in, height=3.5in]{../Figs/trAAVYYldLT1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Trade off plots of the probability that average annual variability in yield (AAVY) <20\%, versus  longterm yield among simulation runs for the base scenario.
+Plots are based on data for the last 10 years of the projection period.}
+\label{fig:trAAVYYldLT1}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=7in, height=3.5in]{../Figs/trP100YldLT1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Trade off plots of the probability that $\mathrm{SSB > SSB_{MSY}}$ versus  longterm yield among simulation runs for the base scenario.
+Plots are based on data for the last 10 years of the projection period.}
+\label{fig:trP100YldLT1}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=7in, height=3.5in]{../Figs/trPNOFP1001.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Trade off plots of the probability that $\mathrm{F < F_{MSY}}$  versus  the probability that $\mathrm{SSB > SSB_{MSY}}$ among simulation runs for the base scenario.
+Plots are based on data for the last 10 years of the projection period.}
+\label{fig:trPNOFP1001}
+\end{flushleft}
+\end{figure}
+\clearpage
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=7in, height=3.5in]{../Figs/phasePlot1.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Phase plots of the probability that $\mathrm{F > F_{MSY}}$  versus  the probability that $\mathrm{SSB > SSB_{MSY}}$ among simulation runs for the base scenario.}
 \label{fig:phasePlot1}
@@
 \end{figure}
+\clearpage
+%% APPENDIX
+\begin{appendix}
 
-% \begin{figure}[!ht]
-% \begin{center}
-% \includegraphics[width=6in,height=7in]{../Figs/phasePlot2.pdf}
-% \end{center}
-% \begin{flushleft}
-% \caption{Phase plots for the base scenario and the second set of experimental scenarios}
-% \label{fig:phasePlot2}
-% \end{flushleft}
-% \end{figure}
+\clearpage
+\section*{Appendix}
 
-%% APPENDIX
-% \begin{appendix}
-%
-% \clearpage
-% \section*{Appendix S1}
-%
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{S\arabic{figure}}
+
 % \setcounter{table}{0}
@@
 %
-% \end{appendix}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/boxplotSBSBMSY2.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Box plots of $\mathrm{SSB/SSB_{MSY}}$ for the base and alternative scenarios.
+Grouped boxes represent sequential time periods during the projection period.
+Boxes represent interquartile range (IQR).
+Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
+\label{fig:boxplotSBSBMSY2}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/boxplotFFMSY2.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Box plots of $\mathrm{F/F_{MSY}}$ for the base and alternative scenarios.
+Grouped boxes represent sequential time periods during the projection period.
+Boxes represent interquartile range (IQR).
+Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
+\label{fig:boxplotFFMSY2}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/boxplotCatchTotal2.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Box plots of total catch (annual catches summed across each time period) for the base and alternative scenarios.
+Grouped boxes represent sequential time periods during the projection period.
+Boxes represent interquartile range (IQR).
+Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
+\label{fig:boxplotCatchTotal2}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/boxplotAAVY2.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Box plots of average annual variation in yield ($\mathrm{AAVY}$) for the base and alternative scenarios.
+Grouped boxes represent sequential time periods during the projection period.
+Boxes represent interquartile range (IQR).
+Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
+\label{fig:boxplotAAVY2}
+\end{flushleft}
+\end{figure}
+\clearpage
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/tsCatchMSY2.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of median $\mathrm{catch/MSY}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 10 yr intervals.}
+\label{fig:tsCatchMSY2}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/tsCatchMSY2B.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of median $\mathrm{catch/MSY}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 5 yr intervals.}
+\label{fig:tsCatchMSY2B}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/tsFFmsy2.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of median $\mathrm{F/F_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 10 yr intervals.}
+\label{fig:tsFFmsy2}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/tsFFmsy2B.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of median $\mathrm{F/F_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 5 yr intervals.}
+\label{fig:tsFFmsy2B}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/tsSSBSSBmsy2.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of median $\mathrm{SSB/SSB_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 10 yr intervals.}
+\label{fig:tsSSBSSBmsy2}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=6in, height=7in]{../Figs/tsSSBSSBmsy2B.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Time series of median $\mathrm{SSB/SSB_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 5 yr intervals.}
+\label{fig:tsSSBSSBmsy2B}
+\end{flushleft}
+\end{figure}
+\clearpage
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=7in, height=8in]{../Figs/trAAVYP1002.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Trade off plots of the probability that average annual variability in yield (AAVY) <20\%, versus  the probability that $\mathrm{SSB > SSB_{MSY}}$ among simulation runs for the base and alternative scenarios.
+Plots are based on data for the last 10 years of the projection period.}
+\label{fig:trAAVYP1002}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=7in, height=8in]{../Figs/trAAVYPNOF2.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Trade off plots of the probability that average annual variability in yield (AAVY) <20\%, versus  the probability that $\mathrm{F > F_{MSY}}$ among simulation runs for the base and alternative scenarios.
+Plots are based on data for the last 10 years of the projection period.}
+\label{fig:trAAVYPNOF2}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=7in, height=8in]{../Figs/trAAVYYldLT2.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Trade off plots of the probability that average annual variability in yield (AAVY) <20\%, versus  longterm yield among simulation runs for the base and alternative scenarios.
+Plots are based on data for the last 10 years of the projection period.}
+\label{fig:trAAVYYldLT2}
+\end{flushleft}
+\end{figure}
+\clearpage\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=7in, height=8in]{../Figs/trPNOFP1002.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Trade off plots of the probability that $\mathrm{F > F_{MSY}}$  versus  the probability that $\mathrm{SSB > SSB_{MSY}}$ among simulation runs for the base and alternative scenarios.
+Plots are based on data for the last 10 years of the projection period.}
+\label{fig:trPNOFP1002}
+\end{flushleft}
+\end{figure}
+\clearpage
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=7in, height=8in]{../Figs/phasePlot2.pdf}
+\end{center}
+\begin{flushleft}
+\caption{Phase plots of the probability that $\mathrm{F > F_{MSY}}$  versus  the probability that $\mathrm{SSB > SSB_{MSY}}$ among simulation runs for the base and alternative scenarios.}
+\label{fig:phasePlot2}
+\end{flushleft}
+\end{figure}
+\clearpage
+
+\end{appendix}
 

### 2022-06-02 BuildOM/2022-02-14/rdat_to_Data_input_tmp.R

@@ -1,153 +1,0 @@
-rdat=rdat_BlackSeaBass
-length_sc = length_sc
-Data = new('Data')
-herm = NULL
-nsim=48
-genus_species=NULL
-Region="Southeast US Atlantic"
-Fref_name = "Fmsy"
-Rec="bam_recruits"
-CAA_abb="all"
-CAL_abb="all"
-Ind_abb="all"
-CV_vbK=0.001
-CV_vbLinf=0.001
-CV_vbt0=0.001
-CV_Cat=NULL
-Mat_age1_max=Mat_age1_max
-length_sc=length_sc
-wla_sc=NULL
-wla_unit="lbs"
-wla_unit_mult=1000
-catch_sc=1
-
-
-# Begin function
-
-rdat <- standardize_rdat(rdat)
-
-info <- rdat$info
-parms <- rdat$parms
-parm.cons <- rdat$parm.cons
-parm.tvec <- rdat$parm.tvec
-a.series <- rdat$a.series
-t.series <- rdat$t.series
-comp.mats <- rdat$comp.mats
-styr <- parms$styr
-endyr <- parms$endyr
-
-Name <- gsub(" ","",str_to_title(info$species))
-
-# MSEtool expects age-based data to begin with age 0
-if(min(a.series$age)>0){
-  warning(paste(Name,": Minimum age > 0. Age-based data extrapolated to age-0"))
-  a.series <- data_polate(a.series,xout=0:max(a.series$age))
-  a.series <- data_lim(a.series,xlim=c(0,Inf))
-  a.series <- data_lim(a.series,xname=c("prop.female","prop.male","mat.female","mat.male"),xlim=c(0,1))
-  a.series <- as.data.frame(a.series)
-  rownames(a.series) <- a.series$age
-}
-age <- a.series$age
-
-t.series <- t.series[paste(styr:endyr),]
-
-Common_Name <- str_replace_all(Name,"(?<=[a-z])(?=[A-Z])"," ")
-if(is.null(genus_species)){genus_species <- bamStockMisc[Name,"Species"]}
-if(is.null(herm)){herm <- bamStockMisc[Name,"herm"]}
-
-B.to.klb <- local({
-  if(info$units.biomass%in%c("mt","metric tons")){
-    out <- 2.204624}else{
-      warning("units.biomass not equal to metric tons")
-    }
-  return(out)
-})
-
-catch.raw <- t.series$total.L.klb*catch_sc
[…]

### 2022-06-02 RunMSE/SEFSC/fn/Assess_diagnostic_NK.R

@@ -27,7 +27,7 @@ Assess_diagnostic_NK <- function (x, Data, Assessment, include_assessment = TRUE
                R0 = R0, h = h,
                MSY = MSY, FSY = FSY, SSBMSY = SSBMSY,
                F_FMSY = F_FMSY, SSB_SSBMSY = SSB_SSBMSY
-               )
+    )
   }
   else {
     dg <- list(hess = FALSE, msg = msg, maxgrad = 1e+10,

### 2022-06-02 RunMSE/SEFSC/fn/iMP.R

@@ -25,10 +25,12 @@ SCA_5 <- SCA_10 <- SCA_1 <- do.call(make_MP_NK,
                                     )
 # Projection MPs
 pMP_5 <- do.call(make_projection_MP_NK,
-                 c(list(assessment_interval = 5,process_error = NULL, p_sim = 1),
+                 c(list(assessment_interval = 5,process_error = NULL, p_sim = 1,
+                        Ftarget = expression(MSY_frac * Assessment@FMSY)),
                    MP_args, BAM_SCA_args)
                  )
 pMP_10 <- do.call(make_projection_MP_NK,
-                 c(list(assessment_interval = 10,process_error = NULL, p_sim = 1),
+                 c(list(assessment_interval = 10,process_error = NULL, p_sim = 1,
+                        Ftarget = expression(MSY_frac * Assessment@FMSY)),
                    MP_args, BAM_SCA_args)
 )

### 2022-06-02 RunMSE/SEFSC/fn/iMP_nolag.R

@@ -34,10 +34,12 @@ SCA_5 <- SCA_10 <- SCA_1 <- do.call(make_MP,
                                     )
 # Projection MPs
 pMP_5 <- do.call(make_projection_MP,
-                 c(list(assessment_interval = 5,process_error = NULL, p_sim = 1),
+                 c(list(assessment_interval = 5,process_error = NULL, p_sim = 1,
+                   Ftarget = expression(MSY_frac * Assessment@FMSY)),
                    MP_args, BAM_SCA_args)
                  )
 pMP_10 <- do.call(make_projection_MP,
-                 c(list(assessment_interval = 10,process_error = NULL, p_sim = 1),
+                 c(list(assessment_interval = 10,process_error = NULL, p_sim = 1,
+                   Ftarget = expression(MSY_frac * Assessment@FMSY)),
                    MP_args, BAM_SCA_args)
 )

### 2022-06-02 RunMSE/SEFSC/run_script.R

@@ -14,7 +14,9 @@ source("fn/make_interim_MP_NK.R")
 source("fn/make_projection_MP_NK.R")
 source("fn/SCA_NK.R")
 
-nsim <- 48 #250
+ncores <- 10
+
+nsim <- 50#250
 runScenarios <- TRUE # Run scenarios to do MSE or just generate historical data?
 runMSE_args <- list("parallel"=TRUE,"extended"=TRUE,"silent"=FALSE)
 lag_Assess_Init <- 2 # Number of years between terminal year of assessment and first year of management. May be modified in scenarios
@@ -23,22 +25,29 @@ MSY_frac_Init <- 1 # Fraction of MSY for setting TAC. May be modified in scenari
 AddInd_val_Init <- 1  # Index used in interim procedures and possibly assessments. May be modified in scenarios
 AddInd_all_assess_Init <- TRUE # Should all available indices be used in assessments? Only works with SCA_NK() May be modified in scenarios
 MP_diagnostic <- "min"
-#M_OM_agevariant <- FALSE # Should M be age-variant in the operating model? Note that the SCA function currently treats M as a constant
+maxF <- 3 # set maximum F allowed in simulations
 
+OMName_scen_complete <- NA
+#   local({
+#   a <- gsub(".rds","",list.files("MSE_obj"))
+#   b <- gsub("MSE","OM",a)
+#   b
+# })
 
-OMName_scen_complete <-
-  local({
-  a <- gsub(".rds","",list.files("MSE_obj"))
-  b <- gsub("MSE","OM",a)
-  b
-})
+MPs_user <- c(
+  #"CC1","SPMSY", # "AvC", "DCAC", "DBSRA", # simple MPs
+  "SCA_1","SCA_5","SCA_10",        # assessment only MPs
+  "iMP_avg_5",    "iMP_avg_10",    # interim average MPs
+  "iMP_buffer_5", "iMP_buffer_10", # interim buffered MPs
+  "pMP_5","pMP_10"                 # projection MPs
+)
 
 # OMName_all <- gsub(".rds","",list.files("OM"))
 # OMName <- OMName_all[!OMName_all%in%OMName_complete]
-OMName <- c("OM_RedPorgy" # Runs,
-            ,"OM_BlackSeaBass" # Runs
-            ,"OM_VermilionSnapper" # Runs
-            ,"OM_SnowyGrouper" # Runs 2022-1-20 batch 1 for base took only 25 min
+OMName <- c("OM_BlackSeaBass", # Runs
[…]
